### 2013-02-21 paper.tex
Initial template

\documentclass{article}
\usepackage{url,color,xspace,verbatim,subfig,ctable,multirow,listings}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{txfonts}
\usepackage{rotating}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{graphics}
\usepackage{enumitem}
\usepackage{times}

% ==================================================

\graphicspath{{figs/}}
\urlstyle{sf}

% tikz stuff
\usepackage{tikz}
\usetikzlibrary{shapes,positioning,calc}

\lstset{
  language=C,
  basicstyle=\ttfamily \small,
  flexiblecolumns=false,
  basewidth={0.5em,0.45em},
  boxpos=t,
}

\definecolor{skRed}{RGB}{155,25,25}
\newcommand{\stefan}[1]{
  {\color{skRed}[{\color{red}{SK}} #1]}}

% ==================================================

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\bibliographystyle{plain}
\bibliography{defs,db,mendeley}

\label{LastPage}

\end{document}

### 2013-02-21 paper.tex
Added a title page and the Intel research proposal questions.
Ansered Intel questions

@@
 \usepackage{times}
+\usepackage[colorlinks=true]{hyperref}
 
@@
 
+\title{Replication on multicore considering hierarchy and
+  characteristics of the network}
+
+% email address
+\newcommand{\eaddr}{stefan.kaestle@inf.ethz.ch}
+\newcommand{\email}{\href{mailto:\eaddr}{\eaddr}}
+
+\author{Stefan Kaestle\\
+  \email \\
+  Systems Group, ETH Zurich}
+
+\maketitle
+
+\paragraph{What do you want to enable?} Increase algorithm performance
+on multicores by applying distributed principles, particularly
+replication. Consistency using hierarchical group communication.
+
+\paragraph{What problem are you solving, and why is it hard?}
+\begin{description}
+\item[placement] machine dependent
+\item[consistency] need to consider machine \emph{characteristics};
+  multicores are \emph{different} from classical distributed systems.
+\item[machine characteristics] diverse, fast changing
+\end{description}
+
+\paragraph{What's the related work?} People do replication to deal
+with scalability challenges on multicores, e.g.\
+databases~\cite{Salomie2011, Wiesmann2000} and operating
+systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}.
+
+\paragraph{What new idea(s) will solve the problems?} Consider machine
+characteristics and keep in mind, that multicore machines are
+different.
+
+\paragraph{How will you go about it?} Replicas on NUMA domains, show
+that overall throughput is higher. Use a quorum based approach for
+consistency. Consistency by doing a hierarchical group communication
+approach instead of sequential send from same nodes.
+
+\paragraph{How will you know and show it works?} Database?
+Microbenchmark? Compare to primary backup, which is typically used.
+
+\paragraph{What is your hypothesis?} We can do much better if machine
+characteristics are considered.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-02-21 paper.tex
Couple of changes

@@
 
-\paragraph{What problem are you solving, and why is it hard?}
+\paragraph{What problem are you solving, and why is it hard?} Three problems:
 \begin{description}
@@
   multicores are \emph{different} from classical distributed systems.
-\item[machine characteristics] diverse, fast changing
+\item[machine characteristics] diverse, fast changing, complex
 \end{description}
@@
 databases~\cite{Salomie2011, Wiesmann2000} and operating
-systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}.
+systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}. But they
+don't to it properly. They do not consider machine characteristics.
 
@@
 characteristics and keep in mind, that multicore machines are
-different.
+different. \\
+{\footnotesize Example: sequential consistency on shared memory, do
+  not really need to have primary backup.}
 
 \paragraph{How will you go about it?} Replicas on NUMA domains, show
-that overall throughput is higher. Use a quorum based approach for
+that overall throughput is higher. Then, use a quorum based approach for
 consistency. Consistency by doing a hierarchical group communication
@@
 \paragraph{How will you know and show it works?} Database?
-Microbenchmark? Compare to primary backup, which is typically used.
+Microbenchmark? Compare to primary backup, which is typically
+used. Measure time required to apply an update.
 

### 2013-02-25 paper.tex
Integrated some more concrete ideas on which algorithms to work on.

@@
 on multicores by applying distributed principles, particularly
-replication. Consistency using hierarchical group communication.
+replication. The challenge then is to guarantee consistency. Previous
+work was using primary copy protocols to do that~\cite{Wiesmann2000}, a
+passive replication scheme (i.e.\ nodes do not have to contact all
+replicas). They do that because they claim that it is not suitable for
+clients to know about replication details.
 
@@
 systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}. But they
-don't to it properly. They do not consider machine characteristics.
+don't to it properly. They do not consider machine characteristics or
+apply the wrong distributed technologies.
 
-\paragraph{What new idea(s) will solve the problems?} Consider machine
-characteristics and keep in mind, that multicore machines are
-different. \\
+\paragraph{What new idea(s) will solve the problems?} We do a
+hierarchical group communication, which implements an atomic
+broadcast on multicore machines. It has message complexity of
+$O(\frac{n}{2})$ and time complexity $O(log(n))$ as opposed to
+algorithms from traditional distributed systems having $O(2)$ message
+complexity and $O(n)$ time complexity. %
+\\
 {\footnotesize Example: sequential consistency on shared memory, do

### 2013-03-14 paper.tex
Some first measurements

@@
 \usepackage{times}
+\usepackage{amssymb}
 \usepackage[colorlinks=true]{hyperref}
@@
 \usepackage{tikz}
+\usepackage{pgfplots}
 \usetikzlibrary{shapes,positioning,calc}
@@
 replicas). They do that because they claim that it is not suitable for
-clients to know about replication details.
+clients to know about replication details. An atomic broadcast is
+often used as foundation of such algorithms. It guarantees in reliable
+delivery of messages to every node.
 
@@
   multicores are \emph{different} from classical distributed systems.
-\item[machine characteristics] diverse, fast changing, complex
+\item[machine characteristics] diverse, fast changing, complex. One
+  example is the batch size for sending a broadcast.
 \end{description}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Mechanisms}
+
+\subsubsection{Aggregation}
+
+Similarly to what has been done in wireless sensor networks (where it
+also matters to reduce the number of messages, but other reasons:
+power consumption), we can do aggregation in nodes. In difference to
+traditional distributed systems, this works, because it is easy to
+deploy custom software on every node in the network. Classical
+distributed systems do not typically allow this. Furthermore, reducing
+the number of messages at the price of higher complexity does not make
+sense there.
+
+Examples for aggregation: number of nodes agreeing to something, find
+capabilities (concatenate core ids).
+
+Open questions: How does this work with several senders (everyone is
+potentially a sender). Maybe something like in navigation
+systems. Every node has an entry point, which forwards the
+messages. Nodes are then clustered \ldots
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Implementation}
+
+Build a tree. Every node has parents and children (except for the root
+and the leafs). The number of children does not really matter for the
+algorithm. In the init phase, we construct the tree (e.g. broadcast:
+one root node, all other nodes are children of the root node,
+multicast: every node has two children, NUMA tree: two layers, two
+different implementations?
+
+Reducing the number of children also helps in select. It reduces the
+number of ``channels'' to poll, and therefore the latency of detecting
+messages. Instead of
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Experimental results}
+
+on revision 1190:a787513fd28c, experiments for sequential and batch
+broadcast working on nos5 and appenzeller
+
+\begin{table}[htb]
+  \centering
+  \begin{tabular}{lrrrr}
+    \toprule
+    broadcast algorithm & \multicolumn{2}{c}{nos5} & \multicolumn{2}{c}{gruyere} \\
+      & cycles & error & cycles & error \\
+    \midrule
+    sequential &  4096.1 &  105.2 & 136751.9 &   3061.5 \\
+    batch      &  2408.0 &  181.9 &  57360.8 &   5271.5 \\
+    tree\footnote{This only works for the first 200 runs, after that,
+      performance breaks down, don't know why, but the first 200 runs
+      are quite stable}%
+               &  \sout{1471.8} &  \sout{187.9} &          &          \\
+    \bottomrule
+  \end{tabular}
+  \caption{Broadcast measurements}
+  \label{tab:bc_measurements}
+\end{table}
+
+\paragraph{Measurements to do next} %
+\begin{itemize}
+\item Increase number of cores to talk to in every round. Use a
+  separate waitsets, so that we don't have additional overhead from
+  the bindings not used in each concrete measurement.
+\item Play with batching. Incrementally increase the number of
+  messages send in a batch. I assume this is machine specific, which
+  means, that this is something programmers do not want to deal
+  with. We measure this at dynamically at run-time and find the right
+  batch size.
+\end{itemize}
+
+\input{gruyere_bc_seq}
+
+\begin{itemize}
+\item Move server to a core != 0
+\item Use low-level UMP stuff
+{
+\renewcommand{\labelitemi}{\checkmark}
+\item disable yielding set 
+}
+\item some other item
+\item run several request in parallel, give them IDs, can use in the
+  measurement struct. Good for everything having transactions (DB,
+  transactional memory, consistency in replication systems)
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage

### 2013-03-14 paper.tex
Updated numbers. Added graph showing broadcast tree on gruyere

@@
 \usepackage{pgfplots}
-\usetikzlibrary{shapes,positioning,calc}
+\usetikzlibrary{shapes,positioning,calc,snakes,arrows,shapes}
 
@@
 
-on revision 1190:a787513fd28c, experiments for sequential and batch
-broadcast working on nos5 and appenzeller
+\paragraph{Current numbers}
 
@@
     batch      &  2408.0 &  181.9 &  57360.8 &   5271.5 \\
-    tree\footnote{This only works for the first 200 runs, after that,
-      performance breaks down, don't know why, but the first 200 runs
-      are quite stable}%
-               &  \sout{1471.8} &  \sout{187.9} &          &          \\
     \bottomrule
@@
 \end{table}
+
+\paragraph{Tree setup} \stefan{describe}
 
@@
 \end{itemize}
+
+\paragraph{Minimal cost of sending a tree-broadcast} %
+Plot~\ref{pgfplot:201303141819} shows the minimal cost of flooding a
+sub-tree. The group communication is based on a binary tree. Core 0 is
+the root, cores 1 and 2 are its children etc.
+
+The average cost is really high (so something is wrong with my
+code). But the minimal numbers show what is possible. The numbers
+achieved are easily explainable. The cost is increasing
+logarithmic with the number of nodes reached by the broadcast (as
+expected). Every level in the tree adds an additional 3500 cycles to
+the tree. Node 0 takes significantly longer. I don't know yet why that
+is.
+
+\begin{figure}
+  \caption{Plot}
+  \label{pgfplot:201303141819}
+  \begin{tikzpicture}
+    \begin{axis}[
+      xlabel=core id,
+      ylabel={cost for subtree [cycles]}]
+    \addplot[color=red,mark=x] coordinates {
+      (0,9475.0)
+      (1,7935.0)
+      (2,7894.0)
+      (3,5965.0)
+      (4,5604.0)
+      (5,5718.0)
+      (6,5647.0)
+      (7,4316.0)
+      (8,2989.0)
+      (9,3173.0)
+      (10,3395.0)
+      (11,3332.0)
+      (12,3284.0)
+      (13,3310.0)
+      (14,3231.0)
+      (15,2542.0)
+      (16,586.0)
+      (17,588.0)
+      (18,576.0)
+      (19,583.0)
+      (20,536.0)
+      (21,539.0)
+      (22,533.0)
+      (23,516.0)
+      (24,546.0)
+      (25,552.0)
+      (26,541.0)
+      (27,543.0)
+      (28,537.0)
+      (29,527.0)
+      (30,533.0)
+      (31,534.0)
+    };
+    \end{axis}
+  \end{tikzpicture}
+
+\end{figure}
+
+\begin{figure}
+  \input{qrm_tree_gruyere}
+  \caption{Tree of cores for broadcast on gruyere}
+\end{figure}
 

### 2013-03-15 qrm_tree_gruyere.tex
Ooops, forgot another thing! Shame on me!

% Start of code
% \begin{tikzpicture}[anchor=mid,>=latex',line join=bevel,]
\begin{tikzpicture}[>=latex',line join=bevel,scale=.35]
  \pgfsetlinewidth{1bp}
%%
\pgfsetcolor{black}
  % Edge: 15 -> 31
  \draw [->] (27bp,74.327bp) .. controls (27bp,66.264bp) and (27bp,56.648bp)  .. (27bp,37.667bp);
  % Edge: 9 -> 19
  \draw [->] (459bp,148.33bp) .. controls (459bp,140.26bp) and (459bp,130.65bp)  .. (459bp,111.67bp);
  % Edge: 14 -> 30
  \draw [->] (1050.3bp,151.31bp) .. controls (1060.4bp,140.94bp) and (1073.7bp,127.18bp)  .. (1092bp,108.42bp);
  % Edge: 14 -> 29
  \draw [->] (1035bp,148.33bp) .. controls (1035bp,140.26bp) and (1035bp,130.65bp)  .. (1035bp,111.67bp);
  % Edge: 11 -> 23
  \draw [->] (659.73bp,151.31bp) .. controls (649.64bp,140.94bp) and (636.25bp,127.18bp)  .. (618bp,108.42bp);
  % Edge: 7 -> 15
  \draw [->] (83.731bp,151.31bp) .. controls (73.64bp,140.94bp) and (60.253bp,127.18bp)  .. (42bp,108.42bp);
  % Edge: 0 -> 2
  \draw [->] (588.87bp,377.76bp) .. controls (613.22bp,365.25bp) and (652.76bp,344.93bp)  .. (689.4bp,326.1bp);
  % Edge: 10 -> 22
  \draw [->] (387bp,148.33bp) .. controls (387bp,140.26bp) and (387bp,130.65bp)  .. (387bp,111.67bp);
  % Edge: 13 -> 28
  \draw [->] (935.71bp,149.09bp) .. controls (939.96bp,140.36bp) and (945.15bp,129.68bp)  .. (954.37bp,110.75bp);
  % Edge: 1 -> 3
  \draw [->] (398.64bp,306.66bp) .. controls (360.05bp,293.43bp) and (284.76bp,267.64bp)  .. (231.27bp,249.31bp);
  % Edge: 6 -> 14
  \draw [->] (946.31bp,227.77bp) .. controls (963.36bp,216.09bp) and (988.4bp,198.93bp)  .. (1015.9bp,180.12bp);
  % Edge: 3 -> 8
  \draw [->] (207bp,222.33bp) .. controls (207bp,214.26bp) and (207bp,204.65bp)  .. (207bp,185.67bp);
  % Edge: 13 -> 27
  \draw [->] (918.29bp,149.09bp) .. controls (914.04bp,140.36bp) and (908.85bp,129.68bp)  .. (899.63bp,110.75bp);
  % Edge: 10 -> 21
  \draw [->] (371.73bp,151.31bp) .. controls (361.64bp,140.94bp) and (348.25bp,127.18bp)  .. (330bp,108.42bp);
  % Edge: 12 -> 26
  \draw [->] (762.27bp,151.31bp) .. controls (772.36bp,140.94bp) and (785.75bp,127.18bp)  .. (804bp,108.42bp);
  % Edge: 3 -> 7
  \draw [->] (187.69bp,227.77bp) .. controls (170.64bp,216.09bp) and (145.6bp,198.93bp)  .. (118.14bp,180.12bp);
  % Edge: 5 -> 12
  \draw [->] (719.71bp,223.09bp) .. controls (723.96bp,214.36bp) and (729.15bp,203.68bp)  .. (738.37bp,184.75bp);
  % Edge: 9 -> 20
  \draw [->] (474.27bp,151.31bp) .. controls (484.36bp,140.94bp) and (497.75bp,127.18bp)  .. (516bp,108.42bp);
  % Edge: 1 -> 4
  \draw [->] (423bp,296.33bp) .. controls (423bp,288.26bp) and (423bp,278.65bp)  .. (423bp,259.67bp);
  % Edge: 0 -> 1
  \draw [->] (545.13bp,377.76bp) .. controls (520.78bp,365.25bp) and (481.24bp,344.93bp)  .. (444.6bp,326.1bp);
  % Edge: 2 -> 5
  \draw [->] (711bp,296.33bp) .. controls (711bp,288.26bp) and (711bp,278.65bp)  .. (711bp,259.67bp);
  % Edge: 11 -> 24
  \draw [->] (675bp,148.33bp) .. controls (675bp,140.26bp) and (675bp,130.65bp)  .. (675bp,111.67bp);
  % Edge: 4 -> 10
  \draw [->] (414.29bp,223.09bp) .. controls (410.04bp,214.36bp) and (404.85bp,203.68bp)  .. (395.63bp,184.75bp);
  % Edge: 12 -> 25
  \draw [->] (747bp,148.33bp) .. controls (747bp,140.26bp) and (747bp,130.65bp)  .. (747bp,111.67bp);
  % Edge: 8 -> 17
  \draw [->] (198.29bp,149.09bp) .. controls (194.04bp,140.36bp) and (188.85bp,129.68bp)  .. (179.63bp,110.75bp);
  % Edge: 6 -> 13
  \draw [->] (927bp,222.33bp) .. controls (927bp,214.26bp) and (927bp,204.65bp)  .. (927bp,185.67bp);
  % Edge: 5 -> 11
  \draw [->] (702.29bp,223.09bp) .. controls (698.04bp,214.36bp) and (692.85bp,203.68bp)  .. (683.63bp,184.75bp);
  % Edge: 7 -> 16
  \draw [->] (99bp,148.33bp) .. controls (99bp,140.26bp) and (99bp,130.65bp)  .. (99bp,111.67bp);
  % Edge: 2 -> 6
  \draw [->] (735.36bp,306.66bp) .. controls (773.95bp,293.43bp) and (849.24bp,267.64bp)  .. (902.73bp,249.31bp);
  % Edge: 8 -> 18
  \draw [->] (215.71bp,149.09bp) .. controls (219.96bp,140.36bp) and (225.15bp,129.68bp)  .. (234.37bp,110.75bp);
  % Edge: 4 -> 9
  \draw [->] (431.71bp,223.09bp) .. controls (435.96bp,214.36bp) and (441.15bp,203.68bp)  .. (450.37bp,184.75bp);
  % Node: 24
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (675bp,93bp) ellipse (27bp and 18bp);
  \draw (675bp,93bp) node {24};
\end{scope}
  % Node: 25
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (747bp,93bp) ellipse (27bp and 18bp);
  \draw (747bp,93bp) node {25};
\end{scope}
  % Node: 26
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (819bp,93bp) ellipse (27bp and 18bp);
  \draw (819bp,93bp) node {26};
\end{scope}
  % Node: 27
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (891bp,93bp) ellipse (27bp and 18bp);
  \draw (891bp,93bp) node {27};
\end{scope}
  % Node: 20
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (531bp,93bp) ellipse (27bp and 18bp);
  \draw (531bp,93bp) node {20};
\end{scope}
  % Node: 21
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (315bp,93bp) ellipse (27bp and 18bp);
  \draw (315bp,93bp) node {21};
\end{scope}
  % Node: 22
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (387bp,93bp) ellipse (27bp and 18bp);
  \draw (387bp,93bp) node {22};
\end{scope}
  % Node: 23
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (603bp,93bp) ellipse (27bp and 18bp);
  \draw (603bp,93bp) node {23};
\end{scope}
  % Node: 28
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (963bp,93bp) ellipse (27bp and 18bp);
  \draw (963bp,93bp) node {28};
\end{scope}
  % Node: 29
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (1035bp,93bp) ellipse (27bp and 18bp);
  \draw (1035bp,93bp) node {29};
\end{scope}
  % Node: 1
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (423bp,315bp) ellipse (27bp and 18bp);
  \draw (423bp,315bp) node {1};
\end{scope}
  % Node: 0
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (567bp,389bp) ellipse (27bp and 18bp);
  \draw (567bp,389bp) node {0};
\end{scope}
  % Node: 3
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (207bp,241bp) ellipse (27bp and 18bp);
  \draw (207bp,241bp) node {3};
\end{scope}
  % Node: 2
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (711bp,315bp) ellipse (27bp and 18bp);
  \draw (711bp,315bp) node {2};
\end{scope}
  % Node: 5
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (711bp,241bp) ellipse (27bp and 18bp);
  \draw (711bp,241bp) node {5};
\end{scope}
  % Node: 4
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (423bp,241bp) ellipse (27bp and 18bp);
  \draw (423bp,241bp) node {4};
\end{scope}
  % Node: 7
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (99bp,167bp) ellipse (27bp and 18bp);
  \draw (99bp,167bp) node {7};
\end{scope}
  % Node: 6
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (927bp,241bp) ellipse (27bp and 18bp);
  \draw (927bp,241bp) node {6};
\end{scope}
  % Node: 9
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (459bp,167bp) ellipse (27bp and 18bp);
  \draw (459bp,167bp) node {9};
\end{scope}
  % Node: 8
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (207bp,167bp) ellipse (27bp and 18bp);
  \draw (207bp,167bp) node {8};
\end{scope}
  % Node: 11
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (675bp,167bp) ellipse (27bp and 18bp);
  \draw (675bp,167bp) node {11};
\end{scope}
  % Node: 10
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (387bp,167bp) ellipse (27bp and 18bp);
  \draw (387bp,167bp) node {10};
\end{scope}
  % Node: 13
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (927bp,167bp) ellipse (27bp and 18bp);
  \draw (927bp,167bp) node {13};
\end{scope}
  % Node: 12
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (747bp,167bp) ellipse (27bp and 18bp);
  \draw (747bp,167bp) node {12};
\end{scope}
  % Node: 15
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (27bp,93bp) ellipse (27bp and 18bp);
  \draw (27bp,93bp) node {15};
\end{scope}
  % Node: 14
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (1035bp,167bp) ellipse (27bp and 18bp);
  \draw (1035bp,167bp) node {14};
\end{scope}
  % Node: 17
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (171bp,93bp) ellipse (27bp and 18bp);
  \draw (171bp,93bp) node {17};
\end{scope}
  % Node: 16
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (99bp,93bp) ellipse (27bp and 18bp);
  \draw (99bp,93bp) node {16};
\end{scope}
  % Node: 19
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (459bp,93bp) ellipse (27bp and 18bp);
  \draw (459bp,93bp) node {19};
\end{scope}
  % Node: 18
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (243bp,93bp) ellipse (27bp and 18bp);
  \draw (243bp,93bp) node {18};
\end{scope}
  % Node: 31
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (27bp,19bp) ellipse (27bp and 18bp);
  \draw (27bp,19bp) node {31};
\end{scope}
  % Node: 30
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (1107bp,93bp) ellipse (27bp and 18bp);
  \draw (1107bp,93bp) node {30};
\end{scope}
%
\end{tikzpicture}
% End of code

### 2013-03-20 paper.tex
Added a section on the network model

@@
 \usepackage{pgfplots}
+% configuration
 \usetikzlibrary{shapes,positioning,calc,snakes,arrows,shapes}
+\pgfplotsset{width=.9\linewidth}
 
@@
 % ==================================================
-
+\setcounter{section}{0} % Start sections with 1, not 0
 \begin{document}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+
 \paragraph{What do you want to enable?} Increase algorithm performance
-on multicores by applying distributed principles, particularly
-replication. The challenge then is to guarantee consistency. Previous
-work was using primary copy protocols to do that~\cite{Wiesmann2000}, a
-passive replication scheme (i.e.\ nodes do not have to contact all
-replicas). They do that because they claim that it is not suitable for
-clients to know about replication details. An atomic broadcast is
-often used as foundation of such algorithms. It guarantees in reliable
-delivery of messages to every node.
+on multicores by applying distributed principles to overcome
+scalability challenges on such machines.
 
-\paragraph{What problem are you solving, and why is it hard?} Three problems:
-\begin{description}
-\item[placement] machine dependent
-\item[consistency] need to consider machine \emph{characteristics};
-  multicores are \emph{different} from classical distributed systems.
-\item[machine characteristics] diverse, fast changing, complex. One
-  example is the batch size for sending a broadcast.
-\end{description}
+\paragraph{What problem are you solving, and why is it hard?} We are
+applying distributed algorithms to multicores to enable better
+scalability. However, characteristics of a multicore a different to
+those of traditional distributed systems. Traditional algorithms need
+to be reevaluated for multicores.
 
-\paragraph{What's the related work?} People do replication to deal
-with scalability challenges on multicores, e.g.\
-databases~\cite{Salomie2011, Wiesmann2000} and operating
+\paragraph{What's the related work?} People apply techniques from
+distributed systems to deal with scalability challenges on multicores,
+e.g.\ databases~\cite{Salomie2011, Wiesmann2000} and operating
 systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}. But they
 don't to it properly. They do not consider machine characteristics or
-apply the wrong distributed technologies.
+apply the wrong distributed technologies. Also, what they do is rather
+ad hoc.
 
-\paragraph{What new idea(s) will solve the problems?} We do a
-hierarchical group communication, which implements an atomic
-broadcast on multicore machines. It has message complexity of
-$O(\frac{n}{2})$ and time complexity $O(log(n))$ as opposed to
-algorithms from traditional distributed systems having $O(2)$ message
-complexity and $O(n)$ time complexity. %
-\\
-{\footnotesize Example: sequential consistency on shared memory, do
-  not really need to have primary backup.}
+\paragraph{What new idea(s) will solve the problems?} Instead of just
+reusing distributed algorithms, we reevaluate them for multicores and
+investigate the impact of the multicore network model on algorithm
+performance.
 
-\paragraph{How will you go about it?} Replicas on NUMA domains, show
-that overall throughput is higher. Then, use a quorum based approach for
-consistency. Consistency by doing a hierarchical group communication
-approach instead of sequential send from same nodes.
+\paragraph{How will you go about it?} We investigate the problem for
+atomic-broadcasts since many problems in distributed systems can be
+reduced to this communication primitive. Traditional implementations
+are sending requests to all nodes in parallel to hide high propagation
+delays. %
+However, this does not work on multicores, since the propagation time
+is not dominating any longer. %
+Instead, we build a tree for communication to parallelize transmit and
+receive cost across nodes. This has been done before (BF SOSP, IBM,
+.. ), but not for the general case of multicore communication.
 
-\paragraph{How will you know and show it works?} Database?
-Microbenchmark? Compare to primary backup, which is typically
-used. Measure time required to apply an update.
+\paragraph{How will you know and show it works?} We will use a
+microbenchmark measuring broadcast cost and compare our tree
+implementation to the sequential case. Maybe we put some high-level
+applications on top of it.
 
-\paragraph{What is your hypothesis?} We can do much better if machine
-characteristics are considered.
+\paragraph{What is your hypothesis?} Performance of distributed
+algorithms can be improved if characteristics of multicores are
+considered when building and/or selecting them. %
+For the broadcast example, this means: the time complexity for a
+networks with dominating transmit and receive time will be $O(log(n))$
+instead of $O(n)$.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Mechanisms}
+\section{Related work}
 
-\subsubsection{Aggregation}
+A multicore aware broadcast has been implemented in~\cite{Tu2008}. It
+takes the cache architecture of the machine into consideration for
+building the broadcast. It is however for larger messages (starting at
+4K) and it does not seem to be performing very well (numbers are given
+in microseconds -6). 4K messages are 52 microseconds, which is 150000
+cycles. For synchronization primitives, a cache line is sufficient.
+
+Another tree implementation with MPI in mind was done
+in~\cite{Graham2008}. They have comparable numbers to what we found.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Model}
+
+The selection of distributed algorithms depends on the characteristics
+of a network. Multicores networks are heterogeneous combinations of
+complex networks. %
+Their diversity makes manual selection tedious. Hence, we aim for an
+automatic approach for selecting algorithms for a specific
+network. %
+We express the network characteristics in a multicore network
+model. This model is currently by no means complete. We are going to
+extend it over time to address more complexities of current and future
+multicores.
+
+The network model is defined by communication channels, which in turn
+are defined by a set of attributes, i.e.\
+\begin{itemize}
+\item reliability (loss, link failure, in-order delivery, phantoms,
+  corruption, duplicated messages): Ethernet is not reliable,
+  multicore interconnect networks often are
+\item synchronized clocks: sychronized clocks + bound on propagation
+  time $\rightarrow$ \emph{synchronous network} model. \\Then:
+  $\exists$ algorithm for synchronous networks $\rightarrow
+  \exists$ algorithm for asynchronous
+\item Security \& and failure detection (and the cost for that)
+\end{itemize}
+
+These are more about performance:
+\begin{itemize}
+\item ``breakdown'' of message send cost: Ethernet has dominating
+  propagation time vs.\ dominating send and receive time on multicores
+\item latency between each pair of nodes
+\end{itemize}
+
+% Model given
+We assume that the model is given (if it is not, we can do online
+measurements and read some specs to find the relevant information). We
+just define one ourselves for now or build one manually for a
+particular machine. In a real-world scenario, this does not work. The
+model needs to be created automatically for a particular machine (due
+to the diversity of machines, and also the pace at which hardware changes)
+
+% Express as:
+We express the model in a graph, where nodes are processors and edges
+are (on-hop?) communication links.
+
+% How to deduct tree from model?
+We then use this graph to build a group-communication
+tree. Interesting techniques could be: clustering, to find closely
+connected subsets, distributed messages across cluster first, and then
+within cluster. Maybe also a spanning-tree protocol, to find a minimal
+graph such that all nodes can be reached.
+% Tree -> scheduling
+Assuming the tree, there is a scheduling problems for the order in
+which to send messages to children. The intuition is to send on
+long-delay links first to hide the more expensive latencies.
+
+% Limitations
+What we do not consider yet is link congestion.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Mechanisms}
+
+\subsection{Aggregation}
 
@@
 
-Open questions: How does this work with several senders (everyone is
-potentially a sender). Maybe something like in navigation
-systems. Every node has an entry point, which forwards the
-messages. Nodes are then clustered \ldots
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Implementation}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Implementation}
+We implement our quorum protocol on Barrelfish using the UMP
+interconnect driver. UMP provides channels between
+endpoints. Communication is reliable, and messages are delivered
+in-order within a channel. Although UMP channels are uni-directional,
+Barrelfish automatically established two uni-directional channels on
+bind time. Hence, we consider them as being bi-directional. Every UMP
+channels has independent buffers associated with it.
+
+First, we establish connections such that we get a fully connected
+graph with vertices being the quorum instances and edges being UMP
+channels between them. For that, we need $O(n^2)$ UMP channels.
+
+We build up UMP channels in rounds $r_i$. The quorum instance on core
+$i$ is creating a UMP channel to all nodes $j$ with $j>i$ in
+$r_i$. The beginning of a round needs to be synchronized such that
+node $i+1$ only starts establishing connections when all other nodes
+completed $i$. Synchronization is required since UMP channels are
+scheduled round-robin. Messages on different channels are received
+non-deterministically.
 
@@
 
-Reducing the number of children also helps in select. It reduces the
-number of ``channels'' to poll, and therefore the latency of detecting
-messages. Instead of
+We show an example broadcast tree for a 8x4x1 AMD Barcelona machine
+(gruyere) in Figure~\ref{fig:qrm_tree_gruyere}.
+
+\begin{figure}
+  \input{qrm_tree_gruyere}
+  \caption{Tree of cores for broadcast on gruyere}
+  \label{fig:qrm_tree_gruyere}
+\end{figure}
+
+\paragraph{Observations} Reducing the number of children also helps in
+select. It reduces the number of ``channels'' to poll, and therefore
+the latency of detecting messages. Instead of
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Experimental results}
+\section{Experimental results}
 
-\paragraph{Current numbers}
+\paragraph{Current numbers} Current numbers are listed in
+Table~\ref{tab:bc_measurements}.
 
@@
 
-\paragraph{Tree setup} \stefan{describe}
-
 \paragraph{Measurements to do next} %
 \begin{itemize}
-\item Increase number of cores to talk to in every round. Use a
-  separate waitsets, so that we don't have additional overhead from
-  the bindings not used in each concrete measurement.
 \item Play with batching. Incrementally increase the number of
@@
 \paragraph{Minimal cost of sending a tree-broadcast} %
-Plot~\ref{pgfplot:201303141819} shows the minimal cost of flooding a
-sub-tree. The group communication is based on a binary tree. Core 0 is
-the root, cores 1 and 2 are its children etc.
+Plot~\ref{pgfplot:201303141819} shows the cost of flooding a sub-tree
+(with the 50\% worst measurements dropped). The group communication is
+based on a binary tree. Core 0 is the root, cores 1 and 2 are its
+children etc.
 
@@
 \begin{figure}
-  \caption{Plot}
+  \caption{Execution time for a broadcast with ACK on gruyere. The
+    cost is for execution for the sub-graph starting at the given
+    node. Refer to Figure~\ref{fig:qrm_tree_gruyere} for a
+    visualization of the broadcast tree used. }
   \label{pgfplot:201303141819}
@@
       xlabel=core id,
+      scaled y ticks = false, % prevent 10^x stuff
+      y tick label style={/pgf/number format/fixed},
       ylabel={cost for subtree [cycles]}]
-    \addplot[color=red,mark=x] coordinates {
-      (0,9475.0)
-      (1,7935.0)
-      (2,7894.0)
-      (3,5965.0)
-      (4,5604.0)
-      (5,5718.0)
-      (6,5647.0)
-      (7,4316.0)
-      (8,2989.0)
-      (9,3173.0)
-      (10,3395.0)
-      (11,3332.0)
-      (12,3284.0)
-      (13,3310.0)
-      (14,3231.0)
-      (15,2542.0)
-      (16,586.0)
-      (17,588.0)
-      (18,576.0)
-      (19,583.0)
-      (20,536.0)
-      (21,539.0)
-      (22,533.0)
-      (23,516.0)
-      (24,546.0)
-      (25,552.0)
-      (26,541.0)
-      (27,543.0)
-      (28,537.0)
-      (29,527.0)
-      (30,533.0)
-      (31,534.0)
+    \addplot[
+      color=red,
+      very thin,
+      mark=*,
+      mark options={%
+        scale=.4
+      },
+      error bars/y dir=both,
+      error bars/y explicit] coordinates {
+      (0,9932.3) +- (564.4,564.4)
+      (1,8240.1) +- (298.5,298.5)
+      (2,8259.6) +- (549.4,549.4)
+      (3,6206.3) +- (225.1,225.1)
+      (4,5914.9) +- (399.2,399.2)
+      (5,6033.5) +- (462.2,462.2)
+      (6,6070.4) +- (434.3,434.3)
+      (7,4530.4) +- (188.6,188.6)
+      (8,3163.4) +- (246.1,246.1)
+      (9,3403.0) +- (285.3,285.3)
+      (10,3650.7) +- (336.5,336.5)
+      (11,3559.0) +- (318.8,318.8)
+      (12,3558.1) +- (284.8,284.8)
+      (13,3567.5) +- (304.5,304.5)
+      (14,3476.3) +- (290.2,290.2)
+      (15,2711.7) +- (151.9,151.9)
+      (16,614.0) +- (17.5,17.5)
+      (17,606.2) +- (17.3,17.3)
+      (18,636.2) +- (72.5,72.5)
+      (19,641.3) +- (46.3,46.3)
+      (20,583.8) +- (46.7,46.7)
+      (21,577.8) +- (38.3,38.3)
+      (22,561.8) +- (18.1,18.1)
+      (23,603.5) +- (56.6,56.6)
+      (24,589.0) +- (33.4,33.4)
+      (25,582.9) +- (33.2,33.2)
+      (26,571.7) +- (16.3,16.3)
+      (27,581.6) +- (36.6,36.6)
+      (28,564.0) +- (16.4,16.4)
+      (29,564.0) +- (20.8,20.8)
+      (30,551.6) +- (13.0,13.0)
+      (31,596.2) +- (51.4,51.4)
     };
@@
 
-\end{figure}
-
-\begin{figure}
-  \input{qrm_tree_gruyere}
-  \caption{Tree of cores for broadcast on gruyere}
 \end{figure}
@@
 \renewcommand{\labelitemi}{\checkmark}
-\item disable yielding set 
+\item disable yielding
 }
-\item some other item
 \item run several request in parallel, give them IDs, can use in the
@@
 \end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Future work}
+
+\begin{itemize}
+\item Need higher-level applications, such as:
+  \begin{itemize}
+  \item octopus
+    \begin{itemize}
+    \item higher level application?
+    \end{itemize}
+  \item capability system? \stefan{Ask Simon how expensive revocation
+      currently is}
+  \item a database with replication and consistency maintenance
+    \begin{itemize}
+    \item SharedDB? (buffers between operators, but no synchronization
+      except for access to buffers, which are multiple writers, one
+      reader)
+    \item Crescando (some kind of state machine replication)
+    \end{itemize}
+  \end{itemize}
+\item Machine model for topology aware tree
+  \begin{itemize}
+  \item Talked to Pravin about this a bit
+  \end{itemize}
+\item MPI collectives (as in~\cite{Tu2008})
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Open questions}
+
+\paragraph{How does this work with several senders} 
+Maybe something like in navigation systems. Every node has an entry
+point, which forwards the messages. Nodes are then clustered
+\ldots. Or: send the request up to the root and then down again? This
+keeps the message complexity the same and doubles the time
+complexity.
 

### 2013-03-20 paper.tex
Machine model section

@@
 
-The selection of distributed algorithms depends on the characteristics
-of a network. Multicores networks are heterogeneous combinations of
-complex networks. %
-Their diversity makes manual selection tedious. Hence, we aim for an
-automatic approach for selecting algorithms for a specific
+Characteristics of the network influence the performance of
+distributed algorithms. Multicores networks are heterogeneous
+combinations of complex networks, which makes algorithm selection
+hard. %
+Furthermore, their diversity makes manual selection tedious. Hence, we
+aim for an automatic approach for selecting algorithms for a specific
 network. %
 We express the network characteristics in a multicore network
-model. This model is currently by no means complete. We are going to
+model. This model at this stage is by no means complete. We are going to
 extend it over time to address more complexities of current and future

### 2013-03-21 paper.tex
Added a simple graph and prioritiesed attributes for network model

@@
 The network model is defined by communication channels, which in turn
-are defined by a set of attributes, i.e.\
+are defined by a set of attributes (here sorted by priority):
 \begin{itemize}
-\item reliability (loss, link failure, in-order delivery, phantoms,
-  corruption, duplicated messages): Ethernet is not reliable,
-  multicore interconnect networks often are
+\item latency (quantitative) between each pair of nodes
+\item ``breakdown'' (quantitative) of message send cost: Ethernet has
+  dominating propagation time vs.\ dominating send and receive time on
+  multicores
 \item synchronized clocks: sychronized clocks + bound on propagation
@@
   \exists$ algorithm for asynchronous
+\item reliability (loss, link failure, in-order delivery, phantoms,
+  corruption, duplicated messages): Ethernet is not reliable,
+  multicore interconnect networks often are
 \item Security \& and failure detection (and the cost for that)
-\end{itemize}
-
-These are more about performance:
-\begin{itemize}
-\item ``breakdown'' of message send cost: Ethernet has dominating
-  propagation time vs.\ dominating send and receive time on multicores
-\item latency between each pair of nodes
 \end{itemize}
@@
 We express the model in a graph, where nodes are processors and edges
-are (on-hop?) communication links.
+are (on-hop?) communication links. The machines we consider for now
+only have bi-directional communication links. Other machines (like the
+SCC) have uni-directional links, which is why we model the graph with
+directed graph.
 

### 2013-03-21 graphs/links.hs
Haskell program to build a more or less suitable model for a very basic NUMA machine

@@ -1,0 +1,46 @@
+import Debug.Trace
+
+links = [(1,2),(1,4),(2,3)]
+
+--------------------------------------------------
+-- Logic
+--------------------------------------------------
+
+maxInt :: Int
+maxInt = maxBound::Int
+
+-- Get the number of hops between a pair of cores
+linkCost :: (Int, Int) -> Int
+linkCost (x,y)
+  | x == y     = trace ("linkCost eq with " ++ show (x,y)) (0)
+  | otherwise  = trace ("linkCost other with " ++ show (x,y)) nb_min_costs_plus
+  where 
+    nb_min_costs_plus  | nb_min_costs == maxInt    = maxInt
+                       | otherwise                 = nb_min_costs + 1
+    nb_min_costs    | (length nb_costs) == 0    = maxInt
+                    | otherwise                 = trace ("calculating minimum for list " ++ show nb_costs) minimum nb_costs -- get minimum of these costs
+    nb_costs = trace ("calculating nb cost for " ++ show nb_list) (map linkCost nb_list) -- get cost of these links
+    nb_list = trace ("getting nbs reached by links " ++ show nb ) (map (\ (s,e) -> (e,y)) nb) -- prepare input tuples for recursive call
+    nb = filter ((==x).fst) links -- find links to neighbors
+
+main :: IO()
+main = print (linkCost (1,3))
+
+--------------------------------------------------
+-- Playground
+--------------------------------------------------
+
+skt :: (Int, Int) -> Int
+skt (a,b) = b
+
+-- Get the number of hops between a pair of cores
+linkCostTest :: (Int, Int) -> IO()
+linkCostTest (x,y) = print nb_list
+  where 
+    nb_list = map (\ (s,e) -> (e,y)) nb
+    nb = filter ((==x).fst) links -- find links to neighbors
+
+
+test :: IO()
+test = (linkCostTest (1,3))
+

### 2013-03-25 paper.tex
Haskell program to build a more or less suitable model for a very basic NUMA machine
Included first multicast try found for gruyere.

@@
 \begin{itemize}
-\item latency (quantitative) between each pair of nodes
+\item latency (quantitative) between each pair of nodes (per-edge)
 \item ``breakdown'' (quantitative) of message send cost: Ethernet has
   dominating propagation time vs.\ dominating send and receive time on
-  multicores
+  multicores (per-node)
 \item synchronized clocks: sychronized clocks + bound on propagation
@@
 
+% Assumptions
+We assume that the cost of sending a message to the same node is 0,
+which is not true, since even using a highly optimized implementation
+for local communication (like LMP) has a non-negligible cost.
+
 % Limitations
 What we do not consider yet is link congestion.
+
+% EXAMPLE
+An example of a machine model, which approximates gruyere can be found
+in ..
+
+\begin{tikzpicture}[>=latex,line join=bevel,scale=3.0]
+  \pgfsetlinewidth{1bp}
+\input{graphs/full_gruyere}
+\end{tikzpicture}
+
+We show the multicast tree automatically generated from a fully meshed
+machine model of a 8x4x1 sample multicore (gruyere) in
+Figure~\ref{fig:mst_gruyere}. We get this tree by applying a minimum
+spanning tree algorithm on a multicore model encoding link latencies.
+
+\begin{figure}
+\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
+  \pgfsetlinewidth{1bp}
+\input{graphs/mst_gruyere}
+\end{tikzpicture}
+\caption{Multicast tree automatically found for a 8x4x1 multicore}
+\label{fig:mst_gruyere}
+\end{figure}
 
@@
 \begin{itemize}
+\item Arguing that group communication/atomic broadcast and showing
+  that we can do it well might be enough (appeal to atomic broadcasts
+  as the foundation for other distributed algorithms, and the MPI
+  primitives, that can/need to be mapped to group-communication (have
+  a list of them) 
 \item Need higher-level applications, such as:

### 2013-03-28 paper.tex
Added pseudo-code for how to initialize channels for a fully-meshed network

@@
 \usepackage[colorlinks=true]{hyperref}
+\usepackage[ruled,vlined]{algorithm2e}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Model}
+\section{The multicore network model}
 
+% selecting hard
 Characteristics of the network influence the performance of
-distributed algorithms. Multicores networks are heterogeneous
-combinations of complex networks, which makes algorithm selection
-hard. %
-Furthermore, their diversity makes manual selection tedious. Hence, we
-aim for an automatic approach for selecting algorithms for a specific
-network. %
+distributed algorithms. Due to the heterogeneous combinations of
+complex networks on multicores, selection of algorithms is
+particularly hard.
+
+% model
 We express the network characteristics in a multicore network
@@
 
+% graph
+We represent the multicore network as a graph. The nodes in this graph
+correspond to cores, and edges the communication channels between
+nodes. The machines we consider for now only have bi-directional
+communication links. Other machines (like the SCC) have
+uni-directional links, which is why we model the graph as directed
+graph.
+
+% shared memory -> fully meshed
+This graph is fully meshed for shared memory machines. Every core can
+communicate with every other node via the cache coherence protocol.
+
+\subsection{Node characteristics}
+
+Every node (i.e.\ core) in the system has characteristics associated
+with it:
+
+\begin{description}
+\item[synchrony] Parts of a multicore machine are synchronous. Hence,
+  one characteristic of a node is an identifier for the synchrony
+  cluster of a node.
+\item[$t_{send}$] Time required to send a message, i.e.\ marshalling
+  and queuing the message
+\item[$t_{recv}$] Time required to receive a message, i.e.\
+  dequeuing, unmarshalling and demultiplexing a channel. 
+\end{description}
+
+\subsection{Link characteristics}
+
 The network model is defined by communication channels, which in turn
 are defined by a set of attributes (here sorted by priority):
-\begin{itemize}
-\item latency (quantitative) between each pair of nodes (per-edge)
-\item ``breakdown'' (quantitative) of message send cost: Ethernet has
+
+\begin{description}
+\item[latency] (quantitative) between each pair of nodes (per-edge)
+\item[breakdown] (quantitative) of message send cost: Ethernet has
   dominating propagation time vs.\ dominating send and receive time on
   multicores (per-node)
-\item synchronized clocks: sychronized clocks + bound on propagation
-  time $\rightarrow$ \emph{synchronous network} model. \\Then:
-  $\exists$ algorithm for synchronous networks $\rightarrow
-  \exists$ algorithm for asynchronous
-\item reliability (loss, link failure, in-order delivery, phantoms,
+\item[bounded delivery]
+\item[reliability] (loss, link failure, in-order delivery, phantoms,
   corruption, duplicated messages): Ethernet is not reliable,
   multicore interconnect networks often are
-\item Security \& and failure detection (and the cost for that)
-\end{itemize}
+\item[Security] \& and failure detection (and the cost for that)
+\end{description}
+
+% Assumptions
+We assume that the cost of sending a message to the same node is 0,
+which is not true, since even using a highly optimized implementation
+for local communication (like LMP) has a non-negligible cost.
+
+% Limitations
+What we do not consider yet is link congestion.
+
+\subsection{Acquiring the model}
 
@@
 
-% Express as:
-We express the model in a graph, where nodes are processors and edges
-are (on-hop?) communication links. The machines we consider for now
-only have bi-directional communication links. Other machines (like the
-SCC) have uni-directional links, which is why we model the graph with
-directed graph.
+\subsection{Example}
+
+An example of a machine model, which approximates a 2x2x1 nos box can
+be found in Figure~\ref{fig:full_nos}
+
+\begin{figure}
+\begin{tikzpicture}[>=latex,line join=bevel]
+  \pgfsetlinewidth{1bp}
+\input{graphs/full_nos}
+\end{tikzpicture}
+\caption{Network model of a 2x2x1 machine}
+\label{fig:full_nos}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Example: Atomic broadcast
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Atomic Broadcast}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Building the tree}
+
+First, we build the broadcast tree. We kick-start our protocol
+connecting every process with all other processes to get a
+fully-meshed network of channels.
+
+We use a round-based algorithm to open channels. Then, every node
+knows exactly the source of an incoming connection. We formalize this
+algorithm in Algorithm~\ref{algo:ab_bind}.
+
+\begin{algorithm}[H]
+  %
+  \SetKwInOut{Assumptions}{assumptions}
+  \Assumptions{Processes have unique contiguous
+    identifiers starting at 0}
+  \BlankLine
+  %
+  \SetKwArray{c}{channels}
+  \SetKwFunction{connectNode}{connectNode}
+  \SetKwFunction{listen}{listen}
+  % 
+  \KwData{process id $p$, round $r$, %
+    each process an array of channels \c}
+  \KwResult{Fully-meshed network of processes}
+  % 
+  \BlankLine
+  %
+  $r \leftarrow 0$\;
+  \For{$i \leftarrow 0$ \KwTo $num(p)$}{
+    \eIf{$p=i$}{
+      \For{$o \leftarrow i+1$ \KwTo $num(p)$}{
+        \c{$o$} $\leftarrow$ \connectNode{$o$}\;
+      }
+    }{
+        \c{$i$} $\leftarrow$ \listen{}\;
+    }
+  }
+  \caption{Atomic broadcast on reliable communication channels}
+  \label{algo:ab}
+\end{algorithm}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Broadcast protocol}
+
+% Our implementation
+We now build an atomic broadcast for multicore machines. Our
+implementation is based on the Barrelfish UMP interconnect driver. It
+provides reliable channels with in-order delivery. Communication
+starts at the root node, which acts as a
+sequentializer. See~\ref{algo:ab} for details.
+
+\begin{algorithm}[H]
+  \SetAlgoLined
+  %
+  \KwData{List of processes $p$, broadcast tree as graph $(V, E)$}
+  \KwResult{Tree based atomic broadcast using a sequentializer}
+  % 
+  $(V, E)$ = build\_graph\;
+  \While{not at end of this document}{
+    read current\;
+    \eIf{understand}{
+      go to next section\;
+      current section becomes this one\;
+    }{
+      go back to the beginning of current section\;
+    }
+  }
+  \caption{Atomic broadcast on reliable communication channels}
+  \label{algo:ab}
+\end{algorithm}
 
@@
 graph such that all nodes can be reached.
+
 % Tree -> scheduling
@@
 long-delay links first to hide the more expensive latencies.
-
-% Assumptions
-We assume that the cost of sending a message to the same node is 0,
-which is not true, since even using a highly optimized implementation
-for local communication (like LMP) has a non-negligible cost.
-
-% Limitations
-What we do not consider yet is link congestion.
-
-% EXAMPLE
-An example of a machine model, which approximates gruyere can be found
-in ..
-
-\begin{tikzpicture}[>=latex,line join=bevel,scale=3.0]
-  \pgfsetlinewidth{1bp}
-\input{graphs/full_gruyere}
-\end{tikzpicture}
 

### 2013-03-28 graphs/graph_example.py

@@ -20,8 +20,8 @@ from pygraph.algorithms.minmax import minimal_spanning_tree
 
 # --------------------------------------------------
 
-CORES_PER_NODE = 4
-NUM_NUMA_NODES = 8
+CORES_PER_NODE = 2
+NUM_NUMA_NODES = 2
 NUM_CORES = (CORES_PER_NODE*NUM_NUMA_NODES)
 HOPCOST = 10
 NUMACOST = 1
@@ -90,17 +90,18 @@ print "Expecting %d edges" % dbg_num_edges
 
 g_numa.add_nodes(range(NUM_NUMA_NODES))
 
-for i in range(3):
-    g_numa.add_edge((i, i+1)) # to right, top row
-    g_numa.add_edge((i, i+4)) # top to bottom row
+# for i in range(3):
+#     g_numa.add_edge((i, i+1)) # to right, top row
+#     g_numa.add_edge((i, i+4)) # top to bottom row
 
-for i in range(4,7):
-    g_numa.add_edge((i, i+1)) # to right, bottom row
+# for i in range(4,7):
+#     g_numa.add_edge((i, i+1)) # to right, bottom row
 
-# remainig edges
-g_numa.add_edge((2,7))
-g_numa.add_edge((3,6))
-g_numa.add_edge((3,7))
+# # remainig edges
+# g_numa.add_edge((2,7))
+# g_numa.add_edge((3,6))
+# g_numa.add_edge((3,7))
+g_numa.add_edge((0,1))
 
 # --------------------------------------------------
 # Build fully meshed machine graph

### 2013-04-10 paper.tex
Added algorithm2e LaTeX module

@@
 
+This is required for Barrelfish UMP communication channels since on
+bind, no source identifier is send along\footnote{Check if this is
+  actually true, and even if it is true, if is a Barrelfish problem,
+  and not a general one}.
+
 \begin{algorithm}[H]
@@
   \SetKwFunction{listen}{listen}
+  \SetKwFunction{barrier}{barrier}
   % 
@@
     }
+    \barrier{} \tcp*{Otherwise, reordering possible}
   }
-  \caption{Atomic broadcast on reliable communication channels}
-  \label{algo:ab}
+  \caption{Establish fully-meshed network of channels}
+  \label{algo:ab_bindOB}
 \end{algorithm}
@@
 \begin{algorithm}[H]
-  \SetAlgoLined
+\SetKwProg{Fn}{Function}{}{end}%
+\SetKwFunction{receive}{receive}%
+\SetKwFunction{send}{send}%
   %
@@
   % 
-  $(V, E)$ = build\_graph\;
-  \While{not at end of this document}{
-    read current\;
-    \eIf{understand}{
-      go to next section\;
-      current section becomes this one\;
-    }{
-      go back to the beginning of current section\;
+  \BlankLine
+  \Fn(\tcp*{Receive a message}){\receive{$m$}}{
+    $i \leftarrow 5$
+    \tcp{Receive a message}
   }
+  % 
+  \BlankLine
+  \Fn(\tcp*{Send a message}){\send{void}}{
+    $i \leftarrow 5$
   }

### 2013-04-14 paper.tex
Wrote down the algorithm I believe implements atomic broadcast
Fixed the algorithm pseudocode, fixed a label, synced the bibliography
Removed some old stuff

@@
   dequeuing, unmarshalling and demultiplexing a channel.
+\item[failure] Can nodes fail? If so, how? (Byzantine, \ldots)
 \end{description}
@@
   \caption{Establish fully-meshed network of channels}
-  \label{algo:ab_bindOB}
+  \label{algo:ab_bind}
 \end{algorithm}
@@
 
+\newcommand{\textc}[1]{{\color{gray} {\footnotesize #1}}}
 \begin{algorithm}[H]
+\SetCommentSty{textc}
+\SetKwInOut{Assumptions}{assumptions}
+\Assumptions{Underlying communication channel is reliable and in-order}
 \SetKwProg{Fn}{Function}{}{end}%
-\SetKwFunction{receive}{receive}%
+\SetKwFunction{receive}{on\_receive}%
+\SetKwFunction{waitchild}{wait\_for\_children}%
 \SetKwFunction{send}{send}%
+\SetKwFunction{icsend}{send\_bc\_request}%
+\SetKwFunction{icsendack}{send\_bc\_ack}%
+\SetKwFunction{handlemessages}{handle\_other\_messages}%
   %
@@
   \BlankLine
-  \Fn(\tcp*{Receive a message}){\receive{$m$}}{
-    $i \leftarrow 5$
-    \tcp{Receive a message}
+  \Fn(\tcp*{Receive a message}){\receive{$client$, $m$}}{
+    \For(\tcp*{For all children}){$c \leftarrow \{ c: \exists (self, c) \in E \} $}{
+      \icsend{c}
+    }
+    \waitchild{}\;
+    \icsendack{$client$}\;
   }
@@
   \Fn(\tcp*{Send a message}){\send{void}}{
-    $i \leftarrow 5$
+    \tcc{Need to wait for acknowledgment before returning to
+      caller. Otherwise, sender might see his own request before some
+      other request, that the sequentializer decided to handle first}
+    \icsend{$V_{root}$}\tcp*{Relay msg (sequentializer)}
+    \While{no answer received}{
+      \handlemessages{}\tcp*{Otherwise, deadlocks}
+    }
   }
@@
 connected subsets, distributed messages across cluster first, and then
-within cluster. Maybe also a spanning-tree protocol, to find a minimal
-graph such that all nodes can be reached.
+within cluster.
+
+Maybe also a minimum spanning-tree (MST) protocol, to find a minimal
+graph such that all nodes can be reached. The problem with the MST is
+that it does not consider parallelism. While it is true that the
+global cost is minimal in such a tree, it does not take into account
+that sending in parallel does not increase the time required to reach
+every node. %
+\stefan{Find an example, the MST could be a path through the graph
+  with weights 1, where it might make more sense to use a link with
+  cost 2 in the beginning and then send messages on two ``branches''
+  of the tree in parallel.}
+
+% Radix degree
+If the send cost $t_s$ is smaller than the propagation time $t_p$,
+\stefan{round up}%
+$d = \frac{t_p}{t_s}$ messages can be send to hide propagation of
+messages. Hence, a tree with degree $d$ should be ideal to minimize
+latency, but only for an acknowledged protocol.
 
 % Tree -> scheduling
-Assuming the tree, there is a scheduling problems for the order in
+Assuming the tree, there is a \emph{scheduling problems} for the order in
 which to send messages to children. The intuition is to send on
-long-delay links first to hide the more expensive latencies.
+long-delay links first to hide the more expensive latencies, as this
+link is dominating total send cost.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Implementation}
-
-We implement our quorum protocol on Barrelfish using the UMP
-interconnect driver. UMP provides channels between
-endpoints. Communication is reliable, and messages are delivered
-in-order within a channel. Although UMP channels are uni-directional,
-Barrelfish automatically established two uni-directional channels on
-bind time. Hence, we consider them as being bi-directional. Every UMP
-channels has independent buffers associated with it.
-
-First, we establish connections such that we get a fully connected
-graph with vertices being the quorum instances and edges being UMP
-channels between them. For that, we need $O(n^2)$ UMP channels.
-
-We build up UMP channels in rounds $r_i$. The quorum instance on core
-$i$ is creating a UMP channel to all nodes $j$ with $j>i$ in
-$r_i$. The beginning of a round needs to be synchronized such that
-node $i+1$ only starts establishing connections when all other nodes
-completed $i$. Synchronization is required since UMP channels are
-scheduled round-robin. Messages on different channels are received
-non-deterministically.
-
-Build a tree. Every node has parents and children (except for the root
-and the leafs). The number of children does not really matter for the
-algorithm. In the init phase, we construct the tree (e.g. broadcast:
-one root node, all other nodes are children of the root node,
-multicast: every node has two children, NUMA tree: two layers, two
-different implementations?
+\section{Example}
 
@@
 
-\paragraph{Measurements to do next} %
-\begin{itemize}
-\item Play with batching. Incrementally increase the number of
-  messages send in a batch. I assume this is machine specific, which
-  means, that this is something programmers do not want to deal
-  with. We measure this at dynamically at run-time and find the right
-  batch size.
-\end{itemize}
-
 \paragraph{Minimal cost of sending a tree-broadcast} %
@@
 
-The average cost is really high (so something is wrong with my
-code). But the minimal numbers show what is possible. The numbers
-achieved are easily explainable. The cost is increasing
-logarithmic with the number of nodes reached by the broadcast (as
-expected). Every level in the tree adds an additional 3500 cycles to
-the tree. Node 0 takes significantly longer. I don't know yet why that
-is.
+The average cost is really high (probably a scheduling issue). But the
+minimal numbers show what is possible. The numbers achieved are easily
+explainable. The cost is increasing logarithmic with the number of
+nodes reached by the broadcast (as expected). Every level in the tree
+adds an additional 3500 cycles to the tree. Node 0 takes significantly
+longer. I don't know yet why that is.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Open questions}
-
-\paragraph{How does this work with several senders} 
-Maybe something like in navigation systems. Every node has an entry
-point, which forwards the messages. Nodes are then clustered
-\ldots. Or: send the request up to the root and then down again? This
-keeps the message complexity the same and doubles the time
-complexity.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage

### 2013-04-27 paper.tex
Program to evaluate model The current version seems to properly calculate cost for sending a broadcast along the 'gruyere' tree

@@
 \section{Introduction}
+
+There are two problems:
+\begin{enumerate}
+\item Performance of distributed algorithms on multicores. Programmers
+  don't get it right due to different complexity measures. We deal
+  with this by improving these algorithms. This will lead to higher
+  performance of existing algorithms.
+\item Diversity of hardware. Hand-tuning algorithms is tedious. Need
+  to do this automatically. To evaluate this, we compare the average
+  performance of our automatic configuration on a wide range of
+  multicores with performance of a single hand-tuned implementation.
+\end{enumerate}
 

### 2013-04-27 graphs/evaluate.py

@@ -1,0 +1,96 @@
+import events
+import heapq
+
+# Evaluation is round-based
+
+# Assumptions:
+# 1) nodes never have to process different events at the same time
+
+round = 0
+event_queue = []
+model = {}
+
+def evalute(tree, root):
+    """
+    Evaluate the latency of sending an individual message along the tree
+    """
+    global round
+    global node_queues
+    global model
+
+    model = tree
+    
+    send(root, round, [])
+
+    while not terminate():
+        consume_event()
+
+    # XXX dirty hack: receive of last node is missing
+    # as our nodes are homogeneous, we just add the receive time of the root
+    return round + receive_cost(root)
+
+def consume_event():
+    """
+    Consume event from event queue
+    This will increase the round counter
+    """
+    global round
+    (p, e) = heapq.heappop(event_queue)
+    assert(p>=round)
+    round = p
+
+    if isinstance(e, events.Propagate):
+        propagate(e.src, e.dest)
+
+    if isinstance(e, events.Receive):
+        receive(e.src, e.dest)
+
+def propagate(src, dest):
+    """
+    Process propagation event.
+    This will queue a receive event on the receiving side
+    """
+    w = model.edge_weight((src, dest))
+    heapq.heappush(event_queue, (round + w, events.Receive(src, dest)))
+
+def receive(src, dest):
+    """
+    Receive a message on dest
+    Send will be called to trigger sending of messages to children
+    """
+    print "{%d}: receiving message from {%d} in round %d" \
+        % (dest, src, round)
+    send(dest, round+receive_cost(dest), [src])
+
+def send_cost(node):
+    """
+    Return send cost. This is constant for the time being as we
+    evaluate heterogeneous machines only.
+    """
+    return 10
+
+def receive_cost(node):
+    """
+    Return send cost. This is constant for the time being as we
+    evaluate heterogeneous machines only.
+    """
+    return 10
+
+def send(src, cost, omit):
+    """
+    Simulate sending a message from given node.
+    No message will be send towards nodes given in omit
+    XXX Scheduling decision here
+    """
+    for n in model.neighbors(src):
+        if not n in omit:
+            cost+=send_cost(src)
+            heapq.heappush(event_queue, \
+                               (cost, events.Propagate(src, n)))
+
+def terminate():
+    """
+    Return whether evaluation is termiated
+    """
+    return len(event_queue)==0
+

### 2013-04-27 graphs/graph_example.py

@@ -1,8 +1,5 @@
 #!/usr/bin/env python
 
-# Copyright (c) 2007-2008 Pedro Matiello <pmatiello@gmail.com>
-# License: MIT (see COPYING file)
-
 # Import graphviz
 import sys
 sys.path.append('..')
@@ -18,10 +15,13 @@ from pygraph.readwrite.dot import write
 from pygraph.algorithms.minmax import shortest_path
 from pygraph.algorithms.minmax import minimal_spanning_tree
 
+# Import own code
+import evaluate
+
 # --------------------------------------------------
 
-CORES_PER_NODE = 2
-NUM_NUMA_NODES = 2
+CORES_PER_NODE = 4
+NUM_NUMA_NODES = 8
 NUM_CORES = (CORES_PER_NODE*NUM_NUMA_NODES)
 HOPCOST = 10
 NUMACOST = 1
@@ -53,7 +53,7 @@ def add_numa(graph, node1, node2, cost):
                     (src, dest, cost)
                 graph.add_edge((src, dest), cost)
 
-def connect_numa_nodes(g, g_numa, src):
+def connect_numa_nodes(g, g_numa, src, ):
     # assuming that routing is taking the shortes path,
     # NOT true on e.g. SCC
     connect_numa_internal(g, src)
@@ -74,56 +74,77 @@ def connect_numa_internal(graph, numa_node):
                 graph.add_edge((node1, node2), NUMACOST)
 
 # --------------------------------------------------
+def build_and_simulate():
+    """
+    Build a tree model and simulate sending a message along it
+    """
 
-# Graph creation
-gr = graph()
-g_numa = graph()
+    # Graph creation
+    gr = graph()
+    g_numa = graph()
 
-dbg_num_edges = 0
-for n in range(NUM_CORES):
-    dbg_num_edges += n
+    dbg_num_edges = 0
+    for n in range(NUM_CORES):
+        dbg_num_edges += n
 
-print "Expecting %d edges" % dbg_num_edges
+    print "Expecting %d edges" % dbg_num_edges
 
-# --------------------------------------------------
-# Construct graph of NUMA nodes
+    # --------------------------------------------------
+    # --- g_numa
+    # Construct graph of NUMA nodes
+    # This graph expresses the cost of sending messages between
+    # NUMA nodes.
 
-g_numa.add_nodes(range(NUM_NUMA_NODES))
+    g_numa.add_nodes(range(NUM_NUMA_NODES))
 
[…]

### 2013-04-28 graphs/draw.py
Added basic visualization based on tikz and LaTeX

@@ -1,0 +1,46 @@
+# Draw result of evaluation
+
+class Output():
+    "Wrapper to enable visualization output to file"
+    def __init__(self, name, num_cores):
+        self.name = name
+        self.f = open(name, 'w')
+        for i in range(num_cores):
+            self.f.write("\\node at (0mm,%dmm) {core %02d};\n" % \
+                             (self._y_coord_for_core(i), i))
+            self.f.write("\\draw[color=black!10] (20mm,%dmm) -- (30cm,%dmm);\n" % \
+                             (self._y_coord_for_core(i), \
+                                  self._y_coord_for_core(i)))
+
+    def _y_coord_for_core(self, core):
+        "Determines padding between cores"
+        return core*15
+
+    def _scale_time(self, time):
+        "Determines scale factor for time"
+        return time + 50
+
+    def _scale_cost(self, cost):
+        return cost
+
+    def send(self, core, to, time, cost):
+        "Visualize send operation"
+        self.f.write("\\node[draw,fill=red!20,minimum size=%dmm] "\
+                         "(s_%d_%d) at (%dmm,%dmm) {};\n" % \
+                         (self._scale_cost(cost), \
+                              core, to, \
+                              self._scale_time(time), \
+                              self._y_coord_for_core(core)))
+
+    def receive(self, core, sender, time, cost):
+        "Visualize receive operation"
+        # Box indicating receive operation
+        self.f.write("\\node[draw,fill=blue!20,minimum size=%dmm] "\
+                         "(r_%d_%d) at (%dmm,%dmm) {};\n" % \
+                         (self._scale_cost(cost), \
+                              sender, core, \
+                              self._scale_time(time), \
+                              self._y_coord_for_core(core)))
+        # Arrow indicating flow
+        self.f.write("\\draw[->] (s_%d_%d.center) -- (r_%d_%d.center); \n" % \
+                         (sender, core, sender, core))

### 2013-04-28 graphs/evaluate.py

@@ -1,5 +1,6 @@
 import events
 import heapq
+import draw
 
 # Evaluation is round-based
 
@@ -19,6 +20,10 @@ def evalute(tree, root):
     global model
 
     model = tree
+
+    # Construct visualization instance
+    global visu
+    visu = draw.Output("visu.tex", len(model))
     
     send(root, round, [])
 
@@ -60,6 +65,7 @@ def receive(src, dest):
     """
     print "{%d}: receiving message from {%d} in round %d" \
         % (dest, src, round)
+    visu.receive(dest, src, round, receive_cost(dest))
     send(dest, round+receive_cost(dest), [src])
 
 def send_cost(node):
@@ -82,11 +88,14 @@ def send(src, cost, omit):
     No message will be send towards nodes given in omit
     XXX Scheduling decision here
     """
-    for n in model.neighbors(src):
-        if not n in omit:
-            cost+=send_cost(src)
-            heapq.heappush(event_queue, \
-                               (cost, events.Propagate(src, n)))
+    send_time = cost
+    for dest in model.neighbors(src):
+        if not dest in omit:
+            visu.send(src, dest, send_time, send_cost(src))
+            send_time += send_cost(src)
+            heapq.heappush(\
+                event_queue, \
+                    (send_time, events.Propagate(src, dest)))
 
 def terminate():
     """

### 2013-04-28 graphs/events.py

@@ -1,0 +1,14 @@
+class Event():
+    "Empty base object"
+    def __init__(self, src, dest):
+        self.src = src
+        self.dest = dest
+
+class Send(Event):
+    "Represents a send operation"
+
+class Receive(Event):
+    "Represents a receive operation"
+
+class Propagate(Event):
+    "Represent propagation of event"

### 2013-04-29 paper.tex
Restructured Section on how to deduce the tree from the network model and added a couple of new ideas

@@
 
+We build our atomic broadcast based on an overlay network connecting
+all nodes of a given multicore machine.
+
+As a first step, we evaluate tree based overlay networks. Other
+potentially interesting topologies are rings.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Building the tree}
+\subsection{Tree}
 
-First, we build the broadcast tree. We kick-start our protocol
-connecting every process with all other processes to get a
-fully-meshed network of channels.
+We now look at tree based atomic broadcast implementations.
+
+The first challenge is to find efficient spanning trees for arbitrary
+machines. These machines are represented by a model, which we
+described earlier.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Divide and conquer}
+
+We divide the space into clusters. In every round, we further split up
+all cluster into smaller clusters and connect them with the minimal
+link.
+
+We find this link by searching for links that have start and
+end node in different regions of the most recent split. Out of these
+links, we pick the cheapest ones. We ignore links whose start or end
+node have a too high degree in the spanning tree already.
+
+Assuming that the choice of node IDs represents the topology to some
+extend, splitting them up into distinct clusters avoids contention, as
+two separate sub-trees are processed in different areas of the
+interconnect network.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Clustering}
+
+Another idea is to employ clustering. One example is to base this on
+NUMA domains such that every NUMA domain corresponds to one cluster.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Minimum-Spanning Tree}
+
+We can apply a minimum spanning tree algorithm to the machine model
+graph to find a number of links such that these links connect all
+nodes at a minimum cost.
+
+We have implemented such an algorithm and found out, that it is not a
+good solution in the general case, since it does not consider
+parallelism. Naturally, we would like to parallelize send operations
+to different nodes, which allows them to send messages in parallel.
+
+\stefan{We have an example for this, where the MST is essentially a
+  path through the graph}
+
+An important variable in constructing such a tree is the degree of
+nodes. If the send cost $t_s$ is smaller than the propagation time
+$t_p$,  $d = \lceil \frac{t_p}{t_s} \rceil$ messages can be send to
+hide propagation of messages. Hence, a tree with degree $d$ should be
+ideal to minimize latency, but only for an acknowledged protocol.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Scheduling}
+
+% Tree -> scheduling
+Assuming the tree (or some other kind of overlay network), there is a
+\emph{scheduling problems} for the order in which to send messages to
+children. The intuition is to send on long-delay links first to hide
+the more expensive latencies, as this link is dominating total send
+cost.
+
+\stefan{We have experiments showing this}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Example tree}
+
+We show the multicast tree automatically generated from a fully meshed
+machine model of a 8x4x1 sample multicore (gruyere) in
+Figure~\ref{fig:mst_gruyere}. We get this tree by applying a minimum
+spanning tree algorithm on a multicore model encoding link latencies.
+
+\begin{figure}
+\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
+  \pgfsetlinewidth{1bp}
+\input{graphs/mst_gruyere}
+\end{tikzpicture}
+\caption{Multicast tree automatically found for a 8x4x1 multicore}
+\label{fig:mst_gruyere}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Broadcast protocol}
+
+% Our implementation
+Assuming the tree, we now build an atomic broadcast for multicore
+machines. Our implementation is based on the Barrelfish UMP
+interconnect driver. It provides reliable channels with in-order
+delivery. Communication starts at the root node, which acts as a
+sequentializer. See~\ref{algo:ab} for details.
+
+\newcommand{\textc}[1]{{\color{gray} {\footnotesize #1}}}
+\begin{algorithm}[H]
+\SetCommentSty{textc}
+\SetKwInOut{Assumptions}{assumptions}
+\Assumptions{Underlying communication channel is reliable and in-order}
+\SetKwProg{Fn}{Function}{}{end}%
+\SetKwFunction{receive}{on\_receive}%
+\SetKwFunction{waitchild}{wait\_for\_children}%
+\SetKwFunction{send}{send}%
+\SetKwFunction{icsend}{send\_bc\_request}%
+\SetKwFunction{icsendack}{send\_bc\_ack}%
+\SetKwFunction{handlemessages}{handle\_other\_messages}%
+  %
+  \KwData{List of processes $p$, broadcast tree as graph $(V, E)$}
+  \KwResult{Tree based atomic broadcast using a sequentializer}
+  % 
+  \BlankLine
+  \Fn(\tcp*{Receive a message}){\receive{$client$, $m$}}{
+    \For(\tcp*{For all children}){$c \leftarrow \{ c: \exists (self, c) \in E \} $}{
+      \icsend{c}
+    }
+    \waitchild{}\;
+    \icsendack{$client$}\;
+  }
+  % 
+  \BlankLine
+  \Fn(\tcp*{Send a message}){\send{void}}{
+    \tcc{Need to wait for acknowledgment before returning to
+      caller. Otherwise, sender might see his own request before some
+      other request, that the sequentializer decided to handle first}
+    \icsend{$V_{root}$}\tcp*{Relay msg (sequentializer)}
+    \While{no answer received}{
+      \handlemessages{}\tcp*{Otherwise, deadlocks}
+    }
+  }
+  \caption{Atomic broadcast on reliable communication channels}
+  \label{algo:ab}
+
+\end{algorithm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Barrelfish implementation}
+
+When implementing the protocol in Barrelfish, we found several
+practical problems, which we will discuss briefly in this section.
+
+We kick-start our protocol connecting every process with all other
+processes to get a fully-meshed network of channels.
 
@@
 \end{algorithm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Broadcast protocol}
-
-% Our implementation
-We now build an atomic broadcast for multicore machines. Our
-implementation is based on the Barrelfish UMP interconnect driver. It
-provides reliable channels with in-order delivery. Communication
-starts at the root node, which acts as a
-sequentializer. See~\ref{algo:ab} for details.
-
-\newcommand{\textc}[1]{{\color{gray} {\footnotesize #1}}}
-\begin{algorithm}[H]
-\SetCommentSty{textc}
-\SetKwInOut{Assumptions}{assumptions}
-\Assumptions{Underlying communication channel is reliable and in-order}
-\SetKwProg{Fn}{Function}{}{end}%
-\SetKwFunction{receive}{on\_receive}%
-\SetKwFunction{waitchild}{wait\_for\_children}%
-\SetKwFunction{send}{send}%
-\SetKwFunction{icsend}{send\_bc\_request}%
-\SetKwFunction{icsendack}{send\_bc\_ack}%
-\SetKwFunction{handlemessages}{handle\_other\_messages}%
-  %
-  \KwData{List of processes $p$, broadcast tree as graph $(V, E)$}
-  \KwResult{Tree based atomic broadcast using a sequentializer}
-  % 
-  \BlankLine
-  \Fn(\tcp*{Receive a message}){\receive{$client$, $m$}}{
-    \For(\tcp*{For all children}){$c \leftarrow \{ c: \exists (self, c) \in E \} $}{
-      \icsend{c}
-    }
-    \waitchild{}\;
-    \icsendack{$client$}\;
-  }
-  % 
-  \BlankLine
-  \Fn(\tcp*{Send a message}){\send{void}}{
-    \tcc{Need to wait for acknowledgment before returning to
-      caller. Otherwise, sender might see his own request before some
-      other request, that the sequentializer decided to handle first}
-    \icsend{$V_{root}$}\tcp*{Relay msg (sequentializer)}
-    \While{no answer received}{
-      \handlemessages{}\tcp*{Otherwise, deadlocks}
-    }
-  }
-  \caption{Atomic broadcast on reliable communication channels}
-  \label{algo:ab}
-\end{algorithm}
-
-% How to deduct tree from model?
-We then use this graph to build a group-communication
-tree. Interesting techniques could be: clustering, to find closely
-connected subsets, distributed messages across cluster first, and then
-within cluster.
-
-Maybe also a minimum spanning-tree (MST) protocol, to find a minimal
-graph such that all nodes can be reached. The problem with the MST is
-that it does not consider parallelism. While it is true that the
-global cost is minimal in such a tree, it does not take into account
-that sending in parallel does not increase the time required to reach
-every node. %
-\stefan{Find an example, the MST could be a path through the graph
-  with weights 1, where it might make more sense to use a link with
-  cost 2 in the beginning and then send messages on two ``branches''
-  of the tree in parallel.}
-
-% Radix degree
-If the send cost $t_s$ is smaller than the propagation time $t_p$,
-\stefan{round up}%
-$d = \frac{t_p}{t_s}$ messages can be send to hide propagation of
-messages. Hence, a tree with degree $d$ should be ideal to minimize
-latency, but only for an acknowledged protocol.
-
-% Tree -> scheduling
-Assuming the tree, there is a \emph{scheduling problems} for the order in
-which to send messages to children. The intuition is to send on
-long-delay links first to hide the more expensive latencies, as this
-link is dominating total send cost.
-
-We show the multicast tree automatically generated from a fully meshed
-machine model of a 8x4x1 sample multicore (gruyere) in
-Figure~\ref{fig:mst_gruyere}. We get this tree by applying a minimum
-spanning tree algorithm on a multicore model encoding link latencies.
-
-\begin{figure}
-\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
-  \pgfsetlinewidth{1bp}
-\input{graphs/mst_gruyere}
-\end{tikzpicture}
-\caption{Multicast tree automatically found for a 8x4x1 multicore}
-\label{fig:mst_gruyere}
-\end{figure}
 

### 2013-04-29 paper.tex
Added visualization of broadcast simulation on MST tree.

@@
 
-\stefan{We have an example for this, where the MST is essentially a
-  path through the graph}
+An example is obvious in Figure~\ref{fig:mst_gruyere_operations}. The
+level of parallelism is only two. Cores 00 to 15 are dealt with in
+parallel to cores 16 to 31. Other than that, there is no further
+parallelism although it is possible to ``split up'' communication with
+every new ``round'' (i.e.\ send operations of nodes).
 
@@
 
-\stefan{We have experiments showing this}
+We show an example of bad scheduling in
+Figure~\ref{fig:mst_gruyere_operations}. When core 08 sends its six
+messages, it does so in naive order (here: in increasing node ID
+order). This is inefficient, as the latency of the broadcast is
+dominated by cores 12, 24 and 28 rather than cores 9, 10 and 11. A
+better schedule for sending messages to the children of core 8 would
+be to start with the child from which the longest path emerges.
 
@@
 \label{fig:mst_gruyere}
+\end{figure}
+
+In Figure~\ref{fig:mst_gruyere_operations}, we show the order of
+operations for sending a broadcast message along the MST given in
+Figure~\ref{fig:mst_gruyere}.
+
+\begin{figure}[htb]
+  \centering
+  \begin{tikzpicture}[scale=.35,transform shape]
+    % Insert visualization
+    \input{graphs/visu}
+  \end{tikzpicture}
+  \caption{Visualization of operations for sending a message along the
+    tree. Red boxes represent send operations, blue boxes represent
+    receive operations and arrows messages sent between cores.}
+  \label{fig:mst_gruyere_operations}
 \end{figure}

### 2013-04-29 paper.tex
Rewrote Introduction.
New version is much more concrete: automatic configuraiton of atomic broadcast for diverse and complex multicores

@@
 
-\title{Replication on multicore considering hierarchy and
-  characteristics of the network}
+\title{Adaptive broadcast tree for multicores}
 
@@
 
-There are two problems:
 \begin{enumerate}
@@
 \end{enumerate}
+We deal with the latter one for now.
 
-\paragraph{What do you want to enable?} Increase algorithm performance
-on multicores by applying distributed principles to overcome
-scalability challenges on such machines.
+% 
+Atomic broadcast is a building-block for many higher-level distributed
+algorithm such as state-machine replication. Such distributed
+algorithms are increasingly used to overcome scalability challenges on
+multicore machines. Examples are databases~\cite{Salomie2011,
+  Wiesmann2000} and operating systems~\cite{fos:osr09, tornado:osdi99,
+  barrelfish:sosp09}.
 
-\paragraph{What problem are you solving, and why is it hard?} We are
-applying distributed algorithms to multicores to enable better
-scalability. However, characteristics of a multicore a different to
-those of traditional distributed systems. Traditional algorithms need
-to be reevaluated for multicores.
+% What do you want to enable?
+We want to investigate how to achieve better performance of atomic
+broadcast across a wide range of multicore machines without manually
+tuning the implementation to concrete machines.
 
-\paragraph{What's the related work?} People apply techniques from
-distributed systems to deal with scalability challenges on multicores,
-e.g.\ databases~\cite{Salomie2011, Wiesmann2000} and operating
-systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}. But they
-don't to it properly. They do not consider machine characteristics or
-apply the wrong distributed technologies. Also, what they do is rather
-ad hoc.
+% What problem are you solving, and why is it hard?
+The problem is complexity and diversity of modern multicore
+machines. Multicores come in many flavors depending on vendor and
+generation of the machine. All of these machines have fundamentally
+different characteristics such as number of nodes, NUMA
+characteristics, interconnect topologies, propagation time on
+interconnect and use of shared caches. These characteristics are hard
+to understand, but important to consider for application performance.
 
-\paragraph{What new idea(s) will solve the problems?} Instead of just
-reusing distributed algorithms, we reevaluate them for multicores and
-investigate the impact of the multicore network model on algorithm
-performance.
+% Related work
+\stefan{Fill in related work: in a nutshell, they do tuning, but only
+  for specific machines}
 
-\paragraph{How will you go about it?} We investigate the problem for
-atomic-broadcasts since many problems in distributed systems can be
-reduced to this communication primitive. Traditional implementations
-are sending requests to all nodes in parallel to hide high propagation
-delays. %
-However, this does not work on multicores, since the propagation time
-is not dominating any longer. %
-Instead, we build a tree for communication to parallelize transmit and
-receive cost across nodes. This has been done before (BF SOSP, IBM,
-.. ), but not for the general case of multicore communication.
+% New ideas
+Instead of manually tuning algorithms to characteristics of individual
+machines, we automatically configure our atomic broadcast
+implementation based on a machine model.
+% How will you go about it?
+We will base our atomic broadcast on overlay networks, which we
+automatically configure based on the machine model. One questions is
+which information should actually be encoded in the machine model. %
+Our idea is to then explore different approaches (such as MST
+algorithms, clustering) to \emph{find good overlay networks} based on
+the network model to base the atomic broadcast on. Then, for every
+node, we need to decide which message to send first. This is a
+\emph{scheduling} problem.
 
-\paragraph{How will you know and show it works?} We will use a
-microbenchmark measuring broadcast cost and compare our tree
-implementation to the sequential case. Maybe we put some high-level
-applications on top of it.
+% How do we show it works
+We auto-configure a wide range of different multicore machines and
+show the performance of our implementation comes close to the
+performance of hand-tuned implementations for all of these machines.
 
-\paragraph{What is your hypothesis?} Performance of distributed
-algorithms can be improved if characteristics of multicores are
-considered when building and/or selecting them. %
-For the broadcast example, this means: the time complexity for a
-networks with dominating transmit and receive time will be $O(log(n))$
-instead of $O(n)$.
+% Hypothesis
+My hypothesis is that automatic tuning of atomic broadcast (and other
+distributed algorithms) to machine characteristics is worth
+doing. Obviously, we cannot achieve performance of hand-tuned
+implementations, but we can get close enough to argue that loosing a
+bit of performance to avoid tedious manual reconfiguration is worth if
+for many applications (while others, where performance \emph{really}
+matters, might still want to manually configure their stuff).
 

### 2013-04-29 paper.tex
Added some information on gruyere (which is the machine we base our sample model on)

@@
 
-\subsection{Example}
+\subsubsection{Example model approximating a 8x4x1 machine}
 
-An example of a machine model, which approximates a 2x2x1 nos box can
-be found in Figure~\ref{fig:full_nos}
+We now make up a machine model for evaluation. This model is based on
+a 8x4x1 AMD Shanghai machine. The topology of such a machine is shown
+in Figure~\ref{fig:gruyere}.
 
-\begin{figure}
-\begin{tikzpicture}[>=latex,line join=bevel]
-  \pgfsetlinewidth{1bp}
-\input{graphs/full_nos}
+Each of the eight nodes consists of four cores. We approximate the
+cost of sending messages within nodes as $1$ and across nodes as
+$10*num(hops)$.
+
+\begin{figure}[htb]
+  \centering
+  \begin{tikzpicture}[
+    xscale=.7,
+    yscale=.5,
+    every node/.style={draw,fill=red!10,minimum width=2cm,minimum height=1cm}
+    ]
+    \node (c1) at ( 0, 4) {node 0};
+    \node (c2) at ( 4, 4) {node 1};
+    \node (c3) at ( 8, 4) {node 2};
+    \node (c4) at (12, 4) {node 3};
+
+    \node (c5) at ( 0, 0) {node 4};
+    \node (c6) at ( 4, 0) {node 5};
+    \node (c7) at ( 8, 0) {node 6};
+    \node (c8) at (12, 0) {node 7};
+
+    % top horizontal
+    \draw[thick] (c1) -- (c2);
+    \draw[thick] (c2) -- (c3);
+    \draw[thick] (c3) -- (c4);
+    % bottom horizontal
+    \draw[thick] (c5) -- (c6);
+    \draw[thick] (c6) -- (c7);
+    \draw[thick] (c7) -- (c8);
+    % vertical
+    \draw[thick] (c1) -- (c5);
+    \draw[thick] (c2) -- (c6);
+    \draw[thick] (c3) -- (c7);
+    \draw[thick] (c4) -- (c8);
+    % cross
+    \draw[thick] (c3) -- (c8);
+    \draw[thick] (c4) -- (c7);
   \end{tikzpicture}
-\caption{Network model of a 2x2x1 machine}
-\label{fig:full_nos}
+  \caption{Interconnect topology of 8x4x1 AMD Shanghai machine}
+  \label{fig:gruyere}
 \end{figure}
@@
 nodes. If the send cost $t_s$ is smaller than the propagation time
-$t_p$,  $d = \lceil \frac{t_p}{t_s} \rceil$ messages can be send to
+$t_p$,  $d = \lfloor \frac{t_p}{t_s} \rfloor$ messages can be send to
 hide propagation of messages. Hence, a tree with degree $d$ should be
@@
     % Insert visualization
-    \input{graphs/visu}
+    \input{visu_only_mst}
   \end{tikzpicture}
@@
     tree. Red boxes represent send operations, blue boxes represent
-    receive operations and arrows messages sent between cores.}
+    receive operations and arrows messages sent between cores. The
+    tree has been acquired using an MST algorithm.}
   \label{fig:mst_gruyere_operations}
+\end{figure}
+
+\begin{figure}[htb]
+  \centering
+  \begin{tikzpicture}[scale=.35,transform shape]
+    % Insert visualization
+    \input{visu_mst_sort}
+  \end{tikzpicture}
+  \caption{Visualization of operations for sending a message along the
+    tree. Red boxes represent send operations, blue boxes represent
+    receive operations and arrows messages sent between cores. After
+    running the MST algorithm, we optimize scheduling in every node to
+    send messages to in decreasing order of their latency.}
+  \label{fig:mst_gruyere_operations_sorted}
 \end{figure}

### 2013-04-29 paper.tex
Explanation of aggregation

@@
 
+Aggregation is the act of collecting information from nodes (i.e.\ it
+is kind of the reverse of a broadcast). In node on the return path,
+information can be aggregated. One example is batching, where several
+pieces of information are grouped in the same message to reduce packet
+processing overhead. Another example is pre-processing of data. One
+example is pre-calculating the average value of child messages if the
+sink node is not interested in individual values.
+
 Similarly to what has been done in wireless sensor networks (where it
-also matters to reduce the number of messages, but other reasons:
+also matters to reduce the number of messages, but for other reasons:
 power consumption), we can do aggregation in nodes. In difference to

### 2013-04-29 paper.tex
Update of description for link characteristics

@@
 \item[latency] (quantitative) between each pair of nodes (per-edge)
-\item[breakdown] (quantitative) of message send cost: Ethernet has
+\item[breakdown] (quantitative) of message send cost:
   dominating propagation time vs.\ dominating send and receive time on
@@
 \item[reliability] (loss, link failure, in-order delivery, phantoms,
-  corruption, duplicated messages): Ethernet is not reliable,
+  corruption, duplicated messages): 
   multicore interconnect networks often are
-\item[Security] \& and failure detection (and the cost for that)
+%\item[Security] \& and failure detection (and the cost for that)
 \end{description}

### 2013-04-29 paper.tex
Better distinction from related work

@@
 Another tree implementation with MPI in mind was done
-in~\cite{Graham2008}. They have comparable numbers to what we found.
+in~\cite{Graham2008}. They have comparable numbers to what we found,
+but they cannot automatically tune to different machine
+characteristics. Our hypothesis is that we can do achieve higher
+average performance across a wide range of different multicore
+machines without manually adapting the implementation.
 

### 2013-04-29 paper.tex
Mentioned send and receive cost in model + table of simulation results

@@
 \subsubsection{Example model approximating a 8x4x1 machine}
+\label{sec:example_model}
 
@@
 $10*num(hops)$.
+
+Send and receive time are $10$ each, i.e.\ in the order of propagation
+over a cross-NUMA link.
 
@@
 
+\subsection{Simulation in model}
+
+This section shows results for a simulation based on the model
+introduced in Section~\ref{sec:example_model}
+
+The time given is a fictional time unit at this point.
+
+\begin{table}[htb]
+  \centering
+  \begin{tabular}{llll}
+    \toprule
+    overlay & scheduling & time & factor \\
+    \midrule
+    MST & naive         & 241 & 1.00 \\
+    MST & longest first & 151 & 0.63 \\
+    \bottomrule
+  \end{tabular}
+  \caption{Simulation results for simplified machine model}
+  \label{tab:sim_results}
+\end{table}
+
+\subsection{Real hardware}
+
 \paragraph{Current numbers} Current numbers are listed in

### 2013-04-29 paper.tex
Ideas on Octopus

@@
 
-\begin{enumerate}
-\item Performance of distributed algorithms on multicores. Programmers
-  don't get it right due to different complexity measures. We deal
-  with this by improving these algorithms. This will lead to higher
-  performance of existing algorithms.
-\item Diversity of hardware. Hand-tuning algorithms is tedious. Need
-  to do this automatically. To evaluate this, we compare the average
-  performance of our automatic configuration on a wide range of
-  multicores with performance of a single hand-tuned implementation.
-\end{enumerate}
-We deal with the latter one for now.
-
-% 
 Atomic broadcast is a building-block for many higher-level distributed
@@
 to understand, but important to consider for application performance.
-
-% Related work
-\stefan{Fill in related work: in a nutshell, they do tuning, but only
-  for specific machines}
 
@@
 A multicore aware broadcast has been implemented in~\cite{Tu2008}. It
-takes the cache architecture of the machine into consideration for
-building the broadcast. It is however for larger messages (starting at
-4K) and it does not seem to be performing very well (numbers are given
-in microseconds -6). 4K messages are 52 microseconds, which is 150000
-cycles. For synchronization primitives, a cache line is sufficient.
+takes the cache architecture of the machine (and only one particular?)
+into consideration for building the broadcast. It is however for
+larger messages (starting at 4K) and it does not seem to be performing
+very well (numbers are given in microseconds -6). 4K messages are 52
+microseconds, which is 150000 cycles. For synchronization primitives,
+a cache line is sufficient.
 
@@
 
-\subsection{Aggregation}
+\subsection{Aggregation for convergecast}
 
-Aggregation is the act of collecting information from nodes (i.e.\ it
-is kind of the reverse of a broadcast). In node on the return path,
+Convergecast is a way of collecting information from nodes (i.e.\ it
+is kind of the reverse of a broadcast). On the return path,
 information can be aggregated. One example is batching, where several
 pieces of information are grouped in the same message to reduce packet
-processing overhead. Another example is pre-processing of data. One
-example is pre-calculating the average value of child messages if the
-sink node is not interested in individual values.
+processing overhead. Another example is aggregation, i.e.\
+pre-processing of data. One example is pre-calculating the average
+value of child messages if the sink node is not interested in
+individual values.
 
@@
 the number of messages at the price of higher complexity does not make
-sense there.
+sense in classical systems.
 
@@
   \begin{itemize}
-  \item octopus
-    \begin{itemize}
-    \item higher level application?
-    \end{itemize}
   \item capability system? \stefan{Ask Simon how expensive revocation
@@
 
+\subsection{Octopus}
+
+One idea is to make Octopus a decentralized application. Octopus is
+a coordination service implemented for the Barrelfish Multikernel
+operating system. It is, however, centralized.
+
+The idea is to extend Octopus such that it can be replicated within a
+multicore machine. This will retain scalability for future manycore
+machines and potentially outperform a centralized version of Octopus
+especially in contented systems.
+
+One foundation block of Octopus is a key-value store. Since there is
+only one copy, the data in there is always consistent. If replicated,
+some sort of consistency guarantee would have to be implemented. One
+example is \emph{linearizability}, i.e.\ ``accesses occur one at a time
+in, some sequential order that is consistent with the order of
+invocations and responses''~\cite{lynch}.
+
+The question is whether a key-value store as a backend for
+synchronization primitives even makes sense.
+
+One concrete idea is to have one copy of the Octopus data-store
+replicated on every NUMA node. One core on every node acts as
+\emph{coordinator}, we call the other nodes \emph{slaves}.
+Coordinators communicate on a ring. Communication on a local NUMA node
+can be realized using read-only shared memory for read access. Write
+access needs to be globally ordered and hence communication with other
+replicas is required.
+
+The idea of having a ring is somewhat related to SharedDB. It
+optimizes for throughput, not latency!
+
+\begin{description}
+\item[Updates on global state] Slaves direct their updates to the
+  local coordinator. Coordinators send the update request $r$ along
+  the ring and wait for them to be send back. While passing on
+  requests, coordinators can set a flag to indicate conflicts. A
+  conflict is another colliding request $r_o$ that is already in
+  flight. I think we will have to send activity vectors along with
+  this information! Otherwise, the coordinators requesting $r$ and
+  $r_o$ will both prevent the other thing from happening and none of
+  them will be applied! Maybe we need a two-phase commit.
+\item[Barriers] The coordinator knows how many of its slaves need to
+  enter the barrier. It can then just aggregate local barrier\_enters
+  calls and only communicate this information to the others once all
+  children are ready. 
+\end{description}
+
+\subsubsection{Load balancing}
+
+We could build several rings, that do not always include all
+coordinators and work with read- and write-sets. We can select these
+rings such that they nicely integrate with the physical topology. They
+can also have different sizes (e.g.\ a smaller one for read
+operations and larger ones for writes).
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-04-30 paper.tex
After meeting Kornilios

@@
 
-% ==================================================
 \setcounter{section}{0} % Start sections with 1, not 0
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Related work}
@@
 
+Alistarh\etal~\cite{Alistarh2012} show composition of shared-memory
+algorithms that perform efficiently under different conditions at
+negligible overhead. A similar approach can potentially be applied to
+deal with diversity of multicore machines. However, we would have
+to extend it to support both shared-memory and message-passing
+implementations.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Node characteristics} 
+\label{sec:model_nodes}
 
@@
   dequeuing, unmarshalling and demultiplexing a channel.
-\item[failure] Can nodes fail? If so, how? (Byzantine, \ldots)
+\item[failure] Can nodes fail? If so, how? (Byzantine, crash)
 \end{description}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Link characteristics} 
+\label{sec:model_links}
 
@@
   multicore interconnect networks often are
-%\item[Security] \& and failure detection (and the cost for that)
 \end{description}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Hierarchical model}
+\label{sec:model_hierarchy}
+
+Multicore machines are hierarchical. Processor cores are grouped in
+NUMA nodes with shared caches. These NUMA nodes are then connected to
+each by increasingly complex interconnect networks.
+
+We encode NUMA node affinity in our model. This allows to break down
+programming of a multicore machine into two distinct instances. We
+solve one instance of the problem between NUMA nodes, and then, in a
+second step, within each NUMA node. These two steps can be executed
+independently and different algorithms can be used in either case.
+
+If cores on the same NUMA node share a cache, it makes sense to
+leverage this hardware feature to implement shared-memory algorithms
+on top of it. %
+Communication across NUMA nodes is realized sending messages across
+the packet-based interconnect network. Using message-passing based
+implementations is the natural choice. %
+Shared memory algorithms and message-passing based algorithms can be
+composed together to program hierarchical machines similarly to what
+was previously shown for combinations of shared-memory
+algorithms~\cite{Alistarh2012}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Acquiring the model}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Example: Atomic broadcast
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We build our atomic broadcast based on an overlay network connecting
-all nodes of a given multicore machine.
+all nodes of a given multicore machine. First, we discuss what
+kind of overlay networks make sense on multicores.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Tree}
+\subsection{Tree overlay}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%-------------------------------------------------
 \subsubsection{Divide and conquer}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%-------------------------------------------------
 \subsubsection{Clustering}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%-------------------------------------------------
 \subsubsection{Minimum-Spanning Tree}
@@
 ideal to minimize latency, but only for an acknowledged protocol.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Rings}
+
+\stefan{Just a random collection of ideas}
+
+%-------------------------------------------------
+\subsubsection{Load balancing in a tree}
+
+We could build several rings, that do not always include all
+coordinators and work with read- and write-sets. We can select these
+rings such that they nicely integrate with the physical topology. They
+can also have different sizes (e.g.\ a smaller one for read operations
+and larger ones for writes).
 
@@
 
+\stefan{This section feels out of place. Rewrite it and put it
+  somewhere else}
+
 \subsection{Aggregation for convergecast}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Experimental results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Evaluation}
 
-\subsection{Simulation in model}
+\stefan{Compare to pure shared-memory implementations, otherwise
+  reviewers might argue that there is no need for distributed
+  algorithms.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Atomic broadcast}
+
+%-------------------------------------------------
+\subsubsection{Simulation}
 
@@
 
+%-------------------------------------------------
 \subsection{Real hardware}
 
-\paragraph{Current numbers} Current numbers are listed in
-Table~\ref{tab:bc_measurements}.
+Current numbers are listed in Table~\ref{tab:bc_measurements}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Future work}
@@
 \begin{itemize}
-\item Arguing that group communication/atomic broadcast and showing
-  that we can do it well might be enough (appeal to atomic broadcasts
-  as the foundation for other distributed algorithms, and the MPI
-  primitives, that can/need to be mapped to group-communication (have
-  a list of them) 
+\item Arguing that group communication/atomic broadcast is important
+  and showing that we can do it well might be enough (appeal to atomic
+  broadcasts as the foundation for other distributed algorithms, and
+  the MPI primitives, that can/need to be mapped to
+  group-communication (have a list of them)
 \item Need higher-level applications, such as:
@@
   \end{itemize}
-\item Machine model for topology aware tree
-  \begin{itemize}
-  \item Talked to Pravin about this a bit
-  \end{itemize}
 \item MPI collectives (as in~\cite{Tu2008})
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Octopus}
 
-One idea is to make Octopus a decentralized application. Octopus is
-a coordination service implemented for the Barrelfish Multikernel
-operating system. It is, however, centralized.
+Octopus is a coordination service implementation for the Barrelfish
+Multikernel operating system. It is, however, centralized. The idea is
+to make Octopus a decentralized application.
 
-The idea is to extend Octopus such that it can be replicated within a
+For that, we extend Octopus such that it can be replicated within a
 multicore machine. This will retain scalability for future manycore
@@
 
+%--------------------------------------------------
+\subsubsection{Key-value store}
+
 The question is whether a key-value store as a backend for
-synchronization primitives even makes sense.
+synchronization primitives even makes sense. As we want to show
+efficiency, we probably rather want to implement new synchronization
+algorithms from scratch.
 
@@
 
-\subsubsection{Load balancing}
-
-We could build several rings, that do not always include all
-coordinators and work with read- and write-sets. We can select these
-rings such that they nicely integrate with the physical topology. They
-can also have different sizes (e.g.\ a smaller one for read
-operations and larger ones for writes).
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-04-30 paper.tex
Some more restructuring

@@
 }
+
+\newcommand{\etal}{{\it et al.}\xspace}
 
@@
   cluster of a node.
-\item[$t_{send}$] Time required to send a message, i.e.\ marshalling
+\item[send time $t_{send}$] Time required to send a message, i.e.\ marshalling
   and queuing the message
-\item[$t_{recv}$] Time required to receive a message, i.e.\
+\item[receive $t_{recv}$] Time required to receive a message, i.e.\
   dequeuing, unmarshalling and demultiplexing a channel.
@@
 % Model given
-We assume that the model is given (if it is not, we can do online
-measurements and read some specs to find the relevant information). We
-just define one ourselves for now or build one manually for a
-particular machine. In a real-world scenario, this does not work. The
-model needs to be created automatically for a particular machine (due
-to the diversity of machines, and also the pace at which hardware changes)
-
-\subsubsection{Example model approximating a 8x4x1 machine}
-\label{sec:example_model}
+We assume that the model is given. We just define one ourselves for
+now or build one manually for a particular machine. In a real-world
+scenario, this does not work. The model needs to be created
+automatically for a particular machine (due to the diversity of
+machines, and also the pace at which hardware changes)
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Atomic Broadcast}
+\section{Atomic Broadcast for Multicores}
 
-We build our atomic broadcast based on an overlay network connecting
-all nodes of a given multicore machine. First, we discuss what
-kind of overlay networks make sense on multicores.
+For a specific model, we now need to find ``the right'' implementation
+of algorithms to program it. We build our atomic broadcast based on a
+subset of links offered by the model such that all nodes of a given
+multicore machine can be reached. Atomic broadcast guarantees that 1)
+if one node receives a message, all other nodes receive it as well,
+and 2) that all nodes see the message in the same order.
 
-As a first step, we evaluate tree based overlay networks. Other
+First, we discuss what kind of topologies we use to communicate
+between nodes. We evaluate tree based implementations. Other
 potentially interesting topologies are rings.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Tree overlay}
+\subsection{Tree Topology}
 
-We now look at tree based atomic broadcast implementations.
-
-The first challenge is to find efficient spanning trees for arbitrary
-machines. These machines are represented by a model, which we
-described earlier.
-
-%-------------------------------------------------
-\subsubsection{Divide and conquer}
-
-We divide the space into clusters. In every round, we further split up
-all cluster into smaller clusters and connect them with the minimal
-link.
-
-We find this link by searching for links that have start and
-end node in different regions of the most recent split. Out of these
-links, we pick the cheapest ones. We ignore links whose start or end
-node have a too high degree in the spanning tree already.
-
-Assuming that the choice of node IDs represents the topology to some
-extend, splitting them up into distinct clusters avoids contention, as
-two separate sub-trees are processed in different areas of the
-interconnect network.
-
-%-------------------------------------------------
-\subsubsection{Clustering}
-
-Another idea is to employ clustering. One example is to base this on
-NUMA domains such that every NUMA domain corresponds to one cluster.
+We now look at tree-based atomic broadcast implementations. The first
+challenge is to find efficient spanning trees for arbitrary
+machines. We now discuss different strategies to select trees based on
+the model representing the machine.
 
@@
 \subsubsection{Minimum-Spanning Tree}
+\label{sec:mst_tree}
 
@@
 hide propagation of messages. Hence, a tree with degree $d$ should be
-ideal to minimize latency, but only for an acknowledged protocol.
+ideal to minimize latency. For multicore interconnect networks,
+however, we expect $d<1$. Thus, we do not look into this in detail
+right now.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Rings}
+Reducing the degree of nodes also helps for the select operation. It
+reduces the number of memory locations to poll, and therefore the
+latency of detecting messages.
 
-\stefan{Just a random collection of ideas}
+We show an example broadcast tree for a 8x4x1 AMD Barcelona machine
+(gruyere) in Figure~\ref{fig:qrm_tree_gruyere}.
+
+\begin{figure}
+  \input{qrm_tree_gruyere}
+  \caption{Tree of cores for broadcast on gruyere}
+  \label{fig:qrm_tree_gruyere}
+\end{figure}
 
 %-------------------------------------------------
-\subsubsection{Load balancing in a tree}
+\subsubsection{Clustering}
 
-We could build several rings, that do not always include all
-coordinators and work with read- and write-sets. We can select these
-rings such that they nicely integrate with the physical topology. They
-can also have different sizes (e.g.\ a smaller one for read operations
-and larger ones for writes).
+We discussed earlier in Section~\ref{sec:model_hierarchy} that
+multicore machines are hierarchical.%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scheduling}
+We divide the space into clusters. In every round, we further split up
+all cluster into smaller clusters and connect them with the minimal
+link.
 
-% Tree -> scheduling
-Assuming the tree (or some other kind of overlay network), there is a
-\emph{scheduling problems} for the order in which to send messages to
-children. The intuition is to send on long-delay links first to hide
-the more expensive latencies, as this link is dominating total send
-cost.
+We find this link by searching for links that have start and
+end node in different regions of the most recent split. Out of these
+links, we pick the cheapest ones. We ignore links whose start or end
+node have a too high degree in the spanning tree already.
 
-We show an example of bad scheduling in
-Figure~\ref{fig:mst_gruyere_operations}. When core 08 sends its six
-messages, it does so in naive order (here: in increasing node ID
-order). This is inefficient, as the latency of the broadcast is
-dominated by cores 12, 24 and 28 rather than cores 9, 10 and 11. A
-better schedule for sending messages to the children of core 8 would
-be to start with the child from which the longest path emerges.
+Assuming that the choice of node IDs represents the topology to some
+extend, splitting them up into distinct clusters avoids contention, as
+two separate sub-trees are processed in different areas of the
+interconnect network.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Example tree}
+Another idea is to employ clustering on NUMA domains such that every
+NUMA domain corresponds to one cluster.
+
+%-------------------------------------------------
+\subsubsection{Example tree}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Broadcast protocol}
+\subsection{Scheduling}
+
+% Tree -> scheduling
+Assuming the tree (or some other kind of overlay network), there is a
+\emph{scheduling problems} for the order in which to send messages to
+children. The intuition is to send on long-delay links first to hide
+the more expensive latencies, as this link is dominating total send
+cost.
+
+We show an example of bad scheduling in
+Figure~\ref{fig:mst_gruyere_operations}. When core 08 sends its six
+messages, it does so in naive order (here: in increasing node ID
+order). This is inefficient, as the latency of the broadcast is
+dominated by cores 12, 24 and 28 rather than cores 9, 10 and 11. A
+better schedule for sending messages to the children of core 8 would
+be to start with the child from which the longest path emerges.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Implementation}
 
 % Our implementation
-Assuming the tree, we now build an atomic broadcast for multicore
+Assuming the tree, we now implement an atomic broadcast for multicore
 machines. Our implementation is based on the Barrelfish UMP
 interconnect driver. It provides reliable channels with in-order
-delivery. Communication starts at the root node, which acts as a
+delivery. Flow control is build in for reliability. Communication
+starts at the root node, which acts as a
 sequentializer. See~\ref{algo:ab} for details.
@@
 \end{algorithm}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Barrelfish implementation}
+\subsection{Issues with the Barrelfish implementation}
 
@@
 practical problems, which we will discuss briefly in this section.
-
 We kick-start our protocol connecting every process with all other
 processes to get a fully-meshed network of channels.
-
 We use a round-based algorithm to open channels. Then, every node
@@
 algorithm in Algorithm~\ref{algo:ab_bind}.
-
 This is required for Barrelfish UMP communication channels since on
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Mechanisms}
-
-\stefan{This section feels out of place. Rewrite it and put it
-  somewhere else}
-
-\subsection{Aggregation for convergecast}
-
-Convergecast is a way of collecting information from nodes (i.e.\ it
-is kind of the reverse of a broadcast). On the return path,
-information can be aggregated. One example is batching, where several
-pieces of information are grouped in the same message to reduce packet
-processing overhead. Another example is aggregation, i.e.\
-pre-processing of data. One example is pre-calculating the average
-value of child messages if the sink node is not interested in
-individual values.
-
-Similarly to what has been done in wireless sensor networks (where it
-also matters to reduce the number of messages, but for other reasons:
-power consumption), we can do aggregation in nodes. In difference to
-traditional distributed systems, this works, because it is easy to
-deploy custom software on every node in the network. Classical
-distributed systems do not typically allow this. Furthermore, reducing
-the number of messages at the price of higher complexity does not make
-sense in classical systems.
-
-Examples for aggregation: number of nodes agreeing to something, find
-capabilities (concatenate core ids).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Example}
-
-We show an example broadcast tree for a 8x4x1 AMD Barcelona machine
-(gruyere) in Figure~\ref{fig:qrm_tree_gruyere}.
-
-\begin{figure}
-  \input{qrm_tree_gruyere}
-  \caption{Tree of cores for broadcast on gruyere}
-  \label{fig:qrm_tree_gruyere}
-\end{figure}
-
-\paragraph{Observations} Reducing the number of children also helps in
-select. It reduces the number of ``channels'' to poll, and therefore
-the latency of detecting messages. Instead of
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 This section shows results for a simulation based on the model
-introduced in Section~\ref{sec:example_model}
-
-The time given is a fictional time unit at this point.
+introduced in Section~\ref{sec:mst_tree}. The time given is a
+fictional time unit at this point.
 
@@
     \toprule
-    overlay & scheduling & time & factor \\
+    topology & scheduling & time & factor \\
     \midrule
@@
 %-------------------------------------------------
-\subsection{Real hardware}
+\subsubsection{Real hardware}
 
@@
 
-\paragraph{Minimal cost of sending a tree-broadcast} %
 Plot~\ref{pgfplot:201303141819} shows the cost of flooding a sub-tree
@@
 nodes reached by the broadcast (as expected). Every level in the tree
-adds an additional 3500 cycles to the tree. Node 0 takes significantly
-longer. I don't know yet why that is.
+adds an additional 2500 to 3000 cycles to the tree. Node 0 takes
+significantly longer. I don't know yet why that is.
 
@@
 
-\input{gruyere_bc_seq}
-
-\begin{itemize}
-\item Move server to a core != 0
-\item Use low-level UMP stuff
-{
-\renewcommand{\labelitemi}{\checkmark}
-\item disable yielding
-}
-\item run several request in parallel, give them IDs, can use in the
-  measurement struct. Good for everything having transactions (DB,
-  transactional memory, consistency in replication systems)
-\end{itemize}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \item MPI collectives (as in~\cite{Tu2008})
+\item Try other topologies (Frans Kaashoek), e.g.\ rings
+\item \emph{Load balancing in a tree} We could build several rings,
+  that do not always include all coordinators and work with read- and
+  write-sets. We can select these rings such that they nicely
+  integrate with the physical topology. They can also have different
+  sizes (e.g.\ a smaller one for read operations and larger ones for
+  writes).
+\item \emph{Aggregation for convergecast} %
+  Convergecast is a way of collecting information from nodes (i.e.\ it
+  is kind of the reverse of a broadcast). On the return path,
+  information can be aggregated. One example is batching, where several
+  pieces of information are grouped in the same message to reduce packet
+  processing overhead. Another example is aggregation, i.e.\
+  pre-processing of data. One example is pre-calculating the average
+  value of child messages if the sink node is not interested in
+  individual values. %
+  Similarly to what has been done in wireless sensor networks (where it
+  also matters to reduce the number of messages, but for other reasons:
+  power consumption), we can do aggregation in nodes. In difference to
+  traditional distributed systems, this works, because it is easy to
+  deploy custom software on every node in the network. Classical
+  distributed systems do not typically allow this. Furthermore, reducing
+  the number of messages at the price of higher complexity does not make
+  sense in classical systems. %
+  Examples for aggregation: number of nodes agreeing to something, find
+  capabilities (concatenate core ids). 
 \end{itemize}
@@
 Octopus is a coordination service implementation for the Barrelfish
-Multikernel operating system. It is, however, centralized. The idea is
-to make Octopus a decentralized application.
+Multikernel operating system based on a key-value store
+data-backend. It is, however, centralized. The idea is to make Octopus
+a decentralized application.
 
@@
 especially in contented systems.
+
+%--------------------------------------------------
+\subsubsection{Key-value store}
 
@@
 invocations and responses''~\cite{lynch}.
-
-%--------------------------------------------------
-\subsubsection{Key-value store}
-
-The question is whether a key-value store as a backend for
-synchronization primitives even makes sense. As we want to show
-efficiency, we probably rather want to implement new synchronization
-algorithms from scratch.
 
@@
 
+Slaves direct their updates to the local coordinator. Coordinators
+send the update request $r$ along the ring and wait for them to be
+send back. While passing on requests, coordinators can set a flag to
+indicate conflicts. A conflict is another colliding request $r_o$ that
+is already in flight. I think we will have to send activity vectors
+along with this information! Otherwise, the coordinators requesting
+$r$ and $r_o$ will both prevent the other thing from happening and
+none of them will be applied! Maybe we need a two-phase commit.
+
 The idea of having a ring is somewhat related to SharedDB. It
@@
 
-\begin{description}
-\item[Updates on global state] Slaves direct their updates to the
-  local coordinator. Coordinators send the update request $r$ along
-  the ring and wait for them to be send back. While passing on
-  requests, coordinators can set a flag to indicate conflicts. A
-  conflict is another colliding request $r_o$ that is already in
-  flight. I think we will have to send activity vectors along with
-  this information! Otherwise, the coordinators requesting $r$ and
-  $r_o$ will both prevent the other thing from happening and none of
-  them will be applied! Maybe we need a two-phase commit.
-\item[Barriers] The coordinator knows how many of its slaves need to
-  enter the barrier. It can then just aggregate local barrier\_enters
-  calls and only communicate this information to the others once all
-  children are ready. 
-\end{description}
+%-------------------------------------------------
+\subsubsection{Synchronization}
+
+It is doubtful that a key-value store as a backend for synchronization
+primitives makes sense. As we want to show efficiency, we probably
+rather want to implement new synchronization algorithms from scratch.
+
+The coordinator knows how many of its slaves need to enter the
+barrier. It can then just aggregate local barrier\_enters calls and
+only communicate this information to the others once all children are
+ready. Local communication can be shared-memory based, while global
+communication should probably rather be message-passing based.
+
+We will have to compare the performance of such an implementation with
+a purely shared-memory based implementation like pthreads and
+something entirely message-passing based like MPI versions.
 

### 2013-05-02 paper.tex
Write-up of link weight scheduling and some restructuring

@@
 \newcommand{\etal}{{\it et al.}\xspace}
+\newcommand{\naive}{na\"{\i}ve\xspace}
+\newcommand{\Naive}{Na\"{\i}ve\xspace}
+\newcommand{\textc}[1]{{\color{gray} {\footnotesize #1}}}
 
@@
 NUMA nodes with shared caches. These NUMA nodes are then connected to
-each by increasingly complex interconnect networks.
+each other by increasingly complex interconnect networks.
 
@@
 second step, within each NUMA node. These two steps can be executed
-independently and different algorithms can be used in either case.
+independently and different algorithms can be used in both case.
 
@@
 composed together to program hierarchical machines similarly to what
-was previously shown for combinations of shared-memory
+was previously shown for composing of shared-memory
 algorithms~\cite{Alistarh2012}.
@@
 %-------------------------------------------------
+\subsubsection{Binary Tree}
+
+A very \naive strategy to build a tree from machine models is the use
+of a binary tree with root in core 0. Every node $n$ has two children
+$2(n+1)-1$ and $2(n+1)$.
+
+The benefit of such a tree is that the time complexity is guaranteed
+to be $O(\log{n})$. The downside is that it is not considering the
+machine topology. Unnecessary communication across NUMA nodes might be
+introduced.
+
+We show an example for such a tree for a 8x4x1 AMD Barcelona machine
+(gruyere) in Figure~\ref{fig:qrm_tree_gruyere}.
+
+\begin{figure}
+  \input{qrm_tree_gruyere}
+  \caption{\Naive binary tree of cores for broadcast on gruyere}
+  \label{fig:qrm_tree_gruyere}
+\end{figure}
+
+%-------------------------------------------------
 \subsubsection{Minimum-Spanning Tree}
@@
 
-We show an example broadcast tree for a 8x4x1 AMD Barcelona machine
-(gruyere) in Figure~\ref{fig:qrm_tree_gruyere}.
+We show the multicast tree automatically generated from a fully meshed
+machine model by applying a minimum spanning tree algorithm in
+Figure~\ref{fig:mst_gruyere}.
 
 \begin{figure}
-  \input{qrm_tree_gruyere}
-  \caption{Tree of cores for broadcast on gruyere}
-  \label{fig:qrm_tree_gruyere}
+\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
+  \pgfsetlinewidth{1bp}
+\input{graphs/mst_gruyere}
+\end{tikzpicture}
+\caption{Multicast tree automatically found for a 8x4x1 multicore}
+\label{fig:mst_gruyere}
 \end{figure}
@@
 
-%-------------------------------------------------
-\subsubsection{Example tree}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Scheduling}
 
-We show the multicast tree automatically generated from a fully meshed
-machine model of a 8x4x1 sample multicore (gruyere) in
-Figure~\ref{fig:mst_gruyere}. We get this tree by applying a minimum
-spanning tree algorithm on a multicore model encoding link latencies.
+% Tree -> scheduling
+Assuming the tree (or some other kind of overlay network), there is a
+\emph{scheduling problems} for the order in which to send messages to
+children. The intuition is to send on long-delay links first to hide
+the more expensive latencies, as this link is dominating total send
+cost.
 
-\begin{figure}
-\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
-  \pgfsetlinewidth{1bp}
-\input{graphs/mst_gruyere}
-\end{tikzpicture}
-\caption{Multicast tree automatically found for a 8x4x1 multicore}
-\label{fig:mst_gruyere}
-\end{figure}
-
-In Figure~\ref{fig:mst_gruyere_operations}, we show the order of
-operations for sending a broadcast message along the MST given in
-Figure~\ref{fig:mst_gruyere}.
+In Figure~\ref{fig:mst_gruyere_operations}, we visualize sending of a
+broadcast message in \naive order. We use the MST given in
+Figure~\ref{fig:mst_gruyere}.  When core 08 sends its six messages, it
+does so in random order (here: in increasing node ID order). This is
+inefficient, as the latency of the broadcast is dominated by cores 12,
+24 and 28 rather than cores 9, 10 and 11. A better schedule for
+sending messages to the children of core 8 would be to start with the
+child from which the longest path emerges.
 
@@
 \end{figure}
+
+In Figure~\ref{fig:mst_gruyere_operations_sorted} we schedule sending
+of messages based on link cost. We sort the outgoing edges by their
+weights and send on the most expensive links first. See
+Algorithm~\ref{algo:scheduling_link_weight}
+
+\begin{algorithm}[htb]
+\SetCommentSty{textc}
+\SetKwFunction{weight}{edge\_weight}%
+\SetKwFunction{sort}{sort\_by\_edge\_weight}%
+\SetKwFunction{icsend}{send}%
+  %
+  \KwData{Node $n$ sending messages, \\ %
+    broadcast tree as graph $(V, E)$, \\ %
+    weight function \weight{$E$}
+    %
+  }
+  % 
+  \BlankLine
+  $nb \leftarrow \{ c: \exists (self, c) \in E \}$\tcp*{Get children}
+  $nb \leftarrow $ \sort{$nb$, \weight{}}\tcp*{Sort by edge weight}
+  \For(\tcp*{For all children}){$c \leftarrow nb$}{
+    \icsend{$c$}
+  }
+  % 
+  \caption{Scheduling in order of outgoing link weight}
+  \label{algo:scheduling_link_weight}
+\end{algorithm}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scheduling}
-
-% Tree -> scheduling
-Assuming the tree (or some other kind of overlay network), there is a
-\emph{scheduling problems} for the order in which to send messages to
-children. The intuition is to send on long-delay links first to hide
-the more expensive latencies, as this link is dominating total send
-cost.
-
-We show an example of bad scheduling in
-Figure~\ref{fig:mst_gruyere_operations}. When core 08 sends its six
-messages, it does so in naive order (here: in increasing node ID
-order). This is inefficient, as the latency of the broadcast is
-dominated by cores 12, 24 and 28 rather than cores 9, 10 and 11. A
-better schedule for sending messages to the children of core 8 would
-be to start with the child from which the longest path emerges.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Implementation}
@@
 
-\newcommand{\textc}[1]{{\color{gray} {\footnotesize #1}}}
-\begin{algorithm}[H]
+\begin{algorithm}[htb]
 \SetCommentSty{textc}
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[htb]
   %

### 2013-05-02 paper.tex
Moved the barrier ideas to a different section and added some more content

@@
 
-The coordinator knows how many of its slaves need to enter the
-barrier. It can then just aggregate local barrier\_enters calls and
-only communicate this information to the others once all children are
-ready. Local communication can be shared-memory based, while global
-communication should probably rather be message-passing based.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Barriers}
+
+The idea is to explore barrier implementations. The idea is to
+leverage information about the NUMA topology for better performance of
+barrier intensive workloads. Every NUMA node has a coordinator node,
+that knows how many threads on that node want to enter the
+barrier. There is only local communication (possibly using a
+share-memory implementation to exploit the shared cache) until the
+point where all NUMA local threads did enter the barrier.  Then there
+is ``global'' communication with other coordinators on other nodes
+using a message-passing based algorithm. We believe that this scales
+better than pure shared-memory implementations due to less
+interconnect contention.
 

### 2013-05-02 paper.tex
Clean-up of node and link characteristics

@@
 Every node (i.e.\ core) in the system has characteristics associated
-with it:
+with it.
 
@@
   cluster of a node.
-\item[send time $t_{send}$] Time required to send a message, i.e.\ marshalling
-  and queuing the message
-\item[receive $t_{recv}$] Time required to receive a message, i.e.\
-  dequeuing, unmarshalling and demultiplexing a channel.
 \item[failure] Can nodes fail? If so, how? (Byzantine, crash)
 \end{description}
+
+These are currently not encoded in the model. The send and receive
+cost are in part node specific. The faster a core is, the faster it
+can to the multiplexing and marshalling. However, they are also link
+dependent, so we view them as link characteristics.
 
@@
 \begin{description}
-\item[latency] (quantitative) between each pair of nodes (per-edge)
 \item[breakdown] (quantitative) of message send cost:
   dominating propagation time vs.\ dominating send and receive time on
-  multicores (per-node)
+  multicores (per-node). Our model is currently limited to only the
+  breakdown of the cost for sending messages.
+\item[latency] (quantitative) between each pair of nodes (per-edge)
 \item[bounded delivery]
@@
 It is doubtful that a key-value store as a backend for synchronization
-primitives makes sense. As we want to show efficiency, we probably
-rather want to implement new synchronization algorithms from scratch.
+primitives as we want to show efficiency rather than ease of use and
+flexibility. We probably rather want to implement new synchronization
+algorithms from scratch. See Section~\ref{barriers} for ideas.
 
@@
 \subsection{Barriers}
+\label{barriers}
 

### 2013-05-02 paper.tex
Added new numbers

@@
 inefficient, as the latency of the broadcast is dominated by cores 12,
-24 and 28 rather than cores 9, 10 and 11. A better schedule for
-sending messages to the children of core 8 would be to start with the
-child from which the longest path emerges.
+24 and 28 rather than cores 9, 10 and 11.
 
@@
 \end{figure}
+
+A better schedule for sending messages to the children of core 8 would
+be to start with the child from which the longest path emerges.
+
+\stefan{TODO: write down algorithm}
 
@@
     MST & naive                     & 241 & 1.00 \\
-    MST & longest first & 151 & 0.63 \\
+    MST & highest link weight first & 151 & 0.63 \\
+    MST & longest path first        & 151 & 0.63 \\
     \bottomrule
@@
 \end{table}
+
+Scheduling based on the longest path does not make a difference for
+the current MST, but will be better in many cases. \stefan{We need to
+  find a model where this is actually true. But we also need to
+  evaluate if the increase in complexity is worth it}
 

### 2013-05-06 paper.tex
Binary tree for outer network

@@
 \begin{description}
+\item[NUMA affinity] A list of cores on the same NUMA node
 \item[synchrony] Parts of a multicore machine are synchronous. Hence,
@@
 dependent, so we view them as link characteristics.
+
+%-------------------------------------------------
+\subsection{NUMA characteristics}
+\label{sec:model_numa_nodes}
+
+The cost of sending a message in a multicore machines does not so much
+depend on the distance on the interconnect networks as on the number
+of hops on such a path. Propagation on the wire is essentially for
+free due to short distances between cores.
+
+On a multi-hop path, however, packages traversing the interconnect
+need to be buffered. This is expensive. Depending on the machine,
+some routing is executed on every intermediate route, which increases
+the latency further.
+
+\begin{description}
+\item[hop count] Number of hops to every other NUMA node.
+\item[hop count histogram] For every NUMA node, we want to know how
+  many other NUMA nodes can be reached with $n$ hops. This tells us
+  something about how well such nodes are connected to other NUMA
+  nodes. The intuition is that it makes sense to send a message to a
+  well connected NUMA node early in time, to ``spread'' out a message
+  as quickly as possible.
+\end{description}
 
@@
   multicores (per-node). Our model is currently limited to only the
-  breakdown of the cost for sending messages.
-\item[latency] (quantitative) between each pair of nodes (per-edge)
+  breakdown of the cost for sending messages. Maybe we do not strictly
+  need to know about propagation time, as it is negligible independent
+  of were messages are sent. Relevant seems to be the number of hops
+  rather than the latency expressed in a concrete time.
 \item[bounded delivery]

### 2013-05-06 graphs/algorithms.py

@@ -1,0 +1,30 @@
+# Copyright (c) 2007, 2008, 2009, 2010, 2011, 2012, 2013 ETH Zurich.
+
+from pygraph.classes.graph import graph
+import Queue
+
+def binary_tree(model, out_degree=2):
+    """
+    Construct a binary tree for the given g
+    """
+    assert(len(model.nodes())>0) # graph has nodes
+
+    g = graph()
+    nodes = model.nodes()
+    num = len(nodes)
+
+    for n in nodes:
+        g.add_node(n)
+    
+    for i in range(num):
+        p = 2*(i+1)-1
+        pp = 2*(i+1)
+        if p < num:
+            g.add_edge((nodes[i],  nodes[p]))
+            if pp < num:
+                g.add_edge((nodes[i], nodes[pp]))
+
+    return g
+            
+        
+    

### 2013-05-06 graphs/cluster.py

@@ -1,0 +1,88 @@
+# Copyright (c) 2007, 2008, 2009, 2010, 2011, 2012, 2013 ETH Zurich.
+
+# Import graphviz
+import sys
+sys.path.append('..')
+sys.path.append('/usr/lib/graphviz/python/')
+sys.path.append('/usr/lib64/graphviz/python/')
+import gv
+
+# Import pygraph
+from pygraph.classes.graph import graph
+from pygraph.classes.digraph import digraph
+from pygraph.algorithms.searching import breadth_first_search
+from pygraph.readwrite.dot import write
+from pygraph.algorithms.minmax import shortest_path
+from pygraph.algorithms.minmax import minimal_spanning_tree
+
+# Import own code
+import evaluate
+import model
+import helpers
+import algorithms
+
+class Cluster:
+    
+    def __init__(self, mod):
+        """
+        Initialize the clustering algorithm
+        """
+        assert isinstance(mod, model.Model)
+        self.mod = mod
+        self.coordinators=[]
+        for core in range(len(mod.get_graph())):
+            new_coordinator = True
+            for c in self.coordinators:
+                if mod.on_same_numa_node(core, c):
+                    new_coordinator = False
+            if new_coordinator:
+                self.coordinators.append(core)
+        print "Coordinator nodes are: %s" % str(self.coordinators)
+
+    def get_broadcast_tree(self):
+        """
+        Return the broadcast tree as a graph
+        """
+
+        # Build NUMA node graph with weights first
+        g_numa = graph()
+        for c in self.coordinators:
+            g_numa.add_node(c)
+            for co in self.coordinators:
+                if co<c:
+                    g_numa.add_edge((c, co),
+                                    self.mod.get_graph().edge_weight((c, co)))
+
+        # Print graph
+        helpers.output_graph(g_numa, 'cluster_numa', 'dot')
+
+        # Now: find a tree for this graph
+        # Observation: Machines today typically don't have more than 8 nodes
+        # core 0 sends one message "across" the machine, all others: MST
+
+        # max-hops: 3
+        # core 0 histogram (question: why would we start at 0?)
+        # - 1 hops: 2
+        # - 2 hops: 2
+        # - 3 hops: 3
+        # core 2 histogram
+        # - 1 hops: 4
+        # - 2 hops: 2
+        # - 3 hops: 1
+
+        # might be able to do some clustering: split up nodes such
+        # that half of them are in one cluster afterwards, the the
[…]

### 2013-05-06 graphs/config.py

@@ -2,3 +2,6 @@
 
 SCHEDULING_SORT=False
 SCHEDULING_SORT_LONGEST_PATH=True
+
+TOPO_TREE=False
+TOPO_CLUSTER=True

### 2013-05-06 graphs/graph_example.py

@@ -1,22 +1,20 @@
 #!/usr/bin/env python
 
-# Import graphviz
-import sys
-sys.path.append('..')
-sys.path.append('/usr/lib/graphviz/python/')
-sys.path.append('/usr/lib64/graphviz/python/')
-import gv
-
 # Import pygraph
 from pygraph.classes.graph import graph
 from pygraph.classes.digraph import digraph
 from pygraph.algorithms.searching import breadth_first_search
-from pygraph.readwrite.dot import write
 from pygraph.algorithms.minmax import shortest_path
 from pygraph.algorithms.minmax import minimal_spanning_tree
 
 # Import own code
 import evaluate
+import config
+import model
+import cluster
+import helpers
+
+import pdb
 
 # --------------------------------------------------
 
@@ -25,20 +23,6 @@ NUM_NUMA_NODES = 8
 NUM_CORES = (CORES_PER_NODE*NUM_NUMA_NODES)
 HOPCOST = 10
 NUMACOST = 1
-
-def output_graph(graph, name):
-    """
-    Output the graph as png image and also as text file
-    """
-    dot = write(graph, True)
-    gvv = gv.readstring(dot)
-    
-    with open('%s.dot'%name, 'w') as f:
-        f.write(dot)
-
-    gv.layout(gvv, 'neato')
-    gv.render(gvv, 'png', ('%s.png' % name))
-
 
 # Wrapper function to add edges between two NUMA nodes. 
 def add_numa(graph, node1, node2, cost):
@@ -109,7 +93,7 @@ def build_and_simulate():
     g_numa.add_edge((3,6))
     g_numa.add_edge((3,7))
 
-    output_graph(g_numa, 'g_numa_tmp')
+    helpers.output_graph(g_numa, 'g_numa_tmp')
 
 
     # --------------------------------------------------
@@ -126,8 +110,32 @@ def build_and_simulate():
     # for n in range(NUM_NUMA_NODES, 2*NUM_NUMA_NODES):
     #     connect_numa_nodes(gr, g_numa, n)
 
+
+    if config.TOPO_TREE:
+        final_graph = _run_mst(gr)
+
+    elif config.TOPO_CLUSTER:
+        # Build a model for gruyere
+        # XXX all the above code should go there!
+        m = model.Gruyere(gr)
+        clustering = cluster.Cluster(m)
+        final_graph = clustering.get_broadcast_tree()
+        pdb.set_trace() # XXX Evaluation does not work at this point
+
     # --------------------------------------------------
[…]

### 2013-05-06 graphs/helpers.py

@@ -1,0 +1,25 @@
+# Copyright (c) 2007, 2008, 2009, 2010, 2011, 2012, 2013 ETH Zurich.
+
+# Import graphviz
+import sys
+sys.path.append('..')
+sys.path.append('/usr/lib/graphviz/python/')
+sys.path.append('/usr/lib64/graphviz/python/')
+import gv
+
+from pygraph.readwrite.dot import write
+
+def output_graph(graph, name, algorithm='neato'):
+    """
+    Output the graph as png image and also as text file
+    """
+    dot = write(graph, True)
+    gvv = gv.readstring(dot)
+    
+    with open('%s.dot'%name, 'w') as f:
+        f.write(dot)
+
+    gv.layout(gvv, algorithm)
+    gv.render(gvv, 'png', ('%s.png' % name))
+
+

### 2013-05-06 graphs/model.py

@@ -1,0 +1,47 @@
+# Copyright (c) 2007, 2008, 2009, 2010, 2011, 2012, 2013 ETH Zurich.
+
+import pdb
+
+# --------------------------------------------------
+class Model:
+
+    def on_same_numa_node(self, core1, core2):
+        """
+        Base model does not have any NUMA nodes
+        """
+        return True
+
+    def __init__(self, graph):
+        """
+        We initialize models with the graph
+        """
+        self.graph = graph
+        
+    def get_graph(self):
+        return self.graph
+        
+# --------------------------------------------------
+class Gruyere(Model):
+
+    # Definition of NUMA topology
+    numa = ( 
+        (0,1,2,3,), 
+        (4,5,6,7,), 
+        (8,9,10,11,), 
+        (12,13,14,15,), 
+        (16,17,18,19,), 
+        (20,21,22,23,), 
+        (24,25,26,27,), 
+        (28,29,30,31) 
+        )
+    
+    def on_same_numa_node(self, core1, core2):
+        """
+        Return whether two nodes are in the same NUMA region
+        """
+        for node in self.numa:
+            if core1 in node:
+                return core2 in node
+        pdb.set_trace()
+        return None
+        

### 2013-05-06 paper.tex
Simulation for ring-based outer communication

@@
 \maketitle
+
+% keywords: modeling, simulation, overlay networks, scheduling
 
@@
 First, we discuss what kind of topologies we use to communicate
-between nodes. We evaluate tree based implementations. Other
-potentially interesting topologies are rings.
+between nodes. We evaluate tree based implementations: binary trees,
+minimum spanning trees, hierarchical tress and clustering
+techniques. Other potentially interesting topologies are rings.
 
@@
 %-------------------------------------------------
+\subsubsection{Hierarchical}
+
+We now consider NUMA node for coming up with a broadcast tree. We
+select one coordinator node in every node and build a binary tree
+for the coordinators. We call this topology connecting nodes across
+NUMA domains the \emph{outer} network.
+
+Each coordinator is also responsible for sending a message to all
+other cores of the node. We currently do this sequentially, since the
+number of cores in a node is typically very small. Alternatively, a
+binary tree could be used as well. We call overlay networks within
+NUMA nodes \emph{inner} networks.
+
+We show an example hierarchical tree in
+Figure~\ref{fig:gruyere_hierarchy}.
+
+\begin{figure}
+\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
+  \pgfsetlinewidth{.5bp}
+\input{figs/final_gruyere_hierarchical}
+\end{tikzpicture}
+\caption{Hierarchical tree for a 8x4x1 multicore}
+\label{fig:gruyere_hierarchy}
+\end{figure}
+
+%-------------------------------------------------
 \subsubsection{Clustering}
@@
 NUMA domain corresponds to one cluster.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Ring topology}
+
+Next, we evaluate ring topologies. Rings have the advantage that the
+implicitly acknowledge messages once they arrive back to the
+sender. This is beneficial for some algorithms such as quorums, where
+nodes report back to the sender.
+
+The downside is that some state is required on every node to remember
+whether or not a message was received before. This however only works
+if forwarding along the ring is only done after all local nodes
+acknowledge a message. If messages are just forwarded as they arrive,
+message transport does never terminate.
+
+To add more parallelism, we add a second ring, which we send the
+message on in parallel. The overlay ring network is visualized in
+Figure~\ref{fig:gruyere_ring}.
+
+\begin{figure}
+\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
+  \pgfsetlinewidth{.5bp}
+\input{graphs/final_ring}
+\end{tikzpicture}
+\caption{Outer overlay as ring with sequential inner overlay for a
+  8x4x1 multicore}
+\label{fig:gruyere_ring}
+\end{figure}
 
@@
     running the MST algorithm, we optimize scheduling in every node to
-    send messages to in decreasing order of their latency.}
+    send messages in decreasing order of their latency.}
   \label{fig:mst_gruyere_operations_sorted}
@@
   \centering
-  \begin{tabular}{llll}
+  \begin{tabular}{lllll}
     \toprule
-    topology & scheduling & time & factor \\
+    topology & scheduling & time & factor & figure \\
     \midrule
-    MST & naive                     & 241 & 1.00 \\
-    MST & highest link weight first & 151 & 0.63 \\
-    MST & longest path first        & 151 & 0.63 \\
+    MST & naive                     & 241 & 1.00 & 
+        \ref{fig:mst_gruyere_operations} \\
+    MST & highest link weight first & 151 & 0.63 & 
+        \ref{fig:mst_gruyere_operations_sorted} \\
+    MST & longest path first        & 151 & 0.63 & 
+        \stefan{? AFAIK, same as
+        \ref{fig:mst_gruyere_operations_sorted} } \\
+    hierarchical & highest link weight first & 151 & 0.63 &
+        \ref{fig:visu_hierarchy} \\
+    ring & highest link weight first & 181 & 0.75 &
+        \ref{fig:visu_ring} \\
     \bottomrule
@@
   evaluate if the increase in complexity is worth it}
+
+\begin{figure}[htb]
+  \centering
+  \begin{tikzpicture}[scale=.35,transform shape]
+    % Insert visualization
+    \input{visu_hierarchy}
+  \end{tikzpicture}
+  \caption{Visualization of hierarchical tree broadcast. A binary tree
+    spans across NUMA nodes followed by sequential send operations
+    within the NUMA node. %
+    Red boxes represent send operations, blue boxes represent receive
+    operations and arrows messages sent between cores.  }
+  \label{fig:visu_hierarchy}
+\end{figure}
+
+\begin{figure}[htb]
+  \centering
+  \begin{tikzpicture}[scale=.35,transform shape]
+    % Insert visualization
+    \input{visu_ring}
+  \end{tikzpicture}
+  \caption{Visualization of ring based broadcast. Two rings
+    spans across NUMA nodes followed by sequential send operations
+    within the NUMA node. %
+    Red boxes represent send operations, blue boxes represent receive
+    operations and arrows messages sent between
+    cores. \stefan{Scheduling is broken. If we want acks, we can only
+      forward a message along the ring when all the local nodes
+      acknowledge a message}}
+  \label{fig:visu_ring}
+\end{figure}
 

### 2013-05-06 graphs/algorithms.py

@@ -1,16 +1,31 @@
 # Copyright (c) 2007, 2008, 2009, 2010, 2011, 2012, 2013 ETH Zurich.
 
 from pygraph.classes.graph import graph
+from pygraph.classes.digraph import digraph
 import Queue
 
-def binary_tree(model, out_degree=2):
+def binary_tree(m, nodes=[], out_degree=2):
     """
     Construct a binary tree for the given g
+    XXX Currently, this works only for out_degree=2
+
+    @type m: graph
+    @param m: The machine model. The weights for the edges in the binary_tree
+        will be extracted from the model
+
+    @type nodes: list
+    @param nodes: list of nodes to build a binary tree for. If list is
+        empty, it will default to m.nodes()
+
+    @type out_degree: number
+    @param out_degree: outdegree of nodes in the generated graph. Currently,
+        this is ignored
     """
-    assert(len(model.nodes())>0) # graph has nodes
+    assert(len(m.nodes())>0) # graph has nodes
 
     g = graph()
-    nodes = model.nodes()
+    if len(nodes)==0:
+        nodes = m.nodes()
     num = len(nodes)
 
     for n in nodes:
@@ -20,11 +35,71 @@ def binary_tree(model, out_degree=2):
         p = 2*(i+1)-1
         pp = 2*(i+1)
         if p < num:
-            g.add_edge((nodes[i],  nodes[p]))
+            g.add_edge((nodes[i],  nodes[p]), \
+                           m.edge_weight((nodes[i], nodes[p])))
             if pp < num:
-                g.add_edge((nodes[i], nodes[pp]))
+                g.add_edge((nodes[i], nodes[pp]), \
+                               m.edge_weight((nodes[i], nodes[pp])))
 
     return g
+
+def simple_tree(m, nodes, coordinator):
+    """
+    Construct a simple two-level tree. The coordinator is the root, and all 
+    the other nodes are its children
+
+    @type m: graph
+    @param m: The machine model. The weights for the edges in the binary_tree
+        will be extracted from the model
+
+    @type nodes: list
+    @param nodes: list of nodes to build a tree for. If list is
+        empty, it will default to m.nodes()
+
+    @type coordinator: number
+    @param coordinator: This node will be the root of the tree
+    """
+    assert(len(m.nodes())>0) # graph has nodes
+
+    g = graph()
+    g.add_node(coordinator)
+
+    for n in nodes:
[…]

### 2013-05-06 graphs/config.py

@@ -1,7 +1,10 @@
+# Copyright (c) 2007, 2008, 2009, 2010, 2011, 2012, 2013 ETH Zurich.
 # This is meant to hold all sort of configuration options
 
-SCHEDULING_SORT=False
-SCHEDULING_SORT_LONGEST_PATH=True
+SCHEDULING_SORT=True
+SCHEDULING_SORT_ID=False
+SCHEDULING_SORT_LONGEST_PATH=False
 
 TOPO_TREE=False
-TOPO_CLUSTER=True
+TOPO_RING=True
+TOPO_CLUSTER=False

### 2013-05-06 graphs/evaluate.py

@@ -14,6 +14,15 @@ import pdb
 round = 0
 event_queue = []
 model = {}
+node_state = []
+
+class NodeState(object):
+    """
+    Store node state for evaluation
+    """
+    def __init__(self):
+        self.seq_no = 0
+
 
 def evalute(tree, root):
     """
@@ -22,8 +31,11 @@ def evalute(tree, root):
     global round
     global node_queues
     global model
+    global node_state
 
     model = tree
+
+    node_state = [NodeState()]*len(model)
 
     # Construct visualization instance
     global visu
@@ -130,8 +142,15 @@ def send(src, cost, omit):
     No message will be send towards nodes given in omit
     """
     assert isinstance(omit, list)
+    assert src<len(model)
     send_time = cost
     nb = []
+    # For rings: sequence number
+    if isinstance(node_state[src], NodeState) and node_state[src].seq_no > 0:
+        print "Node %d Received message that was send before, aborting!" % src
+        return
+    node_state[src] = NodeState()
+    node_state[src].seq_no = 1
     # Create list of children first, and the cost of the message list
     for dest in model.neighbors(src):
         if not dest in omit:
@@ -144,6 +163,9 @@ def send(src, cost, omit):
     # Sort this list
     if config.SCHEDULING_SORT or config.SCHEDULING_SORT_LONGEST_PATH:
         nb.sort(key=lambda tup: tup[0], reverse=True)
+    # Sort this list
+    if config.SCHEDULING_SORT_ID:
+        nb.sort(key=lambda tup: tup[1], reverse=False) # Sort by node ID
     # Walk the list and send messages
     for (cost, dest) in nb:
             visu.send(src, dest, send_time, send_cost(src))

### 2013-05-06 graphs/graph_example.py

@@ -12,6 +12,7 @@ import evaluate
 import config
 import model
 import cluster
+import ring
 import helpers
 
 import pdb
@@ -111,16 +112,20 @@ def build_and_simulate():
     #     connect_numa_nodes(gr, g_numa, n)
 
 
+    root = 0
     if config.TOPO_TREE:
         final_graph = _run_mst(gr)
 
     elif config.TOPO_CLUSTER:
-        # Build a model for gruyere
-        # XXX all the above code should go there!
         m = model.Gruyere(gr)
         clustering = cluster.Cluster(m)
         final_graph = clustering.get_broadcast_tree()
-        pdb.set_trace() # XXX Evaluation does not work at this point
+
+    elif config.TOPO_RING:
+        m = model.Gruyere(gr)
+        r = ring.Ring(m)
+        final_graph = r.get_broadcast_tree()
+        root = 8
 
     # --------------------------------------------------
     # Output graphs
@@ -130,7 +135,7 @@ def build_and_simulate():
     # helpers.output_graph(final_graph, 'mst')
 
     # --------------------------------------------------
-    print "Cost for tree is: %d" % evaluate.evalute(final_graph, 0)
+    print "Cost for tree is: %d" % evaluate.evalute(final_graph, root)
 
 def _run_mst(gr):
     """

### 2013-05-06 graphs/model.py

@@ -19,6 +19,16 @@ class Model:
         
     def get_graph(self):
         return self.graph
+
+    def get_numa_node(self, core1):
+        """
+        Return all cores that are on the same NUMA node then the given core
+        """
+        numa_node = []
+        for node in self.graph.nodes():
+            if self.on_same_numa_node(core1, node):
+                numa_node.append(node)
+        return numa_node
         
 # --------------------------------------------------
 class Gruyere(Model):

### 2013-05-06 graphs/overlay.py

@@ -1,0 +1,36 @@
+# Copyright (c) 2007, 2008, 2009, 2010, 2011, 2012, 2013 ETH Zurich.
+
+import model
+
+class Overlay(object):
+    """
+    Base class for finding the right overlay topology for a model
+    """
+
+    def __init__(self, mod):
+        """
+        Initialize the clustering algorithm
+        """
+        assert isinstance(mod, model.Model)
+        self.mod = mod
+
+    def get_broadcast_tree(self):
+        return None
+
+    def get_coordinators(self):
+        """
+        Selects one coordinator per node for given model. 
+        """
+        coordinators=[]
+        for core in range(len(mod.get_graph())):
+            new_coordinator = True
+            for c in coordinators:
+                if mod.on_same_numa_node(core, c):
+                    new_coordinator = False
+            if new_coordinator:
+                coordinators.append(core)
+        print "Coordinator nodes are: %s" % str(coordinators)
+        return coordinators
+
+
+

### 2013-05-06 graphs/ring.py

@@ -1,0 +1,81 @@
+# Copyright (c) 2007, 2008, 2009, 2010, 2011, 2012, 2013 ETH Zurich.
+
+# Import graphviz
+import sys
+sys.path.append('..')
+sys.path.append('/usr/lib/graphviz/python/')
+sys.path.append('/usr/lib64/graphviz/python/')
+import gv
+
+# Import pygraph
+from pygraph.classes.graph import graph
+from pygraph.classes.digraph import digraph
+from pygraph.algorithms.searching import breadth_first_search
+from pygraph.readwrite.dot import write
+from pygraph.algorithms.minmax import shortest_path
+from pygraph.algorithms.minmax import minimal_spanning_tree
+
+# Import own code
+import evaluate
+import model
+import helpers
+import algorithms
+import overlay
+
+class Ring(overlay.Overlay):
+    """
+    Build a ring topology for a model
+    
+    The outer topology is going to be a ring. We need a directed graph
+    to represent the model here, while previously, a undirected graph
+    would work as well and we would just not send messages from where
+    we received them from.
+    """
+    
+    def __init__(self, mod):
+        """
+        Initialize the ring algorithm
+        """
+        super(Ring, self).__init__(mod)
+
+    def get_broadcast_tree(self):
+        """
+        This currently only works for 8x4x1 model
+        """
+        
+        # Sanity check. Is the model an 8x4x1 model?
+        assert(len(self.mod.get_graph().nodes())==32)
+        for i in range(32):
+            assert (i in self.mod.get_graph().nodes())
+
+        g = self._get_outer_rings()
+        for i in [0, 4, 8, 12, 16, 20, 24, 28]:
+            numa_node = self.mod.get_numa_node(i)
+            g = algorithms.merge_graphs(algorithms.simple_tree(\
+                    self.mod.get_graph(), numa_node, i), g)
+
+        helpers.output_graph(g, 'ring', 'neato')
+        return g
+
+
+
+    def _get_outer_rings(self):
+        """
+        Get rings connecting the NUMA nodes
+        """
+        g = digraph()
+        for i in [0, 4, 8, 12, 16, 20, 24, 28]:
+            g.add_node(i)
+
+        for e in [(8,12),\
+                      (12,28),\
+                      (28,24),\
+                      (24,8),\
+                      (8,4),\
+                      (4,0),\
+                      (0,16),\
+                      (16,20),\
+                      (20,8)]:
+            g.add_edge(e, self.mod.get_graph().edge_weight(e))
+
+        return g    

### 2013-05-07 paper.tex
Did try other topologies now
Scheduling as a separate section
Restructuring and general improvements

@@
 machines, we automatically configure our atomic broadcast
-implementation based on a machine model.
+implementation based on a machine model. We represent this model as an
+annotated graph. One question we are looking at is which information
+should actually be part of this machine model.
+
 % How will you go about it?
-We will base our atomic broadcast on overlay networks, which we
-automatically configure based on the machine model. One questions is
-which information should actually be encoded in the machine model. %
-Our idea is to then explore different approaches (such as MST
-algorithms, clustering) to \emph{find good overlay networks} based on
-the network model to base the atomic broadcast on. Then, for every
-node, we need to decide which message to send first. This is a
-\emph{scheduling} problem.
+We will base our atomic broadcast on \emph{overlay networks}, which we
+automatically configure. We execute our configuration stage on a model
+representing the concrete machine the algorithm is intended to run
+on. %
+Our idea is to then explore different approaches for finding overlay
+networks based on the network model graph. Approaches we are currently
+investigating are: minimum spanning tree algorithms, binary trees,
+clustering techniques as well as treating the problem
+hierarchically. Assuming the overlay network, we then need to decide
+on every node which message to send first. This is a \emph{scheduling}
+problem.
 
@@
 We auto-configure a wide range of different multicore machines and
-show the performance of our implementation comes close to the
-performance of hand-tuned implementations for all of these machines.
-
+compare the performance of our implementation with hand-tuned
+implementations on all of these machines.
 % Hypothesis
-My hypothesis is that automatic tuning of atomic broadcast (and other
+Our hypothesis is that automatic tuning of atomic broadcast (and other
 distributed algorithms) to machine characteristics is worth
 doing. Obviously, we cannot achieve performance of hand-tuned
-implementations, but we can get close enough to argue that loosing a
-bit of performance to avoid tedious manual reconfiguration is worth if
-for many applications (while others, where performance \emph{really}
-matters, might still want to manually configure their stuff).
+implementations, but we hope to get close enough to argue that loosing
+a bit of performance to avoid tedious manual reconfiguration is worth
+if for many applications (while others, where performance
+\emph{really} matters, might still want to manually configure their
+stuff).
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Related work}
-
-A multicore aware broadcast has been implemented in~\cite{Tu2008}. It
-takes the cache architecture of the machine (and only one particular?)
-into consideration for building the broadcast. It is however for
-larger messages (starting at 4K) and it does not seem to be performing
-very well (numbers are given in microseconds -6). 4K messages are 52
-microseconds, which is 150000 cycles. For synchronization primitives,
-a cache line is sufficient.
-
-Another tree implementation with MPI in mind was done
-in~\cite{Graham2008}. They have comparable numbers to what we found,
-but they cannot automatically tune to different machine
-characteristics. Our hypothesis is that we can do achieve higher
-average performance across a wide range of different multicore
-machines without manually adapting the implementation.
-
-Alistarh\etal~\cite{Alistarh2012} show composition of shared-memory
-algorithms that perform efficiently under different conditions at
-negligible overhead. A similar approach can potentially be applied to
-deal with diversity of multicore machines. However, we would have
-to extend it to support both shared-memory and message-passing
-implementations.
+% three-step approach
+We break the problem down into three steps:
+\begin{inparaenum}[\itshape 1\upshape)]
+\item We first represent multicore machines by a model. We describe
+  this model in Section~\ref{sec:model},
+\item We then find an overlay for a concrete network model. This
+  overlay network describes a topology (such as a tree or a ring) for
+  communication within the machine. Algorithms to select overlay
+  networks are described in Section~\ref{sec:overlay}, and
+\item Given the overlay, we need to decide for every node in which
+  order to send messages. We investigate this scheduling problem in
+  Section~\ref{sec:scheduling}.
+\end{inparaenum}
 
@@
 \section{The multicore network model}
+\label{sec:model}
 
@@
 Characteristics of the network influence the performance of
-distributed algorithms. Due to the heterogeneous combinations of
-complex networks on multicores, selection of algorithms is
-particularly hard.
-
+distributed algorithms. 
 % model
-We express the network characteristics in a multicore network
+We express these network characteristics in a multicore network
 model. This model at this stage is by no means complete. We are going to
@@
 multicores.
+% static
+Our network model is \emph{static}, which in particular implies that
+we do not consider run-time effect such as congestion for the moment.
 
 % graph
-We represent the multicore network as a graph. The nodes in this graph
-correspond to cores, and edges the communication channels between
-nodes. The machines we consider for now only have bi-directional
-communication links. Other machines (like the SCC) have
+We represent the multicore network as a \emph{directed graph}. The nodes in
+this graph correspond to cores, and edges to communication channels
+between nodes. The machines we consider for now only have
+bi-directional communication links. Other machines (like the SCC) have
 uni-directional links, which is why we model the graph as directed
 graph.
+% shared memory -> fully meshed
+This graph is \emph{fully meshed} for shared memory machines. Every core can
+communicate with every other node via the cache coherence protocol.
 
-% shared memory -> fully meshed
-This graph is fully meshed for shared memory machines. Every core can
-communicate with every other node via the cache coherence protocol.
+% machines hierarchical
+Multicore machines are hierarchical. Processor cores are grouped in
+NUMA nodes with shared caches. These NUMA nodes are then connected to
+each other by increasingly complex interconnect networks. 
+% NUMA affinity -> model
+We encode NUMA node affinity in our model. This allows to break down
+programming of a multicore machine into two distinct instances. We
+solve one instance of the problem between NUMA nodes, and then, in a
+second step, within each NUMA node. These two steps can be executed
+independently and different algorithms can be used in both case.
+
+% why it makes sense?
+If cores on the same NUMA node share a cache, it makes sense to
+leverage this hardware feature to implement shared-memory algorithms
+on top of it. %
+Communication across NUMA nodes is realized sending messages across
+the packet-based interconnect network. Using message-passing based
+implementations is the natural choice. %
+Shared memory algorithms and message-passing based algorithms can be
+composed together to program hierarchical machines similarly to what
+was previously shown for composing of shared-memory
+algorithms~\cite{Alistarh2012}.
 
@@
 
+\stefan{Not sure yet if we really need this, but it should be helpful
+  for treating the machine hierarchically}
+
 Every node (i.e.\ core) in the system has characteristics associated
@@
 \begin{description}
-\item[NUMA affinity] A list of cores on the same NUMA node
-\item[synchrony] Parts of a multicore machine are synchronous. Hence,
-  one characteristic of a node is an identifier for the synchrony
-  cluster of a node.
-\item[failure] Can nodes fail? If so, how? (Byzantine, crash)
+\item[NUMA affinity] A list of cores on the same NUMA node.
+\item[synchrony] Parts of a multicore machine are synchronous, i.e.\
+  cores execute in lock-steps, where every node can send a message to
+  every other node in one such step. This implies that there is a
+  global time and message delivery time is bound. Both can be assumed
+  on today's multicores. The global time comes from the fact that
+  cores are driven by the same quartz or, if not, they are
+  synchronized such that the jitter is less than a cycle, which leads
+  to cores seeing the same time. %
+  For these reasons, synchrony is not part of our current machine
+  model. Within today's multicores, synchrony can be
+  assumed. \stefan{Can it?}
+\item[failure] Can nodes fail? If so, how? (Byzantine, crash). We do
+  not consider failures at the moment, but believe that we will
+  inevitably have to do so for future multicores, where it is unlikely
+  that hardware can hide failures from software.
 \end{description}
-
-These are currently not encoded in the model. The send and receive
-cost are in part node specific. The faster a core is, the faster it
-can to the multiplexing and marshalling. However, they are also link
-dependent, so we view them as link characteristics.
 
@@
 
-The cost of sending a message in a multicore machines does not so much
-depend on the distance on the interconnect networks as on the number
-of hops on such a path. Propagation on the wire is essentially for
-free due to short distances between cores.
+\stefan{Maybe characteristics of NUMA nodes do not have to be encoded
+  separately, but as part of the node characteristics?}
 
+Some characteristics of multicore communication stem from the NUMA
+hierarchy. Thus, such characteristics can be encoded separately in the
+model.
+
+\begin{description}
+\item[hop count] Number of hops to every other NUMA node. The cost of
+  sending a message in a multicore machines does not so much depend on
+  the distance on the interconnect networks as on the number of hops
+  on such a path. Propagation on the wire is essentially for free due
+  to short distances between cores. %
   On a multi-hop path, however, packages traversing the interconnect
   need to be buffered. This is expensive. Depending on the machine,
-some routing is executed on every intermediate route, which increases
-the latency further.
-
-\begin{description}
-\item[hop count] Number of hops to every other NUMA node.
+  some routing is executed on every intermediate route, which
+  increases the latency further.
 \item[hop count histogram] For every NUMA node, we want to know how
@@
 \begin{description}
-\item[breakdown] (quantitative) of message send cost:
+\item[cost breakdown] (quantitative) of message send cost:
   dominating propagation time vs.\ dominating send and receive time on
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Hierarchical model}
-\label{sec:model_hierarchy}
-
-Multicore machines are hierarchical. Processor cores are grouped in
-NUMA nodes with shared caches. These NUMA nodes are then connected to
-each other by increasingly complex interconnect networks.
-
-We encode NUMA node affinity in our model. This allows to break down
-programming of a multicore machine into two distinct instances. We
-solve one instance of the problem between NUMA nodes, and then, in a
-second step, within each NUMA node. These two steps can be executed
-independently and different algorithms can be used in both case.
-
-If cores on the same NUMA node share a cache, it makes sense to
-leverage this hardware feature to implement shared-memory algorithms
-on top of it. %
-Communication across NUMA nodes is realized sending messages across
-the packet-based interconnect network. Using message-passing based
-implementations is the natural choice. %
-Shared memory algorithms and message-passing based algorithms can be
-composed together to program hierarchical machines similarly to what
-was previously shown for composing of shared-memory
-algorithms~\cite{Alistarh2012}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Acquiring the model}
@@
 
-Each of the eight nodes consists of four cores. We approximate the
+Each of the eight NUMA nodes consists of four cores. We approximate the
 cost of sending messages within nodes as $1$ and across nodes as
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Atomic Broadcast for Multicores}
+\section{Overlay selection}
+\label{sec:overlay}
 
@@
 \end{tikzpicture}
-\caption{Hierarchical tree for a 8x4x1 multicore}
+\caption{Hierarchical tree for a 8x4x1 multicore. Nodes 0, 4, 8, 12,
+  16, 20, 24 and 28 are coordinators. They are arranged in a binary
+  tree starting at node 0. Communication within NUMA nodes is
+  sequential (as an example: coordinator node 24 sends a message to
+  all cores on the same NUMA node, namely 25, 26 and 27)}
 \label{fig:gruyere_hierarchy}
@@
 
-We discussed earlier in Section~\ref{sec:model_hierarchy} that
+\stefan{Have not implemented this, but it might be interesting to try
+  out later}
+
+We discussed earlier in Section~\ref{sec:model} that
 multicore machines are hierarchical.%
@@
 sender. This is beneficial for some algorithms such as quorums, where
-nodes report back to the sender.
+nodes report back to the sender. This, however, only works if forwarding
+along the ring is only done after all local nodes acknowledge a
+message.
 
 The downside is that some state is required on every node to remember
-whether or not a message was received before. This however only works
-if forwarding along the ring is only done after all local nodes
-acknowledge a message. If messages are just forwarded as they arrive,
-message transport does never terminate.
+whether or not a message was received before. If messages are just
+forwarded as they arrive, message transport does never terminate.
 
@@
 message on in parallel. The overlay ring network is visualized in
-Figure~\ref{fig:gruyere_ring}.
+Figure~\ref{fig:gruyere_ring}. Node that the link from node 20 to 8 is
+a two hop link and, thus, has a cost of 20 instead of the usual 10.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Scheduling}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Scheduling}
+\label{sec:scheduling}
 
@@
 
-Current numbers are listed in Table~\ref{tab:bc_measurements}.
+\stefan{These numbers are outdated. Keeping them for reference}
+
+Some numbers are listed in Table~\ref{tab:bc_measurements}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Related work}
+
+A multicore aware broadcast has been implemented in~\cite{Tu2008}. It
+takes the cache architecture of the machine (and only one particular?)
+into consideration for building the broadcast. It is however for
+larger messages (starting at 4K) and it does not seem to be performing
+very well (numbers are given in microseconds -6). 4K messages are 52
+microseconds, which is 150000 cycles. For synchronization primitives,
+a cache line is sufficient.
+
+Another tree implementation with MPI in mind was done
+in~\cite{Graham2008}. They have comparable numbers to what we found,
+but they cannot automatically tune to different machine
+characteristics. Our hypothesis is that we can do achieve higher
+average performance across a wide range of different multicore
+machines without manually adapting the implementation.
+
+Alistarh\etal~\cite{Alistarh2012} show composition of shared-memory
+algorithms that perform efficiently under different conditions at
+negligible overhead. A similar approach can potentially be applied to
+deal with diversity of multicore machines. However, we would have
+to extend it to support both shared-memory and message-passing
+implementations.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Future work}
@@
 \item MPI collectives (as in~\cite{Tu2008})
-\item Try other topologies (Frans Kaashoek), e.g.\ rings
 \item \emph{Load balancing in a tree} We could build several rings,

### 2013-05-07 visu_only_mst.tex
Oops some files missing

\node at (0mm,0mm) {core 00};
\draw[color=black!10] (20mm,0mm) -- (30cm,0mm);
\node at (0mm,15mm) {core 01};
\draw[color=black!10] (20mm,15mm) -- (30cm,15mm);
\node at (0mm,30mm) {core 02};
\draw[color=black!10] (20mm,30mm) -- (30cm,30mm);
\node at (0mm,45mm) {core 03};
\draw[color=black!10] (20mm,45mm) -- (30cm,45mm);
\node at (0mm,60mm) {core 04};
\draw[color=black!10] (20mm,60mm) -- (30cm,60mm);
\node at (0mm,75mm) {core 05};
\draw[color=black!10] (20mm,75mm) -- (30cm,75mm);
\node at (0mm,90mm) {core 06};
\draw[color=black!10] (20mm,90mm) -- (30cm,90mm);
\node at (0mm,105mm) {core 07};
\draw[color=black!10] (20mm,105mm) -- (30cm,105mm);
\node at (0mm,120mm) {core 08};
\draw[color=black!10] (20mm,120mm) -- (30cm,120mm);
\node at (0mm,135mm) {core 09};
\draw[color=black!10] (20mm,135mm) -- (30cm,135mm);
\node at (0mm,150mm) {core 10};
\draw[color=black!10] (20mm,150mm) -- (30cm,150mm);
\node at (0mm,165mm) {core 11};
\draw[color=black!10] (20mm,165mm) -- (30cm,165mm);
\node at (0mm,180mm) {core 12};
\draw[color=black!10] (20mm,180mm) -- (30cm,180mm);
\node at (0mm,195mm) {core 13};
\draw[color=black!10] (20mm,195mm) -- (30cm,195mm);
\node at (0mm,210mm) {core 14};
\draw[color=black!10] (20mm,210mm) -- (30cm,210mm);
\node at (0mm,225mm) {core 15};
\draw[color=black!10] (20mm,225mm) -- (30cm,225mm);
\node at (0mm,240mm) {core 16};
\draw[color=black!10] (20mm,240mm) -- (30cm,240mm);
\node at (0mm,255mm) {core 17};
\draw[color=black!10] (20mm,255mm) -- (30cm,255mm);
\node at (0mm,270mm) {core 18};
\draw[color=black!10] (20mm,270mm) -- (30cm,270mm);
\node at (0mm,285mm) {core 19};
\draw[color=black!10] (20mm,285mm) -- (30cm,285mm);
\node at (0mm,300mm) {core 20};
\draw[color=black!10] (20mm,300mm) -- (30cm,300mm);
\node at (0mm,315mm) {core 21};
\draw[color=black!10] (20mm,315mm) -- (30cm,315mm);
\node at (0mm,330mm) {core 22};
\draw[color=black!10] (20mm,330mm) -- (30cm,330mm);
\node at (0mm,345mm) {core 23};
\draw[color=black!10] (20mm,345mm) -- (30cm,345mm);
\node at (0mm,360mm) {core 24};
\draw[color=black!10] (20mm,360mm) -- (30cm,360mm);
\node at (0mm,375mm) {core 25};
\draw[color=black!10] (20mm,375mm) -- (30cm,375mm);
\node at (0mm,390mm) {core 26};
\draw[color=black!10] (20mm,390mm) -- (30cm,390mm);
\node at (0mm,405mm) {core 27};
\draw[color=black!10] (20mm,405mm) -- (30cm,405mm);
\node at (0mm,420mm) {core 28};
\draw[color=black!10] (20mm,420mm) -- (30cm,420mm);
\node at (0mm,435mm) {core 29};
\draw[color=black!10] (20mm,435mm) -- (30cm,435mm);
\node at (0mm,450mm) {core 30};
\draw[color=black!10] (20mm,450mm) -- (30cm,450mm);
\node at (0mm,465mm) {core 31};
\draw[color=black!10] (20mm,465mm) -- (30cm,465mm);
\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (60mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (80mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (90mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (61mm,15mm) {};
\draw[->] (s_0_1.center) -- (r_0_1.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (71mm,30mm) {};
\draw[->] (s_0_2.center) -- (r_0_2.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
\draw[->] (s_0_3.center) -- (r_0_3.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (100mm,60mm) {};
\draw[->] (s_0_4.center) -- (r_0_4.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (110mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (130mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (140mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (150mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (110mm,240mm) {};
\draw[->] (s_0_16.center) -- (r_0_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (120mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (130mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (140mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (121mm,75mm) {};
\draw[->] (s_4_5.center) -- (r_4_5.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (131mm,255mm) {};
\draw[->] (s_16_17.center) -- (r_16_17.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (131mm,90mm) {};
\draw[->] (s_4_6.center) -- (r_4_6.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (141mm,270mm) {};
\draw[->] (s_16_18.center) -- (r_16_18.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (141mm,105mm) {};
\draw[->] (s_4_7.center) -- (r_4_7.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (151mm,285mm) {};
\draw[->] (s_16_19.center) -- (r_16_19.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (160mm,120mm) {};
\draw[->] (s_4_8.center) -- (r_4_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (170mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (180mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (190mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (200mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (210mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (220mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (170mm,300mm) {};
\draw[->] (s_4_20.center) -- (r_4_20.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (180mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (190mm,300mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (200mm,300mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (181mm,135mm) {};
\draw[->] (s_8_9.center) -- (r_8_9.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (191mm,315mm) {};
\draw[->] (s_20_21.center) -- (r_20_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (191mm,150mm) {};
\draw[->] (s_8_10.center) -- (r_8_10.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (201mm,330mm) {};
\draw[->] (s_20_22.center) -- (r_20_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (201mm,165mm) {};
\draw[->] (s_8_11.center) -- (r_8_11.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (211mm,345mm) {};
\draw[->] (s_20_23.center) -- (r_20_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (220mm,180mm) {};
\draw[->] (s_8_12.center) -- (r_8_12.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (230mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (240mm,180mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (250mm,180mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (230mm,360mm) {};
\draw[->] (s_8_24.center) -- (r_8_24.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (240mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (250mm,360mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (260mm,360mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (240mm,420mm) {};
\draw[->] (s_8_28.center) -- (r_8_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (250mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (260mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (270mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (241mm,195mm) {};
\draw[->] (s_12_13.center) -- (r_12_13.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (251mm,210mm) {};
\draw[->] (s_12_14.center) -- (r_12_14.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (251mm,375mm) {};
\draw[->] (s_24_25.center) -- (r_24_25.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (261mm,435mm) {};
\draw[->] (s_28_29.center) -- (r_28_29.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (261mm,390mm) {};
\draw[->] (s_24_26.center) -- (r_24_26.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (261mm,225mm) {};
\draw[->] (s_12_15.center) -- (r_12_15.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (271mm,450mm) {};
\draw[->] (s_28_30.center) -- (r_28_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (271mm,405mm) {};
\draw[->] (s_24_27.center) -- (r_24_27.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (281mm,465mm) {};
\draw[->] (s_28_31.center) -- (r_28_31.center);

### 2013-05-07 visu_hierarchy.tex
Oops some files missing

--- 2013-05-07 visu_only_mst.tex
@@
 \draw[color=black!10] (20mm,465mm) -- (30cm,465mm);
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (60mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (50mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (60mm,0mm) {};
 \node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (90mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (61mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (71mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
+\draw[->] (s_0_8.center) -- (r_0_8.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (90mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (100mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (110mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (120mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (130mm,120mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (80mm,60mm) {};
+\draw[->] (s_0_4.center) -- (r_0_4.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (90mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_16) at (100mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (110mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (130mm,60mm) {};
 \node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
 \draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (100mm,60mm) {};
-\draw[->] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (110mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (130mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (140mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (150mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (110mm,240mm) {};
-\draw[->] (s_0_16.center) -- (r_0_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (120mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (130mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (140mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (121mm,75mm) {};
-\draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (131mm,255mm) {};
-\draw[->] (s_16_17.center) -- (r_16_17.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
+\draw[->] (s_0_2.center) -- (r_0_2.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
+\draw[->] (s_0_1.center) -- (r_0_1.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (120mm,300mm) {};
+\draw[->] (s_8_20.center) -- (r_8_20.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (130mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (140mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (150mm,300mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (120mm,360mm) {};
+\draw[->] (s_8_24.center) -- (r_8_24.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (130mm,360mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (140mm,360mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (150mm,360mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (120mm,180mm) {};
+\draw[->] (s_4_12.center) -- (r_4_12.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (130mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (140mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (160mm,180mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (121mm,150mm) {};
+\draw[->] (s_8_10.center) -- (r_8_10.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (121mm,105mm) {};
+\draw[->] (s_4_7.center) -- (r_4_7.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_16) at (130mm,240mm) {};
+\draw[->] (s_4_16.center) -- (r_4_16.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (140mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (150mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (160mm,240mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (131mm,135mm) {};
+\draw[->] (s_8_9.center) -- (r_8_9.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (131mm,90mm) {};
 \draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (141mm,270mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (141mm,75mm) {};
+\draw[->] (s_4_5.center) -- (r_4_5.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (141mm,165mm) {};
+\draw[->] (s_8_11.center) -- (r_8_11.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (141mm,390mm) {};
+\draw[->] (s_24_26.center) -- (r_24_26.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (141mm,315mm) {};
+\draw[->] (s_20_21.center) -- (r_20_21.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (150mm,420mm) {};
+\draw[->] (s_12_28.center) -- (r_12_28.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (160mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (170mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (180mm,420mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (151mm,255mm) {};
+\draw[->] (s_16_17.center) -- (r_16_17.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (151mm,330mm) {};
+\draw[->] (s_20_22.center) -- (r_20_22.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (151mm,405mm) {};
+\draw[->] (s_24_27.center) -- (r_24_27.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (151mm,225mm) {};
+\draw[->] (s_12_15.center) -- (r_12_15.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (161mm,345mm) {};
+\draw[->] (s_20_23.center) -- (r_20_23.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (161mm,375mm) {};
+\draw[->] (s_24_25.center) -- (r_24_25.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};
+\draw[->] (s_12_14.center) -- (r_12_14.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (161mm,270mm) {};
 \draw[->] (s_16_18.center) -- (r_16_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (141mm,105mm) {};
-\draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (151mm,285mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (171mm,285mm) {};
 \draw[->] (s_16_19.center) -- (r_16_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (160mm,120mm) {};
-\draw[->] (s_4_8.center) -- (r_4_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (170mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (180mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (190mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (200mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (210mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (220mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (170mm,300mm) {};
-\draw[->] (s_4_20.center) -- (r_4_20.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (180mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (190mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (200mm,300mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (181mm,135mm) {};
-\draw[->] (s_8_9.center) -- (r_8_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (191mm,315mm) {};
-\draw[->] (s_20_21.center) -- (r_20_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (191mm,150mm) {};
-\draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (201mm,330mm) {};
-\draw[->] (s_20_22.center) -- (r_20_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (201mm,165mm) {};
-\draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (211mm,345mm) {};
-\draw[->] (s_20_23.center) -- (r_20_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (220mm,180mm) {};
-\draw[->] (s_8_12.center) -- (r_8_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (230mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (240mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (250mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (230mm,360mm) {};
-\draw[->] (s_8_24.center) -- (r_8_24.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (240mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (250mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (260mm,360mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (240mm,420mm) {};
-\draw[->] (s_8_28.center) -- (r_8_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (250mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (260mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (270mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (241mm,195mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (171mm,465mm) {};
+\draw[->] (s_28_31.center) -- (r_28_31.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (171mm,195mm) {};
 \draw[->] (s_12_13.center) -- (r_12_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (251mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (251mm,375mm) {};
-\draw[->] (s_24_25.center) -- (r_24_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (261mm,435mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (181mm,435mm) {};
 \draw[->] (s_28_29.center) -- (r_28_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (261mm,390mm) {};
-\draw[->] (s_24_26.center) -- (r_24_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (261mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (271mm,450mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (191mm,450mm) {};
 \draw[->] (s_28_30.center) -- (r_28_30.center);
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (271mm,405mm) {};
-\draw[->] (s_24_27.center) -- (r_24_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (281mm,465mm) {};
-\draw[->] (s_28_31.center) -- (r_28_31.center);

### 2013-05-07 visu_mst_sort.tex
Oops some files missing

--- 2013-05-07 visu_hierarchy.tex
@@
 \draw[color=black!10] (20mm,465mm) -- (30cm,465mm);
-\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (70mm,0mm) {};
 \node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
-\draw[->] (s_0_8.center) -- (r_0_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (90mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (100mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (110mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (120mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (130mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (80mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (90mm,0mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};
 \draw[->] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (90mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_16) at (100mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (110mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (130mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
-\draw[->] (s_0_3.center) -- (r_0_3.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (90mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (100mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (110mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (120mm,60mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
+\draw[->] (s_0_16.center) -- (r_0_16.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (90mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (100mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (110mm,240mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (81mm,15mm) {};
+\draw[->] (s_0_1.center) -- (r_0_1.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
 \draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (120mm,300mm) {};
-\draw[->] (s_8_20.center) -- (r_8_20.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (130mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (140mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (150mm,300mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (120mm,360mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
+\draw[->] (s_4_8.center) -- (r_4_8.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (110mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (120mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (130mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (140mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (150mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (160mm,120mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (101mm,45mm) {};
+\draw[->] (s_0_3.center) -- (r_0_3.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (101mm,255mm) {};
+\draw[->] (s_16_17.center) -- (r_16_17.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (110mm,300mm) {};
+\draw[->] (s_4_20.center) -- (r_4_20.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (120mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (130mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (140mm,300mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (111mm,75mm) {};
+\draw[->] (s_4_5.center) -- (r_4_5.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (111mm,270mm) {};
+\draw[->] (s_16_18.center) -- (r_16_18.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (121mm,90mm) {};
+\draw[->] (s_4_6.center) -- (r_4_6.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (121mm,285mm) {};
+\draw[->] (s_16_19.center) -- (r_16_19.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (130mm,180mm) {};
+\draw[->] (s_8_12.center) -- (r_8_12.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (160mm,180mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (131mm,315mm) {};
+\draw[->] (s_20_21.center) -- (r_20_21.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (131mm,105mm) {};
+\draw[->] (s_4_7.center) -- (r_4_7.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (140mm,360mm) {};
 \draw[->] (s_8_24.center) -- (r_8_24.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (130mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (140mm,360mm) {};
 \node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (150mm,360mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (120mm,180mm) {};
-\draw[->] (s_4_12.center) -- (r_4_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (130mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (140mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (160mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (121mm,150mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (160mm,360mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (170mm,360mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (141mm,330mm) {};
+\draw[->] (s_20_22.center) -- (r_20_22.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (150mm,420mm) {};
+\draw[->] (s_8_28.center) -- (r_8_28.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (160mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (170mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (180mm,420mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (151mm,345mm) {};
+\draw[->] (s_20_23.center) -- (r_20_23.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};
+\draw[->] (s_12_13.center) -- (r_12_13.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (151mm,135mm) {};
+\draw[->] (s_8_9.center) -- (r_8_9.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};
+\draw[->] (s_12_14.center) -- (r_12_14.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (161mm,150mm) {};
 \draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (121mm,105mm) {};
-\draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_16) at (130mm,240mm) {};
-\draw[->] (s_4_16.center) -- (r_4_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (140mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (150mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (160mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (131mm,135mm) {};
-\draw[->] (s_8_9.center) -- (r_8_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (131mm,90mm) {};
-\draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (141mm,75mm) {};
-\draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (141mm,165mm) {};
-\draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (141mm,390mm) {};
-\draw[->] (s_24_26.center) -- (r_24_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (141mm,315mm) {};
-\draw[->] (s_20_21.center) -- (r_20_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (150mm,420mm) {};
-\draw[->] (s_12_28.center) -- (r_12_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (160mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (170mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (180mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (151mm,255mm) {};
-\draw[->] (s_16_17.center) -- (r_16_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (151mm,330mm) {};
-\draw[->] (s_20_22.center) -- (r_20_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (151mm,405mm) {};
-\draw[->] (s_24_27.center) -- (r_24_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (151mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (161mm,345mm) {};
-\draw[->] (s_20_23.center) -- (r_20_23.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (161mm,375mm) {};
 \draw[->] (s_24_25.center) -- (r_24_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (161mm,270mm) {};
-\draw[->] (s_16_18.center) -- (r_16_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (171mm,285mm) {};
-\draw[->] (s_16_19.center) -- (r_16_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (171mm,465mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (171mm,435mm) {};
+\draw[->] (s_28_29.center) -- (r_28_29.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (171mm,225mm) {};
+\draw[->] (s_12_15.center) -- (r_12_15.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (171mm,390mm) {};
+\draw[->] (s_24_26.center) -- (r_24_26.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (171mm,165mm) {};
+\draw[->] (s_8_11.center) -- (r_8_11.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (181mm,450mm) {};
+\draw[->] (s_28_30.center) -- (r_28_30.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (181mm,405mm) {};
+\draw[->] (s_24_27.center) -- (r_24_27.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (191mm,465mm) {};
 \draw[->] (s_28_31.center) -- (r_28_31.center);
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (171mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (181mm,435mm) {};
-\draw[->] (s_28_29.center) -- (r_28_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (191mm,450mm) {};
-\draw[->] (s_28_30.center) -- (r_28_30.center);

### 2013-05-07 visu_ring.tex
Oops some files missing

--- 2013-05-07 visu_mst_sort.tex
@@
 \draw[color=black!10] (20mm,465mm) -- (30cm,465mm);
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (90mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};
-\draw[->] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (90mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (100mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (110mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (50mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_4) at (60mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (70mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (80mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (90mm,120mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (70mm,180mm) {};
+\draw[->] (s_8_12.center) -- (r_8_12.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (80mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (90mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (100mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (110mm,180mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_4) at (80mm,60mm) {};
+\draw[->] (s_8_4.center) -- (r_8_4.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_4_0) at (90mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (100mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (110mm,60mm) {};
 \node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (120mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
-\draw[->] (s_0_16.center) -- (r_0_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (90mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (100mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (110mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (81mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
-\draw[->] (s_4_8.center) -- (r_4_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (110mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (120mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (130mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (140mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (150mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (160mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (101mm,45mm) {};
-\draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (101mm,255mm) {};
-\draw[->] (s_16_17.center) -- (r_16_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (110mm,300mm) {};
-\draw[->] (s_4_20.center) -- (r_4_20.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (120mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (130mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (140mm,300mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (111mm,75mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (81mm,150mm) {};
+\draw[->] (s_8_10.center) -- (r_8_10.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (91mm,135mm) {};
+\draw[->] (s_8_9.center) -- (r_8_9.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (100mm,420mm) {};
+\draw[->] (s_12_28.center) -- (r_12_28.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_28_24) at (110mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (120mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (130mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (140mm,420mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (101mm,165mm) {};
+\draw[->] (s_8_11.center) -- (r_8_11.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (101mm,210mm) {};
+\draw[->] (s_12_14.center) -- (r_12_14.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_0) at (110mm,0mm) {};
+\draw[->] (s_4_0.center) -- (r_4_0.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (120mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (130mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (140mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (150mm,0mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (111mm,90mm) {};
+\draw[->] (s_4_6.center) -- (r_4_6.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (111mm,195mm) {};
+\draw[->] (s_12_13.center) -- (r_12_13.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (121mm,75mm) {};
 \draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (111mm,270mm) {};
-\draw[->] (s_16_18.center) -- (r_16_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (121mm,90mm) {};
-\draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (121mm,285mm) {};
-\draw[->] (s_16_19.center) -- (r_16_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (130mm,180mm) {};
-\draw[->] (s_8_12.center) -- (r_8_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (160mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (131mm,315mm) {};
-\draw[->] (s_20_21.center) -- (r_20_21.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (121mm,225mm) {};
+\draw[->] (s_12_15.center) -- (r_12_15.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_24) at (130mm,360mm) {};
+\draw[->] (s_28_24.center) -- (r_28_24.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_24_8) at (140mm,360mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (150mm,360mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (160mm,360mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (170mm,360mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (131mm,450mm) {};
+\draw[->] (s_28_30.center) -- (r_28_30.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (131mm,105mm) {};
 \draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (140mm,360mm) {};
-\draw[->] (s_8_24.center) -- (r_8_24.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (150mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (160mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (170mm,360mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (141mm,330mm) {};
-\draw[->] (s_20_22.center) -- (r_20_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (150mm,420mm) {};
-\draw[->] (s_8_28.center) -- (r_8_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (160mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (170mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (180mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (151mm,345mm) {};
-\draw[->] (s_20_23.center) -- (r_20_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (151mm,135mm) {};
-\draw[->] (s_8_9.center) -- (r_8_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (161mm,150mm) {};
-\draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (161mm,375mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (140mm,240mm) {};
+\draw[->] (s_0_16.center) -- (r_0_16.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_16_20) at (150mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (160mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (170mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (180mm,240mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (141mm,435mm) {};
+\draw[->] (s_28_29.center) -- (r_28_29.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (141mm,15mm) {};
+\draw[->] (s_0_1.center) -- (r_0_1.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (151mm,30mm) {};
+\draw[->] (s_0_2.center) -- (r_0_2.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (151mm,465mm) {};
+\draw[->] (s_28_31.center) -- (r_28_31.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_8) at (160mm,120mm) {};
+\draw[->] (s_24_8.center) -- (r_24_8.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (161mm,45mm) {};
+\draw[->] (s_0_3.center) -- (r_0_3.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (161mm,390mm) {};
+\draw[->] (s_24_26.center) -- (r_24_26.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_20) at (170mm,300mm) {};
+\draw[->] (s_16_20.center) -- (r_16_20.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_20_8) at (180mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (190mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (200mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (210mm,300mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (171mm,375mm) {};
 \draw[->] (s_24_25.center) -- (r_24_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (171mm,435mm) {};
-\draw[->] (s_28_29.center) -- (r_28_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (171mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (171mm,390mm) {};
-\draw[->] (s_24_26.center) -- (r_24_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (171mm,165mm) {};
-\draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (181mm,450mm) {};
-\draw[->] (s_28_30.center) -- (r_28_30.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (171mm,255mm) {};
+\draw[->] (s_16_17.center) -- (r_16_17.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (181mm,270mm) {};
+\draw[->] (s_16_18.center) -- (r_16_18.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (181mm,405mm) {};
 \draw[->] (s_24_27.center) -- (r_24_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (191mm,465mm) {};
-\draw[->] (s_28_31.center) -- (r_28_31.center);
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (191mm,285mm) {};
+\draw[->] (s_16_19.center) -- (r_16_19.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (201mm,330mm) {};
+\draw[->] (s_20_22.center) -- (r_20_22.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_8) at (210mm,120mm) {};
+\draw[->] (s_20_8.center) -- (r_20_8.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (211mm,315mm) {};
+\draw[->] (s_20_21.center) -- (r_20_21.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (221mm,345mm) {};
+\draw[->] (s_20_23.center) -- (r_20_23.center);

### 2013-05-14 paper.tex
Fixed the include path fro a figure
Added some measurements from real hardware

@@
   \pgfsetlinewidth{.5bp}
-\input{figs/final_gruyere_hierarchical}
+\input{graphs/final_gruyere_hierarchical}
 \end{tikzpicture}
@@
 
-\stefan{These numbers are outdated. Keeping them for reference}
-
-Some numbers are listed in Table~\ref{tab:bc_measurements}.
-
-\begin{table}[htb]
+\paragraph{Binary tree on sbrinz2}
+
+Plot~\ref{pgfplot:201305101058} shows the time in cycles until a
+message send from core $n$ is received back via the broadcast tree
+show in Figure~\ref{fig:binary_tree_sbrinz2}. We were expecting
+increasing cost with the depth of the tree. If a message is sent from
+one of the leave nodes, it takes longer to receive this message back
+on the tree.
+
+The result is quite unexpected. We would expect nodes far down in the
+tree to experience a longer waiting time for receiving own messages
+back on the tree (due to more hops). This observation does not seem to
+be true.
+
+Lukas Humbel, who was also working on sbrinz1 was observing that the
+Barrelfish core IDs might not properly correspond to physical core
+IDs. This could explain the numbers we observe in our measurement.
+
+\begin{figure}[htb]
   \centering
-  \begin{tabular}{lrrrr}
-    \toprule
-    broadcast algorithm & \multicolumn{2}{c}{nos5} & \multicolumn{2}{c}{gruyere} \\
-      & cycles & error & cycles & error \\
-    \midrule
-    sequential &  4096.1 &  105.2 & 136751.9 &   3061.5 \\
-    batch      &  2408.0 &  181.9 &  57360.8 &   5271.5 \\
-    \bottomrule
-  \end{tabular}
-  \caption{Broadcast measurements}
-  \label{tab:bc_measurements}
-\end{table}
+  \includegraphics[width=\linewidth]{binary_tree_sbrinz2}
+  \caption{Binary tree for sbrinz2}
+  \label{fig:binary_tree_sbrinz2}
+\end{figure}
+
+\begin{figure}
+  \caption{Cost for receiving a message back on the tree. This is the
+    time for which the send call needs to be blocked to retain atomic
+    broadcast properties.}
+  \label{pgfplot:201305101058}
+  \begin{tikzpicture}
+    \begin{axis}[%
+        xlabel=sender core ID,%
+        ylabel={Cost [cycles]}%
+        ]
+    \addplot[%
+        color=red,%
+        mark=x,%  
+        error bars/y dir=both,%
+        error bars/y explicit%
+        ] coordinates {
+      (1,276.1) +- (291.3,291.3)
+      (2,876.1) +- (56.6,56.6)
+      (3,863.0) +- (108.3,108.3)
+      (4,899.7) +- (102.3,102.3)
+      (5,893.5) +- (44.5,44.5)
+      (6,880.5) +- (39.4,39.4)
+      (7,520.9) +- (41.7,41.7)
+      (8,171.9) +- (91.5,91.5)
+      (9,155.7) +- (51.4,51.4)
+      (10,174.6) +- (99.9,99.9)
+      (11,175.1) +- (99.3,99.3)
+      (12,154.5) +- (50.5,50.5)
+      (13,176.8) +- (109.7,109.7)
+      (14,173.1) +- (99.4,99.4)
+      (15,150.4) +- (43.3,43.3)
+    };
+    \end{axis}
+  \end{tikzpicture}
+\end{figure}
+
+\paragraph{Older numbers}
 

### 2013-05-17 paper.tex
Ooops

@@
 \subsection{Atomic broadcast}
+
+%--------------------------------------------------
+\subsubsection{Comparison to shared-memory implementations}
+
+A shared memory equivalent implementation for atomic broadcasts could
+be:
+\begin{itemize}
+\item Messages should (but don't have to be) cache-line size. This
+  prevents false-sharing. Larger messages can be fragmented. 
+\item A FIFO queue that guarantees the order of messages (and therefore
+  a lock)
+\item A counter that is incremented whenever a process reads the
+  message from the FIFO queue. To guarantee atomic broadcast
+  attributes, elements from the queue must not be removed before all
+  processes have read it.
+\end{itemize}
+
+This sounds pretty expensive. Need to evaluate this. The question is
+whether any sane person would use such a queue for high level
+applications. If so, which ones?
+
+There are some libraries providing synchronization primitives such as
+barriers, critical sections, atomic updates and locks.
+
+\begin{itemize}
+\item Is there an OpenMP equivalent? \emph{OpenMP} has a shared-memory
+  based programming model that is targeted to the HPC
+  world. \stefan{So what exactly is the relationship between OpenMP
+    and MPI? MPI seems to be more low-level. Does OpenMP implement
+    MPI?}
+\item \emph{Pthreads} also has a shared-memory model for low-end
+  systems~\cite{OpenMP_paper}
+\end{itemize}
 

### 2013-05-17 graphs/numa_model.py

@@ -1,0 +1,33 @@
+#!/usr/bin/env python
+
+import model
+import helpers
+
+from pygraph.classes.graph import graph
+
+# --------------------------------------------------
+class NUMAModel(model.Model):
+
+    def __init__(self, g):
+        super(NUMAModel, self).__init__(g)
+
+
+    def _build_numa_graph(self):
+        return None
+
+    def _build_graph(self):
+        """
+        Build a graph model for a NUMA machine
+        """
+        g_numa = self._build_numa_graph()
+        helpers.output_graph(g_numa, '%s_numa' % self.get_name())
+
+        gr = graph()
+        gr.add_nodes(range(self.get_num_cores()))
+
+        for n in range(self.get_num_numa_nodes()):
+            self._connect_numa_nodes(gr, g_numa, n)
+
+        return gr
+        
+

### 2013-05-21 paper.tex
Rewrote text about synchrony and added a list of MPI communication primitives

@@
 
-Atomic broadcast is a building-block for many higher-level distributed
-algorithm such as state-machine replication. Such distributed
-algorithms are increasingly used to overcome scalability challenges on
-multicore machines. Examples are databases~\cite{Salomie2011,
-  Wiesmann2000} and operating systems~\cite{fos:osr09, tornado:osdi99,
-  barrelfish:sosp09}.
+Distributed algorithms are increasingly used to overcome scalability
+challenges on multicore machines. Examples are
+databases~\cite{Salomie2011, Wiesmann2000} and operating
+systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}.
 
@@
 Instead of manually tuning algorithms to characteristics of individual
-machines, we automatically configure our atomic broadcast
-implementation based on a machine model. We represent this model as an
+machines, we automatically configure distributed algorithm
+implementations based on a machine model. We represent this model as an
 annotated graph. One question we are looking at is which information
@@
 % How will you go about it?
-We will base our atomic broadcast on \emph{overlay networks}, which we
+We base the configuration of algorithms on \emph{overlay networks}, which we
 automatically configure. We execute our configuration stage on a model
@@
 % Hypothesis
-Our hypothesis is that automatic tuning of atomic broadcast (and other
-distributed algorithms) to machine characteristics is worth
+Our hypothesis is that automatic tuning of distributed algorithms 
+to machine characteristics is worth
 doing. Obviously, we cannot achieve performance of hand-tuned
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Distributed algorithms}
+\label{sec:distalgo}
+
+In order to evaluate our ideas, we pick two concrete distributed
+algorithms and implement them for a multicore machine:
+
+\paragraph{Atomic broadcast} \stefan{Explain the guarantees provided
+  by atomic broadcasts}. Atomic broadcasts are frequently used to
+implement higher-level distributed algorithms on top of it: examples
+are replication such as state machine replication.
+
+\paragraph{Barriers} \stefan{Explain}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{The multicore network model}
@@
 \item[NUMA affinity] A list of cores on the same NUMA node.
-\item[synchrony] Parts of a multicore machine are synchronous, i.e.\
-  cores execute in lock-steps, where every node can send a message to
-  every other node in one such step. This implies that there is a
-  global time and message delivery time is bound. Both can be assumed
-  on today's multicores. The global time comes from the fact that
-  cores are driven by the same quartz or, if not, they are
-  synchronized such that the jitter is less than a cycle, which leads
-  to cores seeing the same time. %
-  For these reasons, synchrony is not part of our current machine
-  model. Within today's multicores, synchrony can be
-  assumed. \stefan{Can it?}
-\item[failure] Can nodes fail? If so, how? (Byzantine, crash). We do
+\item[Synchrony] Synchronous systems are characterized by two
+  attributes: First, cores execute their programs in lock-steps and
+  second that message delivery time is bound.
+  % 
+  The existence of lock-steps implies the existence of a global time.
+  This is often true on multicore machines since cores are driven by
+  the same quartz or, if not, they are synchronized such that the
+  jitter is less than a cycle, which leads to cores seeing the same
+  time. %
+  Bounded delivery time is harder to reason about. CPUs on multicores
+  are typically time-multiplexed. On such systems, several programs
+  execute on the same processing unit one at a time. A scheduler
+  decides the order in which to run these applications. In very
+  contented systems, timely receipt of messages cannot be guaranteed
+  globally for all applications since many of them compete for a CPU
+  core. Even if we could guarantee timely delivery of messages by use
+  of a deterministic scheduler, worst-case propagation times would
+  still be orders of magnitude higher than best-case propagation
+  (which is essentially zero). \stefan{gang-scheduling?}
+\item[Failure] Can nodes fail? If so, how? (Byzantine, crash). We do
   not consider failures at the moment, but believe that we will
@@
 \begin{itemize}
+\item Think about synchronous implementations and see if they are
+  applicable for some of our machines.
 \item Arguing that group communication/atomic broadcast is important
@@
   group-communication (have a list of them)
+  \begin{itemize}
+  \item MPI_Bcast: send a broadcast message to every node (including
+    the sending one)
+  \item MPI_Scatter
+  \item MPI_Gather
+  \item MPI_Reduce
+  \end{itemize}
+  These primitives are synchronous. They return only once every other
+  node received the message. 
 \item Need higher-level applications, such as:

### 2013-05-26 graphs/algorithms.py
Added code to parse measurement. Include the evaluation result (in particular the last node) to the model and the C representation

@@ -46,6 +46,13 @@ def binary_tree(m, nodes=[], out_degree=2):
 
 def simple_tree(m, nodes, coordinator):
     """
+    @deprecated Use sequential instead
+    """
+    return sequential(m, nodes, coordinator)
+
+
+def sequential(m, nodes, coordinator):
+    """
     Construct a simple two-level tree. The coordinator is the root, and all 
     the other nodes are its children
 
@@ -71,6 +78,7 @@ def simple_tree(m, nodes, coordinator):
             g.add_edge((n, coordinator), \
                            m.edge_weight((n, coordinator)))
     return g
+
 
 def merge_graphs(g1, g2):
     """
@@ -98,9 +106,3 @@ def merge_graphs(g1, g2):
         except:
             logging.info("merge_graphs: adding edge %d %d" % (e[0], e[1]))
     return g
-
-    
-
-            
-        
-    

### 2013-05-26 graphs/evaluate.py

@@ -15,6 +15,7 @@ round = 0
 event_queue = []
 model = {}
 node_state = []
+last_node = -1
 
 class NodeState(object):
     """
@@ -22,6 +23,14 @@ class NodeState(object):
     """
     def __init__(self):
         self.seq_no = 0
+
+class Result():
+    """
+    Store result of evaluation
+    """
+    def __init__(self, time, last_node):
+        self.time = time
+        self.last_node = last_node
 
 
 def evalute(tree, root, m, sched):
@@ -36,6 +45,7 @@ def evalute(tree, root, m, sched):
     global model
     global node_state
     global schedule
+    global last_node
 
     model = tree
     schedule = sched
@@ -53,7 +63,9 @@ def evalute(tree, root, m, sched):
 
     # XXX dirty hack: receive of last node is missing
     # as our nodes are homogeneous, we just add the receive time of the root
-    return round + receive_cost(root)
+    r = Result((round + receive_cost(root)), last_node)
+    m.set_evaluation_result(r)
+    return r
 
 def consume_event():
     """
@@ -86,6 +98,8 @@ def receive(src, dest):
     """
     print "{%d}: receiving message from {%d} in round %d" \
         % (dest, src, round)
+    global last_node
+    last_node = dest
     visu.receive(dest, src, round, receive_cost(dest))
     send(dest, round+receive_cost(dest), [src])
 

### 2013-05-26 graphs/helpers.py

@@ -6,11 +6,12 @@ sys.path.append('..')
 sys.path.append('/usr/lib/graphviz/python/')
 sys.path.append('/usr/lib64/graphviz/python/')
 import gv
-
 import Queue
+from numpy import *
+from datetime import *
 
 from pygraph.readwrite.dot import write
-
+from pygraph.algorithms.minmax import shortest_path
 
 def output_graph(graph, name, algorithm='neato'):
     """
@@ -33,13 +34,19 @@ def output_quorum_configuration(model, graph, root, sched):
     
     dim = model.get_num_cores()
     mat = [[0 for x in xrange(dim)] for x in xrange(dim)]
-    # for s in range(dim):
-    #     i = 1
-    #     for (cost,r) in sched.find_schedule(s):
-    #         mat[s][r] = i
-    #         i += 1
+
+    # Build the matrix
     walk_graph(graph, root, fill_matrix, mat, sched)
-    __matrix_to_c(mat)
+
+    # Determine longest path with most expensive node
+    sp = shortest_path(graph, root)[1].items()
+    sp.sort(key=lambda tup: tup[1], reverse=True)
+
+    # Generate c code
+    stream = open("model.h", "w")
+    __c_header(stream, model.evaluation.last_node)
+    __matrix_to_c(stream, mat)
+    __c_footer(stream)
 
 
 def walk_graph(graph, root, func, mat, sched):
@@ -84,21 +91,17 @@ def fill_matrix(s, children, parent, mat, sched):
         mat[s][parent] = 99
 
 
-def __matrix_to_c(mat):
+def __matrix_to_c(stream, mat):
     """
     Print given matrix as C code
     """
-#    stream = sys.stdout
-    stream = open("model.h", "w")
     dim = len(mat)
-    stream.write("#ifndef MULTICORE_MODEL\n")
-    stream.write("#define MULTICORE_MODEL 1\n\n")
     stream.write(("#define MODEL_NUM_CORES %d\n\n" % dim))
     stream.write(("int model[%d][%d] = {\n" % (dim, dim)))
     for x in range(dim):
         stream.write("    {")
         for y in range(dim):
-            stream.write("%d" % mat[x][y])
+            stream.write("%2d" % mat[x][y])
             if y+1 != dim:
                 stream.write(",")
         stream.write("}")
@@ -106,6 +109,127 @@ def __matrix_to_c(mat):
             stream.write(",")
         stream.write("\n")
     stream.write("};\n\n")
+
+
[…]

### 2013-05-26 graphs/model.py

@@ -2,6 +2,7 @@
 
 import pdb
 import logging
+import evaluate
 
 from pygraph.algorithms.minmax import shortest_path
 from pygraph.classes.graph import graph
@@ -9,6 +10,8 @@ from pygraph.classes.digraph import digraph
 
 # --------------------------------------------------
 class Model(object):
+
+    evaluation = None
 
     def __init__(self, graph):
         """
@@ -43,6 +46,17 @@ class Model(object):
         and the inner list the cores in that NUMA node.
         """
         return None
+
+    # --------------------------------------------------
+    # Results from evaluation
+    def set_evaluation_result(self, ev):
+        """
+        Save the evaluation result as part of the model. The estimated
+        cost should be part of the model
+
+        @param t Result as in evaluate.Result
+        """
+        self.evaluation = ev
 
     # --------------------------------------------------
     # Methods used for building overlay + scheduling

### 2013-05-26 graphs/run_experiments.sh

@@ -4,12 +4,13 @@ MODEL=model.h
 QDIR=$HOME/bf/quorum/usr/quorum/
 TMP=`mktemp`
 RESULTDIR=~/measurements/atomic_broadcast/
+PATTERN="Quorum.*everything done.*exiting"
 
 # check the output
 # --------------------------------------------------
 function wait_result() {
 
-    while [[ ! grep "workload_thread terminating" $TMP x]]
+    while ! grep -q "$PATTERN" $TMP
     do
 	sleep 2
     done
@@ -19,7 +20,7 @@ function wait_result() {
 # --------------------------------------------------
 for m in gruyere
 do
-    for t in cluster
+    for t in sequential
     do
 	# Cleanup 
 	rm -f $MODEL
@@ -32,7 +33,7 @@ do
 	if [[ ! -e $MODEL ]]
 	then
 	    echo "The simulator failed to find the model"
-	    return 1
+	    exit 1
 	fi
 
 	# Copy the model
@@ -42,13 +43,19 @@ do
 	ssh emmentaler2.ethz.ch emntlr_make_generic /local/skaestle/bf.quorum
 
 	# Run the machine
-	console $m >$TMP & ;; PID=$! # Start console process and get PID
-	rackboot.sh -c $m # Reboot the machine
-	wait_result() # Wait for result
+	console $m >$TMP & # Start console process .. 
+	PID=$! # .. and get PID
+	rackboot.sh $m # Reboot the machine
+	wait_result # Wait for result
+	kill $PID # Kill console process
+
+	echo "Benchmark terminating"
 
 	# Copy result
-	cp -b $TMP $RESULTDIR/${m}_${t}-`date +%Y%m%d%H%I%S`
+	cp -b $TMP $RESULTDIR/${m}_${t}
+	
+	./simulator.py --evaluate $m $t
     done
 done
 
-return 0
+exit 0

### 2013-05-26 graphs/sequential.py

@@ -1,0 +1,50 @@
+# Copyright (c) 2007, 2008, 2009, 2010, 2011, 2012, 2013 ETH Zurich.
+
+# Import graphviz
+import sys
+sys.path.append('..')
+sys.path.append('/usr/lib/graphviz/python/')
+sys.path.append('/usr/lib64/graphviz/python/')
+import gv
+import logging
+
+# Import pygraph
+from pygraph.classes.graph import graph
+from pygraph.classes.digraph import digraph
+from pygraph.algorithms.searching import breadth_first_search
+from pygraph.readwrite.dot import write
+from pygraph.algorithms.minmax import shortest_path
+from pygraph.algorithms.minmax import minimal_spanning_tree
+
+# Import own code
+import evaluate
+import model
+import helpers
+import algorithms
+import overlay
+
+class Sequential(overlay.Overlay):
+    """
+    Build a cluster topology for a model
+    """
+    
+    def __init__(self, mod):
+        """
+        Initialize the clustering algorithm
+        """
+        super(Sequential, self).__init__(mod)
+        
+    def get_broadcast_tree(self):
+        """
+        Return the broadcast tree as a graph
+        """
+
+        # Run binary tree algorithm
+        sequential = algorithms.sequential(self.mod.get_graph(),
+                                           self.mod.get_graph().nodes(),
+                                           0)
+
+        # Print graph
+        helpers.output_graph(sequential, 'sequential', 'dot')
+
+        return sequential

### 2013-05-26 graphs/simulator.py

@@ -21,6 +21,7 @@ import nos6
 import cluster
 import ring
 import binarytree
+import sequential
 
 import scheduling
 import sort_longest
@@ -54,7 +55,8 @@ def build_and_simulate():
     parser.add_argument('overlay', choices=[ "ring", 
                                              "cluster", 
                                              "mst", 
-                                             "bintree" 
+                                             "bintree",
+                                             "sequential"
                                              ],
                         help="Overlay to use for atomic broadcast")
     args = parser.parse_args()
@@ -81,6 +83,11 @@ def build_and_simulate():
         final_graph = r.get_broadcast_tree()
         root = 0
 
+    elif args.overlay == "sequential":
+        r = sequential.Sequential(m)
+        final_graph = r.get_broadcast_tree()
+        root = 0
+
     if args.action == "simulate":
         print "Starting simulation"
     elif args.action == "evaluate":
@@ -100,13 +107,13 @@ def build_and_simulate():
     sched = sort_longest.SortLongest(final_graph)
 
     # --------------------------------------------------
-    # Output c configuration for quorum program
-    helpers.output_quorum_configuration(m, final_graph, root, sched)
+    # Evaluate
+    ev = evaluate.evalute(final_graph, root, m, sched) 
+    print "Cost for tree is: %d, last node is %d" % (ev.time, ev.last_node)
 
     # --------------------------------------------------
-    # Evaluate
-    print "Cost for tree is: %d" % \
-        evaluate.evalute(final_graph, root, m, sched)
+    # Output c configuration for quorum program
+    helpers.output_quorum_configuration(m, final_graph, root, sched)
 
 
 def _run_mst(gr, model):

### 2013-06-01 paper.tex
Ooops
Added code to parse measurement. Include the evaluation result (in particular the last node) to the model and the C representation
Fibonacci

@@
 implement higher-level distributed algorithms on top of it: examples
-are replication such as state machine replication.
+are replication such as state machine replication. As a first step, we
+evaluate the performance of sending one message as a broadcast to all
+nodes. Broadcasts are one of the most important communication
+operations for parallel applications~\cite{Bruck1992} \stefan{Database
+  joins}.
 
@@
 the model representing the machine.
+
+Several optimizations are possible. First, nodes further up the tree
+should have a higher degree i.e.\ send more messages so that they do
+not idle~\cite{Bar-Noy1994}. An example of such a tree is a Fibonacci
+tree.
 
@@
   \begin{itemize}
-  \item MPI_Bcast: send a broadcast message to every node (including
+  \item MPI\_Bcast: send a broadcast message to every node (including
     the sending one)
-  \item MPI_Scatter
-  \item MPI_Gather
-  \item MPI_Reduce
+  \item MPI\_Scatter
+  \item MPI\_Gather
+  \item MPI\_Reduce
   \end{itemize}
@@
 
+\newpage
+\input{measurements/gruyere_topologies}
+\input{measurements/ziger1_topologies}
+\input{measurements/sbrinz1_topologies}
+
 \end{document}

### 2013-06-01 graphs/gottardo.py

@@ -1,0 +1,32 @@
+#!/usr/bin/env python
+
+import model
+import numa_model
+import helpers
+from pygraph.algorithms.minmax import shortest_path
+from pygraph.classes.graph import graph
+from pygraph.classes.digraph import digraph
+
+# --------------------------------------------------
+class Gottardo(numa_model.NUMAModel):
+
+    def __init__(self):
+        """
+        Build the model and use it to initialize the Model superclass
+        """
+        g = super(Gottardo, self)._build_graph()
+        super(Gottardo, self).__init__(g)
+
+    # --------------------------------------------------
+    # Characteritics of model
+    def get_name(self):
+        return "gottardo"
+
+    def get_num_numa_nodes(self):
+        return 4
+
+    def get_num_cores(self):
+        return 32 # XXX Hyperthreading still disabled?
+
+    def get_numa_information(self):
+        return super(Gottardo, self)._auto_generate_numa_information()

### 2013-06-01 graphs/helpers.py

@@ -233,23 +233,32 @@ def do_pgf_plot(f, data, caption, xlabel, ylabel):
     _pgf_plot_footer(f)
 
 
-def parse_measurement(coreids, machine, topo, f):
+def parse_measurement(f, coreids=None):
     """
     Parse the given file for measurements
     """
+
     print "parse_measurement for file %s" % f
     dic = dict()
-    for c in coreids:
-        dic[c] = []
-    for line in open(f):
+    coresfound = []
+
+    # If argument is a path (i.e. string), we need to open it
+    if isinstance(f, basestring):
+        f = open(f)
+
+    for line in f:
         if line.startswith("sk_m"):
             d = unpack_line(clear_line(line))
             assert len(d)==4
-            if d[0] in coreids:
+            if coreids == None or d[0] in coreids:
+                if not d[0] in dic:
+                    dic[d[0]] = []
                 dic[d[0]].append(d[3])
+                if not d[0] in coresfound:
+                    coresfound.append(d[0])
     result = []
     stat = []
-    for c in coreids:
+    for c in coresfound:
         l = len(dic[c])
         if l > 0:
             print "core %d, length %d" % (c, len(dic[c]))
@@ -260,11 +269,53 @@ def parse_measurement(coreids, machine, topo, f):
     return stat
 
 
-def parse_and_plot_measurements(coreids, machine, topo, f):
-    stat = parse_measurement(coreids, machine, topo, f)
+def parse_and_plot_measurement(coreids, machine, topo, f):
+    stat = parse_measurement(f, coreids)
     do_pgf_plot(open("../measurements/%s_%s.tex" % (machine, topo), "w+"), stat,
                 "Atomic broadcast on %s with %s topology" % (machine, topo), 
                 "coreid", "cost [cycles]")
-                
 
-    
+
+def _output_table_header(f):
+    f.write(("\\begin{table}[htb]\n"
+             "  \\centering\n"
+             "  \\begin{tabular}{lrrrrr}\n"
+             "  \\toprule\n"
+             "  & \\multicolumn{3}{c}{Real hardware} & \\multicolumn{2}{c}{Simulation} \\\\\n"
+             "  topology & time [cycles] & factor & stderr & time [units] & factor \\\\\n"
+             "  \\midrule\n"
+             ))
+
+
+def _output_table_footer(f, label, caption):
+    f.write(("  \\midrule\n"
+             "  \\end{tabular}\n"
+             "  \\caption{%s}\n"
[…]

### 2013-06-01 graphs/measurements.py

@@ -1,0 +1,59 @@
+#!/usr/bin/env python
+
+# Import pygraph
+from pygraph.classes.graph import graph
+from pygraph.classes.digraph import digraph
+from pygraph.algorithms.searching import breadth_first_search
+from pygraph.algorithms.minmax import shortest_path
+from pygraph.algorithms.minmax import minimal_spanning_tree
+
+# Import own code
+import evaluate
+import config
+import model
+import helpers
+
+# Machines
+import gruyere
+import nos6
+import ziger
+import sbrinz
+import gottardo
+import appenzeller
+
+# Overlays
+import cluster
+import ring
+import binarytree
+import sequential
+import badtree
+
+import scheduling
+import sort_longest
+
+import pdb
+import argparse
+import logging
+import sys
+import os
+
+# --------------------------------------------------
+def evaluate_file():
+    """
+    Build a tree model and simulate sending a message along it
+    """
+    parser = argparse.ArgumentParser(
+        description='Parse measurements for multicore machines')
+    parser.add_argument(
+        'infile', 
+        type = argparse.FileType('r'), 
+        nargs = '?', 
+        default = sys.stdin,
+        help='File to parse or stdin'
+        )
+    args = parser.parse_args()
+
+    print helpers.parse_measurement(args.infile)
+
+if __name__ == "__main__":
+    evaluate_file()

### 2013-06-01 graphs/numa_model.py

@@ -29,5 +29,38 @@ class NUMAModel(model.Model):
             self._connect_numa_nodes(gr, g_numa, n)
 
         return gr
+
+    def _auto_generate_numa_information(self):
+        res = []
+        l = []
+        for c in range(self.get_num_cores()):
+            if c % self.get_cores_per_node() == 0: 
+                if len(l)>0:
+                    res.append(l)
+                l = []
+            l.append(c)
+        assert len(l)>0
+        res.append(l)
+        return res
+
+
+    def _build_numa_graph(self):
+        """
+        Graph of NUMA nodes. This graph is used to calculate cost for
+        fully-meshed machine model.
+
+        This graph expresses the cost of sending messages between NUMA
+        nodes.
+        """
+        g_numa = graph()
+        g_numa.add_nodes(range(self.get_num_numa_nodes()))
+        for n in range(self.get_num_numa_nodes()):
+            g_numa.add_edge((n, (n+1) % self.get_num_numa_nodes()))
+
+        helpers.output_graph(g_numa, '%s_numa' % self.get_name());
+
+        return g_numa
+
+
         
 

### 2013-06-01 graphs/run_experiments.sh

@@ -10,17 +10,33 @@ PATTERN="Quorum.*everything done.*exiting"
 # --------------------------------------------------
 function wait_result() {
 
+	m=$1
+	i=0
+
+	# one iteration = 2 seconds
+	# This should terminate after 5 minutes = 300 seconds = 150 iterations
     while ! grep -q "$PATTERN" $TMP
     do
-	sleep 2
+		sleep 2
+		i=$(($i+1))
+
+		if [[ i -ge 150 ]]
+		then
+			echo "Timeout, restarting machine"
+			rackpower -r $m
+			i=0
+		fi
     done
 }
 
 # main
 # --------------------------------------------------
-for m in gruyere
+# gruyere sbrinz1
+for m in ziger1 gruyere sbrinz1 
 do
-    for t in sequential
+	# ring,cluster,mst,bintree,sequential,badtree
+	# cluster mst bintree sequential 
+    for t in badtree cluster mst bintree sequential 
     do
 	# Cleanup 
 	rm -f $MODEL
@@ -50,16 +66,19 @@ do
 	# Run the machine
 	console $m >$TMP & # Start console process .. 
 	PID=$! # .. and get PID
+	ps -p $PID
 	rackboot.sh $m # Reboot the machine
-	wait_result # Wait for result
+	wait_result $m # Wait for result
 	kill $PID # Kill console process
+	ps -p $PID
 
 	echo "Benchmark terminating"
 
 	# Copy result
 	cp -b $TMP $RESULTDIR/${m}_${t}
+	rm $TMP
 	
-	./simulator.py --evaluate $m $t
+	./simulator.py --evaluate-model $m $t
     done
 done
 

### 2013-06-01 graphs/simulator.py

@@ -16,6 +16,10 @@ import helpers
 # Machines
 import gruyere
 import nos6
+import ziger
+import sbrinz
+import gottardo
+import appenzeller
 
 # Overlays
 import cluster
@@ -33,11 +37,21 @@ import logging
 import sys
 import os
 
-def arg_machine(string):
+def arg_machine(s):
+    # Remove digits from machine name!
+    string = ''.join([i for i in s if not i.isdigit()])
     if string == "gruyere":
         return gruyere.Gruyere()
-    elif string == "nos6":
+    elif string == "nos":
         return nos6.Nos()
+    elif string == 'ziger':
+        return ziger.Ziger()
+    elif string == 'sbrinz':
+        return sbrinz.Sbrinz()
+    elif string == 'gottardo':
+        return gottardo.Gottardo()
+    elif string == 'appenzeller':
+        return appenzeller.Appenzeller()
     else:
         return None
 
@@ -54,6 +68,14 @@ def build_and_simulate():
         "sequential",
         "badtree"
         ]
+    machines = [
+        "nos6",
+        "ziger1",
+        "gruyere",
+        'sbrinz1', 'sbrinz2',
+        'gottardo',
+        'appenzeller'
+        ]
     parser = argparse.ArgumentParser(
         description='Simulator for multicore machines')
     parser.add_argument('--evaluate-model', dest="action", action="store_const",
@@ -62,15 +84,67 @@ def build_and_simulate():
     parser.add_argument('--evaluate-machine', dest="action", action="store_const",
                         const="evaluate-machine", default="simulate", 
                         help="Dump machine model instead of simulating")
-    parser.add_argument('machine', choices=['nos6', 'gruyere'],
+    parser.add_argument('machine', choices=machines,
                         help="Machine to simulate")
     parser.add_argument('overlay', choices=topologies,
                         help="Overlay to use for atomic broadcast")
     args = parser.parse_args()
 
     m = arg_machine(args.machine)
+    assert m != None
     gr = m.get_graph()
     
+    # --------------------------------------------------
+    # Switch main action
+    # XXX Cleanup required
+    if args.action == "simulate":
+        (final_graph, ev, root, sched, topology) = _simulation_wrapper(args, m, gr)
+        print "Cost for tree is: %d, last node is %d" % (ev.time, ev.last_node)
+        # Output c configuration for quorum program
+        helpers.output_quorum_configuration(m, final_graph, root, sched, topology)
+
+    elif args.action == "evaluate":
[…]

### 2013-06-01 graphs/test.py

@@ -1,0 +1,45 @@
+#!/usr/bin/env python
+
+# Import pygraph
+from pygraph.classes.graph import graph
+from pygraph.classes.digraph import digraph
+from pygraph.algorithms.searching import breadth_first_search
+from pygraph.algorithms.minmax import shortest_path
+from pygraph.algorithms.minmax import minimal_spanning_tree
+
+# Import own code
+import evaluate
+import config
+import model
+import helpers
+
+# Machines
+import gruyere
+import nos6
+
+# Overlays
+import cluster
+import ring
+import binarytree
+import sequential
+import badtree
+
+import scheduling
+import sort_longest
+
+import pdb
+import argparse
+import logging
+import sys
+import os
+
+import ziger
+
+# z = ziger.Ziger()
+# print z.get_numa_information()
+
+
+helpers.output_machine_results("testmachine", 
+                               [(100, 5), (200, 10), (300, 15)], 
+                               [(10, 5.5), (20, 10.1), (30, 12.3)]
+                               )

### 2013-06-01 graphs/ziger.py

@@ -1,0 +1,32 @@
+#!/usr/bin/env python
+
+import model
+import numa_model
+import helpers
+from pygraph.algorithms.minmax import shortest_path
+from pygraph.classes.graph import graph
+from pygraph.classes.digraph import digraph
+
+# --------------------------------------------------
+class Ziger(numa_model.NUMAModel):
+
+    def __init__(self):
+        """
+        Build the model and use it to initialize the Model superclass
+        """
+        g = super(Ziger, self)._build_graph()
+        super(Ziger, self).__init__(g)
+
+    # --------------------------------------------------
+    # Characteritics of model
+    def get_name(self):
+        return "ziger"
+
+    def get_num_numa_nodes(self):
+        return 4
+
+    def get_num_cores(self):
+        return 24
+
+    def get_numa_information(self):
+        return super(Ziger, self)._auto_generate_numa_information()

### 2013-06-03 paper.tex
First thoughts and start of implementation for Fibonacci trees

@@
 not idle~\cite{Bar-Noy1994}. An example of such a tree is a Fibonacci
-tree.
+tree, which is known to be optimal for the case that send and receive
+time are equal~\cite{Bar-Noy1994}.
+
+In contrast, we assume that the model is given, which allows us to
+simulate sending messages along the broadcast tree. Whenever a node is
+idle in the model, it will send a message to one of the cores, that
+did not receive any messages yet. For the special case that send
+equals receive time, this should also yield a Fibonacci tree.
 

### 2013-06-03 graphs/fibonacci.py

@@ -1,0 +1,59 @@
+# Copyright (c) 2007, 2008, 2009, 2010, 2011, 2012, 2013 ETH Zurich.
+
+# Import graphviz
+import sys
+sys.path.append('..')
+sys.path.append('/usr/lib/graphviz/python/')
+sys.path.append('/usr/lib64/graphviz/python/')
+import gv
+import logging
+
+# Import pygraph
+from pygraph.classes.graph import graph
+from pygraph.classes.digraph import digraph
+from pygraph.algorithms.searching import breadth_first_search
+from pygraph.readwrite.dot import write
+from pygraph.algorithms.minmax import shortest_path
+from pygraph.algorithms.minmax import minimal_spanning_tree
+
+# Import own code
+import evaluate
+import model
+import helpers
+import algorithms
+import overlay
+
+class Fibonacci(overlay.Overlay):
+    """
+    Build a cluster topology for a model
+    """
+    
+    def __init__(self, mod):
+        """
+        Initialize the clustering algorithm
+        """
+        super(Fibonacci, self).__init__(mod)
+        self.coordinators = self.get_coordinators()
+
+
+    def fibonacci(self, depth):
+        g = digraph()
+        if depth==1:
+            g.add_node(1)
+        elif depth==2:
+            g.add_node(1)
+            g.add_node(2)
+            g.add_edge((1,2))
+        else:
+            g_r = self.fibonacci(depth-1)
+            g_l = self.fibonacci(depth-2)
+            g.add_node(depth)
+            g = algorithms.merge_graphs(g_r, g_l)
+    
+
+        
+    def get_broadcast_tree(self):
+        """
+        Return the broadcast tree as a graph
+        """
+

### 2013-06-03 graphs/badtree.py
Simulator visualization is now easily and automatically appended to paper

@@ -36,7 +36,10 @@ class BadTree(overlay.Overlay):
         """
         super(BadTree, self).__init__(mod)
         
-    def get_broadcast_tree(self):
+    def get_name(self):
+        return "badtree"
+
+    def _get_broadcast_tree(self):
         """
         Return the broadcast tree as a graph
         """

### 2013-06-03 graphs/binarytree.py

@@ -34,7 +34,10 @@ class BinaryTree(overlay.Overlay):
         """
         super(BinaryTree, self).__init__(mod)
         
-    def get_broadcast_tree(self):
+    def get_name(self):
+        return "binarytree"
+
+    def _get_broadcast_tree(self):
         """
         Return the broadcast tree as a graph
         """

### 2013-06-03 graphs/cluster.py

@@ -35,7 +35,10 @@ class Cluster(overlay.Overlay):
         super(Cluster, self).__init__(mod)
         self.coordinators = self.get_coordinators()
         
-    def get_broadcast_tree(self):
+    def get_name(self):
+        return "cluster"
+
+    def _get_broadcast_tree(self):
         """
         Return the broadcast tree as a graph
         """

### 2013-06-03 graphs/draw.py

@@ -8,9 +8,10 @@ class Output():
     height_per_core = 15
 
     "Wrapper to enable visualization output to file"
-    def __init__(self, name, model):
+    def __init__(self, name, model, topo):
         self.name = name
         self.model = model
+        self.topo =  topo
         self.f = open(name, 'w')
         for i in range(self.model.get_num_cores()):
             # Background
@@ -29,6 +30,11 @@ class Output():
             self.f.write("\\draw[color=black!30] (20mm,%dmm) -- (30cm,%dmm);\n" % \
                              (self._y_coord_for_core(i), \
                                   self._y_coord_for_core(i)))
+        self.f.write("\\node at (0mm,%dmm) {Machine: %s, topology: %s};\n" % (
+                self._y_coord_for_core(self.model.get_num_cores()),
+                self.model.get_name(),
+                self.topo.get_name()
+                ))
 
     def _y_coord_for_core(self, core):
         "Determines padding between cores"
@@ -64,6 +70,7 @@ class Output():
         if isinstance(self.model, numa_model.NUMAModel):
             if not self.model.on_same_numa_node(core, sender):
                 settings.append('very thick')
+                settings.append('color=red')
         # Arrow indicating flow
         self.f.write("\\draw[->%s] (s_%d_%d.center) -- (r_%d_%d.center); \n" % \
                          (','.join(settings), sender, core, sender, core))

### 2013-06-03 graphs/evaluate.py

@@ -33,7 +33,7 @@ class Result():
         self.last_node = last_node
 
 
-def evalute(tree, root, m, sched):
+def evalute(topo, root, m, sched):
     """
     Evaluate the latency of sending an individual message along the tree
     @param tree: Overlay as determined by simulator
@@ -47,14 +47,17 @@ def evalute(tree, root, m, sched):
     global schedule
     global last_node
 
+    tree = topo.get_broadcast_tree()
     model = tree
     schedule = sched
+    round = 0
 
     node_state = [NodeState()]*len(model)
 
     # Construct visualization instance
     global visu
-    visu = draw.Output("visu.tex", m)
+    visu = draw.Output(("visu_%s_%s.tex" % (m.get_name(), topo.get_name())), 
+                       m, topo)
     
     send(root, round, [])
 

### 2013-06-03 graphs/fibonacci.py

@@ -35,6 +35,8 @@ class Fibonacci(overlay.Overlay):
         super(Fibonacci, self).__init__(mod)
         self.coordinators = self.get_coordinators()
 
+    def get_name(self):
+        return "fibonacci"
 
     def fibonacci(self, depth):
         g = digraph()
@@ -52,7 +54,7 @@ class Fibonacci(overlay.Overlay):
     
 
         
-    def get_broadcast_tree(self):
+    def _get_broadcast_tree(self):
         """
         Return the broadcast tree as a graph
         """

### 2013-06-03 graphs/overlay.py

@@ -6,16 +6,34 @@ class Overlay(object):
     """
     Base class for finding the right overlay topology for a model
     """
-
     def __init__(self, mod):
         """
         Initialize the clustering algorithm
         """
         assert isinstance(mod, model.Model)
         self.mod = mod
+        self.broadcast_tree = None
 
-    def get_broadcast_tree(self):
+    def _get_broadcast_tree(self):
         return None
+
+    def get_root_node(self):
+        return 0
+
+    def get_name(self):
+        return None
+    
+    def get_broadcast_tree(self):
+        """
+        Return broadcast tree
+        
+        Will call _get_broadcast_tree on first execution and store
+        tree in broadcast_tree
+        """
+        if self.broadcast_tree is None:
+            self.broadcast_tree = self._get_broadcast_tree()
+        assert not self.broadcast_tree is None
+        return self.broadcast_tree
 
     def get_coordinators(self):
         """

### 2013-06-03 graphs/ring.py

@@ -38,7 +38,10 @@ class Ring(overlay.Overlay):
         """
         super(Ring, self).__init__(mod)
 
-    def get_broadcast_tree(self):
+    def get_name(self):
+        return "ring"
+
+    def _get_broadcast_tree(self):
         """
         This currently only works for 8x4x1 model
         """
@@ -57,7 +60,8 @@ class Ring(overlay.Overlay):
         helpers.output_graph(g, 'ring', 'neato')
         return g
 
-
+    def get_root_node(self):
+        return 8
 
     def _get_outer_rings(self):
         """

### 2013-06-03 graphs/run_simulation.py

@@ -1,0 +1,55 @@
+#!/usr/bin/env python
+
+import simulator
+import random
+import string
+import os
+
+f = open('visall.tex', 'w+')
+
+def w(s):
+    f.write(s)
+
+def command(command, argument=None):
+    if argument is None:
+        return '\\%s' % (command)        
+    else:
+        return '\\%s{%s}' % (command, argument)
+
+def section(title, level=1):
+    d = { 1: 'section', 2: 'subsection' }
+    return command(d[level], title) + '\n\n'
+
+def tikz(content,options=[]):
+    return (
+        '\\begin{tikzpicture}[%s]\n'
+        '%s\n'
+        '\\end{tikzpicture}\n') % (','.join(options), content)
+
+def figure(content, caption='', 
+           ref=''.join(random.sample(string.ascii_letters*6,6))):
+    if not ref.startswith('fig:'):
+        ref = 'fig:%s' % ref
+    return (
+        '\\begin{figure}[h]\n'
+        '%s\n'
+        '\\caption{%s}\n'
+        '\\label{%s}\n'
+        '\\end{figure}\n') % (content, caption, ref)
+
+# --------------------------------------------------
+
+for m in simulator.machines:
+    m = ''.join([i for i in m if not i.isdigit()])
+    w(section(m))
+    for t in simulator.topologies:
+        tex = 'visu_%s_%s' % (m, t)
+        if os.path.exists(tex + '.tex'):
+            command('newpage')
+            w(section(t, 2))
+            opt = [ 'transform shape', 'scale=.25' ]
+#            w(tikz('\\input{graphs/%s}' % tex, opt))
+            w(figure(tikz('\\input{graphs/%s}' % tex, opt), 
+                     'Atomic broadcast on %s using %s topology' % (m, t),
+                     'ab_%s_%s' % (m, t)))
+            w(command('clearpage'))

### 2013-06-03 graphs/sequential.py

@@ -34,7 +34,10 @@ class Sequential(overlay.Overlay):
         """
         super(Sequential, self).__init__(mod)
         
-    def get_broadcast_tree(self):
+    def get_name(self):
+        return "sequential"
+
+    def _get_broadcast_tree(self):
         """
         Return the broadcast tree as a graph
         """

### 2013-06-03 graphs/simulator.py

@@ -5,7 +5,6 @@ from pygraph.classes.graph import graph
 from pygraph.classes.digraph import digraph
 from pygraph.algorithms.searching import breadth_first_search
 from pygraph.algorithms.minmax import shortest_path
-from pygraph.algorithms.minmax import minimal_spanning_tree
 
 # Import own code
 import evaluate
@@ -27,6 +26,7 @@ import ring
 import binarytree
 import sequential
 import badtree
+import mst
 
 import scheduling
 import sort_longest
@@ -36,6 +36,24 @@ import argparse
 import logging
 import sys
 import os
+
+topologies = [
+    "ring", 
+    "cluster", 
+    "mst", 
+    "bintree",
+    "sequential",
+    "badtree"
+    ]
+machines = [
+    "nos6",
+    "ziger1",
+    "gruyere",
+    'sbrinz1', 'sbrinz2',
+    'gottardo',
+    'appenzeller'
+    ]
+
 
 def arg_machine(s):
     # Remove digits from machine name!
@@ -60,22 +78,6 @@ def build_and_simulate():
     """
     Build a tree model and simulate sending a message along it
     """
-    topologies = [
-        "ring", 
-        "cluster", 
-        "mst", 
-        "bintree",
-        "sequential",
-        "badtree"
-        ]
-    machines = [
-        "nos6",
-        "ziger1",
-        "gruyere",
-        'sbrinz1', 'sbrinz2',
-        'gottardo',
-        'appenzeller'
-        ]
     parser = argparse.ArgumentParser(
         description='Simulator for multicore machines')
     parser.add_argument('--evaluate-model', dest="action", action="store_const",
@@ -98,7 +100,8 @@ def build_and_simulate():
     # Switch main action
     # XXX Cleanup required
     if args.action == "simulate":
-        (final_graph, ev, root, sched, topology) = _simulation_wrapper(args, m, gr)
+        (topo, ev, root, sched, topology) = _simulation_wrapper(args, m, gr)
+        final_graph = topo.get_broadcast_tree()
         print "Cost for tree is: %d, last node is %d" % (ev.time, ev.last_node)
         # Output c configuration for quorum program
         helpers.output_quorum_configuration(m, final_graph, root, sched, topology)
@@ -125,7 +128,8 @@ def build_and_simulate():
             assert len(stat) == 1 # Only measurements for one core
             results.append((t, stat[0][1], stat[0][2]))
             # XXX Simulation
[…]

### 2013-06-04 paper.tex
Simulator visualization is now easily and automatically appended to paper
Added forgotten file

@@
 
+\newcommand{\nary}{$n$-ary\xspace}
+
 \begin{itemize}
+\item Other topologies (mainly based on~\cite{Bruck1992}):
+  \begin{itemize}
+  \item Fibonacci trees: more efficient since nodes further up the
+    tree send more messages, but not considering the hierarchy of the
+    machine 
+  \item \nary trees: play with the out-degree of nodes. The ideal
+    value for the out-degree depends on the machine. For
+    $t_{propagation} << max(t_{send}, t_{receive})$, $n = 2$ should be
+    optimal, since it still increases parallelism, but the latency
+    induced by the $n$ send operation is not too high.
+  \end{itemize}
 \item Think about synchronous implementations and see if they are
@@
 
+\input{graphs/visall}
+
 \end{document}

### 2013-06-04 graphs/visu_gruyere_badtree.tex
Added forgotten file

\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
\node at (0mm,0mm) {core 00};
\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
\node at (0mm,15mm) {core 01};
\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
\node at (0mm,30mm) {core 02};
\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
\node at (0mm,45mm) {core 03};
\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
\node at (0mm,60mm) {core 04};
\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
\node at (0mm,75mm) {core 05};
\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
\node at (0mm,90mm) {core 06};
\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
\node at (0mm,105mm) {core 07};
\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
\node at (0mm,120mm) {core 08};
\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
\node at (0mm,135mm) {core 09};
\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
\node at (0mm,150mm) {core 10};
\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
\node at (0mm,165mm) {core 11};
\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
\node at (0mm,180mm) {core 12};
\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
\node at (0mm,195mm) {core 13};
\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
\node at (0mm,210mm) {core 14};
\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
\node at (0mm,225mm) {core 15};
\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
\node at (0mm,240mm) {core 16};
\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
\node at (0mm,255mm) {core 17};
\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
\node at (0mm,270mm) {core 18};
\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
\node at (0mm,285mm) {core 19};
\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
\node at (0mm,300mm) {core 20};
\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
\node at (0mm,315mm) {core 21};
\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
\node at (0mm,330mm) {core 22};
\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
\node at (0mm,345mm) {core 23};
\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
\node at (0mm,360mm) {core 24};
\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
\node at (0mm,375mm) {core 25};
\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
\node at (0mm,390mm) {core 26};
\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
\node at (0mm,405mm) {core 27};
\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
\node at (0mm,420mm) {core 28};
\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
\node at (0mm,435mm) {core 29};
\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
\node at (0mm,450mm) {core 30};
\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
\node at (0mm,465mm) {core 31};
\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
\node at (0mm,480mm) {Machine: gruyere, topology: badtree};
\node[draw,fill=red!20,minimum size=10mm] (s_0_14) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_28) at (60mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_14) at (90mm,210mm) {};
\draw[->,very thick,color=red] (s_0_14.center) -- (r_0_14.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_14_1) at (100mm,210mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_14_19) at (110mm,210mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_28) at (100mm,420mm) {};
\draw[->,very thick,color=red] (s_0_28.center) -- (r_0_28.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_28_3) at (110mm,420mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_28_17) at (120mm,420mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_14_1) at (140mm,15mm) {};
\draw[->,very thick,color=red] (s_14_1.center) -- (r_14_1.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_1_27) at (150mm,15mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_1_15) at (160mm,15mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_14_19) at (150mm,285mm) {};
\draw[->,very thick,color=red] (s_14_19.center) -- (r_14_19.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_19_13) at (160mm,285mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_19_9) at (170mm,285mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_3) at (150mm,45mm) {};
\draw[->,very thick,color=red] (s_28_3.center) -- (r_28_3.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_3_26) at (160mm,45mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_3_25) at (170mm,45mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_28_17) at (160mm,255mm) {};
\draw[->,very thick,color=red] (s_28_17.center) -- (r_28_17.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_17_29) at (170mm,255mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_17_12) at (180mm,255mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_27) at (190mm,405mm) {};
\draw[->,very thick,color=red] (s_1_27.center) -- (r_1_27.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_27_2) at (200mm,405mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_27_6) at (210mm,405mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_26) at (200mm,390mm) {};
\draw[->,very thick,color=red] (s_3_26.center) -- (r_3_26.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_26_5) at (210mm,390mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_19_13) at (200mm,195mm) {};
\draw[->,very thick,color=red] (s_19_13.center) -- (r_19_13.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_13_21) at (210mm,195mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_13_20) at (220mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_1_15) at (200mm,225mm) {};
\draw[->,very thick,color=red] (s_1_15.center) -- (r_1_15.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_15_18) at (210mm,225mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_15_16) at (220mm,225mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_25) at (210mm,375mm) {};
\draw[->,very thick,color=red] (s_3_25.center) -- (r_3_25.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_25_7) at (220mm,375mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_25_4) at (230mm,375mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_19_9) at (210mm,135mm) {};
\draw[->,very thick,color=red] (s_19_9.center) -- (r_19_9.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_9_23) at (220mm,135mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_9_22) at (230mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_17_29) at (210mm,435mm) {};
\draw[->,very thick,color=red] (s_17_29.center) -- (r_17_29.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_17_12) at (220mm,180mm) {};
\draw[->,very thick,color=red] (s_17_12.center) -- (r_17_12.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_27_2) at (240mm,30mm) {};
\draw[->,very thick,color=red] (s_27_2.center) -- (r_27_2.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_2_30) at (250mm,30mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_2_24) at (260mm,30mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_26_5) at (240mm,75mm) {};
\draw[->,very thick,color=red] (s_26_5.center) -- (r_26_5.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_27_6) at (240mm,90mm) {};
\draw[->,very thick,color=red] (s_27_6.center) -- (r_27_6.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_21) at (240mm,315mm) {};
\draw[->,very thick,color=red] (s_13_21.center) -- (r_13_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_13_20) at (250mm,300mm) {};
\draw[->,very thick,color=red] (s_13_20.center) -- (r_13_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_15_18) at (250mm,270mm) {};
\draw[->,very thick,color=red] (s_15_18.center) -- (r_15_18.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_18_10) at (260mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_8) at (270mm,270mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_25_7) at (250mm,105mm) {};
\draw[->,very thick,color=red] (s_25_7.center) -- (r_25_7.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_23) at (250mm,345mm) {};
\draw[->,very thick,color=red] (s_9_23.center) -- (r_9_23.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_22) at (260mm,330mm) {};
\draw[->,very thick,color=red] (s_9_22.center) -- (r_9_22.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_25_4) at (260mm,60mm) {};
\draw[->,very thick,color=red] (s_25_4.center) -- (r_25_4.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_15_16) at (260mm,240mm) {};
\draw[->,very thick,color=red] (s_15_16.center) -- (r_15_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_31) at (270mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_11) at (280mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_30) at (290mm,450mm) {};
\draw[->,very thick,color=red] (s_2_30.center) -- (r_2_30.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_2_24) at (300mm,360mm) {};
\draw[->,very thick,color=red] (s_2_24.center) -- (r_2_24.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_18_10) at (300mm,150mm) {};
\draw[->,very thick,color=red] (s_18_10.center) -- (r_18_10.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_18_8) at (310mm,120mm) {};
\draw[->,very thick,color=red] (s_18_8.center) -- (r_18_8.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_31) at (310mm,465mm) {};
\draw[->,very thick,color=red] (s_16_31.center) -- (r_16_31.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_16_11) at (320mm,165mm) {};
\draw[->,very thick,color=red] (s_16_11.center) -- (r_16_11.center);

### 2013-06-04 graphs/visu_gruyere_binarytree.tex
Added forgotten file

--- 2013-06-04 graphs/visu_gruyere_badtree.tex
@@
 \draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: badtree};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_14) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_28) at (60mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_14) at (90mm,210mm) {};
-\draw[->,very thick,color=red] (s_0_14.center) -- (r_0_14.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_14_1) at (100mm,210mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_14_19) at (110mm,210mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_28) at (100mm,420mm) {};
-\draw[->,very thick,color=red] (s_0_28.center) -- (r_0_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_3) at (110mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_17) at (120mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_1) at (140mm,15mm) {};
-\draw[->,very thick,color=red] (s_14_1.center) -- (r_14_1.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_1_27) at (150mm,15mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_1_15) at (160mm,15mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_19) at (150mm,285mm) {};
-\draw[->,very thick,color=red] (s_14_19.center) -- (r_14_19.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_19_13) at (160mm,285mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_19_9) at (170mm,285mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_3) at (150mm,45mm) {};
-\draw[->,very thick,color=red] (s_28_3.center) -- (r_28_3.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_3_26) at (160mm,45mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_3_25) at (170mm,45mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_17) at (160mm,255mm) {};
-\draw[->,very thick,color=red] (s_28_17.center) -- (r_28_17.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_17_29) at (170mm,255mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_17_12) at (180mm,255mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_27) at (190mm,405mm) {};
-\draw[->,very thick,color=red] (s_1_27.center) -- (r_1_27.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_27_2) at (200mm,405mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_27_6) at (210mm,405mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_26) at (200mm,390mm) {};
-\draw[->,very thick,color=red] (s_3_26.center) -- (r_3_26.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_26_5) at (210mm,390mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_19_13) at (200mm,195mm) {};
-\draw[->,very thick,color=red] (s_19_13.center) -- (r_19_13.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_13_21) at (210mm,195mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_13_20) at (220mm,195mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_15) at (200mm,225mm) {};
-\draw[->,very thick,color=red] (s_1_15.center) -- (r_1_15.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_15_18) at (210mm,225mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_15_16) at (220mm,225mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_25) at (210mm,375mm) {};
-\draw[->,very thick,color=red] (s_3_25.center) -- (r_3_25.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_25_7) at (220mm,375mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_25_4) at (230mm,375mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_19_9) at (210mm,135mm) {};
-\draw[->,very thick,color=red] (s_19_9.center) -- (r_19_9.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_9_23) at (220mm,135mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_9_22) at (230mm,135mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_17_29) at (210mm,435mm) {};
-\draw[->,very thick,color=red] (s_17_29.center) -- (r_17_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_17_12) at (220mm,180mm) {};
-\draw[->,very thick,color=red] (s_17_12.center) -- (r_17_12.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_27_2) at (240mm,30mm) {};
-\draw[->,very thick,color=red] (s_27_2.center) -- (r_27_2.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_2_30) at (250mm,30mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_2_24) at (260mm,30mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_26_5) at (240mm,75mm) {};
-\draw[->,very thick,color=red] (s_26_5.center) -- (r_26_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_27_6) at (240mm,90mm) {};
-\draw[->,very thick,color=red] (s_27_6.center) -- (r_27_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_21) at (240mm,315mm) {};
-\draw[->,very thick,color=red] (s_13_21.center) -- (r_13_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_20) at (250mm,300mm) {};
-\draw[->,very thick,color=red] (s_13_20.center) -- (r_13_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_15_18) at (250mm,270mm) {};
-\draw[->,very thick,color=red] (s_15_18.center) -- (r_15_18.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_18_10) at (260mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_8) at (270mm,270mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_25_7) at (250mm,105mm) {};
-\draw[->,very thick,color=red] (s_25_7.center) -- (r_25_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_23) at (250mm,345mm) {};
-\draw[->,very thick,color=red] (s_9_23.center) -- (r_9_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_22) at (260mm,330mm) {};
-\draw[->,very thick,color=red] (s_9_22.center) -- (r_9_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_25_4) at (260mm,60mm) {};
-\draw[->,very thick,color=red] (s_25_4.center) -- (r_25_4.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_15_16) at (260mm,240mm) {};
-\draw[->,very thick,color=red] (s_15_16.center) -- (r_15_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_31) at (270mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_11) at (280mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_30) at (290mm,450mm) {};
-\draw[->,very thick,color=red] (s_2_30.center) -- (r_2_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_24) at (300mm,360mm) {};
-\draw[->,very thick,color=red] (s_2_24.center) -- (r_2_24.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_10) at (300mm,150mm) {};
-\draw[->,very thick,color=red] (s_18_10.center) -- (r_18_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_8) at (310mm,120mm) {};
-\draw[->,very thick,color=red] (s_18_8.center) -- (r_18_8.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_31) at (310mm,465mm) {};
-\draw[->,very thick,color=red] (s_16_31.center) -- (r_16_31.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_11) at (320mm,165mm) {};
-\draw[->,very thick,color=red] (s_16_11.center) -- (r_16_11.center);
+\node at (0mm,480mm) {Machine: gruyere, topology: binarytree};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (60mm,0mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (61mm,15mm) {};
+\draw[->] (s_0_1.center) -- (r_0_1.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (71mm,15mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_1_4) at (81mm,15mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (71mm,30mm) {};
+\draw[->] (s_0_2.center) -- (r_0_2.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (91mm,30mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (82mm,45mm) {};
+\draw[->] (s_1_3.center) -- (r_1_3.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (92mm,45mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (102mm,45mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (101mm,60mm) {};
+\draw[->,very thick,color=red] (s_1_4.center) -- (r_1_4.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (111mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (121mm,60mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
+\draw[->,very thick,color=red] (s_2_6.center) -- (r_2_6.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_6_14) at (111mm,90mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (111mm,75mm) {};
+\draw[->,very thick,color=red] (s_2_5.center) -- (r_2_5.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (121mm,75mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (131mm,75mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (122mm,105mm) {};
+\draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (132mm,105mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (142mm,105mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (122mm,120mm) {};
+\draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (132mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (142mm,120mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (131mm,135mm) {};
+\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (141mm,135mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (151mm,135mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (141mm,210mm) {};
+\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_14_30) at (151mm,210mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_14_29) at (161mm,210mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (141mm,150mm) {};
+\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (151mm,150mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (161mm,150mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (151mm,195mm) {};
+\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_13_28) at (161mm,195mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_13_27) at (171mm,195mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (151mm,165mm) {};
+\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (161mm,165mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_11_24) at (171mm,165mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (151mm,180mm) {};
+\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_12_26) at (161mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_25) at (171mm,180mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (162mm,225mm) {};
+\draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_15_31) at (172mm,225mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_14_30) at (171mm,450mm) {};
+\draw[->,very thick,color=red] (s_14_30.center) -- (r_14_30.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
+\draw[->,very thick,color=red] (s_7_16.center) -- (r_7_16.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_18) at (172mm,270mm) {};
+\draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (181mm,285mm) {};
+\draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (181mm,300mm) {};
+\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_13_28) at (181mm,420mm) {};
+\draw[->,very thick,color=red] (s_13_28.center) -- (r_13_28.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (181mm,330mm) {};
+\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_26) at (181mm,390mm) {};
+\draw[->,very thick,color=red] (s_12_26.center) -- (r_12_26.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_14_29) at (181mm,435mm) {};
+\draw[->,very thick,color=red] (s_14_29.center) -- (r_14_29.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (182mm,255mm) {};
+\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_13_27) at (191mm,405mm) {};
+\draw[->,very thick,color=red] (s_13_27.center) -- (r_13_27.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_25) at (191mm,375mm) {};
+\draw[->,very thick,color=red] (s_12_25.center) -- (r_12_25.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_11_24) at (191mm,360mm) {};
+\draw[->,very thick,color=red] (s_11_24.center) -- (r_11_24.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (191mm,345mm) {};
+\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (191mm,315mm) {};
+\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_15_31) at (192mm,465mm) {};
+\draw[->,very thick,color=red] (s_15_31.center) -- (r_15_31.center);

### 2013-06-04 graphs/visu_gruyere_cluster.tex
Added forgotten file

--- 2013-06-04 graphs/visu_gruyere_binarytree.tex
@@
 \draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: binarytree};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (60mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (61mm,15mm) {};
+\node at (0mm,480mm) {Machine: gruyere, topology: cluster};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (50mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (60mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (80mm,60mm) {};
+\draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (90mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_16) at (100mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (110mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (130mm,60mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
+\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (90mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (100mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (110mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (120mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (130mm,120mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
+\draw[->] (s_0_3.center) -- (r_0_3.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
+\draw[->] (s_0_2.center) -- (r_0_2.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
 \draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (71mm,15mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_1_4) at (81mm,15mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (71mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (91mm,30mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (82mm,45mm) {};
-\draw[->] (s_1_3.center) -- (r_1_3.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (92mm,45mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (102mm,45mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (101mm,60mm) {};
-\draw[->,very thick,color=red] (s_1_4.center) -- (r_1_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (111mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (121mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
-\draw[->,very thick,color=red] (s_2_6.center) -- (r_2_6.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_6_14) at (111mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (111mm,75mm) {};
-\draw[->,very thick,color=red] (s_2_5.center) -- (r_2_5.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (121mm,75mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (131mm,75mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (122mm,105mm) {};
-\draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (132mm,105mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (142mm,105mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (122mm,120mm) {};
-\draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (132mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (142mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (131mm,135mm) {};
-\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (141mm,135mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (151mm,135mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (141mm,210mm) {};
-\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_14_30) at (151mm,210mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_14_29) at (161mm,210mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (141mm,150mm) {};
-\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (151mm,150mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (161mm,150mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (151mm,195mm) {};
-\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_13_28) at (161mm,195mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_13_27) at (171mm,195mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (151mm,165mm) {};
-\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (161mm,165mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_11_24) at (171mm,165mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (151mm,180mm) {};
-\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_26) at (161mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_25) at (171mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (162mm,225mm) {};
-\draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_15_31) at (172mm,225mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_30) at (171mm,450mm) {};
-\draw[->,very thick,color=red] (s_14_30.center) -- (r_14_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
-\draw[->,very thick,color=red] (s_7_16.center) -- (r_7_16.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_18) at (172mm,270mm) {};
-\draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (181mm,285mm) {};
-\draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (181mm,300mm) {};
-\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_28) at (181mm,420mm) {};
-\draw[->,very thick,color=red] (s_13_28.center) -- (r_13_28.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (181mm,330mm) {};
-\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_26) at (181mm,390mm) {};
-\draw[->,very thick,color=red] (s_12_26.center) -- (r_12_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_29) at (181mm,435mm) {};
-\draw[->,very thick,color=red] (s_14_29.center) -- (r_14_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (182mm,255mm) {};
-\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_27) at (191mm,405mm) {};
-\draw[->,very thick,color=red] (s_13_27.center) -- (r_13_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_25) at (191mm,375mm) {};
-\draw[->,very thick,color=red] (s_12_25.center) -- (r_12_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_11_24) at (191mm,360mm) {};
-\draw[->,very thick,color=red] (s_11_24.center) -- (r_11_24.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (191mm,345mm) {};
-\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (191mm,315mm) {};
-\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_15_31) at (192mm,465mm) {};
-\draw[->,very thick,color=red] (s_15_31.center) -- (r_15_31.center);
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (120mm,360mm) {};
+\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (130mm,360mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (140mm,360mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (150mm,360mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (120mm,180mm) {};
+\draw[->,very thick,color=red] (s_4_12.center) -- (r_4_12.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (130mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (140mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (160mm,180mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (120mm,300mm) {};
+\draw[->,very thick,color=red] (s_8_20.center) -- (r_8_20.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (130mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (140mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (150mm,300mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (121mm,165mm) {};
+\draw[->] (s_8_11.center) -- (r_8_11.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (121mm,105mm) {};
+\draw[->] (s_4_7.center) -- (r_4_7.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_16) at (130mm,240mm) {};
+\draw[->,very thick,color=red] (s_4_16.center) -- (r_4_16.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (140mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (150mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (160mm,240mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (131mm,150mm) {};
+\draw[->] (s_8_10.center) -- (r_8_10.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (131mm,90mm) {};
+\draw[->] (s_4_6.center) -- (r_4_6.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (141mm,75mm) {};
+\draw[->] (s_4_5.center) -- (r_4_5.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (141mm,405mm) {};
+\draw[->] (s_24_27.center) -- (r_24_27.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (141mm,135mm) {};
+\draw[->] (s_8_9.center) -- (r_8_9.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (141mm,345mm) {};
+\draw[->] (s_20_23.center) -- (r_20_23.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (150mm,420mm) {};
+\draw[->,very thick,color=red] (s_12_28.center) -- (r_12_28.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (160mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (170mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (180mm,420mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (151mm,330mm) {};
+\draw[->] (s_20_22.center) -- (r_20_22.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (151mm,225mm) {};
+\draw[->] (s_12_15.center) -- (r_12_15.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (151mm,285mm) {};
+\draw[->] (s_16_19.center) -- (r_16_19.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (151mm,390mm) {};
+\draw[->] (s_24_26.center) -- (r_24_26.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (161mm,315mm) {};
+\draw[->] (s_20_21.center) -- (r_20_21.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (161mm,270mm) {};
+\draw[->] (s_16_18.center) -- (r_16_18.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (161mm,375mm) {};
+\draw[->] (s_24_25.center) -- (r_24_25.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};
+\draw[->] (s_12_14.center) -- (r_12_14.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (171mm,255mm) {};
+\draw[->] (s_16_17.center) -- (r_16_17.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (171mm,465mm) {};
+\draw[->] (s_28_31.center) -- (r_28_31.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (171mm,195mm) {};
+\draw[->] (s_12_13.center) -- (r_12_13.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (181mm,450mm) {};
+\draw[->] (s_28_30.center) -- (r_28_30.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (191mm,435mm) {};
+\draw[->] (s_28_29.center) -- (r_28_29.center);

### 2013-06-04 graphs/visu_gruyere_mst.tex
Added forgotten file

--- 2013-06-04 graphs/visu_gruyere_cluster.tex
@@
 \draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: cluster};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (60mm,0mm) {};
+\node at (0mm,480mm) {Machine: gruyere, topology: mst};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
 \node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
@@
 \node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (80mm,60mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};
 \draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (90mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_16) at (100mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (110mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (130mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
-\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (90mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (100mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (110mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (120mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (130mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (90mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (100mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (110mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (120mm,60mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
+\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (90mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (100mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (110mm,240mm) {};
 \node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
@@
 \draw[->] (s_0_2.center) -- (r_0_2.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
+\draw[->,very thick,color=red] (s_4_8.center) -- (r_4_8.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (110mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (120mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (130mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (140mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (150mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (160mm,120mm) {};
 \node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
 \draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (120mm,360mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (101mm,285mm) {};
+\draw[->] (s_16_19.center) -- (r_16_19.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (110mm,300mm) {};
+\draw[->,very thick,color=red] (s_4_20.center) -- (r_4_20.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (120mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (130mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (140mm,300mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (111mm,105mm) {};
+\draw[->] (s_4_7.center) -- (r_4_7.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (111mm,270mm) {};
+\draw[->] (s_16_18.center) -- (r_16_18.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (121mm,255mm) {};
+\draw[->] (s_16_17.center) -- (r_16_17.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (121mm,90mm) {};
+\draw[->] (s_4_6.center) -- (r_4_6.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (130mm,420mm) {};
+\draw[->,very thick,color=red] (s_8_28.center) -- (r_8_28.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (140mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (150mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (160mm,420mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (131mm,345mm) {};
+\draw[->] (s_20_23.center) -- (r_20_23.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (131mm,75mm) {};
+\draw[->] (s_4_5.center) -- (r_4_5.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (140mm,360mm) {};
 \draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (130mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (140mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (150mm,360mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (120mm,180mm) {};
-\draw[->,very thick,color=red] (s_4_12.center) -- (r_4_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (130mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (140mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (160mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (120mm,300mm) {};
-\draw[->,very thick,color=red] (s_8_20.center) -- (r_8_20.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (130mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (140mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (150mm,300mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (121mm,165mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (150mm,360mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (160mm,360mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (170mm,360mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (141mm,330mm) {};
+\draw[->] (s_20_22.center) -- (r_20_22.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (150mm,180mm) {};
+\draw[->,very thick,color=red] (s_8_12.center) -- (r_8_12.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (160mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (170mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (180mm,180mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (151mm,165mm) {};
 \draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (121mm,105mm) {};
-\draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_16) at (130mm,240mm) {};
-\draw[->,very thick,color=red] (s_4_16.center) -- (r_4_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (140mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (150mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (160mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (131mm,150mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (151mm,465mm) {};
+\draw[->] (s_28_31.center) -- (r_28_31.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (151mm,315mm) {};
+\draw[->] (s_20_21.center) -- (r_20_21.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (161mm,450mm) {};
+\draw[->] (s_28_30.center) -- (r_28_30.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (161mm,405mm) {};
+\draw[->] (s_24_27.center) -- (r_24_27.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (161mm,150mm) {};
 \draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (131mm,90mm) {};
-\draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (141mm,75mm) {};
-\draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (141mm,405mm) {};
-\draw[->] (s_24_27.center) -- (r_24_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (141mm,135mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (171mm,225mm) {};
+\draw[->] (s_12_15.center) -- (r_12_15.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (171mm,390mm) {};
+\draw[->] (s_24_26.center) -- (r_24_26.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (171mm,435mm) {};
+\draw[->] (s_28_29.center) -- (r_28_29.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (171mm,135mm) {};
 \draw[->] (s_8_9.center) -- (r_8_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (141mm,345mm) {};
-\draw[->] (s_20_23.center) -- (r_20_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (150mm,420mm) {};
-\draw[->,very thick,color=red] (s_12_28.center) -- (r_12_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (160mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (170mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (180mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (151mm,330mm) {};
-\draw[->] (s_20_22.center) -- (r_20_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (151mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (151mm,285mm) {};
-\draw[->] (s_16_19.center) -- (r_16_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (151mm,390mm) {};
-\draw[->] (s_24_26.center) -- (r_24_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (161mm,315mm) {};
-\draw[->] (s_20_21.center) -- (r_20_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (161mm,270mm) {};
-\draw[->] (s_16_18.center) -- (r_16_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (161mm,375mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (181mm,210mm) {};
+\draw[->] (s_12_14.center) -- (r_12_14.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (181mm,375mm) {};
 \draw[->] (s_24_25.center) -- (r_24_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (171mm,255mm) {};
-\draw[->] (s_16_17.center) -- (r_16_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (171mm,465mm) {};
-\draw[->] (s_28_31.center) -- (r_28_31.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (171mm,195mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (191mm,195mm) {};
 \draw[->] (s_12_13.center) -- (r_12_13.center);
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (181mm,450mm) {};
-\draw[->] (s_28_30.center) -- (r_28_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (191mm,435mm) {};
-\draw[->] (s_28_29.center) -- (r_28_29.center);

### 2013-06-04 graphs/visu_gruyere_ring.tex
Added forgotten file

--- 2013-06-04 graphs/visu_gruyere_mst.tex
@@
 \draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: mst};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};
-\draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (90mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (100mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (110mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (120mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
+\node at (0mm,480mm) {Machine: gruyere, topology: ring};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_4) at (50mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (60mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (70mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (80mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (90mm,120mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_4) at (70mm,60mm) {};
+\draw[->,very thick,color=red] (s_8_4.center) -- (r_8_4.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_4_0) at (80mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (90mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (100mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (110mm,60mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (80mm,180mm) {};
+\draw[->,very thick,color=red] (s_8_12.center) -- (r_8_12.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (90mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (100mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (110mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (120mm,180mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (81mm,165mm) {};
+\draw[->] (s_8_11.center) -- (r_8_11.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (91mm,150mm) {};
+\draw[->] (s_8_10.center) -- (r_8_10.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_0) at (100mm,0mm) {};
+\draw[->,very thick,color=red] (s_4_0.center) -- (r_4_0.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (110mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (120mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (130mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (140mm,0mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (101mm,105mm) {};
+\draw[->] (s_4_7.center) -- (r_4_7.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (101mm,135mm) {};
+\draw[->] (s_8_9.center) -- (r_8_9.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (110mm,420mm) {};
+\draw[->,very thick,color=red] (s_12_28.center) -- (r_12_28.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_28_24) at (120mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (130mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (140mm,420mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (150mm,420mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (111mm,225mm) {};
+\draw[->] (s_12_15.center) -- (r_12_15.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (111mm,90mm) {};
+\draw[->] (s_4_6.center) -- (r_4_6.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (121mm,75mm) {};
+\draw[->] (s_4_5.center) -- (r_4_5.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (121mm,210mm) {};
+\draw[->] (s_12_14.center) -- (r_12_14.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (130mm,240mm) {};
 \draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (90mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (100mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (110mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_20) at (140mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (150mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (160mm,240mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (170mm,240mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (131mm,195mm) {};
+\draw[->] (s_12_13.center) -- (r_12_13.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (131mm,45mm) {};
 \draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_24) at (140mm,360mm) {};
+\draw[->,very thick,color=red] (s_28_24.center) -- (r_28_24.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_24_8) at (150mm,360mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (160mm,360mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (170mm,360mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (180mm,360mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (141mm,30mm) {};
 \draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
-\draw[->,very thick,color=red] (s_4_8.center) -- (r_4_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (110mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (120mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (130mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (140mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (150mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (160mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (141mm,465mm) {};
+\draw[->] (s_28_31.center) -- (r_28_31.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (151mm,450mm) {};
+\draw[->] (s_28_30.center) -- (r_28_30.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (151mm,15mm) {};
 \draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (101mm,285mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_20) at (160mm,300mm) {};
+\draw[->,very thick,color=red] (s_16_20.center) -- (r_16_20.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_20_8) at (170mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (180mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (190mm,300mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (200mm,300mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (161mm,435mm) {};
+\draw[->] (s_28_29.center) -- (r_28_29.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (161mm,285mm) {};
 \draw[->] (s_16_19.center) -- (r_16_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (110mm,300mm) {};
-\draw[->,very thick,color=red] (s_4_20.center) -- (r_4_20.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (120mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (130mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (140mm,300mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (111mm,105mm) {};
-\draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (111mm,270mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_8) at (170mm,120mm) {};
+\draw[->,very thick,color=red] (s_24_8.center) -- (r_24_8.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (171mm,405mm) {};
+\draw[->] (s_24_27.center) -- (r_24_27.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (171mm,270mm) {};
 \draw[->] (s_16_18.center) -- (r_16_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (121mm,255mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (181mm,255mm) {};
 \draw[->] (s_16_17.center) -- (r_16_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (121mm,90mm) {};
-\draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (130mm,420mm) {};
-\draw[->,very thick,color=red] (s_8_28.center) -- (r_8_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (140mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (150mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (160mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (131mm,345mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (181mm,390mm) {};
+\draw[->] (s_24_26.center) -- (r_24_26.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (191mm,375mm) {};
+\draw[->] (s_24_25.center) -- (r_24_25.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (191mm,345mm) {};
 \draw[->] (s_20_23.center) -- (r_20_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (131mm,75mm) {};
-\draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (140mm,360mm) {};
-\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (150mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (160mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (170mm,360mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (141mm,330mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_8) at (200mm,120mm) {};
+\draw[->,very thick,color=red] (s_20_8.center) -- (r_20_8.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (201mm,330mm) {};
 \draw[->] (s_20_22.center) -- (r_20_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (150mm,180mm) {};
-\draw[->,very thick,color=red] (s_8_12.center) -- (r_8_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (160mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (170mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (180mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (151mm,165mm) {};
-\draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (151mm,465mm) {};
-\draw[->] (s_28_31.center) -- (r_28_31.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (151mm,315mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (211mm,315mm) {};
 \draw[->] (s_20_21.center) -- (r_20_21.center);
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (161mm,450mm) {};
-\draw[->] (s_28_30.center) -- (r_28_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (161mm,405mm) {};
-\draw[->] (s_24_27.center) -- (r_24_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (161mm,150mm) {};
-\draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (171mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (171mm,390mm) {};
-\draw[->] (s_24_26.center) -- (r_24_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (171mm,435mm) {};
-\draw[->] (s_28_29.center) -- (r_28_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (171mm,135mm) {};
-\draw[->] (s_8_9.center) -- (r_8_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (181mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (181mm,375mm) {};
-\draw[->] (s_24_25.center) -- (r_24_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (191mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center);

### 2013-06-04 graphs/visu_gruyere_sequential.tex
Added forgotten file

--- 2013-06-04 graphs/visu_gruyere_mst.tex
@@
 \draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: mst};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};
+\node at (0mm,480mm) {Machine: gruyere, topology: sequential};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_31) at (50mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_30) at (60mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_29) at (70mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_28) at (80mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_27) at (90mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_26) at (100mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_25) at (110mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_24) at (120mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_15) at (130mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_14) at (140mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_13) at (150mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (160mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_23) at (170mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_22) at (180mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_21) at (190mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_20) at (200mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_11) at (210mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_10) at (220mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_9) at (230mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (240mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_19) at (250mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (260mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_17) at (270mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (280mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_7) at (290mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_6) at (300mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (310mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (320mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (330mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (340mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (350mm,0mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_31) at (90mm,465mm) {};
+\draw[->,very thick,color=red] (s_0_31.center) -- (r_0_31.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_30) at (100mm,450mm) {};
+\draw[->,very thick,color=red] (s_0_30.center) -- (r_0_30.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_29) at (110mm,435mm) {};
+\draw[->,very thick,color=red] (s_0_29.center) -- (r_0_29.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_28) at (120mm,420mm) {};
+\draw[->,very thick,color=red] (s_0_28.center) -- (r_0_28.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_27) at (130mm,405mm) {};
+\draw[->,very thick,color=red] (s_0_27.center) -- (r_0_27.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_26) at (140mm,390mm) {};
+\draw[->,very thick,color=red] (s_0_26.center) -- (r_0_26.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_25) at (150mm,375mm) {};
+\draw[->,very thick,color=red] (s_0_25.center) -- (r_0_25.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_24) at (160mm,360mm) {};
+\draw[->,very thick,color=red] (s_0_24.center) -- (r_0_24.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_15) at (170mm,225mm) {};
+\draw[->,very thick,color=red] (s_0_15.center) -- (r_0_15.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_14) at (180mm,210mm) {};
+\draw[->,very thick,color=red] (s_0_14.center) -- (r_0_14.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_13) at (190mm,195mm) {};
+\draw[->,very thick,color=red] (s_0_13.center) -- (r_0_13.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_23) at (200mm,345mm) {};
+\draw[->,very thick,color=red] (s_0_23.center) -- (r_0_23.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (200mm,180mm) {};
+\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_22) at (210mm,330mm) {};
+\draw[->,very thick,color=red] (s_0_22.center) -- (r_0_22.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_21) at (220mm,315mm) {};
+\draw[->,very thick,color=red] (s_0_21.center) -- (r_0_21.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_20) at (230mm,300mm) {};
+\draw[->,very thick,color=red] (s_0_20.center) -- (r_0_20.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_11) at (240mm,165mm) {};
+\draw[->,very thick,color=red] (s_0_11.center) -- (r_0_11.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_10) at (250mm,150mm) {};
+\draw[->,very thick,color=red] (s_0_10.center) -- (r_0_10.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_9) at (260mm,135mm) {};
+\draw[->,very thick,color=red] (s_0_9.center) -- (r_0_9.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (270mm,120mm) {};
+\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_19) at (270mm,285mm) {};
+\draw[->,very thick,color=red] (s_0_19.center) -- (r_0_19.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (280mm,270mm) {};
+\draw[->,very thick,color=red] (s_0_18.center) -- (r_0_18.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_17) at (290mm,255mm) {};
+\draw[->,very thick,color=red] (s_0_17.center) -- (r_0_17.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (300mm,240mm) {};
+\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_7) at (310mm,105mm) {};
+\draw[->,very thick,color=red] (s_0_7.center) -- (r_0_7.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_6) at (320mm,90mm) {};
+\draw[->,very thick,color=red] (s_0_6.center) -- (r_0_6.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (330mm,75mm) {};
+\draw[->,very thick,color=red] (s_0_5.center) -- (r_0_5.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (340mm,60mm) {};
 \draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (90mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (100mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (110mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (120mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
-\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (90mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (100mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (110mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (341mm,45mm) {};
 \draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (351mm,30mm) {};
 \draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
-\draw[->,very thick,color=red] (s_4_8.center) -- (r_4_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (110mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (120mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (130mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (140mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (150mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (160mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (361mm,15mm) {};
 \draw[->] (s_0_1.center) -- (r_0_1.center);
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (101mm,285mm) {};
-\draw[->] (s_16_19.center) -- (r_16_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (110mm,300mm) {};
-\draw[->,very thick,color=red] (s_4_20.center) -- (r_4_20.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (120mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (130mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (140mm,300mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (111mm,105mm) {};
-\draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (111mm,270mm) {};
-\draw[->] (s_16_18.center) -- (r_16_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (121mm,255mm) {};
-\draw[->] (s_16_17.center) -- (r_16_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (121mm,90mm) {};
-\draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (130mm,420mm) {};
-\draw[->,very thick,color=red] (s_8_28.center) -- (r_8_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (140mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (150mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (160mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (131mm,345mm) {};
-\draw[->] (s_20_23.center) -- (r_20_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (131mm,75mm) {};
-\draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (140mm,360mm) {};
-\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (150mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (160mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (170mm,360mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (141mm,330mm) {};
-\draw[->] (s_20_22.center) -- (r_20_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (150mm,180mm) {};
-\draw[->,very thick,color=red] (s_8_12.center) -- (r_8_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (160mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (170mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (180mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (151mm,165mm) {};
-\draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (151mm,465mm) {};
-\draw[->] (s_28_31.center) -- (r_28_31.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (151mm,315mm) {};
-\draw[->] (s_20_21.center) -- (r_20_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (161mm,450mm) {};
-\draw[->] (s_28_30.center) -- (r_28_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (161mm,405mm) {};
-\draw[->] (s_24_27.center) -- (r_24_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (161mm,150mm) {};
-\draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (171mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (171mm,390mm) {};
-\draw[->] (s_24_26.center) -- (r_24_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (171mm,435mm) {};
-\draw[->] (s_28_29.center) -- (r_28_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (171mm,135mm) {};
-\draw[->] (s_8_9.center) -- (r_8_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (181mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (181mm,375mm) {};
-\draw[->] (s_24_25.center) -- (r_24_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (191mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center);

### 2013-06-04 graphs/visu_sbrinz_badtree.tex
Added forgotten file

--- 2013-06-04 graphs/visu_gruyere_binarytree.tex
@@
 \draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
-\node at (0mm,360mm) {core 24};
-\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
-\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
-\node at (0mm,375mm) {core 25};
-\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
-\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
-\node at (0mm,390mm) {core 26};
-\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
-\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
-\node at (0mm,405mm) {core 27};
-\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
-\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
-\node at (0mm,420mm) {core 28};
-\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
-\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
-\node at (0mm,435mm) {core 29};
-\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
-\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
-\node at (0mm,450mm) {core 30};
-\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
-\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
-\node at (0mm,465mm) {core 31};
-\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: binarytree};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (60mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (61mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (71mm,15mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_1_4) at (81mm,15mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (71mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (91mm,30mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (82mm,45mm) {};
-\draw[->] (s_1_3.center) -- (r_1_3.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (92mm,45mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (102mm,45mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (101mm,60mm) {};
-\draw[->,very thick,color=red] (s_1_4.center) -- (r_1_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (111mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (121mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
-\draw[->,very thick,color=red] (s_2_6.center) -- (r_2_6.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_6_14) at (111mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (111mm,75mm) {};
-\draw[->,very thick,color=red] (s_2_5.center) -- (r_2_5.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (121mm,75mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (131mm,75mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (122mm,105mm) {};
-\draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (132mm,105mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (142mm,105mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (122mm,120mm) {};
+\node at (0mm,240mm) {Machine: sbrinz, topology: badtree};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_9) at (50mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_10) at (60mm,0mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_9) at (80mm,135mm) {};
+\draw[->,very thick,color=red] (s_0_9.center) -- (r_0_9.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_9_6) at (90mm,135mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_9_2) at (100mm,135mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_10) at (90mm,150mm) {};
+\draw[->,very thick,color=red] (s_0_10.center) -- (r_0_10.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_10_3) at (100mm,150mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_10_1) at (110mm,150mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_9_6) at (110mm,90mm) {};
+\draw[->,very thick,color=red] (s_9_6.center) -- (r_9_6.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_6_12) at (120mm,90mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (130mm,90mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_10_3) at (130mm,45mm) {};
+\draw[->,very thick,color=red] (s_10_3.center) -- (r_10_3.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_3_11) at (140mm,45mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (150mm,45mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_9_2) at (130mm,30mm) {};
+\draw[->,very thick,color=red] (s_9_2.center) -- (r_9_2.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_10_1) at (140mm,15mm) {};
+\draw[->,very thick,color=red] (s_10_1.center) -- (r_10_1.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_12) at (150mm,180mm) {};
+\draw[->,very thick,color=red] (s_6_12.center) -- (r_6_12.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_12_7) at (160mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_4) at (170mm,180mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (160mm,195mm) {};
+\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_13_5) at (170mm,195mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_3_11) at (170mm,165mm) {};
+\draw[->,very thick,color=red] (s_3_11.center) -- (r_3_11.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (180mm,120mm) {};
 \draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (132mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (142mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (131mm,135mm) {};
-\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (141mm,135mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (151mm,135mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (141mm,210mm) {};
-\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_14_30) at (151mm,210mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_14_29) at (161mm,210mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (141mm,150mm) {};
-\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (151mm,150mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (161mm,150mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (151mm,195mm) {};
-\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_13_28) at (161mm,195mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_13_27) at (171mm,195mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (151mm,165mm) {};
-\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (161mm,165mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_11_24) at (171mm,165mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (151mm,180mm) {};
-\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_26) at (161mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_25) at (171mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (162mm,225mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_7) at (190mm,105mm) {};
+\draw[->,very thick,color=red] (s_12_7.center) -- (r_12_7.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (200mm,105mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_7_14) at (210mm,105mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_13_5) at (200mm,75mm) {};
+\draw[->,very thick,color=red] (s_13_5.center) -- (r_13_5.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_4) at (200mm,60mm) {};
+\draw[->,very thick,color=red] (s_12_4.center) -- (r_12_4.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (230mm,225mm) {};
 \draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_15_31) at (172mm,225mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_30) at (171mm,450mm) {};
-\draw[->,very thick,color=red] (s_14_30.center) -- (r_14_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
-\draw[->,very thick,color=red] (s_7_16.center) -- (r_7_16.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_18) at (172mm,270mm) {};
-\draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (181mm,285mm) {};
-\draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (181mm,300mm) {};
-\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_28) at (181mm,420mm) {};
-\draw[->,very thick,color=red] (s_13_28.center) -- (r_13_28.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (181mm,330mm) {};
-\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_26) at (181mm,390mm) {};
-\draw[->,very thick,color=red] (s_12_26.center) -- (r_12_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_29) at (181mm,435mm) {};
-\draw[->,very thick,color=red] (s_14_29.center) -- (r_14_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (182mm,255mm) {};
-\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_27) at (191mm,405mm) {};
-\draw[->,very thick,color=red] (s_13_27.center) -- (r_13_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_25) at (191mm,375mm) {};
-\draw[->,very thick,color=red] (s_12_25.center) -- (r_12_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_11_24) at (191mm,360mm) {};
-\draw[->,very thick,color=red] (s_11_24.center) -- (r_11_24.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (191mm,345mm) {};
-\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (191mm,315mm) {};
-\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_15_31) at (192mm,465mm) {};
-\draw[->,very thick,color=red] (s_15_31.center) -- (r_15_31.center);
+\node[draw,fill=blue!20,minimum size=10mm] (r_7_14) at (240mm,210mm) {};
+\draw[->,very thick,color=red] (s_7_14.center) -- (r_7_14.center);

### 2013-06-04 graphs/visu_sbrinz_binarytree.tex
Added forgotten file

--- 2013-06-04 graphs/visu_gruyere_binarytree.tex
@@
 \draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
-\node at (0mm,360mm) {core 24};
-\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
-\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
-\node at (0mm,375mm) {core 25};
-\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
-\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
-\node at (0mm,390mm) {core 26};
-\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
-\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
-\node at (0mm,405mm) {core 27};
-\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
-\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
-\node at (0mm,420mm) {core 28};
-\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
-\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
-\node at (0mm,435mm) {core 29};
-\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
-\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
-\node at (0mm,450mm) {core 30};
-\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
-\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
-\node at (0mm,465mm) {core 31};
-\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: binarytree};
+\node at (0mm,240mm) {Machine: sbrinz, topology: binarytree};
 \node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
@@
 \draw[->] (s_1_3.center) -- (r_1_3.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (92mm,45mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (102mm,45mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (101mm,60mm) {};
-\draw[->,very thick,color=red] (s_1_4.center) -- (r_1_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (111mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (121mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (92mm,45mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (102mm,45mm) {};
 \node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
@@
 \node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (101mm,60mm) {};
+\draw[->,very thick,color=red] (s_1_4.center) -- (r_1_4.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (111mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (121mm,60mm) {};
 \node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (111mm,75mm) {};
@@
 \node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (131mm,75mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (122mm,105mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (112mm,105mm) {};
 \draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (132mm,105mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (142mm,105mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (122mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (122mm,105mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (131mm,150mm) {};
+\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (132mm,120mm) {};
 \draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (132mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (142mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (131mm,135mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (141mm,135mm) {};
 \draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (141mm,135mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (151mm,135mm) {};
 \node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (141mm,210mm) {};
 \draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_14_30) at (151mm,210mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_14_29) at (161mm,210mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (141mm,150mm) {};
-\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (151mm,150mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (161mm,150mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (151mm,165mm) {};
+\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (151mm,180mm) {};
+\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (151mm,195mm) {};
 \draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_13_28) at (161mm,195mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_13_27) at (171mm,195mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (151mm,165mm) {};
-\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (161mm,165mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_11_24) at (171mm,165mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (151mm,180mm) {};
-\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_26) at (161mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_25) at (171mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (162mm,225mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (152mm,225mm) {};
 \draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center);
-\node[draw,fill=red!20,minimum size=10mm] (s_15_31) at (172mm,225mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_30) at (171mm,450mm) {};
-\draw[->,very thick,color=red] (s_14_30.center) -- (r_14_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
-\draw[->,very thick,color=red] (s_7_16.center) -- (r_7_16.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_18) at (172mm,270mm) {};
-\draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (181mm,285mm) {};
-\draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (181mm,300mm) {};
-\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_28) at (181mm,420mm) {};
-\draw[->,very thick,color=red] (s_13_28.center) -- (r_13_28.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (181mm,330mm) {};
-\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_26) at (181mm,390mm) {};
-\draw[->,very thick,color=red] (s_12_26.center) -- (r_12_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_29) at (181mm,435mm) {};
-\draw[->,very thick,color=red] (s_14_29.center) -- (r_14_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (182mm,255mm) {};
-\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_27) at (191mm,405mm) {};
-\draw[->,very thick,color=red] (s_13_27.center) -- (r_13_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_25) at (191mm,375mm) {};
-\draw[->,very thick,color=red] (s_12_25.center) -- (r_12_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_11_24) at (191mm,360mm) {};
-\draw[->,very thick,color=red] (s_11_24.center) -- (r_11_24.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (191mm,345mm) {};
-\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (191mm,315mm) {};
-\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_15_31) at (192mm,465mm) {};
-\draw[->,very thick,color=red] (s_15_31.center) -- (r_15_31.center);

### 2013-06-04 graphs/visu_sbrinz_cluster.tex
Added forgotten file

--- 2013-06-04 graphs/visu_gruyere_cluster.tex
@@
 \draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
-\node at (0mm,360mm) {core 24};
-\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
-\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
-\node at (0mm,375mm) {core 25};
-\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
-\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
-\node at (0mm,390mm) {core 26};
-\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
-\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
-\node at (0mm,405mm) {core 27};
-\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
-\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
-\node at (0mm,420mm) {core 28};
-\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
-\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
-\node at (0mm,435mm) {core 29};
-\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
-\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
-\node at (0mm,450mm) {core 30};
-\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
-\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
-\node at (0mm,465mm) {core 31};
-\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: cluster};
+\node at (0mm,240mm) {Machine: sbrinz, topology: cluster};
 \node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (50mm,0mm) {};
@@
 \node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
+\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (90mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (100mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (110mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (120mm,120mm) {};
 \node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (80mm,60mm) {};
 \draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (90mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_16) at (100mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (110mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (130mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
-\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (90mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (100mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (110mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (120mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (130mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (90mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (100mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (110mm,60mm) {};
 \node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
@@
 \draw[->] (s_0_2.center) -- (r_0_2.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (101mm,105mm) {};
+\draw[->] (s_4_7.center) -- (r_4_7.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
 \draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (120mm,360mm) {};
-\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (130mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (140mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (150mm,360mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (120mm,180mm) {};
-\draw[->,very thick,color=red] (s_4_12.center) -- (r_4_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (130mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (140mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (160mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (120mm,300mm) {};
-\draw[->,very thick,color=red] (s_8_20.center) -- (r_8_20.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (130mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (140mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (150mm,300mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (121mm,165mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (110mm,180mm) {};
+\draw[->,very thick,color=red] (s_8_12.center) -- (r_8_12.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (120mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (130mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (111mm,90mm) {};
+\draw[->] (s_4_6.center) -- (r_4_6.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (111mm,165mm) {};
 \draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (121mm,105mm) {};
-\draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_16) at (130mm,240mm) {};
-\draw[->,very thick,color=red] (s_4_16.center) -- (r_4_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (140mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (150mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (160mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (131mm,150mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (121mm,75mm) {};
+\draw[->] (s_4_5.center) -- (r_4_5.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (121mm,150mm) {};
 \draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (131mm,90mm) {};
-\draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (141mm,75mm) {};
-\draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (141mm,405mm) {};
-\draw[->] (s_24_27.center) -- (r_24_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (141mm,135mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (131mm,135mm) {};
 \draw[->] (s_8_9.center) -- (r_8_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (141mm,345mm) {};
-\draw[->] (s_20_23.center) -- (r_20_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (150mm,420mm) {};
-\draw[->,very thick,color=red] (s_12_28.center) -- (r_12_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (160mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (170mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (180mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (151mm,330mm) {};
-\draw[->] (s_20_22.center) -- (r_20_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (151mm,225mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (131mm,225mm) {};
 \draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (151mm,285mm) {};
-\draw[->] (s_16_19.center) -- (r_16_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (151mm,390mm) {};
-\draw[->] (s_24_26.center) -- (r_24_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (161mm,315mm) {};
-\draw[->] (s_20_21.center) -- (r_20_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (161mm,270mm) {};
-\draw[->] (s_16_18.center) -- (r_16_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (161mm,375mm) {};
-\draw[->] (s_24_25.center) -- (r_24_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (141mm,210mm) {};
 \draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (171mm,255mm) {};
-\draw[->] (s_16_17.center) -- (r_16_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (171mm,465mm) {};
-\draw[->] (s_28_31.center) -- (r_28_31.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (171mm,195mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};
 \draw[->] (s_12_13.center) -- (r_12_13.center);
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (181mm,450mm) {};
-\draw[->] (s_28_30.center) -- (r_28_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (191mm,435mm) {};
-\draw[->] (s_28_29.center) -- (r_28_29.center);

### 2013-06-04 graphs/visu_sbrinz_mst.tex
Added forgotten file

--- 2013-06-04 graphs/visu_gruyere_cluster.tex
@@
 \draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
-\node at (0mm,360mm) {core 24};
-\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
-\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
-\node at (0mm,375mm) {core 25};
-\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
-\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
-\node at (0mm,390mm) {core 26};
-\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
-\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
-\node at (0mm,405mm) {core 27};
-\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
-\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
-\node at (0mm,420mm) {core 28};
-\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
-\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
-\node at (0mm,435mm) {core 29};
-\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
-\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
-\node at (0mm,450mm) {core 30};
-\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
-\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
-\node at (0mm,465mm) {core 31};
-\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: cluster};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (60mm,0mm) {};
+\node at (0mm,240mm) {Machine: sbrinz, topology: mst};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (60mm,0mm) {};
 \node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
@@
 \node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (80mm,60mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};
 \draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (90mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_16) at (100mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (110mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (130mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
-\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (90mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (100mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (110mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (120mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (130mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (90mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (100mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (110mm,60mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (80mm,180mm) {};
+\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (90mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (100mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (110mm,180mm) {};
 \node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
@@
 \draw[->] (s_0_2.center) -- (r_0_2.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
+\draw[->,very thick,color=red] (s_4_8.center) -- (r_4_8.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (110mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (120mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (130mm,120mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (101mm,225mm) {};
+\draw[->] (s_12_15.center) -- (r_12_15.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
 \draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (120mm,360mm) {};
-\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (130mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (140mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (150mm,360mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (120mm,180mm) {};
-\draw[->,very thick,color=red] (s_4_12.center) -- (r_4_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (130mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (140mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (160mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (120mm,300mm) {};
-\draw[->,very thick,color=red] (s_8_20.center) -- (r_8_20.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (130mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (140mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (150mm,300mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (101mm,105mm) {};
+\draw[->] (s_4_7.center) -- (r_4_7.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (111mm,90mm) {};
+\draw[->] (s_4_6.center) -- (r_4_6.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (111mm,210mm) {};
+\draw[->] (s_12_14.center) -- (r_12_14.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (121mm,195mm) {};
+\draw[->] (s_12_13.center) -- (r_12_13.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (121mm,75mm) {};
+\draw[->] (s_4_5.center) -- (r_4_5.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (121mm,165mm) {};
 \draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (121mm,105mm) {};
-\draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_16) at (130mm,240mm) {};
-\draw[->,very thick,color=red] (s_4_16.center) -- (r_4_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (140mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (150mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (160mm,240mm) {};
 \node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (131mm,150mm) {};
 \draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (131mm,90mm) {};
-\draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (141mm,75mm) {};
-\draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (141mm,405mm) {};
-\draw[->] (s_24_27.center) -- (r_24_27.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (141mm,135mm) {};
 \draw[->] (s_8_9.center) -- (r_8_9.center);
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (141mm,345mm) {};
-\draw[->] (s_20_23.center) -- (r_20_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (150mm,420mm) {};
-\draw[->,very thick,color=red] (s_12_28.center) -- (r_12_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (160mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (170mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (180mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (151mm,330mm) {};
-\draw[->] (s_20_22.center) -- (r_20_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (151mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (151mm,285mm) {};
-\draw[->] (s_16_19.center) -- (r_16_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (151mm,390mm) {};
-\draw[->] (s_24_26.center) -- (r_24_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (161mm,315mm) {};
-\draw[->] (s_20_21.center) -- (r_20_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (161mm,270mm) {};
-\draw[->] (s_16_18.center) -- (r_16_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (161mm,375mm) {};
-\draw[->] (s_24_25.center) -- (r_24_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (171mm,255mm) {};
-\draw[->] (s_16_17.center) -- (r_16_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (171mm,465mm) {};
-\draw[->] (s_28_31.center) -- (r_28_31.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (171mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (181mm,450mm) {};
-\draw[->] (s_28_30.center) -- (r_28_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (191mm,435mm) {};
-\draw[->] (s_28_29.center) -- (r_28_29.center);

### 2013-06-04 graphs/visu_sbrinz_sequential.tex
Added forgotten file

--- 2013-06-04 graphs/visu_gruyere_sequential.tex
@@
 \draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
-\node at (0mm,360mm) {core 24};
-\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
-\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
-\node at (0mm,375mm) {core 25};
-\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
-\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
-\node at (0mm,390mm) {core 26};
-\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
-\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
-\node at (0mm,405mm) {core 27};
-\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
-\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
-\node at (0mm,420mm) {core 28};
-\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
-\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
-\node at (0mm,435mm) {core 29};
-\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
-\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
-\node at (0mm,450mm) {core 30};
-\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
-\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
-\node at (0mm,465mm) {core 31};
-\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: sequential};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_31) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_30) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_29) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_28) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_27) at (90mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_26) at (100mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_25) at (110mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_24) at (120mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_15) at (130mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_14) at (140mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_13) at (150mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (160mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_23) at (170mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_22) at (180mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_21) at (190mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_20) at (200mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_11) at (210mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_10) at (220mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_9) at (230mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (240mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_19) at (250mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (260mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_17) at (270mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (280mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_7) at (290mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_6) at (300mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (310mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (320mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (330mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (340mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (350mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_31) at (90mm,465mm) {};
-\draw[->,very thick,color=red] (s_0_31.center) -- (r_0_31.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_30) at (100mm,450mm) {};
-\draw[->,very thick,color=red] (s_0_30.center) -- (r_0_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_29) at (110mm,435mm) {};
-\draw[->,very thick,color=red] (s_0_29.center) -- (r_0_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_28) at (120mm,420mm) {};
-\draw[->,very thick,color=red] (s_0_28.center) -- (r_0_28.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_27) at (130mm,405mm) {};
-\draw[->,very thick,color=red] (s_0_27.center) -- (r_0_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_26) at (140mm,390mm) {};
-\draw[->,very thick,color=red] (s_0_26.center) -- (r_0_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_25) at (150mm,375mm) {};
-\draw[->,very thick,color=red] (s_0_25.center) -- (r_0_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_24) at (160mm,360mm) {};
-\draw[->,very thick,color=red] (s_0_24.center) -- (r_0_24.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_15) at (170mm,225mm) {};
+\node at (0mm,240mm) {Machine: sbrinz, topology: sequential};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_11) at (50mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_10) at (60mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_9) at (70mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (80mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_15) at (90mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_14) at (100mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_13) at (110mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (120mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_7) at (130mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_6) at (140mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (150mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (160mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (170mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (180mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (190mm,0mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_11) at (80mm,165mm) {};
+\draw[->,very thick,color=red] (s_0_11.center) -- (r_0_11.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_10) at (90mm,150mm) {};
+\draw[->,very thick,color=red] (s_0_10.center) -- (r_0_10.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_9) at (100mm,135mm) {};
+\draw[->,very thick,color=red] (s_0_9.center) -- (r_0_9.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (110mm,120mm) {};
+\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_15) at (110mm,225mm) {};
 \draw[->,very thick,color=red] (s_0_15.center) -- (r_0_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_14) at (180mm,210mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_14) at (120mm,210mm) {};
 \draw[->,very thick,color=red] (s_0_14.center) -- (r_0_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_13) at (190mm,195mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_13) at (130mm,195mm) {};
 \draw[->,very thick,color=red] (s_0_13.center) -- (r_0_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_23) at (200mm,345mm) {};
-\draw[->,very thick,color=red] (s_0_23.center) -- (r_0_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (200mm,180mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (140mm,180mm) {};
 \draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_22) at (210mm,330mm) {};
-\draw[->,very thick,color=red] (s_0_22.center) -- (r_0_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_21) at (220mm,315mm) {};
-\draw[->,very thick,color=red] (s_0_21.center) -- (r_0_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_20) at (230mm,300mm) {};
-\draw[->,very thick,color=red] (s_0_20.center) -- (r_0_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_11) at (240mm,165mm) {};
-\draw[->,very thick,color=red] (s_0_11.center) -- (r_0_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_10) at (250mm,150mm) {};
-\draw[->,very thick,color=red] (s_0_10.center) -- (r_0_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_9) at (260mm,135mm) {};
-\draw[->,very thick,color=red] (s_0_9.center) -- (r_0_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (270mm,120mm) {};
-\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_19) at (270mm,285mm) {};
-\draw[->,very thick,color=red] (s_0_19.center) -- (r_0_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (280mm,270mm) {};
-\draw[->,very thick,color=red] (s_0_18.center) -- (r_0_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_17) at (290mm,255mm) {};
-\draw[->,very thick,color=red] (s_0_17.center) -- (r_0_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (300mm,240mm) {};
-\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_7) at (310mm,105mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_7) at (150mm,105mm) {};
 \draw[->,very thick,color=red] (s_0_7.center) -- (r_0_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_6) at (320mm,90mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_6) at (160mm,90mm) {};
 \draw[->,very thick,color=red] (s_0_6.center) -- (r_0_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (330mm,75mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (170mm,75mm) {};
 \draw[->,very thick,color=red] (s_0_5.center) -- (r_0_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (340mm,60mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (180mm,60mm) {};
 \draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (341mm,45mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (181mm,45mm) {};
 \draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (351mm,30mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (191mm,30mm) {};
 \draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (361mm,15mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (201mm,15mm) {};
 \draw[->] (s_0_1.center) -- (r_0_1.center);

### 2013-06-04 graphs/visu_ziger_badtree.tex
Added forgotten file

\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
\node at (0mm,0mm) {core 00};
\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
\node at (0mm,15mm) {core 01};
\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
\node at (0mm,30mm) {core 02};
\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
\node at (0mm,45mm) {core 03};
\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
\draw[fill,color=red!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
\node at (0mm,60mm) {core 04};
\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
\draw[fill,color=red!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
\node at (0mm,75mm) {core 05};
\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
\node at (0mm,90mm) {core 06};
\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
\node at (0mm,105mm) {core 07};
\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
\draw[fill,color=green!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
\node at (0mm,120mm) {core 08};
\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
\draw[fill,color=green!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
\node at (0mm,135mm) {core 09};
\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
\draw[fill,color=green!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
\node at (0mm,150mm) {core 10};
\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
\draw[fill,color=green!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
\node at (0mm,165mm) {core 11};
\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
\draw[fill,color=blue!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
\node at (0mm,180mm) {core 12};
\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
\draw[fill,color=blue!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
\node at (0mm,195mm) {core 13};
\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
\draw[fill,color=blue!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
\node at (0mm,210mm) {core 14};
\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
\draw[fill,color=blue!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
\node at (0mm,225mm) {core 15};
\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
\draw[fill,color=blue!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
\node at (0mm,240mm) {core 16};
\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
\draw[fill,color=blue!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
\node at (0mm,255mm) {core 17};
\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
\draw[fill,color=orange!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
\node at (0mm,270mm) {core 18};
\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
\draw[fill,color=orange!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
\node at (0mm,285mm) {core 19};
\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
\draw[fill,color=orange!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
\node at (0mm,300mm) {core 20};
\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
\draw[fill,color=orange!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
\node at (0mm,315mm) {core 21};
\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
\draw[fill,color=orange!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
\node at (0mm,330mm) {core 22};
\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
\draw[fill,color=orange!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
\node at (0mm,345mm) {core 23};
\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
\node at (0mm,360mm) {Machine: ziger, topology: badtree};
\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_17) at (60mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_2) at (90mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_1) at (100mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_17) at (90mm,255mm) {};
\draw[->,very thick,color=red] (s_0_17.center) -- (r_0_17.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_17_3) at (100mm,255mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_17_4) at (110mm,255mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_2) at (120mm,30mm) {};
\draw[->,very thick,color=red] (s_16_2.center) -- (r_16_2.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_2_18) at (130mm,30mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_17_3) at (130mm,45mm) {};
\draw[->,very thick,color=red] (s_17_3.center) -- (r_17_3.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_3_13) at (140mm,45mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_3_15) at (150mm,45mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_1) at (130mm,15mm) {};
\draw[->,very thick,color=red] (s_16_1.center) -- (r_16_1.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_17_4) at (140mm,60mm) {};
\draw[->,very thick,color=red] (s_17_4.center) -- (r_17_4.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_4_14) at (150mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (160mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_18) at (150mm,270mm) {};
\draw[->,very thick,color=red] (s_2_18.center) -- (r_2_18.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_18_10) at (160mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_8) at (170mm,270mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_13) at (170mm,195mm) {};
\draw[->,very thick,color=red] (s_3_13.center) -- (r_3_13.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_13_5) at (180mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_14) at (180mm,210mm) {};
\draw[->,very thick,color=red] (s_4_14.center) -- (r_4_14.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_3_15) at (180mm,225mm) {};
\draw[->,very thick,color=red] (s_3_15.center) -- (r_3_15.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (190mm,180mm) {};
\draw[->,very thick,color=red] (s_4_12.center) -- (r_4_12.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_18_10) at (190mm,150mm) {};
\draw[->,very thick,color=red] (s_18_10.center) -- (r_18_10.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_10_19) at (200mm,150mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (210mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_18_8) at (200mm,120mm) {};
\draw[->,very thick,color=red] (s_18_8.center) -- (r_18_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_21) at (210mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (220mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_13_5) at (210mm,75mm) {};
\draw[->,very thick,color=red] (s_13_5.center) -- (r_13_5.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_19) at (230mm,285mm) {};
\draw[->,very thick,color=red] (s_10_19.center) -- (r_10_19.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_19_9) at (240mm,285mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_19_11) at (250mm,285mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_21) at (240mm,315mm) {};
\draw[->,very thick,color=red] (s_8_21.center) -- (r_8_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (240mm,330mm) {};
\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_22_7) at (250mm,330mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_22_6) at (260mm,330mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (250mm,300mm) {};
\draw[->,very thick,color=red] (s_8_20.center) -- (r_8_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_19_9) at (270mm,135mm) {};
\draw[->,very thick,color=red] (s_19_9.center) -- (r_19_9.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_9_23) at (280mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_22_7) at (280mm,105mm) {};
\draw[->,very thick,color=red] (s_22_7.center) -- (r_22_7.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_19_11) at (280mm,165mm) {};
\draw[->,very thick,color=red] (s_19_11.center) -- (r_19_11.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_22_6) at (290mm,90mm) {};
\draw[->,very thick,color=red] (s_22_6.center) -- (r_22_6.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_23) at (310mm,345mm) {};
\draw[->,very thick,color=red] (s_9_23.center) -- (r_9_23.center);

### 2013-06-04 graphs/visu_ziger_binarytree.tex
Added forgotten file

--- 2013-06-04 graphs/visu_gruyere_binarytree.tex
@@
 \draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
+\draw[fill,color=red!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
 \node at (0mm,60mm) {core 04};
 \draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
+\draw[fill,color=red!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
 \node at (0mm,75mm) {core 05};
@@
 \draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
+\draw[fill,color=green!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
 \node at (0mm,120mm) {core 08};
 \draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
+\draw[fill,color=green!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
 \node at (0mm,135mm) {core 09};
 \draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
+\draw[fill,color=green!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
 \node at (0mm,150mm) {core 10};
 \draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
+\draw[fill,color=green!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
 \node at (0mm,165mm) {core 11};
 \draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
+\draw[fill,color=blue!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
 \node at (0mm,180mm) {core 12};
 \draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
+\draw[fill,color=blue!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
 \node at (0mm,195mm) {core 13};
 \draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
+\draw[fill,color=blue!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
 \node at (0mm,210mm) {core 14};
 \draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
+\draw[fill,color=blue!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
 \node at (0mm,225mm) {core 15};
 \draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
+\draw[fill,color=blue!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
 \node at (0mm,240mm) {core 16};
 \draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
+\draw[fill,color=blue!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
 \node at (0mm,255mm) {core 17};
 \draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
+\draw[fill,color=orange!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
 \node at (0mm,270mm) {core 18};
 \draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
+\draw[fill,color=orange!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
 \node at (0mm,285mm) {core 19};
 \draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
+\draw[fill,color=orange!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
 \node at (0mm,300mm) {core 20};
 \draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
+\draw[fill,color=orange!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
 \node at (0mm,315mm) {core 21};
 \draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
+\draw[fill,color=orange!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
 \node at (0mm,330mm) {core 22};
 \draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
+\draw[fill,color=orange!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
 \node at (0mm,345mm) {core 23};
 \draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
-\node at (0mm,360mm) {core 24};
-\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
-\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
-\node at (0mm,375mm) {core 25};
-\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
-\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
-\node at (0mm,390mm) {core 26};
-\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
-\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
-\node at (0mm,405mm) {core 27};
-\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
-\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
-\node at (0mm,420mm) {core 28};
-\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
-\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
-\node at (0mm,435mm) {core 29};
-\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
-\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
-\node at (0mm,450mm) {core 30};
-\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
-\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
-\node at (0mm,465mm) {core 31};
-\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: binarytree};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (60mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (61mm,15mm) {};
+\node at (0mm,360mm) {Machine: ziger, topology: binarytree};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (50mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (60mm,0mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (61mm,30mm) {};
+\draw[->] (s_0_2.center) -- (r_0_2.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (71mm,30mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (71mm,15mm) {};
 \draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (71mm,15mm) {};
 \node[draw,fill=red!20,minimum size=10mm] (s_1_4) at (81mm,15mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (71mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (91mm,30mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (82mm,45mm) {};
-\draw[->] (s_1_3.center) -- (r_1_3.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (92mm,45mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (102mm,45mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (101mm,60mm) {};
-\draw[->,very thick,color=red] (s_1_4.center) -- (r_1_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (111mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (121mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (91mm,15mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (82mm,75mm) {};
+\draw[->] (s_2_5.center) -- (r_2_5.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (92mm,75mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (102mm,75mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (92mm,60mm) {};
+\draw[->] (s_1_4.center) -- (r_1_4.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (102mm,60mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (112mm,60mm) {};
 \node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
@@
 \node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (111mm,75mm) {};
-\draw[->,very thick,color=red] (s_2_5.center) -- (r_2_5.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (121mm,75mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (131mm,75mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (122mm,105mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (102mm,45mm) {};
+\draw[->] (s_1_3.center) -- (r_1_3.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (112mm,45mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (122mm,45mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (112mm,165mm) {};
+\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (122mm,165mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (122mm,150mm) {};
+\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (132mm,150mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (142mm,150mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (131mm,210mm) {};
+\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (132mm,135mm) {};
+\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (142mm,135mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (152mm,135mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (132mm,180mm) {};
+\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (132mm,120mm) {};
+\draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (142mm,120mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (152mm,120mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (141mm,195mm) {};
+\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (142mm,105mm) {};
 \draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (132mm,105mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (142mm,105mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (122mm,120mm) {};
-\draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (132mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (142mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (131mm,135mm) {};
-\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (141mm,135mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (151mm,135mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (141mm,210mm) {};
-\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_14_30) at (151mm,210mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_14_29) at (161mm,210mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (141mm,150mm) {};
-\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (151mm,150mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (161mm,150mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (151mm,195mm) {};
-\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_13_28) at (161mm,195mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_13_27) at (171mm,195mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (151mm,165mm) {};
-\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (161mm,165mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_11_24) at (171mm,165mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (151mm,180mm) {};
-\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_26) at (161mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_25) at (171mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (162mm,225mm) {};
-\draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_15_31) at (172mm,225mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_30) at (171mm,450mm) {};
-\draw[->,very thick,color=red] (s_14_30.center) -- (r_14_30.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (152mm,105mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (162mm,105mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (152mm,345mm) {};
+\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (162mm,330mm) {};
+\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
@@
 \draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (181mm,285mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (172mm,300mm) {};
+\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (172mm,255mm) {};
+\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (172mm,315mm) {};
+\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (182mm,225mm) {};
+\draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (182mm,285mm) {};
 \draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center);
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (181mm,300mm) {};
-\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_28) at (181mm,420mm) {};
-\draw[->,very thick,color=red] (s_13_28.center) -- (r_13_28.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (181mm,330mm) {};
-\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_26) at (181mm,390mm) {};
-\draw[->,very thick,color=red] (s_12_26.center) -- (r_12_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_29) at (181mm,435mm) {};
-\draw[->,very thick,color=red] (s_14_29.center) -- (r_14_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (182mm,255mm) {};
-\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_27) at (191mm,405mm) {};
-\draw[->,very thick,color=red] (s_13_27.center) -- (r_13_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_25) at (191mm,375mm) {};
-\draw[->,very thick,color=red] (s_12_25.center) -- (r_12_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_11_24) at (191mm,360mm) {};
-\draw[->,very thick,color=red] (s_11_24.center) -- (r_11_24.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (191mm,345mm) {};
-\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (191mm,315mm) {};
-\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_15_31) at (192mm,465mm) {};
-\draw[->,very thick,color=red] (s_15_31.center) -- (r_15_31.center);

### 2013-06-04 graphs/visu_ziger_cluster.tex
Added forgotten file

--- 2013-06-04 graphs/visu_ziger_binarytree.tex
@@
 \draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\node at (0mm,360mm) {Machine: ziger, topology: binarytree};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (60mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (61mm,30mm) {};
+\node at (0mm,360mm) {Machine: ziger, topology: cluster};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (50mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (60mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (70mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (80mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (90mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (100mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (110mm,0mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (70mm,270mm) {};
+\draw[->,very thick,color=red] (s_0_18.center) -- (r_0_18.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_18_6) at (80mm,270mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_18_23) at (90mm,270mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_18_22) at (100mm,270mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_18_21) at (110mm,270mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_18_20) at (120mm,270mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_18_19) at (130mm,270mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (81mm,75mm) {};
+\draw[->] (s_0_5.center) -- (r_0_5.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (90mm,180mm) {};
+\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_12_17) at (100mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_16) at (110mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (120mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (130mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (91mm,60mm) {};
+\draw[->] (s_0_4.center) -- (r_0_4.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (101mm,45mm) {};
+\draw[->] (s_0_3.center) -- (r_0_3.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_18_23) at (101mm,345mm) {};
+\draw[->] (s_18_23.center) -- (r_18_23.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_18_6) at (110mm,90mm) {};
+\draw[->,very thick,color=red] (s_18_6.center) -- (r_18_6.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_6_11) at (120mm,90mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_6_10) at (130mm,90mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_6_9) at (140mm,90mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_6_8) at (150mm,90mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_6_7) at (160mm,90mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_17) at (111mm,255mm) {};
+\draw[->] (s_12_17.center) -- (r_12_17.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (111mm,30mm) {};
 \draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (71mm,30mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (71mm,15mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_18_22) at (111mm,330mm) {};
+\draw[->] (s_18_22.center) -- (r_18_22.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_16) at (121mm,240mm) {};
+\draw[->] (s_12_16.center) -- (r_12_16.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (121mm,15mm) {};
 \draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_1_4) at (81mm,15mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (91mm,15mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (82mm,75mm) {};
-\draw[->] (s_2_5.center) -- (r_2_5.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (92mm,75mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (102mm,75mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (92mm,60mm) {};
-\draw[->] (s_1_4.center) -- (r_1_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (102mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (112mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
-\draw[->,very thick,color=red] (s_2_6.center) -- (r_2_6.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_6_14) at (111mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (102mm,45mm) {};
-\draw[->] (s_1_3.center) -- (r_1_3.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (112mm,45mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (122mm,45mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (112mm,165mm) {};
-\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (122mm,165mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (122mm,150mm) {};
-\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (132mm,150mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (142mm,150mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (131mm,210mm) {};
-\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (132mm,135mm) {};
-\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (142mm,135mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (152mm,135mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (132mm,180mm) {};
-\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (132mm,120mm) {};
-\draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (142mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (152mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (141mm,195mm) {};
-\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (142mm,105mm) {};
-\draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (152mm,105mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (162mm,105mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (152mm,345mm) {};
-\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (162mm,330mm) {};
-\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
-\draw[->,very thick,color=red] (s_7_16.center) -- (r_7_16.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_18) at (172mm,270mm) {};
-\draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (172mm,300mm) {};
-\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (172mm,255mm) {};
-\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (172mm,315mm) {};
-\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (182mm,225mm) {};
-\draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (182mm,285mm) {};
-\draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center);
+\node[draw,fill=blue!20,minimum size=10mm] (r_18_21) at (121mm,315mm) {};
+\draw[->] (s_18_21.center) -- (r_18_21.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_11) at (131mm,165mm) {};
+\draw[->] (s_6_11.center) -- (r_6_11.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_18_20) at (131mm,300mm) {};
+\draw[->] (s_18_20.center) -- (r_18_20.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (131mm,225mm) {};
+\draw[->] (s_12_15.center) -- (r_12_15.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_18_19) at (141mm,285mm) {};
+\draw[->] (s_18_19.center) -- (r_18_19.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (141mm,210mm) {};
+\draw[->] (s_12_14.center) -- (r_12_14.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_10) at (141mm,150mm) {};
+\draw[->] (s_6_10.center) -- (r_6_10.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_9) at (151mm,135mm) {};
+\draw[->] (s_6_9.center) -- (r_6_9.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};
+\draw[->] (s_12_13.center) -- (r_12_13.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_8) at (161mm,120mm) {};
+\draw[->] (s_6_8.center) -- (r_6_8.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_7) at (171mm,105mm) {};
+\draw[->] (s_6_7.center) -- (r_6_7.center);

### 2013-06-04 graphs/visu_ziger_mst.tex
Added forgotten file

--- 2013-06-04 graphs/visu_ziger_cluster.tex
@@
 \draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\node at (0mm,360mm) {Machine: ziger, topology: cluster};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (60mm,0mm) {};
+\node at (0mm,360mm) {Machine: ziger, topology: mst};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_6) at (50mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (60mm,0mm) {};
 \node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (70mm,0mm) {};
@@
 \node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (110mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (70mm,270mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_6) at (70mm,90mm) {};
+\draw[->,very thick,color=red] (s_0_6.center) -- (r_0_6.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_6_12) at (80mm,90mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_6_11) at (90mm,90mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_6_10) at (100mm,90mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_6_9) at (110mm,90mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_6_8) at (120mm,90mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_6_7) at (130mm,90mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (80mm,270mm) {};
 \draw[->,very thick,color=red] (s_0_18.center) -- (r_0_18.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_18_6) at (80mm,270mm) {};
 \node[draw,fill=red!20,minimum size=10mm] (s_18_23) at (90mm,270mm) {};
@@
 \draw[->] (s_0_5.center) -- (r_0_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (90mm,180mm) {};
-\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_17) at (100mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_16) at (110mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (120mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (130mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};
 \node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (91mm,60mm) {};
 \draw[->] (s_0_4.center) -- (r_0_4.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_12) at (100mm,180mm) {};
+\draw[->,very thick,color=red] (s_6_12.center) -- (r_6_12.center); 
+\node[draw,fill=red!20,minimum size=10mm] (s_12_17) at (110mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_16) at (120mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (130mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (140mm,180mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (150mm,180mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_11) at (101mm,165mm) {};
+\draw[->] (s_6_11.center) -- (r_6_11.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (101mm,45mm) {};
@@
 \draw[->] (s_18_23.center) -- (r_18_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_6) at (110mm,90mm) {};
-\draw[->,very thick,color=red] (s_18_6.center) -- (r_18_6.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_6_11) at (120mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_10) at (130mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_9) at (140mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_8) at (150mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_7) at (160mm,90mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_17) at (111mm,255mm) {};
-\draw[->] (s_12_17.center) -- (r_12_17.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (111mm,30mm) {};
@@
 \draw[->] (s_18_22.center) -- (r_18_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_16) at (121mm,240mm) {};
-\draw[->] (s_12_16.center) -- (r_12_16.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_10) at (111mm,150mm) {};
+\draw[->] (s_6_10.center) -- (r_6_10.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_9) at (121mm,135mm) {};
+\draw[->] (s_6_9.center) -- (r_6_9.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (121mm,15mm) {};
 \draw[->] (s_0_1.center) -- (r_0_1.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_17) at (121mm,255mm) {};
+\draw[->] (s_12_17.center) -- (r_12_17.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_18_21) at (121mm,315mm) {};
 \draw[->] (s_18_21.center) -- (r_18_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_11) at (131mm,165mm) {};
-\draw[->] (s_6_11.center) -- (r_6_11.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_8) at (131mm,120mm) {};
+\draw[->] (s_6_8.center) -- (r_6_8.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_16) at (131mm,240mm) {};
+\draw[->] (s_12_16.center) -- (r_12_16.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_18_20) at (131mm,300mm) {};
 \draw[->] (s_18_20.center) -- (r_18_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (131mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_6_7) at (141mm,105mm) {};
+\draw[->] (s_6_7.center) -- (r_6_7.center); 
 \node[draw,fill=blue!20,minimum size=10mm] (r_18_19) at (141mm,285mm) {};
 \draw[->] (s_18_19.center) -- (r_18_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (141mm,210mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (141mm,225mm) {};
+\draw[->] (s_12_15.center) -- (r_12_15.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (151mm,210mm) {};
 \draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_10) at (141mm,150mm) {};
-\draw[->] (s_6_10.center) -- (r_6_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_9) at (151mm,135mm) {};
-\draw[->] (s_6_9.center) -- (r_6_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (161mm,195mm) {};
 \draw[->] (s_12_13.center) -- (r_12_13.center);
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_8) at (161mm,120mm) {};
-\draw[->] (s_6_8.center) -- (r_6_8.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_7) at (171mm,105mm) {};
-\draw[->] (s_6_7.center) -- (r_6_7.center);

### 2013-06-04 graphs/visu_ziger_sequential.tex
Added forgotten file

--- 2013-06-04 graphs/visu_ziger_cluster.tex
@@
 \draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\node at (0mm,360mm) {Machine: ziger, topology: cluster};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (90mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (100mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (110mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (70mm,270mm) {};
+\node at (0mm,360mm) {Machine: ziger, topology: sequential};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_17) at (50mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_15) at (70mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_14) at (80mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_13) at (90mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (100mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_23) at (110mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_22) at (120mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_21) at (130mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_20) at (140mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_19) at (150mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (160mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_11) at (170mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_10) at (180mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_9) at (190mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (200mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_7) at (210mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_6) at (220mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (230mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (240mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (250mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (260mm,0mm) {};
+\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (270mm,0mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_17) at (80mm,255mm) {};
+\draw[->,very thick,color=red] (s_0_17.center) -- (r_0_17.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (90mm,240mm) {};
+\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_15) at (100mm,225mm) {};
+\draw[->,very thick,color=red] (s_0_15.center) -- (r_0_15.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_14) at (110mm,210mm) {};
+\draw[->,very thick,color=red] (s_0_14.center) -- (r_0_14.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_13) at (120mm,195mm) {};
+\draw[->,very thick,color=red] (s_0_13.center) -- (r_0_13.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (130mm,180mm) {};
+\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_23) at (130mm,345mm) {};
+\draw[->,very thick,color=red] (s_0_23.center) -- (r_0_23.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_22) at (140mm,330mm) {};
+\draw[->,very thick,color=red] (s_0_22.center) -- (r_0_22.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_21) at (150mm,315mm) {};
+\draw[->,very thick,color=red] (s_0_21.center) -- (r_0_21.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_20) at (160mm,300mm) {};
+\draw[->,very thick,color=red] (s_0_20.center) -- (r_0_20.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_19) at (170mm,285mm) {};
+\draw[->,very thick,color=red] (s_0_19.center) -- (r_0_19.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (180mm,270mm) {};
 \draw[->,very thick,color=red] (s_0_18.center) -- (r_0_18.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_18_6) at (80mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_23) at (90mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_22) at (100mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_21) at (110mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_20) at (120mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_19) at (130mm,270mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (81mm,75mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_11) at (190mm,165mm) {};
+\draw[->,very thick,color=red] (s_0_11.center) -- (r_0_11.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_10) at (200mm,150mm) {};
+\draw[->,very thick,color=red] (s_0_10.center) -- (r_0_10.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_9) at (210mm,135mm) {};
+\draw[->,very thick,color=red] (s_0_9.center) -- (r_0_9.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (220mm,120mm) {};
+\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_7) at (230mm,105mm) {};
+\draw[->,very thick,color=red] (s_0_7.center) -- (r_0_7.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_6) at (240mm,90mm) {};
+\draw[->,very thick,color=red] (s_0_6.center) -- (r_0_6.center); 
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (241mm,75mm) {};
 \draw[->] (s_0_5.center) -- (r_0_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (90mm,180mm) {};
-\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_17) at (100mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_16) at (110mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (120mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (130mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (91mm,60mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (251mm,60mm) {};
 \draw[->] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (101mm,45mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (261mm,45mm) {};
 \draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_23) at (101mm,345mm) {};
-\draw[->] (s_18_23.center) -- (r_18_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_6) at (110mm,90mm) {};
-\draw[->,very thick,color=red] (s_18_6.center) -- (r_18_6.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_6_11) at (120mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_10) at (130mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_9) at (140mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_8) at (150mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_7) at (160mm,90mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_17) at (111mm,255mm) {};
-\draw[->] (s_12_17.center) -- (r_12_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (111mm,30mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (271mm,30mm) {};
 \draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_22) at (111mm,330mm) {};
-\draw[->] (s_18_22.center) -- (r_18_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_16) at (121mm,240mm) {};
-\draw[->] (s_12_16.center) -- (r_12_16.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (121mm,15mm) {};
+\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (281mm,15mm) {};
 \draw[->] (s_0_1.center) -- (r_0_1.center);
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_21) at (121mm,315mm) {};
-\draw[->] (s_18_21.center) -- (r_18_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_11) at (131mm,165mm) {};
-\draw[->] (s_6_11.center) -- (r_6_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_20) at (131mm,300mm) {};
-\draw[->] (s_18_20.center) -- (r_18_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (131mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_19) at (141mm,285mm) {};
-\draw[->] (s_18_19.center) -- (r_18_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (141mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_10) at (141mm,150mm) {};
-\draw[->] (s_6_10.center) -- (r_6_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_9) at (151mm,135mm) {};
-\draw[->] (s_6_9.center) -- (r_6_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_8) at (161mm,120mm) {};
-\draw[->] (s_6_8.center) -- (r_6_8.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_7) at (171mm,105mm) {};
-\draw[->] (s_6_7.center) -- (r_6_7.center);

### 2013-06-06 paper.tex
Move to Laptop

@@
 \usepackage[ruled,vlined]{algorithm2e}
-
+\usepackage[toc,page]{appendix}
 % ==================================================
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{appendices}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{UMP performance}
+
+Plot~\ref{pgfplot:20130605} shows the latency of UMP on ziger as the
+number of cycles required for a RTT between core 0 and each of the
+other cores.
+
+\begin{figure}
+  \caption{UMP latency between core 0 and target core}
+  \label{pgfplot:20130605}
+  \begin{tikzpicture}
+    \begin{axis}[
+        xlabel={target core},
+        ylabel={cycles},
+        ymin=0
+        ]
+    \addplot[
+        color=red,
+        mark=x,
+        error bars/y dir=both,
+        error bars/y explicit
+        ] coordinates {
+      (0,905.302469) +- (5.475974,5.475974)
+      (1,899.453086) +- (4.273189,4.273189)
+      (2,900.216049) +- (6.050119,6.050119)
+      (3,908.808642) +- (6.189132,6.189132)
+      (4,900.155556) +- (5.692577,5.692577)
+      (5,1139.145679) +- (5.447710,5.447710)
+      (6,1139.200000) +- (5.011050,5.011050)
+      (7,1135.722222) +- (7.258244,7.258244)
+      (8,1141.523457) +- (6.521385,6.521385)
+      (9,1132.918519) +- (5.502482,5.502482)
+      (10,1131.333333) +- (4.893432,4.893432)
+      (11,1151.814815) +- (6.316764,6.316764)
+      (12,1153.251852) +- (6.078156,6.078156)
+      (13,1153.269136) +- (5.148574,5.148574)
+      (14,1150.670370) +- (4.862935,4.862935)
+      (15,1152.801235) +- (7.096426,7.096426)
+      (16,1157.601235) +- (7.356042,7.356042)
+      (17,1395.401235) +- (5.607601,5.607601)
+      (18,1394.076543) +- (7.313209,7.313209)
+      (19,1390.329630) +- (5.080219,5.080219)
+      (20,1391.237037) +- (5.837986,5.837986)
+      (21,1390.192593) +- (4.992087,4.992087)
+      (22,1397.954321) +- (4.711073,4.711073)
+    };
+    \end{axis}
+  \end{tikzpicture}
+\end{figure}
+
+Plot~\ref{pgfplot:20130605_send} shows the send cost for sending a message
+from each core to core 0. This cost is nearly independent from which
+core sends the message.
+
+\begin{figure}
+  \caption{UMP send cost between core 0 and target core}
+  \label{pgfplot:20130605_send}
+  \begin{tikzpicture}
+    \begin{axis}[
+        xlabel={target core},
+        ylabel={cycles},
+        ymin=0
+        ]
+    \addplot[
+        color=red,
+        mark=x,
+        error bars/y dir=both,
+        error bars/y explicit
+        ] coordinates {
+      (0,244.197531) +- (4.324549,4.324549)
+      (1,246.407407) +- (4.943577,4.943577)
+      (2,245.567901) +- (2.985307,2.985307)
+      (3,244.543210) +- (5.632905,5.632905)
+      (4,243.530864) +- (4.237069,4.237069)
+      (5,245.061728) +- (5.160021,5.160021)
+      (6,245.901235) +- (2.386200,2.386200)
+      (7,247.481481) +- (4.643092,4.643092)
+      (8,245.901235) +- (3.723814,3.723814)
+      (9,243.197531) +- (3.305139,3.305139)
+      (10,246.530864) +- (2.277569,2.277569)
+      (11,243.913580) +- (4.795053,4.795053)
+      (12,246.259259) +- (3.640573,3.640573)
+      (13,243.469136) +- (4.121867,4.121867)
+      (14,242.283951) +- (3.732522,3.732522)
+      (15,244.851852) +- (6.142568,6.142568)
+      (16,242.209877) +- (4.302500,4.302500)
+      (17,258.012346) +- (4.010769,4.010769)
+      (18,256.765432) +- (4.266642,4.266642)
+      (19,256.592593) +- (6.050768,6.050768)
+      (20,255.382716) +- (4.226804,4.226804)
+      (21,258.666667) +- (5.003702,5.003702)
+      (22,255.567901) +- (4.219117,4.219117)
+    };
+    \end{axis}
+  \end{tikzpicture}
+\end{figure}
+
+Plot~\ref{pgfplot:20130605} shows the receive time on every core when
+receiving a UMP message from core 0.
+
+\begin{figure}
+  \caption{UMP receive time between core 0 and target core}
+  \label{pgfplot:20130605}
+  \begin{tikzpicture}
+    \begin{axis}[
+        xlabel={target core},
+        ylabel={cycles},
+        ymin=0
+        ]
+    \addplot[
+        color=red,
+        mark=x,
+        error bars/y dir=both,
+        error bars/y explicit
+        ] coordinates {
+      (0,262.716049) +- (19.216913,19.216913)
+      (1,250.864198) +- (18.156897,18.156897)
+      (2,253.271605) +- (16.264794,16.264794)
+      (3,264.481481) +- (19.195621,19.195621)
+      (4,262.876543) +- (20.073558,20.073558)
+      (5,406.592593) +- (12.717032,12.717032)
+      (6,417.086420) +- (16.644576,16.644576)
+      (7,414.913580) +- (19.692198,19.692198)
+      (8,417.024691) +- (15.754267,15.754267)
+      (9,416.345679) +- (20.657800,20.657800)
+      (10,417.320988) +- (15.662984,15.662984)
+      (11,432.172840) +- (28.319513,28.319513)
+      (12,427.814815) +- (22.042110,22.042110)
+      (13,429.234568) +- (26.883963,26.883963)
+      (14,424.814815) +- (18.533994,18.533994)
+      (15,426.283951) +- (17.456991,17.456991)
+      (16,425.444444) +- (15.939701,15.939701)
+      (17,506.333333) +- (9.086688,9.086688)
+      (18,503.679012) +- (7.018190,7.018190)
+      (19,518.222222) +- (9.838197,9.838197)
+      (20,522.506173) +- (9.367824,9.367824)
+      (21,517.111111) +- (9.108401,9.108401)
+      (22,504.703704) +- (6.788597,6.788597)
+    };
+    \end{axis}
+  \end{tikzpicture}
+\end{figure}
+
 \newpage
@@
 
+\end{appendices}
+
 \end{document}

### 2013-06-06 graphs/appenzeller.py

@@ -1,0 +1,57 @@
+#!/usr/bin/env python
+
+import model
+import numa_model
+import helpers
+from pygraph.algorithms.minmax import shortest_path
+from pygraph.classes.graph import graph
+from pygraph.classes.digraph import digraph
+
+# --------------------------------------------------
+class Appenzeller(numa_model.NUMAModel):
+
+    def __init__(self):
+        """
+        Build the model and use it to initialize the Model superclass
+        """
+        g = super(Appenzeller, self)._build_graph()
+        super(Appenzeller, self).__init__(g)
+
+    # --------------------------------------------------
+    # Characteritics of model
+    def get_name(self):
+        return "appenzeller"
+
+    def get_num_numa_nodes(self):
+        return 8
+
+    def get_num_cores(self):
+        return 6
+
+    def get_numa_information(self):
+        g_numa = graph()
+        g_numa.add_nodes(range(self.get_num_numa_nodes()))
+
+        d = dict() # 8x4 /2 = 16 links
+        d[0] = [1,2,4,5]
+        d[1] = [0,3,5,4]
+        d[2] = [0,3,6,7]
+        d[3] = [2,6,7,1]
+        d[4] = [0,1,5,6]
+        d[5] = [0,1,4,7]
+        d[6] = [2,3,7,4]
+        d[7] = [2,3,6,5]
+
+        errors = 0
+        for s in range(8):
+            for d in d[s]:
+                try:
+                    g_numa.add_edge((s,d))
+                except:
+                    errors += 1
+                    
+        assert errors == 16
+
+        helpers.output_graph(g_numa, 'appenzeller_numa');
+
+        return g_numa

### 2013-06-06 graphs/helpers.py

@@ -174,7 +174,7 @@ def statistics_cropped(l, r=.1):
 def statistics(l):
     """
     Print statistics for the given list of integers
-    @return A tuple (mean, stderr, min, max)
+    @return A tuple (mean, stderr, median, min, max)
     """
     if not isinstance(l, list) or len(l)<1:
         return None
@@ -188,17 +188,19 @@ def statistics(l):
     return (m, d, median, nums.min(), nums.max())
 
 
-def _pgf_plot_header(f, plotname, caption, xlabel, ylabel):
+def _pgf_plot_header(f, plotname, caption, xlabel, ylabel, attr=[], desc='...'):
     label = "pgfplot:%s" % plotname
-    s = (("Plot~\\ref{%s} shows ...\n"
+    s = (("Plot~\\ref{%s} shows %s\n"
+          "\\pgfplotsset{width=\linewidth}\n"
           "\\begin{figure}\n"
           "  \\caption{%s}\n"
           "  \\label{%s}\n"
           "  \\begin{tikzpicture}\n"
           "    \\begin{axis}[\n"
+          "        %s,\n" 
           "        xlabel={%s},\n"
           "        ylabel={%s}\n"
-          "        ]\n") % (label, caption, label, xlabel, ylabel))
+          "        ]\n") % (label, desc, caption, label, ','.join(attr), xlabel, ylabel))
     f.write(s)
 
 
@@ -209,7 +211,7 @@ def _pgf_plot_footer(f):
     f.write(s)
 
     
-def do_pgf_plot(f, data, caption, xlabel, ylabel):
+def do_pgf_plot(f, data, caption='', xlabel='', ylabel=''):
     """
     Generate PGF plot code for the given data
     @param f File to write the code to
@@ -230,6 +232,72 @@ def do_pgf_plot(f, data, caption, xlabel, ylabel):
             f.write("      (%d,%f) +- (%f,%f)\n" % (d[0], d[1], d[2], d[2]))
 
     f.write("    };\n");
+    _pgf_plot_footer(f)
+
+def _latex_header(f):
+    header = (
+        "\\documentclass[a4wide]{article}\n"
+        "\\usepackage{url,color,xspace,verbatim,subfig,ctable,multirow,listings}\n"
+        "\\usepackage[utf8]{inputenc}\n"
+        "\\usepackage[T1]{fontenc}\n"
+        "\\usepackage{txfonts}\n"
+        "\\usepackage{rotating}\n"
+        "\\usepackage{paralist}\n"
[…]

### 2013-06-06 graphs/mst.py

@@ -1,0 +1,51 @@
+# Copyright (c) 2007, 2008, 2009, 2010, 2011, 2012, 2013 ETH Zurich.
+
+# Import graphviz
+import sys
+sys.path.append('..')
+sys.path.append('/usr/lib/graphviz/python/')
+sys.path.append('/usr/lib64/graphviz/python/')
+import gv
+import logging
+
+# Import pygraph
+from pygraph.classes.digraph import digraph
+from pygraph.algorithms.minmax import minimal_spanning_tree
+from pygraph.classes.graph import graph
+
+# Import own code
+import overlay
+
+class Mst(overlay.Overlay):
+    """
+    Build overlay based on minimum spanning tree
+
+    Problems with this are:
+    - parallelism not considered, resulting graph could be a path
+
+    """
+    
+    def __init__(self, mod):
+        """
+        Initialize the clustering algorithm
+        """
+        super(Mst, self).__init__(mod)
+        
+    def get_name(self):
+        return "mst"
+
+    def _get_broadcast_tree(self):
+        """
+        Run MST algorithm
+        """
+        mst = graph()
+        mst.add_nodes(range(self.mod.get_num_cores()))
+
+        gr = self.mod.get_graph()
+
+        mst_edges = minimal_spanning_tree(gr)
+        for i in range(len(mst_edges)):
+            if mst_edges[i] != None:
+                mst.add_edge((mst_edges[i], i), \
+                                 gr.edge_weight((mst_edges[i], i)))
+        return mst

### 2013-06-06 graphs/simulator.py

@@ -30,6 +30,7 @@ import mst
 
 import scheduling
 import sort_longest
+import ump
 
 import pdb
 import argparse
@@ -86,6 +87,9 @@ def build_and_simulate():
     parser.add_argument('--evaluate-machine', dest="action", action="store_const",
                         const="evaluate-machine", default="simulate", 
                         help="Dump machine model instead of simulating")
+    parser.add_argument('--ump-breakdown', dest="action", action="store_const",
+                        const="ump-breakdown", default="simulate", 
+                        help="Dump machine model instead of simulating")
     parser.add_argument('machine', choices=machines,
                         help="Machine to simulate")
     parser.add_argument('overlay', choices=topologies,
@@ -105,6 +109,10 @@ def build_and_simulate():
         print "Cost for tree is: %d, last node is %d" % (ev.time, ev.last_node)
         # Output c configuration for quorum program
         helpers.output_quorum_configuration(m, final_graph, root, sched, topology)
+
+    elif args.action == 'ump-breakdown':
+        ump.execute_ump_breakdown()
+        return 0
 
     elif args.action == "evaluate":
         print "Evaluating model"

### 2013-06-06 graphs/ump.py

@@ -1,0 +1,16 @@
+import sys
+import tempfile
+import subprocess
+
+def execute_ump_breakdown():
+
+    build = tempfile.mkdtemp()
+    result = tempfile.mkdtemp()
+
+    print result
+
+    subprocess.call(['/home/skaestle/bf/quorum/tools/harness/scalebench.py',
+                     '-B', build, 
+                     '-m', 'ziger1', 
+                     '-t', 'ump_latency', 
+                     '/home/skaestle/bf/quorum/', result])

### 2013-06-07 graphs/draw.py
Improved visualization

@@ -5,7 +5,11 @@ import numa_model
 class Output():
 
     color_map = [ "red", "green", "blue", "orange" ]
-    height_per_core = 15
+    height_per_core = 5
+    obj_per_node = dict()
+    obj = []
+    scale_x = .6
+    last_node = None
 
     "Wrapper to enable visualization output to file"
     def __init__(self, name, model, topo):
@@ -14,27 +18,24 @@ class Output():
         self.topo =  topo
         self.f = open(name, 'w')
         for i in range(self.model.get_num_cores()):
-            # Background
-            cidx = int(self.model.get_numa_id(i)) % int(len(self.color_map))
-            color = self.color_map[cidx]
-            self.f.write("\\draw[fill,color=%s!10] (-3cm,%fmm) rectangle (30cm,%fmm);\n" % \
-                             ( \
-                    color, 
-                    self._y_coord_for_core(i) + (self.height_per_core/2.), \
-                    self._y_coord_for_core(i) - (self.height_per_core/2.) \
-                    ))
             # Label
-            self.f.write("\\node at (0mm,%dmm) {core %02d};\n" % \
-                             (self._y_coord_for_core(i), i))
-            # y-axis
-            self.f.write("\\draw[color=black!30] (20mm,%dmm) -- (30cm,%dmm);\n" % \
-                             (self._y_coord_for_core(i), \
-                                  self._y_coord_for_core(i)))
-        self.f.write("\\node at (0mm,%dmm) {Machine: %s, topology: %s};\n" % (
-                self._y_coord_for_core(self.model.get_num_cores()),
-                self.model.get_name(),
-                self.topo.get_name()
-                ))
+            node_name = 'core_%d_label' % i
+            self.__add_object(i, node_name)
+            self.f.write("\\node (%s) at (0mm,%dmm) {core %02d};\n" % \
+                             (node_name, self._y_coord_for_core(i), i))
+
+    def __add_object(self, core, label):
+        """
+        Keep track of objects for fit tikz class
+        Assumes that the object printes last is shown all the way to the right
+        """
+        self.obj.append(label)
+        cidx = int(self.model.get_numa_id(core))
+        if not cidx in self.obj_per_node:
+            self.obj_per_node[cidx] = [ label ]
+        else:
+            self.obj_per_node[cidx].append(label)
+        self.last_node = label
 
     def _y_coord_for_core(self, core):
[…]

### 2013-06-07 graphs/visu_gruyere_badtree.tex
New visualization applied to all combinations of machines and topologies except for rings

@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
-\node at (0mm,360mm) {core 24};
-\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
-\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
-\node at (0mm,375mm) {core 25};
-\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
-\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
-\node at (0mm,390mm) {core 26};
-\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
-\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
-\node at (0mm,405mm) {core 27};
-\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
-\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
-\node at (0mm,420mm) {core 28};
-\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
-\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
-\node at (0mm,435mm) {core 29};
-\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
-\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
-\node at (0mm,450mm) {core 30};
-\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
-\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
-\node at (0mm,465mm) {core 31};
-\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: badtree};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_14) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_28) at (60mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_14) at (90mm,210mm) {};
-\draw[->,very thick,color=red] (s_0_14.center) -- (r_0_14.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_14_1) at (100mm,210mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_14_19) at (110mm,210mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_28) at (100mm,420mm) {};
-\draw[->,very thick,color=red] (s_0_28.center) -- (r_0_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_3) at (110mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_17) at (120mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_1) at (140mm,15mm) {};
-\draw[->,very thick,color=red] (s_14_1.center) -- (r_14_1.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_1_27) at (150mm,15mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_1_15) at (160mm,15mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_19) at (150mm,285mm) {};
-\draw[->,very thick,color=red] (s_14_19.center) -- (r_14_19.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_19_13) at (160mm,285mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_19_9) at (170mm,285mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_3) at (150mm,45mm) {};
-\draw[->,very thick,color=red] (s_28_3.center) -- (r_28_3.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_3_26) at (160mm,45mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_3_25) at (170mm,45mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_17) at (160mm,255mm) {};
-\draw[->,very thick,color=red] (s_28_17.center) -- (r_28_17.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_17_29) at (170mm,255mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_17_12) at (180mm,255mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_27) at (190mm,405mm) {};
-\draw[->,very thick,color=red] (s_1_27.center) -- (r_1_27.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_27_2) at (200mm,405mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_27_6) at (210mm,405mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_26) at (200mm,390mm) {};
-\draw[->,very thick,color=red] (s_3_26.center) -- (r_3_26.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_26_5) at (210mm,390mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_19_13) at (200mm,195mm) {};
-\draw[->,very thick,color=red] (s_19_13.center) -- (r_19_13.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_13_21) at (210mm,195mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_13_20) at (220mm,195mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_15) at (200mm,225mm) {};
-\draw[->,very thick,color=red] (s_1_15.center) -- (r_1_15.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_15_18) at (210mm,225mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_15_16) at (220mm,225mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_25) at (210mm,375mm) {};
-\draw[->,very thick,color=red] (s_3_25.center) -- (r_3_25.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_25_7) at (220mm,375mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_25_4) at (230mm,375mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_19_9) at (210mm,135mm) {};
-\draw[->,very thick,color=red] (s_19_9.center) -- (r_19_9.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_9_23) at (220mm,135mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_9_22) at (230mm,135mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_17_29) at (210mm,435mm) {};
-\draw[->,very thick,color=red] (s_17_29.center) -- (r_17_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_17_12) at (220mm,180mm) {};
-\draw[->,very thick,color=red] (s_17_12.center) -- (r_17_12.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_27_2) at (240mm,30mm) {};
-\draw[->,very thick,color=red] (s_27_2.center) -- (r_27_2.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_2_30) at (250mm,30mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_2_24) at (260mm,30mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_26_5) at (240mm,75mm) {};
-\draw[->,very thick,color=red] (s_26_5.center) -- (r_26_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_27_6) at (240mm,90mm) {};
-\draw[->,very thick,color=red] (s_27_6.center) -- (r_27_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_21) at (240mm,315mm) {};
-\draw[->,very thick,color=red] (s_13_21.center) -- (r_13_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_20) at (250mm,300mm) {};
-\draw[->,very thick,color=red] (s_13_20.center) -- (r_13_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_15_18) at (250mm,270mm) {};
-\draw[->,very thick,color=red] (s_15_18.center) -- (r_15_18.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_18_10) at (260mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_8) at (270mm,270mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_25_7) at (250mm,105mm) {};
-\draw[->,very thick,color=red] (s_25_7.center) -- (r_25_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_23) at (250mm,345mm) {};
-\draw[->,very thick,color=red] (s_9_23.center) -- (r_9_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_22) at (260mm,330mm) {};
-\draw[->,very thick,color=red] (s_9_22.center) -- (r_9_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_25_4) at (260mm,60mm) {};
-\draw[->,very thick,color=red] (s_25_4.center) -- (r_25_4.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_15_16) at (260mm,240mm) {};
-\draw[->,very thick,color=red] (s_15_16.center) -- (r_15_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_31) at (270mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_11) at (280mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_30) at (290mm,450mm) {};
-\draw[->,very thick,color=red] (s_2_30.center) -- (r_2_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_24) at (300mm,360mm) {};
-\draw[->,very thick,color=red] (s_2_24.center) -- (r_2_24.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_10) at (300mm,150mm) {};
-\draw[->,very thick,color=red] (s_18_10.center) -- (r_18_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_8) at (310mm,120mm) {};
-\draw[->,very thick,color=red] (s_18_8.center) -- (r_18_8.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_31) at (310mm,465mm) {};
-\draw[->,very thick,color=red] (s_16_31.center) -- (r_16_31.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_11) at (320mm,165mm) {};
-\draw[->,very thick,color=red] (s_16_11.center) -- (r_16_11.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node (core_16_label) at (0mm,80mm) {core 16};
+\node (core_17_label) at (0mm,85mm) {core 17};
+\node (core_18_label) at (0mm,90mm) {core 18};
+\node (core_19_label) at (0mm,95mm) {core 19};
+\node (core_20_label) at (0mm,100mm) {core 20};
+\node (core_21_label) at (0mm,105mm) {core 21};
+\node (core_22_label) at (0mm,110mm) {core 22};
+\node (core_23_label) at (0mm,115mm) {core 23};
+\node (core_24_label) at (0mm,120mm) {core 24};
+\node (core_25_label) at (0mm,125mm) {core 25};
+\node (core_26_label) at (0mm,130mm) {core 26};
+\node (core_27_label) at (0mm,135mm) {core 27};
+\node (core_28_label) at (0mm,140mm) {core 28};
+\node (core_29_label) at (0mm,145mm) {core 29};
+\node (core_30_label) at (0mm,150mm) {core 30};
+\node (core_31_label) at (0mm,155mm) {core 31};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_14) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_28) at (24mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_14) at (36mm,70mm) {};
+\draw[->,semithick,color=red] ($(s_0_14.east)-(1mm,0mm)$) -- ($(r_0_14.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_14_1) at (40mm,70mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_14_19) at (44mm,70mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_28) at (40mm,140mm) {};
+\draw[->,semithick,color=red] ($(s_0_28.east)-(1mm,0mm)$) -- ($(r_0_28.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_28_3) at (44mm,140mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_28_17) at (48mm,140mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_14_1) at (56mm,5mm) {};
+\draw[->,semithick,color=red] ($(s_14_1.east)-(1mm,0mm)$) -- ($(r_14_1.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_1_27) at (60mm,5mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_1_15) at (64mm,5mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_28_3) at (60mm,15mm) {};
+\draw[->,semithick,color=red] ($(s_28_3.east)-(1mm,0mm)$) -- ($(r_28_3.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_26) at (64mm,15mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_25) at (68mm,15mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_14_19) at (60mm,95mm) {};
+\draw[->,semithick,color=red] ($(s_14_19.east)-(1mm,0mm)$) -- ($(r_14_19.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_19_13) at (64mm,95mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_19_9) at (68mm,95mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_28_17) at (64mm,85mm) {};
+\draw[->,semithick,color=red] ($(s_28_17.east)-(1mm,0mm)$) -- ($(r_28_17.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_17_29) at (68mm,85mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_17_12) at (72mm,85mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_1_27) at (76mm,135mm) {};
+\draw[->,semithick,color=red] ($(s_1_27.east)-(1mm,0mm)$) -- ($(r_1_27.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_27_2) at (80mm,135mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_27_6) at (84mm,135mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_19_13) at (80mm,65mm) {};
+\draw[->,semithick,color=red] ($(s_19_13.east)-(1mm,0mm)$) -- ($(r_19_13.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_13_21) at (84mm,65mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_13_20) at (88mm,65mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_1_15) at (80mm,75mm) {};
+\draw[->,semithick,color=red] ($(s_1_15.east)-(1mm,0mm)$) -- ($(r_1_15.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_15_18) at (84mm,75mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_15_16) at (88mm,75mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_26) at (80mm,130mm) {};
+\draw[->,semithick,color=red] ($(s_3_26.east)-(1mm,0mm)$) -- ($(r_3_26.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_26_5) at (84mm,130mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_19_9) at (84mm,45mm) {};
+\draw[->,semithick,color=red] ($(s_19_9.east)-(1mm,0mm)$) -- ($(r_19_9.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_9_23) at (88mm,45mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_9_22) at (92mm,45mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_17_29) at (84mm,145mm) {};
+\draw[->,semithick,color=red] ($(s_17_29.east)-(1mm,0mm)$) -- ($(r_17_29.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_25) at (84mm,125mm) {};
+\draw[->,semithick,color=red] ($(s_3_25.east)-(1mm,0mm)$) -- ($(r_3_25.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_25_7) at (88mm,125mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_25_4) at (92mm,125mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_17_12) at (88mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_17_12.east)-(1mm,0mm)$) -- ($(r_17_12.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_26_5) at (96mm,25mm) {};
+\draw[->,semithick,color=red] ($(s_26_5.east)-(1mm,0mm)$) -- ($(r_26_5.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_13_21) at (96mm,105mm) {};
+\draw[->,semithick,color=red] ($(s_13_21.east)-(1mm,0mm)$) -- ($(r_13_21.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_27_6) at (96mm,30mm) {};
+\draw[->,semithick,color=red] ($(s_27_6.east)-(1mm,0mm)$) -- ($(r_27_6.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_27_2) at (96mm,10mm) {};
+\draw[->,semithick,color=red] ($(s_27_2.east)-(1mm,0mm)$) -- ($(r_27_2.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_2_30) at (100mm,10mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_2_24) at (104mm,10mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_9_23) at (100mm,115mm) {};
+\draw[->,semithick,color=red] ($(s_9_23.east)-(1mm,0mm)$) -- ($(r_9_23.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_15_18) at (100mm,90mm) {};
+\draw[->,semithick,color=red] ($(s_15_18.east)-(1mm,0mm)$) -- ($(r_15_18.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_10) at (104mm,90mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_8) at (108mm,90mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_13_20) at (100mm,100mm) {};
+\draw[->,semithick,color=red] ($(s_13_20.east)-(1mm,0mm)$) -- ($(r_13_20.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_25_7) at (100mm,35mm) {};
+\draw[->,semithick,color=red] ($(s_25_7.east)-(1mm,0mm)$) -- ($(r_25_7.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_25_4) at (104mm,20mm) {};
+\draw[->,semithick,color=red] ($(s_25_4.east)-(1mm,0mm)$) -- ($(r_25_4.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_9_22) at (104mm,110mm) {};
+\draw[->,semithick,color=red] ($(s_9_22.east)-(1mm,0mm)$) -- ($(r_9_22.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_15_16) at (104mm,80mm) {};
+\draw[->,semithick,color=red] ($(s_15_16.east)-(1mm,0mm)$) -- ($(r_15_16.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_16_31) at (108mm,80mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_16_11) at (112mm,80mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_2_30) at (116mm,150mm) {};
+\draw[->,semithick,color=red] ($(s_2_30.east)-(1mm,0mm)$) -- ($(r_2_30.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_2_24) at (120mm,120mm) {};
+\draw[->,semithick,color=red] ($(s_2_24.east)-(1mm,0mm)$) -- ($(r_2_24.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_10) at (120mm,50mm) {};
+\draw[->,semithick,color=red] ($(s_18_10.east)-(1mm,0mm)$) -- ($(r_18_10.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_8) at (124mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_18_8.east)-(1mm,0mm)$) -- ($(r_18_8.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_16_31) at (124mm,155mm) {};
+\draw[->,semithick,color=red] ($(s_16_31.east)-(1mm,0mm)$) -- ($(r_16_31.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_16_11) at (128mm,55mm) {};
+\draw[->,semithick,color=red] ($(s_16_11.east)-(1mm,0mm)$) -- ($(r_16_11.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_14) (s_0_28) (r_0_14) (s_14_1) (s_14_19) (r_0_28) (s_28_3) (s_28_17) (r_14_1) (s_1_27) (s_1_15) (r_14_19) (s_19_13) (s_19_9) (r_28_3) (s_3_26) (s_3_25) (r_28_17) (s_17_29) (s_17_12) (r_1_27) (s_27_2) (s_27_6) (r_3_26) (s_26_5) (r_1_15) (s_15_18) (s_15_16) (r_19_13) (s_13_21) (s_13_20) (r_3_25) (s_25_7) (s_25_4) (r_17_29) (r_19_9) (s_9_23) (s_9_22) (r_17_12) (r_27_2) (s_2_30) (s_2_24) (r_13_21) (r_27_6) (r_26_5) (r_13_20) (r_25_7) (r_15_18) (s_18_10) (s_18_8) (r_9_23) (r_25_4) (r_15_16) (s_16_31) (s_16_11) (r_9_22) (r_2_30) (r_18_10) (r_2_24) (r_18_8) (r_16_31) (r_16_11) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_14) (s_0_28) (r_0_14) (s_14_1) (s_14_19) (r_0_28) (s_28_3) (s_28_17) (r_14_1) (s_1_27) (s_1_15) (r_28_3) (s_3_26) (s_3_25) (r_14_19) (s_19_13) (s_19_9) (r_28_17) (s_17_29) (s_17_12) (r_1_27) (s_27_2) (s_27_6) (r_19_13) (s_13_21) (s_13_20) (r_1_15) (s_15_18) (s_15_16) (r_3_26) (s_26_5) (r_19_9) (s_9_23) (s_9_22) (r_17_29) (r_3_25) (s_25_7) (s_25_4) (r_17_12) (r_26_5) (r_13_21) (r_27_6) (r_27_2) (s_2_30) (s_2_24) (r_9_23) (r_15_18) (s_18_10) (s_18_8) (r_13_20) (r_25_7) (r_25_4) (r_9_22) (r_15_16) (s_16_31) (s_16_11) (r_2_30) (r_2_24) (r_18_10) (r_18_8) (r_16_31) (r_16_11)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_14) (s_0_28) (r_0_14) (s_14_1) (s_14_19) (r_0_28) (s_28_3) (s_28_17) (r_14_1) (s_1_27) (s_1_15) (r_14_19) (s_19_13) (s_19_9) (r_28_3) (s_3_26) (s_3_25) (r_28_17) (s_17_29) (s_17_12) (r_1_27) (s_27_2) (s_27_6) (r_3_26) (s_26_5) (r_1_15) (s_15_18) (s_15_16) (r_19_13) (s_13_21) (s_13_20) (r_3_25) (s_25_7) (s_25_4) (r_17_29) (r_19_9) (s_9_23) (s_9_22) (r_17_12) (r_27_2) (s_2_30) (s_2_24) (r_13_21) (r_27_6) (r_26_5) (r_13_20) (r_25_7) (r_15_18) (s_18_10) (s_18_8) (r_9_23) (r_25_4) (r_15_16) (s_16_31) (s_16_11) (r_9_22) (r_2_30) (r_18_10) (r_2_24) (r_18_8) (r_16_31) (r_16_11) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_14) (s_0_28) (r_0_14) (s_14_1) (s_14_19) (r_0_28) (s_28_3) (s_28_17) (r_14_1) (s_1_27) (s_1_15) (r_28_3) (s_3_26) (s_3_25) (r_14_19) (s_19_13) (s_19_9) (r_28_17) (s_17_29) (s_17_12) (r_1_27) (s_27_2) (s_27_6) (r_19_13) (s_13_21) (s_13_20) (r_1_15) (s_15_18) (s_15_16) (r_3_26) (s_26_5) (r_19_9) (s_9_23) (s_9_22) (r_17_29) (r_3_25) (s_25_7) (s_25_4) (r_17_12) (r_26_5) (r_13_21) (r_27_6) (r_27_2) (s_2_30) (s_2_24) (r_9_23) (r_15_18) (s_18_10) (s_18_8) (r_13_20) (r_25_7) (r_25_4) (r_9_22) (r_15_16) (s_16_31) (s_16_11) (r_2_30) (r_2_24) (r_18_10) (r_18_8) (r_16_31) (r_16_11),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_16) at (\x1,80mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_17) at (\x1,85mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_18) at (\x1,90mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_19) at (\x1,95mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_20) at (\x1,100mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_21) at (\x1,105mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_22) at (\x1,110mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_23) at (\x1,115mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_24) at (\x1,120mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_25) at (\x1,125mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_26) at (\x1,130mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_27) at (\x1,135mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_28) at (\x1,140mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_29) at (\x1,145mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_30) at (\x1,150mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_31) at (\x1,155mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_14) (s_0_28) (r_14_1) (s_1_27) (s_1_15) (r_28_3) (s_3_26) (s_3_25) (r_27_2) (s_2_30) (s_2_24) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_14) (s_0_28) (r_14_1) (s_1_27) (s_1_15) (r_28_3) (s_3_26) (s_3_25) (r_27_2) (s_2_30) (s_2_24) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_27_6) (r_26_5) (r_25_7) (r_25_4) (numa_axis_4.west) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_26_5) (r_27_6) (r_25_7) (r_25_4) (numa_axis_4.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_19_9) (s_9_23) (s_9_22) (r_18_10) (r_18_8) (r_16_11) (numa_axis_8.west) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_19_9) (s_9_23) (s_9_22) (r_18_10) (r_18_8) (r_16_11) (numa_axis_8.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_0_14) (s_14_1) (s_14_19) (r_1_15) (s_15_18) (s_15_16) (r_19_13) (s_13_21) (s_13_20) (r_17_12) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_0_14) (s_14_1) (s_14_19) (r_19_13) (s_13_21) (s_13_20) (r_1_15) (s_15_18) (s_15_16) (r_17_12) (numa_axis_12.west),rounded corners] {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_16_label) (core_17_label) (core_18_label) (core_19_label) (r_14_19) (s_19_13) (s_19_9) (r_28_17) (s_17_29) (s_17_12) (r_15_18) (s_18_10) (s_18_8) (r_15_16) (s_16_31) (s_16_11) (numa_axis_16.west) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (r_14_19) (s_19_13) (s_19_9) (r_28_17) (s_17_29) (s_17_12) (r_15_18) (s_18_10) (s_18_8) (r_15_16) (s_16_31) (s_16_11) (numa_axis_16.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_13_21) (r_13_20) (r_9_23) (r_9_22) (numa_axis_20.west) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_13_21) (r_9_23) (r_13_20) (r_9_22) (numa_axis_20.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_24_label) (core_25_label) (core_26_label) (core_27_label) (r_1_27) (s_27_2) (s_27_6) (r_3_26) (s_26_5) (r_3_25) (s_25_7) (s_25_4) (r_2_24) (numa_axis_24.west) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (r_1_27) (s_27_2) (s_27_6) (r_3_26) (s_26_5) (r_3_25) (s_25_7) (s_25_4) (r_2_24) (numa_axis_24.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_28_label) (core_29_label) (core_30_label) (core_31_label) (r_0_28) (s_28_3) (s_28_17) (r_17_29) (r_2_30) (r_16_31) (numa_axis_28.west) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (r_0_28) (s_28_3) (s_28_17) (r_17_29) (r_2_30) (r_16_31) (numa_axis_28.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,80mm) -- (\x2,80mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,85mm) -- (\x2,85mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,90mm) -- (\x2,90mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,95mm) -- (\x2,95mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,100mm) -- (\x2,100mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,105mm) -- (\x2,105mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,110mm) -- (\x2,110mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,115mm) -- (\x2,115mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,120mm) -- (\x2,120mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,125mm) -- (\x2,125mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,130mm) -- (\x2,130mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,135mm) -- (\x2,135mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,140mm) -- (\x2,140mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,145mm) -- (\x2,145mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,150mm) -- (\x2,150mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,155mm) -- (\x2,155mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: gruyere, topology: badtree};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_gruyere_binarytree.tex
New visualization applied to all combinations of machines and topologies except for rings

@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
-\node at (0mm,360mm) {core 24};
-\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
-\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
-\node at (0mm,375mm) {core 25};
-\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
-\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
-\node at (0mm,390mm) {core 26};
-\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
-\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
-\node at (0mm,405mm) {core 27};
-\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
-\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
-\node at (0mm,420mm) {core 28};
-\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
-\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
-\node at (0mm,435mm) {core 29};
-\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
-\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
-\node at (0mm,450mm) {core 30};
-\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
-\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
-\node at (0mm,465mm) {core 31};
-\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: binarytree};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (60mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (61mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (71mm,15mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_1_4) at (81mm,15mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (71mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (91mm,30mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (82mm,45mm) {};
-\draw[->] (s_1_3.center) -- (r_1_3.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (92mm,45mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (102mm,45mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (101mm,60mm) {};
-\draw[->,very thick,color=red] (s_1_4.center) -- (r_1_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (111mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (121mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
-\draw[->,very thick,color=red] (s_2_6.center) -- (r_2_6.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_6_14) at (111mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (111mm,75mm) {};
-\draw[->,very thick,color=red] (s_2_5.center) -- (r_2_5.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (121mm,75mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (131mm,75mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (122mm,105mm) {};
-\draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (132mm,105mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (142mm,105mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (122mm,120mm) {};
-\draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (132mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (142mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (131mm,135mm) {};
-\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (141mm,135mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (151mm,135mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (141mm,210mm) {};
-\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_14_30) at (151mm,210mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_14_29) at (161mm,210mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (141mm,150mm) {};
-\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (151mm,150mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (161mm,150mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (151mm,195mm) {};
-\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_13_28) at (161mm,195mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_13_27) at (171mm,195mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (151mm,165mm) {};
-\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (161mm,165mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_11_24) at (171mm,165mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (151mm,180mm) {};
-\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_26) at (161mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_25) at (171mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (162mm,225mm) {};
-\draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_15_31) at (172mm,225mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_30) at (171mm,450mm) {};
-\draw[->,very thick,color=red] (s_14_30.center) -- (r_14_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
-\draw[->,very thick,color=red] (s_7_16.center) -- (r_7_16.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_18) at (172mm,270mm) {};
-\draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (181mm,285mm) {};
-\draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (181mm,300mm) {};
-\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_28) at (181mm,420mm) {};
-\draw[->,very thick,color=red] (s_13_28.center) -- (r_13_28.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (181mm,330mm) {};
-\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_26) at (181mm,390mm) {};
-\draw[->,very thick,color=red] (s_12_26.center) -- (r_12_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_14_29) at (181mm,435mm) {};
-\draw[->,very thick,color=red] (s_14_29.center) -- (r_14_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (182mm,255mm) {};
-\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_27) at (191mm,405mm) {};
-\draw[->,very thick,color=red] (s_13_27.center) -- (r_13_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_25) at (191mm,375mm) {};
-\draw[->,very thick,color=red] (s_12_25.center) -- (r_12_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_11_24) at (191mm,360mm) {};
-\draw[->,very thick,color=red] (s_11_24.center) -- (r_11_24.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (191mm,345mm) {};
-\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (191mm,315mm) {};
-\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_15_31) at (192mm,465mm) {};
-\draw[->,very thick,color=red] (s_15_31.center) -- (r_15_31.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node (core_16_label) at (0mm,80mm) {core 16};
+\node (core_17_label) at (0mm,85mm) {core 17};
+\node (core_18_label) at (0mm,90mm) {core 18};
+\node (core_19_label) at (0mm,95mm) {core 19};
+\node (core_20_label) at (0mm,100mm) {core 20};
+\node (core_21_label) at (0mm,105mm) {core 21};
+\node (core_22_label) at (0mm,110mm) {core 22};
+\node (core_23_label) at (0mm,115mm) {core 23};
+\node (core_24_label) at (0mm,120mm) {core 24};
+\node (core_25_label) at (0mm,125mm) {core 25};
+\node (core_26_label) at (0mm,130mm) {core 26};
+\node (core_27_label) at (0mm,135mm) {core 27};
+\node (core_28_label) at (0mm,140mm) {core 28};
+\node (core_29_label) at (0mm,145mm) {core 29};
+\node (core_30_label) at (0mm,150mm) {core 30};
+\node (core_31_label) at (0mm,155mm) {core 31};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (24mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (24mm,5mm) {};
+\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_1_3) at (28mm,5mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_1_4) at (32mm,5mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (28mm,10mm) {};
+\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_2_6) at (32mm,10mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_2_5) at (36mm,10mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_1_3) at (32mm,15mm) {};
+\draw[->] ($(s_1_3.east)-(1mm,0mm)$) -- ($(r_1_3.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_8) at (36mm,15mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_7) at (40mm,15mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_1_4) at (40mm,20mm) {};
+\draw[->,semithick,color=red] ($(s_1_4.east)-(1mm,0mm)$) -- ($(r_1_4.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_9) at (44mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_10) at (48mm,20mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_2_6) at (40mm,30mm) {};
+\draw[->,semithick,color=red] ($(s_2_6.east)-(1mm,0mm)$) -- ($(r_2_6.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_14) at (44mm,30mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_13) at (48mm,30mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_2_5) at (44mm,25mm) {};
+\draw[->,semithick,color=red] ($(s_2_5.east)-(1mm,0mm)$) -- ($(r_2_5.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_5_12) at (48mm,25mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_5_11) at (52mm,25mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_7) at (48mm,35mm) {};
+\draw[->,semithick,color=red] ($(s_3_7.east)-(1mm,0mm)$) -- ($(r_3_7.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_7_15) at (52mm,35mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_7_16) at (56mm,35mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_8) at (48mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_3_8.east)-(1mm,0mm)$) -- ($(r_3_8.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_18) at (52mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_17) at (56mm,40mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_9) at (52mm,45mm) {};
+\draw[->,semithick,color=red] ($(s_4_9.east)-(1mm,0mm)$) -- ($(r_4_9.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_9_19) at (56mm,45mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_9_20) at (60mm,45mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_10) at (56mm,50mm) {};
+\draw[->,semithick,color=red] ($(s_4_10.east)-(1mm,0mm)$) -- ($(r_4_10.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_10_22) at (60mm,50mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_10_21) at (64mm,50mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_14) at (56mm,70mm) {};
+\draw[->,semithick,color=red] ($(s_6_14.east)-(1mm,0mm)$) -- ($(r_6_14.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_14_30) at (60mm,70mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_14_29) at (64mm,70mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_5_11) at (60mm,55mm) {};
+\draw[->,semithick,color=red] ($(s_5_11.east)-(1mm,0mm)$) -- ($(r_5_11.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_11_23) at (64mm,55mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_11_24) at (68mm,55mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_5_12) at (60mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_5_12.east)-(1mm,0mm)$) -- ($(r_5_12.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_26) at (64mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_25) at (68mm,60mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_13) at (60mm,65mm) {};
+\draw[->,semithick,color=red] ($(s_6_13.east)-(1mm,0mm)$) -- ($(r_6_13.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_13_28) at (64mm,65mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_13_27) at (68mm,65mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_7_15) at (64mm,75mm) {};
+\draw[->,semithick,color=red] ($(s_7_15.east)-(1mm,0mm)$) -- ($(r_7_15.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_15_31) at (68mm,75mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_14_30) at (68mm,150mm) {};
+\draw[->,semithick,color=red] ($(s_14_30.east)-(1mm,0mm)$) -- ($(r_14_30.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_18) at (68mm,90mm) {};
+\draw[->,semithick,color=red] ($(s_8_18.east)-(1mm,0mm)$) -- ($(r_8_18.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_7_16) at (68mm,80mm) {};
+\draw[->,semithick,color=red] ($(s_7_16.east)-(1mm,0mm)$) -- ($(r_7_16.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_26) at (72mm,130mm) {};
+\draw[->,semithick,color=red] ($(s_12_26.east)-(1mm,0mm)$) -- ($(r_12_26.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_13_28) at (72mm,140mm) {};
+\draw[->,semithick,color=red] ($(s_13_28.east)-(1mm,0mm)$) -- ($(r_13_28.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_9_19) at (72mm,95mm) {};
+\draw[->,semithick,color=red] ($(s_9_19.east)-(1mm,0mm)$) -- ($(r_9_19.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_10_22) at (72mm,110mm) {};
+\draw[->,semithick,color=red] ($(s_10_22.east)-(1mm,0mm)$) -- ($(r_10_22.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_9_20) at (72mm,100mm) {};
+\draw[->,semithick,color=red] ($(s_9_20.east)-(1mm,0mm)$) -- ($(r_9_20.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_14_29) at (72mm,145mm) {};
+\draw[->,semithick,color=red] ($(s_14_29.east)-(1mm,0mm)$) -- ($(r_14_29.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_17) at (72mm,85mm) {};
+\draw[->,semithick,color=red] ($(s_8_17.east)-(1mm,0mm)$) -- ($(r_8_17.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_11_24) at (76mm,120mm) {};
+\draw[->,semithick,color=red] ($(s_11_24.east)-(1mm,0mm)$) -- ($(r_11_24.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_10_21) at (76mm,105mm) {};
+\draw[->,semithick,color=red] ($(s_10_21.east)-(1mm,0mm)$) -- ($(r_10_21.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_13_27) at (76mm,135mm) {};
+\draw[->,semithick,color=red] ($(s_13_27.east)-(1mm,0mm)$) -- ($(r_13_27.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_11_23) at (76mm,115mm) {};
+\draw[->,semithick,color=red] ($(s_11_23.east)-(1mm,0mm)$) -- ($(r_11_23.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_25) at (76mm,125mm) {};
+\draw[->,semithick,color=red] ($(s_12_25.east)-(1mm,0mm)$) -- ($(r_12_25.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_15_31) at (76mm,155mm) {};
+\draw[->,semithick,color=red] ($(s_15_31.east)-(1mm,0mm)$) -- ($(r_15_31.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_8) (s_3_7) (r_1_4) (s_4_9) (s_4_10) (r_2_6) (s_6_14) (s_6_13) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (s_7_16) (r_3_8) (s_8_18) (s_8_17) (r_4_9) (s_9_19) (s_9_20) (r_4_10) (s_10_22) (s_10_21) (r_6_14) (s_14_30) (s_14_29) (r_6_13) (s_13_28) (s_13_27) (r_5_11) (s_11_23) (s_11_24) (r_5_12) (s_12_26) (s_12_25) (r_7_15) (s_15_31) (r_14_30) (r_7_16) (r_8_18) (r_9_19) (r_12_26) (r_10_22) (r_9_20) (r_14_29) (r_13_28) (r_8_17) (r_11_24) (r_12_25) (r_11_23) (r_13_27) (r_10_21) (r_15_31) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_8) (s_3_7) (r_1_4) (s_4_9) (s_4_10) (r_2_6) (s_6_14) (s_6_13) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (s_7_16) (r_3_8) (s_8_18) (s_8_17) (r_4_9) (s_9_19) (s_9_20) (r_4_10) (s_10_22) (s_10_21) (r_6_14) (s_14_30) (s_14_29) (r_5_11) (s_11_23) (s_11_24) (r_5_12) (s_12_26) (s_12_25) (r_6_13) (s_13_28) (s_13_27) (r_7_15) (s_15_31) (r_14_30) (r_8_18) (r_7_16) (r_12_26) (r_13_28) (r_9_19) (r_10_22) (r_9_20) (r_14_29) (r_8_17) (r_11_24) (r_10_21) (r_13_27) (r_11_23) (r_12_25) (r_15_31)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_8) (s_3_7) (r_1_4) (s_4_9) (s_4_10) (r_2_6) (s_6_14) (s_6_13) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (s_7_16) (r_3_8) (s_8_18) (s_8_17) (r_4_9) (s_9_19) (s_9_20) (r_4_10) (s_10_22) (s_10_21) (r_6_14) (s_14_30) (s_14_29) (r_6_13) (s_13_28) (s_13_27) (r_5_11) (s_11_23) (s_11_24) (r_5_12) (s_12_26) (s_12_25) (r_7_15) (s_15_31) (r_14_30) (r_7_16) (r_8_18) (r_9_19) (r_12_26) (r_10_22) (r_9_20) (r_14_29) (r_13_28) (r_8_17) (r_11_24) (r_12_25) (r_11_23) (r_13_27) (r_10_21) (r_15_31) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_8) (s_3_7) (r_1_4) (s_4_9) (s_4_10) (r_2_6) (s_6_14) (s_6_13) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (s_7_16) (r_3_8) (s_8_18) (s_8_17) (r_4_9) (s_9_19) (s_9_20) (r_4_10) (s_10_22) (s_10_21) (r_6_14) (s_14_30) (s_14_29) (r_5_11) (s_11_23) (s_11_24) (r_5_12) (s_12_26) (s_12_25) (r_6_13) (s_13_28) (s_13_27) (r_7_15) (s_15_31) (r_14_30) (r_8_18) (r_7_16) (r_12_26) (r_13_28) (r_9_19) (r_10_22) (r_9_20) (r_14_29) (r_8_17) (r_11_24) (r_10_21) (r_13_27) (r_11_23) (r_12_25) (r_15_31),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_16) at (\x1,80mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_17) at (\x1,85mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_18) at (\x1,90mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_19) at (\x1,95mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_20) at (\x1,100mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_21) at (\x1,105mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_22) at (\x1,110mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_23) at (\x1,115mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_24) at (\x1,120mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_25) at (\x1,125mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_26) at (\x1,130mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_27) at (\x1,135mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_28) at (\x1,140mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_29) at (\x1,145mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_30) at (\x1,150mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_31) at (\x1,155mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_8) (s_3_7) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_8) (s_3_7) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_1_4) (s_4_9) (s_4_10) (r_2_6) (s_6_14) (s_6_13) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (s_7_16) (numa_axis_4.west) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_1_4) (s_4_9) (s_4_10) (r_2_6) (s_6_14) (s_6_13) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (s_7_16) (numa_axis_4.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_3_8) (s_8_18) (s_8_17) (r_4_9) (s_9_19) (s_9_20) (r_4_10) (s_10_22) (s_10_21) (r_5_11) (s_11_23) (s_11_24) (numa_axis_8.west) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_3_8) (s_8_18) (s_8_17) (r_4_9) (s_9_19) (s_9_20) (r_4_10) (s_10_22) (s_10_21) (r_5_11) (s_11_23) (s_11_24) (numa_axis_8.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_6_14) (s_14_30) (s_14_29) (r_6_13) (s_13_28) (s_13_27) (r_5_12) (s_12_26) (s_12_25) (r_7_15) (s_15_31) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_6_14) (s_14_30) (s_14_29) (r_5_12) (s_12_26) (s_12_25) (r_6_13) (s_13_28) (s_13_27) (r_7_15) (s_15_31) (numa_axis_12.west),rounded corners] {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_16_label) (core_17_label) (core_18_label) (core_19_label) (r_7_16) (r_8_18) (r_9_19) (r_8_17) (numa_axis_16.west) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (r_8_18) (r_7_16) (r_9_19) (r_8_17) (numa_axis_16.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_10_22) (r_9_20) (r_11_23) (r_10_21) (numa_axis_20.west) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_10_22) (r_9_20) (r_10_21) (r_11_23) (numa_axis_20.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_24_label) (core_25_label) (core_26_label) (core_27_label) (r_12_26) (r_11_24) (r_12_25) (r_13_27) (numa_axis_24.west) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (r_12_26) (r_11_24) (r_13_27) (r_12_25) (numa_axis_24.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_28_label) (core_29_label) (core_30_label) (core_31_label) (r_14_30) (r_14_29) (r_13_28) (r_15_31) (numa_axis_28.west) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (r_14_30) (r_13_28) (r_14_29) (r_15_31) (numa_axis_28.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,80mm) -- (\x2,80mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,85mm) -- (\x2,85mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,90mm) -- (\x2,90mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,95mm) -- (\x2,95mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,100mm) -- (\x2,100mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,105mm) -- (\x2,105mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,110mm) -- (\x2,110mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,115mm) -- (\x2,115mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,120mm) -- (\x2,120mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,125mm) -- (\x2,125mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,130mm) -- (\x2,130mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,135mm) -- (\x2,135mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,140mm) -- (\x2,140mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,145mm) -- (\x2,145mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,150mm) -- (\x2,150mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,155mm) -- (\x2,155mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: gruyere, topology: binarytree};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_gruyere_cluster.tex
New visualization applied to all combinations of machines and topologies except for rings

@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
-\node at (0mm,360mm) {core 24};
-\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
-\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
-\node at (0mm,375mm) {core 25};
-\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
-\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
-\node at (0mm,390mm) {core 26};
-\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
-\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
-\node at (0mm,405mm) {core 27};
-\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
-\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
-\node at (0mm,420mm) {core 28};
-\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
-\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
-\node at (0mm,435mm) {core 29};
-\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
-\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
-\node at (0mm,450mm) {core 30};
-\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
-\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
-\node at (0mm,465mm) {core 31};
-\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: cluster};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (80mm,60mm) {};
-\draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (90mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_16) at (100mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (110mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (120mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (130mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
-\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (90mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (100mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (110mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (120mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (130mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
-\draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (120mm,360mm) {};
-\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (130mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (140mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (150mm,360mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (120mm,180mm) {};
-\draw[->,very thick,color=red] (s_4_12.center) -- (r_4_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_28) at (130mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (140mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (150mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (160mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (120mm,300mm) {};
-\draw[->,very thick,color=red] (s_8_20.center) -- (r_8_20.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (130mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (140mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (150mm,300mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (121mm,165mm) {};
-\draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (121mm,105mm) {};
-\draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_16) at (130mm,240mm) {};
-\draw[->,very thick,color=red] (s_4_16.center) -- (r_4_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (140mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (150mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (160mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (131mm,150mm) {};
-\draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (131mm,90mm) {};
-\draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (141mm,75mm) {};
-\draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (141mm,405mm) {};
-\draw[->] (s_24_27.center) -- (r_24_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (141mm,135mm) {};
-\draw[->] (s_8_9.center) -- (r_8_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (141mm,345mm) {};
-\draw[->] (s_20_23.center) -- (r_20_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_28) at (150mm,420mm) {};
-\draw[->,very thick,color=red] (s_12_28.center) -- (r_12_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (160mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (170mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (180mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (151mm,330mm) {};
-\draw[->] (s_20_22.center) -- (r_20_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (151mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (151mm,285mm) {};
-\draw[->] (s_16_19.center) -- (r_16_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (151mm,390mm) {};
-\draw[->] (s_24_26.center) -- (r_24_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (161mm,315mm) {};
-\draw[->] (s_20_21.center) -- (r_20_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (161mm,270mm) {};
-\draw[->] (s_16_18.center) -- (r_16_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (161mm,375mm) {};
-\draw[->] (s_24_25.center) -- (r_24_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (161mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (171mm,255mm) {};
-\draw[->] (s_16_17.center) -- (r_16_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (171mm,465mm) {};
-\draw[->] (s_28_31.center) -- (r_28_31.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (171mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (181mm,450mm) {};
-\draw[->] (s_28_30.center) -- (r_28_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (191mm,435mm) {};
-\draw[->] (s_28_29.center) -- (r_28_29.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node (core_16_label) at (0mm,80mm) {core 16};
+\node (core_17_label) at (0mm,85mm) {core 17};
+\node (core_18_label) at (0mm,90mm) {core 18};
+\node (core_19_label) at (0mm,95mm) {core 19};
+\node (core_20_label) at (0mm,100mm) {core 20};
+\node (core_21_label) at (0mm,105mm) {core 21};
+\node (core_22_label) at (0mm,110mm) {core 22};
+\node (core_23_label) at (0mm,115mm) {core 23};
+\node (core_24_label) at (0mm,120mm) {core 24};
+\node (core_25_label) at (0mm,125mm) {core 25};
+\node (core_26_label) at (0mm,130mm) {core 26};
+\node (core_27_label) at (0mm,135mm) {core 27};
+\node (core_28_label) at (0mm,140mm) {core 28};
+\node (core_29_label) at (0mm,145mm) {core 29};
+\node (core_30_label) at (0mm,150mm) {core 30};
+\node (core_31_label) at (0mm,155mm) {core 31};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_8) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_4) at (24mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_3) at (28mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (32mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (36mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_4) at (32mm,20mm) {};
+\draw[->,semithick,color=red] ($(s_0_4.east)-(1mm,0mm)$) -- ($(r_0_4.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_12) at (36mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_16) at (40mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_7) at (44mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_6) at (48mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_5) at (52mm,20mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_8) at (32mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_0_8.east)-(1mm,0mm)$) -- ($(r_0_8.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_20) at (36mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_24) at (40mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_11) at (44mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_10) at (48mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_9) at (52mm,40mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_3) at (32mm,15mm) {};
+\draw[->] ($(s_0_3.east)-(1mm,0mm)$) -- ($(r_0_3.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (36mm,10mm) {};
+\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (40mm,5mm) {};
+\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_20) at (48mm,100mm) {};
+\draw[->,semithick,color=red] ($(s_8_20.east)-(1mm,0mm)$) -- ($(r_8_20.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_20_23) at (52mm,100mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_20_22) at (56mm,100mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_20_21) at (60mm,100mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_24) at (48mm,120mm) {};
+\draw[->,semithick,color=red] ($(s_8_24.east)-(1mm,0mm)$) -- ($(r_8_24.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_24_27) at (52mm,120mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_24_26) at (56mm,120mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_24_25) at (60mm,120mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_12) at (48mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_4_12.east)-(1mm,0mm)$) -- ($(r_4_12.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_28) at (52mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_15) at (56mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_14) at (60mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_13) at (64mm,60mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_11) at (48mm,55mm) {};
+\draw[->] ($(s_8_11.east)-(1mm,0mm)$) -- ($(r_8_11.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_7) at (48mm,35mm) {};
+\draw[->] ($(s_4_7.east)-(1mm,0mm)$) -- ($(r_4_7.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_16) at (52mm,80mm) {};
+\draw[->,semithick,color=red] ($(s_4_16.east)-(1mm,0mm)$) -- ($(r_4_16.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_16_19) at (56mm,80mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_16_18) at (60mm,80mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_16_17) at (64mm,80mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_10) at (52mm,50mm) {};
+\draw[->] ($(s_8_10.east)-(1mm,0mm)$) -- ($(r_8_10.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_6) at (52mm,30mm) {};
+\draw[->] ($(s_4_6.east)-(1mm,0mm)$) -- ($(r_4_6.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_20_23) at (56mm,115mm) {};
+\draw[->] ($(s_20_23.east)-(1mm,0mm)$) -- ($(r_20_23.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_24_27) at (56mm,135mm) {};
+\draw[->] ($(s_24_27.east)-(1mm,0mm)$) -- ($(r_24_27.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_9) at (56mm,45mm) {};
+\draw[->] ($(s_8_9.east)-(1mm,0mm)$) -- ($(r_8_9.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_5) at (56mm,25mm) {};
+\draw[->] ($(s_4_5.east)-(1mm,0mm)$) -- ($(r_4_5.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_28) at (60mm,140mm) {};
+\draw[->,semithick,color=red] ($(s_12_28.east)-(1mm,0mm)$) -- ($(r_12_28.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_28_31) at (64mm,140mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_28_30) at (68mm,140mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_28_29) at (72mm,140mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_24_26) at (60mm,130mm) {};
+\draw[->] ($(s_24_26.east)-(1mm,0mm)$) -- ($(r_24_26.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_20_22) at (60mm,110mm) {};
+\draw[->] ($(s_20_22.east)-(1mm,0mm)$) -- ($(r_20_22.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_15) at (60mm,75mm) {};
+\draw[->] ($(s_12_15.east)-(1mm,0mm)$) -- ($(r_12_15.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_16_19) at (60mm,95mm) {};
+\draw[->] ($(s_16_19.east)-(1mm,0mm)$) -- ($(r_16_19.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_24_25) at (64mm,125mm) {};
+\draw[->] ($(s_24_25.east)-(1mm,0mm)$) -- ($(r_24_25.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_14) at (64mm,70mm) {};
+\draw[->] ($(s_12_14.east)-(1mm,0mm)$) -- ($(r_12_14.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_20_21) at (64mm,105mm) {};
+\draw[->] ($(s_20_21.east)-(1mm,0mm)$) -- ($(r_20_21.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_16_18) at (64mm,90mm) {};
+\draw[->] ($(s_16_18.east)-(1mm,0mm)$) -- ($(r_16_18.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_16_17) at (68mm,85mm) {};
+\draw[->] ($(s_16_17.east)-(1mm,0mm)$) -- ($(r_16_17.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_13) at (68mm,65mm) {};
+\draw[->] ($(s_12_13.east)-(1mm,0mm)$) -- ($(r_12_13.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_28_31) at (68mm,155mm) {};
+\draw[->] ($(s_28_31.east)-(1mm,0mm)$) -- ($(r_28_31.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_28_30) at (72mm,150mm) {};
+\draw[->] ($(s_28_30.east)-(1mm,0mm)$) -- ($(r_28_30.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_28_29) at (76mm,145mm) {};
+\draw[->] ($(s_28_29.east)-(1mm,0mm)$) -- ($(r_28_29.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_8) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_4) (s_4_12) (s_4_16) (s_4_7) (s_4_6) (s_4_5) (r_0_8) (s_8_20) (s_8_24) (s_8_11) (s_8_10) (s_8_9) (r_0_3) (r_0_2) (r_0_1) (r_4_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_8_24) (s_24_27) (s_24_26) (s_24_25) (r_8_20) (s_20_23) (s_20_22) (s_20_21) (r_4_7) (r_8_11) (r_4_16) (s_16_19) (s_16_18) (s_16_17) (r_8_10) (r_4_6) (r_4_5) (r_20_23) (r_8_9) (r_24_27) (r_12_28) (s_28_31) (s_28_30) (s_28_29) (r_24_26) (r_16_19) (r_12_15) (r_20_22) (r_12_14) (r_20_21) (r_24_25) (r_16_18) (r_28_31) (r_12_13) (r_16_17) (r_28_30) (r_28_29) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_8) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_4) (s_4_12) (s_4_16) (s_4_7) (s_4_6) (s_4_5) (r_0_8) (s_8_20) (s_8_24) (s_8_11) (s_8_10) (s_8_9) (r_0_3) (r_0_2) (r_0_1) (r_8_20) (s_20_23) (s_20_22) (s_20_21) (r_8_24) (s_24_27) (s_24_26) (s_24_25) (r_4_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_8_11) (r_4_7) (r_4_16) (s_16_19) (s_16_18) (s_16_17) (r_8_10) (r_4_6) (r_20_23) (r_24_27) (r_8_9) (r_4_5) (r_12_28) (s_28_31) (s_28_30) (s_28_29) (r_24_26) (r_20_22) (r_12_15) (r_16_19) (r_24_25) (r_12_14) (r_20_21) (r_16_18) (r_16_17) (r_12_13) (r_28_31) (r_28_30) (r_28_29)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_8) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_4) (s_4_12) (s_4_16) (s_4_7) (s_4_6) (s_4_5) (r_0_8) (s_8_20) (s_8_24) (s_8_11) (s_8_10) (s_8_9) (r_0_3) (r_0_2) (r_0_1) (r_4_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_8_24) (s_24_27) (s_24_26) (s_24_25) (r_8_20) (s_20_23) (s_20_22) (s_20_21) (r_4_7) (r_8_11) (r_4_16) (s_16_19) (s_16_18) (s_16_17) (r_8_10) (r_4_6) (r_4_5) (r_20_23) (r_8_9) (r_24_27) (r_12_28) (s_28_31) (s_28_30) (s_28_29) (r_24_26) (r_16_19) (r_12_15) (r_20_22) (r_12_14) (r_20_21) (r_24_25) (r_16_18) (r_28_31) (r_12_13) (r_16_17) (r_28_30) (r_28_29) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_8) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_4) (s_4_12) (s_4_16) (s_4_7) (s_4_6) (s_4_5) (r_0_8) (s_8_20) (s_8_24) (s_8_11) (s_8_10) (s_8_9) (r_0_3) (r_0_2) (r_0_1) (r_8_20) (s_20_23) (s_20_22) (s_20_21) (r_8_24) (s_24_27) (s_24_26) (s_24_25) (r_4_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_8_11) (r_4_7) (r_4_16) (s_16_19) (s_16_18) (s_16_17) (r_8_10) (r_4_6) (r_20_23) (r_24_27) (r_8_9) (r_4_5) (r_12_28) (s_28_31) (s_28_30) (s_28_29) (r_24_26) (r_20_22) (r_12_15) (r_16_19) (r_24_25) (r_12_14) (r_20_21) (r_16_18) (r_16_17) (r_12_13) (r_28_31) (r_28_30) (r_28_29),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_16) at (\x1,80mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_17) at (\x1,85mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_18) at (\x1,90mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_19) at (\x1,95mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_20) at (\x1,100mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_21) at (\x1,105mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_22) at (\x1,110mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_23) at (\x1,115mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_24) at (\x1,120mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_25) at (\x1,125mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_26) at (\x1,130mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_27) at (\x1,135mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_28) at (\x1,140mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_29) at (\x1,145mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_30) at (\x1,150mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_31) at (\x1,155mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_8) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_8) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_4) (s_4_12) (s_4_16) (s_4_7) (s_4_6) (s_4_5) (r_4_7) (r_4_6) (r_4_5) (numa_axis_4.west) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_4) (s_4_12) (s_4_16) (s_4_7) (s_4_6) (s_4_5) (r_4_7) (r_4_6) (r_4_5) (numa_axis_4.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_8) (s_8_20) (s_8_24) (s_8_11) (s_8_10) (s_8_9) (r_8_11) (r_8_10) (r_8_9) (numa_axis_8.west) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_8) (s_8_20) (s_8_24) (s_8_11) (s_8_10) (s_8_9) (r_8_11) (r_8_10) (r_8_9) (numa_axis_8.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_4_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_4_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west),rounded corners] {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_16_label) (core_17_label) (core_18_label) (core_19_label) (r_4_16) (s_16_19) (s_16_18) (s_16_17) (r_16_19) (r_16_18) (r_16_17) (numa_axis_16.west) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (r_4_16) (s_16_19) (s_16_18) (s_16_17) (r_16_19) (r_16_18) (r_16_17) (numa_axis_16.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_8_20) (s_20_23) (s_20_22) (s_20_21) (r_20_23) (r_20_22) (r_20_21) (numa_axis_20.west) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_8_20) (s_20_23) (s_20_22) (s_20_21) (r_20_23) (r_20_22) (r_20_21) (numa_axis_20.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_24_label) (core_25_label) (core_26_label) (core_27_label) (r_8_24) (s_24_27) (s_24_26) (s_24_25) (r_24_27) (r_24_26) (r_24_25) (numa_axis_24.west) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (r_8_24) (s_24_27) (s_24_26) (s_24_25) (r_24_27) (r_24_26) (r_24_25) (numa_axis_24.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_28_label) (core_29_label) (core_30_label) (core_31_label) (r_12_28) (s_28_31) (s_28_30) (s_28_29) (r_28_31) (r_28_30) (r_28_29) (numa_axis_28.west) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (r_12_28) (s_28_31) (s_28_30) (s_28_29) (r_28_31) (r_28_30) (r_28_29) (numa_axis_28.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,80mm) -- (\x2,80mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,85mm) -- (\x2,85mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,90mm) -- (\x2,90mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,95mm) -- (\x2,95mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,100mm) -- (\x2,100mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,105mm) -- (\x2,105mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,110mm) -- (\x2,110mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,115mm) -- (\x2,115mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,120mm) -- (\x2,120mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,125mm) -- (\x2,125mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,130mm) -- (\x2,130mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,135mm) -- (\x2,135mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,140mm) -- (\x2,140mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,145mm) -- (\x2,145mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,150mm) -- (\x2,150mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,155mm) -- (\x2,155mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: gruyere, topology: cluster};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_gruyere_mst.tex
New visualization applied to all combinations of machines and topologies except for rings

@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
-\node at (0mm,360mm) {core 24};
-\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
-\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
-\node at (0mm,375mm) {core 25};
-\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
-\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
-\node at (0mm,390mm) {core 26};
-\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
-\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
-\node at (0mm,405mm) {core 27};
-\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
-\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
-\node at (0mm,420mm) {core 28};
-\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
-\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
-\node at (0mm,435mm) {core 29};
-\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
-\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
-\node at (0mm,450mm) {core 30};
-\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
-\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
-\node at (0mm,465mm) {core 31};
-\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: mst};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};
-\draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (90mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (100mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (110mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (120mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
-\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (90mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (100mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (110mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
-\draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
-\draw[->,very thick,color=red] (s_4_8.center) -- (r_4_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (110mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (120mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (130mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (140mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (150mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (160mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (101mm,285mm) {};
-\draw[->] (s_16_19.center) -- (r_16_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (110mm,300mm) {};
-\draw[->,very thick,color=red] (s_4_20.center) -- (r_4_20.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (120mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (130mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (140mm,300mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (111mm,105mm) {};
-\draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (111mm,270mm) {};
-\draw[->] (s_16_18.center) -- (r_16_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (121mm,255mm) {};
-\draw[->] (s_16_17.center) -- (r_16_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (121mm,90mm) {};
-\draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (130mm,420mm) {};
-\draw[->,very thick,color=red] (s_8_28.center) -- (r_8_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (140mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (150mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (160mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (131mm,345mm) {};
-\draw[->] (s_20_23.center) -- (r_20_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (131mm,75mm) {};
-\draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (140mm,360mm) {};
-\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (150mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (160mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (170mm,360mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (141mm,330mm) {};
-\draw[->] (s_20_22.center) -- (r_20_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (150mm,180mm) {};
-\draw[->,very thick,color=red] (s_8_12.center) -- (r_8_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (160mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (170mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (180mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (151mm,165mm) {};
-\draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (151mm,465mm) {};
-\draw[->] (s_28_31.center) -- (r_28_31.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (151mm,315mm) {};
-\draw[->] (s_20_21.center) -- (r_20_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (161mm,450mm) {};
-\draw[->] (s_28_30.center) -- (r_28_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (161mm,405mm) {};
-\draw[->] (s_24_27.center) -- (r_24_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (161mm,150mm) {};
-\draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (171mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (171mm,390mm) {};
-\draw[->] (s_24_26.center) -- (r_24_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (171mm,435mm) {};
-\draw[->] (s_28_29.center) -- (r_28_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (171mm,135mm) {};
-\draw[->] (s_8_9.center) -- (r_8_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (181mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (181mm,375mm) {};
-\draw[->] (s_24_25.center) -- (r_24_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (191mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node (core_16_label) at (0mm,80mm) {core 16};
+\node (core_17_label) at (0mm,85mm) {core 17};
+\node (core_18_label) at (0mm,90mm) {core 18};
+\node (core_19_label) at (0mm,95mm) {core 19};
+\node (core_20_label) at (0mm,100mm) {core 20};
+\node (core_21_label) at (0mm,105mm) {core 21};
+\node (core_22_label) at (0mm,110mm) {core 22};
+\node (core_23_label) at (0mm,115mm) {core 23};
+\node (core_24_label) at (0mm,120mm) {core 24};
+\node (core_25_label) at (0mm,125mm) {core 25};
+\node (core_26_label) at (0mm,130mm) {core 26};
+\node (core_27_label) at (0mm,135mm) {core 27};
+\node (core_28_label) at (0mm,140mm) {core 28};
+\node (core_29_label) at (0mm,145mm) {core 29};
+\node (core_30_label) at (0mm,150mm) {core 30};
+\node (core_31_label) at (0mm,155mm) {core 31};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_4) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_16) at (24mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_3) at (28mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (32mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (36mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_4) at (28mm,20mm) {};
+\draw[->,semithick,color=red] ($(s_0_4.east)-(1mm,0mm)$) -- ($(r_0_4.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_8) at (32mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_20) at (36mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_7) at (40mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_6) at (44mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_5) at (48mm,20mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_16) at (32mm,80mm) {};
+\draw[->,semithick,color=red] ($(s_0_16.east)-(1mm,0mm)$) -- ($(r_0_16.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_16_19) at (36mm,80mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_16_18) at (40mm,80mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_16_17) at (44mm,80mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_3) at (32mm,15mm) {};
+\draw[->] ($(s_0_3.east)-(1mm,0mm)$) -- ($(r_0_3.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (36mm,10mm) {};
+\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_8) at (40mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_4_8.east)-(1mm,0mm)$) -- ($(r_4_8.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_28) at (44mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_24) at (48mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_12) at (52mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_11) at (56mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_10) at (60mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_9) at (64mm,40mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (40mm,5mm) {};
+\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_16_19) at (40mm,95mm) {};
+\draw[->] ($(s_16_19.east)-(1mm,0mm)$) -- ($(r_16_19.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_20) at (44mm,100mm) {};
+\draw[->,semithick,color=red] ($(s_4_20.east)-(1mm,0mm)$) -- ($(r_4_20.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_20_23) at (48mm,100mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_20_22) at (52mm,100mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_20_21) at (56mm,100mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_16_18) at (44mm,90mm) {};
+\draw[->] ($(s_16_18.east)-(1mm,0mm)$) -- ($(r_16_18.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_7) at (44mm,35mm) {};
+\draw[->] ($(s_4_7.east)-(1mm,0mm)$) -- ($(r_4_7.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_16_17) at (48mm,85mm) {};
+\draw[->] ($(s_16_17.east)-(1mm,0mm)$) -- ($(r_16_17.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_6) at (48mm,30mm) {};
+\draw[->] ($(s_4_6.east)-(1mm,0mm)$) -- ($(r_4_6.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_28) at (52mm,140mm) {};
+\draw[->,semithick,color=red] ($(s_8_28.east)-(1mm,0mm)$) -- ($(r_8_28.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_28_31) at (56mm,140mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_28_30) at (60mm,140mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_28_29) at (64mm,140mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_20_23) at (52mm,115mm) {};
+\draw[->] ($(s_20_23.east)-(1mm,0mm)$) -- ($(r_20_23.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_5) at (52mm,25mm) {};
+\draw[->] ($(s_4_5.east)-(1mm,0mm)$) -- ($(r_4_5.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_24) at (56mm,120mm) {};
+\draw[->,semithick,color=red] ($(s_8_24.east)-(1mm,0mm)$) -- ($(r_8_24.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_24_27) at (60mm,120mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_24_26) at (64mm,120mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_24_25) at (68mm,120mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_20_22) at (56mm,110mm) {};
+\draw[->] ($(s_20_22.east)-(1mm,0mm)$) -- ($(r_20_22.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_12) at (60mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_8_12.east)-(1mm,0mm)$) -- ($(r_8_12.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_15) at (64mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_14) at (68mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_13) at (72mm,60mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_20_21) at (60mm,105mm) {};
+\draw[->] ($(s_20_21.east)-(1mm,0mm)$) -- ($(r_20_21.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_11) at (60mm,55mm) {};
+\draw[->] ($(s_8_11.east)-(1mm,0mm)$) -- ($(r_8_11.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_28_31) at (60mm,155mm) {};
+\draw[->] ($(s_28_31.east)-(1mm,0mm)$) -- ($(r_28_31.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_28_30) at (64mm,150mm) {};
+\draw[->] ($(s_28_30.east)-(1mm,0mm)$) -- ($(r_28_30.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_10) at (64mm,50mm) {};
+\draw[->] ($(s_8_10.east)-(1mm,0mm)$) -- ($(r_8_10.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_24_27) at (64mm,135mm) {};
+\draw[->] ($(s_24_27.east)-(1mm,0mm)$) -- ($(r_24_27.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_15) at (68mm,75mm) {};
+\draw[->] ($(s_12_15.east)-(1mm,0mm)$) -- ($(r_12_15.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_9) at (68mm,45mm) {};
+\draw[->] ($(s_8_9.east)-(1mm,0mm)$) -- ($(r_8_9.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_28_29) at (68mm,145mm) {};
+\draw[->] ($(s_28_29.east)-(1mm,0mm)$) -- ($(r_28_29.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_24_26) at (68mm,130mm) {};
+\draw[->] ($(s_24_26.east)-(1mm,0mm)$) -- ($(r_24_26.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_24_25) at (72mm,125mm) {};
+\draw[->] ($(s_24_25.east)-(1mm,0mm)$) -- ($(r_24_25.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_14) at (72mm,70mm) {};
+\draw[->] ($(s_12_14.east)-(1mm,0mm)$) -- ($(r_12_14.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_13) at (76mm,65mm) {};
+\draw[->] ($(s_12_13.east)-(1mm,0mm)$) -- ($(r_12_13.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_4) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_0_4) (s_4_8) (s_4_20) (s_4_7) (s_4_6) (s_4_5) (r_0_16) (s_16_19) (s_16_18) (s_16_17) (r_0_3) (r_0_2) (r_4_8) (s_8_28) (s_8_24) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_0_1) (r_16_19) (r_4_20) (s_20_23) (s_20_22) (s_20_21) (r_4_7) (r_16_18) (r_4_6) (r_16_17) (r_8_28) (s_28_31) (s_28_30) (s_28_29) (r_20_23) (r_4_5) (r_8_24) (s_24_27) (s_24_26) (s_24_25) (r_20_22) (r_8_12) (s_12_15) (s_12_14) (s_12_13) (r_20_21) (r_28_31) (r_8_11) (r_24_27) (r_8_10) (r_28_30) (r_12_15) (r_28_29) (r_24_26) (r_8_9) (r_12_14) (r_24_25) (r_12_13) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_4) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_0_4) (s_4_8) (s_4_20) (s_4_7) (s_4_6) (s_4_5) (r_0_16) (s_16_19) (s_16_18) (s_16_17) (r_0_3) (r_0_2) (r_4_8) (s_8_28) (s_8_24) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_0_1) (r_16_19) (r_4_20) (s_20_23) (s_20_22) (s_20_21) (r_16_18) (r_4_7) (r_16_17) (r_4_6) (r_8_28) (s_28_31) (s_28_30) (s_28_29) (r_20_23) (r_4_5) (r_8_24) (s_24_27) (s_24_26) (s_24_25) (r_20_22) (r_8_12) (s_12_15) (s_12_14) (s_12_13) (r_20_21) (r_8_11) (r_28_31) (r_28_30) (r_8_10) (r_24_27) (r_12_15) (r_8_9) (r_28_29) (r_24_26) (r_24_25) (r_12_14) (r_12_13)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_4) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_0_4) (s_4_8) (s_4_20) (s_4_7) (s_4_6) (s_4_5) (r_0_16) (s_16_19) (s_16_18) (s_16_17) (r_0_3) (r_0_2) (r_4_8) (s_8_28) (s_8_24) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_0_1) (r_16_19) (r_4_20) (s_20_23) (s_20_22) (s_20_21) (r_4_7) (r_16_18) (r_4_6) (r_16_17) (r_8_28) (s_28_31) (s_28_30) (s_28_29) (r_20_23) (r_4_5) (r_8_24) (s_24_27) (s_24_26) (s_24_25) (r_20_22) (r_8_12) (s_12_15) (s_12_14) (s_12_13) (r_20_21) (r_28_31) (r_8_11) (r_24_27) (r_8_10) (r_28_30) (r_12_15) (r_28_29) (r_24_26) (r_8_9) (r_12_14) (r_24_25) (r_12_13) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_4) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_0_4) (s_4_8) (s_4_20) (s_4_7) (s_4_6) (s_4_5) (r_0_16) (s_16_19) (s_16_18) (s_16_17) (r_0_3) (r_0_2) (r_4_8) (s_8_28) (s_8_24) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_0_1) (r_16_19) (r_4_20) (s_20_23) (s_20_22) (s_20_21) (r_16_18) (r_4_7) (r_16_17) (r_4_6) (r_8_28) (s_28_31) (s_28_30) (s_28_29) (r_20_23) (r_4_5) (r_8_24) (s_24_27) (s_24_26) (s_24_25) (r_20_22) (r_8_12) (s_12_15) (s_12_14) (s_12_13) (r_20_21) (r_8_11) (r_28_31) (r_28_30) (r_8_10) (r_24_27) (r_12_15) (r_8_9) (r_28_29) (r_24_26) (r_24_25) (r_12_14) (r_12_13),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_16) at (\x1,80mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_17) at (\x1,85mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_18) at (\x1,90mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_19) at (\x1,95mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_20) at (\x1,100mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_21) at (\x1,105mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_22) at (\x1,110mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_23) at (\x1,115mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_24) at (\x1,120mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_25) at (\x1,125mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_26) at (\x1,130mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_27) at (\x1,135mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_28) at (\x1,140mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_29) at (\x1,145mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_30) at (\x1,150mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_31) at (\x1,155mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_4) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_4) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_4) (s_4_8) (s_4_20) (s_4_7) (s_4_6) (s_4_5) (r_4_7) (r_4_6) (r_4_5) (numa_axis_4.west) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_4) (s_4_8) (s_4_20) (s_4_7) (s_4_6) (s_4_5) (r_4_7) (r_4_6) (r_4_5) (numa_axis_4.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_4_8) (s_8_28) (s_8_24) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_8_11) (r_8_10) (r_8_9) (numa_axis_8.west) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_4_8) (s_8_28) (s_8_24) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_8_11) (r_8_10) (r_8_9) (numa_axis_8.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_8_12) (s_12_15) (s_12_14) (s_12_13) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_8_12) (s_12_15) (s_12_14) (s_12_13) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west),rounded corners] {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_16_label) (core_17_label) (core_18_label) (core_19_label) (r_0_16) (s_16_19) (s_16_18) (s_16_17) (r_16_19) (r_16_18) (r_16_17) (numa_axis_16.west) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (r_0_16) (s_16_19) (s_16_18) (s_16_17) (r_16_19) (r_16_18) (r_16_17) (numa_axis_16.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_4_20) (s_20_23) (s_20_22) (s_20_21) (r_20_23) (r_20_22) (r_20_21) (numa_axis_20.west) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_4_20) (s_20_23) (s_20_22) (s_20_21) (r_20_23) (r_20_22) (r_20_21) (numa_axis_20.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_24_label) (core_25_label) (core_26_label) (core_27_label) (r_8_24) (s_24_27) (s_24_26) (s_24_25) (r_24_27) (r_24_26) (r_24_25) (numa_axis_24.west) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (r_8_24) (s_24_27) (s_24_26) (s_24_25) (r_24_27) (r_24_26) (r_24_25) (numa_axis_24.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_28_label) (core_29_label) (core_30_label) (core_31_label) (r_8_28) (s_28_31) (s_28_30) (s_28_29) (r_28_31) (r_28_30) (r_28_29) (numa_axis_28.west) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (r_8_28) (s_28_31) (s_28_30) (s_28_29) (r_28_31) (r_28_30) (r_28_29) (numa_axis_28.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,80mm) -- (\x2,80mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,85mm) -- (\x2,85mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,90mm) -- (\x2,90mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,95mm) -- (\x2,95mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,100mm) -- (\x2,100mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,105mm) -- (\x2,105mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,110mm) -- (\x2,110mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,115mm) -- (\x2,115mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,120mm) -- (\x2,120mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,125mm) -- (\x2,125mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,130mm) -- (\x2,130mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,135mm) -- (\x2,135mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,140mm) -- (\x2,140mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,145mm) -- (\x2,145mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,150mm) -- (\x2,150mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,155mm) -- (\x2,155mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: gruyere, topology: mst};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_gruyere_ring.tex
New visualization applied to all combinations of machines and topologies except for rings

--- 2013-06-04 graphs/visu_gruyere_mst.tex
@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
-\node at (0mm,360mm) {core 24};
-\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
-\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
-\node at (0mm,375mm) {core 25};
-\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
-\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
-\node at (0mm,390mm) {core 26};
-\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
-\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
-\node at (0mm,405mm) {core 27};
-\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
-\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
-\node at (0mm,420mm) {core 28};
-\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
-\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
-\node at (0mm,435mm) {core 29};
-\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
-\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
-\node at (0mm,450mm) {core 30};
-\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
-\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
-\node at (0mm,465mm) {core 31};
-\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: mst};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};
-\draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (90mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (100mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (110mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (120mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
-\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (90mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (100mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (110mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
-\draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
-\draw[->,very thick,color=red] (s_4_8.center) -- (r_4_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (110mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (120mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (130mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (140mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (150mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (160mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (101mm,285mm) {};
-\draw[->] (s_16_19.center) -- (r_16_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (110mm,300mm) {};
-\draw[->,very thick,color=red] (s_4_20.center) -- (r_4_20.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (120mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (130mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (140mm,300mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (111mm,105mm) {};
-\draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (111mm,270mm) {};
-\draw[->] (s_16_18.center) -- (r_16_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (121mm,255mm) {};
-\draw[->] (s_16_17.center) -- (r_16_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (121mm,90mm) {};
-\draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (130mm,420mm) {};
-\draw[->,very thick,color=red] (s_8_28.center) -- (r_8_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (140mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (150mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (160mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (131mm,345mm) {};
-\draw[->] (s_20_23.center) -- (r_20_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (131mm,75mm) {};
-\draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (140mm,360mm) {};
-\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (150mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (160mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (170mm,360mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (141mm,330mm) {};
-\draw[->] (s_20_22.center) -- (r_20_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (150mm,180mm) {};
-\draw[->,very thick,color=red] (s_8_12.center) -- (r_8_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (160mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (170mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (180mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (151mm,165mm) {};
-\draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (151mm,465mm) {};
-\draw[->] (s_28_31.center) -- (r_28_31.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (151mm,315mm) {};
-\draw[->] (s_20_21.center) -- (r_20_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (161mm,450mm) {};
-\draw[->] (s_28_30.center) -- (r_28_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (161mm,405mm) {};
-\draw[->] (s_24_27.center) -- (r_24_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (161mm,150mm) {};
-\draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (171mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (171mm,390mm) {};
-\draw[->] (s_24_26.center) -- (r_24_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (171mm,435mm) {};
-\draw[->] (s_28_29.center) -- (r_28_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (171mm,135mm) {};
-\draw[->] (s_8_9.center) -- (r_8_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (181mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (181mm,375mm) {};
-\draw[->] (s_24_25.center) -- (r_24_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (191mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node (core_16_label) at (0mm,80mm) {core 16};
+\node (core_17_label) at (0mm,85mm) {core 17};
+\node (core_18_label) at (0mm,90mm) {core 18};
+\node (core_19_label) at (0mm,95mm) {core 19};
+\node (core_20_label) at (0mm,100mm) {core 20};
+\node (core_21_label) at (0mm,105mm) {core 21};
+\node (core_22_label) at (0mm,110mm) {core 22};
+\node (core_23_label) at (0mm,115mm) {core 23};
+\node (core_24_label) at (0mm,120mm) {core 24};
+\node (core_25_label) at (0mm,125mm) {core 25};
+\node (core_26_label) at (0mm,130mm) {core 26};
+\node (core_27_label) at (0mm,135mm) {core 27};
+\node (core_28_label) at (0mm,140mm) {core 28};
+\node (core_29_label) at (0mm,145mm) {core 29};
+\node (core_30_label) at (0mm,150mm) {core 30};
+\node (core_31_label) at (0mm,155mm) {core 31};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_8_4) at (30mm,40mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_8_12) at (36mm,40mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_8_11) at (42mm,40mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_8_10) at (48mm,40mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_8_9) at (54mm,40mm) {};
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_8_4) at (42mm,20mm) {};
+\draw[->,semithick,color=red] ($(s_8_4.east)-(1mm,0mm)$) -- ($(r_8_4.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_4_0) at (48mm,20mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_4_7) at (54mm,20mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_4_6) at (60mm,20mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_4_5) at (66mm,20mm) {};
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_8_12) at (48mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_8_12.east)-(1mm,0mm)$) -- ($(r_8_12.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_12_28) at (54mm,60mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_12_15) at (60mm,60mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_12_14) at (66mm,60mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_12_13) at (72mm,60mm) {};
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_8_11) at (48mm,55mm) {};
+\draw[->] ($(s_8_11.east)-(1mm,0mm)$) -- ($(r_8_11.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_8_10) at (54mm,50mm) {};
+\draw[->] ($(s_8_10.east)-(1mm,0mm)$) -- ($(r_8_10.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_4_0) at (60mm,0mm) {};
+\draw[->,semithick,color=red] ($(s_4_0.east)-(1mm,0mm)$) -- ($(r_4_0.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_0_16) at (66mm,0mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_0_3) at (72mm,0mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_0_2) at (78mm,0mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_0_1) at (84mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_4_7) at (60mm,35mm) {};
+\draw[->] ($(s_4_7.east)-(1mm,0mm)$) -- ($(r_4_7.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_8_9) at (60mm,45mm) {};
+\draw[->] ($(s_8_9.east)-(1mm,0mm)$) -- ($(r_8_9.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_12_28) at (66mm,140mm) {};
+\draw[->,semithick,color=red] ($(s_12_28.east)-(1mm,0mm)$) -- ($(r_12_28.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_28_24) at (72mm,140mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_28_31) at (78mm,140mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_28_30) at (84mm,140mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_28_29) at (90mm,140mm) {};
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_4_6) at (66mm,30mm) {};
+\draw[->] ($(s_4_6.east)-(1mm,0mm)$) -- ($(r_4_6.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_12_15) at (66mm,75mm) {};
+\draw[->] ($(s_12_15.east)-(1mm,0mm)$) -- ($(r_12_15.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_4_5) at (72mm,25mm) {};
+\draw[->] ($(s_4_5.east)-(1mm,0mm)$) -- ($(r_4_5.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_12_14) at (72mm,70mm) {};
+\draw[->] ($(s_12_14.east)-(1mm,0mm)$) -- ($(r_12_14.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_0_16) at (78mm,80mm) {};
+\draw[->,semithick,color=red] ($(s_0_16.east)-(1mm,0mm)$) -- ($(r_0_16.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_16_20) at (84mm,80mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_16_19) at (90mm,80mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_16_18) at (96mm,80mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_16_17) at (102mm,80mm) {};
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_12_13) at (78mm,65mm) {};
+\draw[->] ($(s_12_13.east)-(1mm,0mm)$) -- ($(r_12_13.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_0_3) at (78mm,15mm) {};
+\draw[->] ($(s_0_3.east)-(1mm,0mm)$) -- ($(r_0_3.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_28_24) at (84mm,120mm) {};
+\draw[->,semithick,color=red] ($(s_28_24.east)-(1mm,0mm)$) -- ($(r_28_24.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_24_8) at (90mm,120mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_24_27) at (96mm,120mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_24_26) at (102mm,120mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_24_25) at (108mm,120mm) {};
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_28_31) at (84mm,155mm) {};
+\draw[->] ($(s_28_31.east)-(1mm,0mm)$) -- ($(r_28_31.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_0_2) at (84mm,10mm) {};
+\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_28_30) at (90mm,150mm) {};
+\draw[->] ($(s_28_30.east)-(1mm,0mm)$) -- ($(r_28_30.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_0_1) at (90mm,5mm) {};
+\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_16_20) at (96mm,100mm) {};
+\draw[->,semithick,color=red] ($(s_16_20.east)-(1mm,0mm)$) -- ($(r_16_20.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_20_8) at (102mm,100mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_20_23) at (108mm,100mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_20_22) at (114mm,100mm) {};
+\node[draw,fill=red!20,minimum width=6mm, minimum height=3mm,anchor=west] (s_20_21) at (120mm,100mm) {};
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_16_19) at (96mm,95mm) {};
+\draw[->] ($(s_16_19.east)-(1mm,0mm)$) -- ($(r_16_19.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_28_29) at (96mm,145mm) {};
+\draw[->] ($(s_28_29.east)-(1mm,0mm)$) -- ($(r_28_29.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_24_8) at (102mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_24_8.east)-(1mm,0mm)$) -- ($(r_24_8.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_16_18) at (102mm,90mm) {};
+\draw[->] ($(s_16_18.east)-(1mm,0mm)$) -- ($(r_16_18.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_24_27) at (102mm,135mm) {};
+\draw[->] ($(s_24_27.east)-(1mm,0mm)$) -- ($(r_24_27.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_24_26) at (108mm,130mm) {};
+\draw[->] ($(s_24_26.east)-(1mm,0mm)$) -- ($(r_24_26.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_16_17) at (108mm,85mm) {};
+\draw[->] ($(s_16_17.east)-(1mm,0mm)$) -- ($(r_16_17.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_20_23) at (114mm,115mm) {};
+\draw[->] ($(s_20_23.east)-(1mm,0mm)$) -- ($(r_20_23.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_24_25) at (114mm,125mm) {};
+\draw[->] ($(s_24_25.east)-(1mm,0mm)$) -- ($(r_24_25.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_20_8) at (120mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_20_8.east)-(1mm,0mm)$) -- ($(r_20_8.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_20_22) at (120mm,110mm) {};
+\draw[->] ($(s_20_22.east)-(1mm,0mm)$) -- ($(r_20_22.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=6mm, minimum height=3mm,anchor=west] (r_20_21) at (126mm,105mm) {};
+\draw[->] ($(s_20_21.east)-(1mm,0mm)$) -- ($(r_20_21.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_8_4) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_8_4) (s_4_0) (s_4_7) (s_4_6) (s_4_5) (r_8_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_8_11) (r_8_10) (r_4_0) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_8_9) (r_4_7) (r_12_28) (s_28_24) (s_28_31) (s_28_30) (s_28_29) (r_4_6) (r_12_15) (r_4_5) (r_12_14) (r_0_16) (s_16_20) (s_16_19) (s_16_18) (s_16_17) (r_12_13) (r_0_3) (r_28_24) (s_24_8) (s_24_27) (s_24_26) (s_24_25) (r_0_2) (r_28_31) (r_0_1) (r_28_30) (r_16_20) (s_20_8) (s_20_23) (s_20_22) (s_20_21) (r_28_29) (r_16_19) (r_24_8) (r_16_18) (r_24_27) (r_24_26) (r_16_17) (r_20_23) (r_24_25) (r_20_8) (r_20_22) (r_20_21) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_8_4) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_8_4) (s_4_0) (s_4_7) (s_4_6) (s_4_5) (r_8_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_8_11) (r_8_10) (r_4_0) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_4_7) (r_8_9) (r_12_28) (s_28_24) (s_28_31) (s_28_30) (s_28_29) (r_4_6) (r_12_15) (r_4_5) (r_12_14) (r_0_16) (s_16_20) (s_16_19) (s_16_18) (s_16_17) (r_12_13) (r_0_3) (r_28_24) (s_24_8) (s_24_27) (s_24_26) (s_24_25) (r_28_31) (r_0_2) (r_28_30) (r_0_1) (r_16_20) (s_20_8) (s_20_23) (s_20_22) (s_20_21) (r_16_19) (r_28_29) (r_24_8) (r_16_18) (r_24_27) (r_24_26) (r_16_17) (r_20_23) (r_24_25) (r_20_8) (r_20_22) (r_20_21)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_8_4) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_8_4) (s_4_0) (s_4_7) (s_4_6) (s_4_5) (r_8_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_8_11) (r_8_10) (r_4_0) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_8_9) (r_4_7) (r_12_28) (s_28_24) (s_28_31) (s_28_30) (s_28_29) (r_4_6) (r_12_15) (r_4_5) (r_12_14) (r_0_16) (s_16_20) (s_16_19) (s_16_18) (s_16_17) (r_12_13) (r_0_3) (r_28_24) (s_24_8) (s_24_27) (s_24_26) (s_24_25) (r_0_2) (r_28_31) (r_0_1) (r_28_30) (r_16_20) (s_20_8) (s_20_23) (s_20_22) (s_20_21) (r_28_29) (r_16_19) (r_24_8) (r_16_18) (r_24_27) (r_24_26) (r_16_17) (r_20_23) (r_24_25) (r_20_8) (r_20_22) (r_20_21) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_8_4) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_8_4) (s_4_0) (s_4_7) (s_4_6) (s_4_5) (r_8_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_8_11) (r_8_10) (r_4_0) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_4_7) (r_8_9) (r_12_28) (s_28_24) (s_28_31) (s_28_30) (s_28_29) (r_4_6) (r_12_15) (r_4_5) (r_12_14) (r_0_16) (s_16_20) (s_16_19) (s_16_18) (s_16_17) (r_12_13) (r_0_3) (r_28_24) (s_24_8) (s_24_27) (s_24_26) (s_24_25) (r_28_31) (r_0_2) (r_28_30) (r_0_1) (r_16_20) (s_20_8) (s_20_23) (s_20_22) (s_20_21) (r_16_19) (r_28_29) (r_24_8) (r_16_18) (r_24_27) (r_24_26) (r_16_17) (r_20_23) (r_24_25) (r_20_8) (r_20_22) (r_20_21),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_16) at (\x1,80mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_17) at (\x1,85mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_18) at (\x1,90mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_19) at (\x1,95mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_20) at (\x1,100mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_21) at (\x1,105mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_22) at (\x1,110mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_23) at (\x1,115mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_24) at (\x1,120mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_25) at (\x1,125mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_26) at (\x1,130mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_27) at (\x1,135mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_28) at (\x1,140mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_29) at (\x1,145mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_30) at (\x1,150mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_31) at (\x1,155mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (r_4_0) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (r_4_0) (s_0_16) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_8_4) (s_4_0) (s_4_7) (s_4_6) (s_4_5) (r_4_7) (r_4_6) (r_4_5) (numa_axis_4.west) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_8_4) (s_4_0) (s_4_7) (s_4_6) (s_4_5) (r_4_7) (r_4_6) (r_4_5) (numa_axis_4.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_8_label) (core_9_label) (core_10_label) (core_11_label) (s_8_4) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_8_11) (r_8_10) (r_8_9) (r_24_8) (r_20_8) (numa_axis_8.west) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (s_8_4) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_8_11) (r_8_10) (r_8_9) (r_24_8) (r_20_8) (numa_axis_8.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_8_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_8_12) (s_12_28) (s_12_15) (s_12_14) (s_12_13) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west),rounded corners] {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_16_label) (core_17_label) (core_18_label) (core_19_label) (r_0_16) (s_16_20) (s_16_19) (s_16_18) (s_16_17) (r_16_19) (r_16_18) (r_16_17) (numa_axis_16.west) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (r_0_16) (s_16_20) (s_16_19) (s_16_18) (s_16_17) (r_16_19) (r_16_18) (r_16_17) (numa_axis_16.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_16_20) (s_20_8) (s_20_23) (s_20_22) (s_20_21) (r_20_23) (r_20_22) (r_20_21) (numa_axis_20.west) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_16_20) (s_20_8) (s_20_23) (s_20_22) (s_20_21) (r_20_23) (r_20_22) (r_20_21) (numa_axis_20.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_24_label) (core_25_label) (core_26_label) (core_27_label) (r_28_24) (s_24_8) (s_24_27) (s_24_26) (s_24_25) (r_24_27) (r_24_26) (r_24_25) (numa_axis_24.west) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (r_28_24) (s_24_8) (s_24_27) (s_24_26) (s_24_25) (r_24_27) (r_24_26) (r_24_25) (numa_axis_24.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_28_label) (core_29_label) (core_30_label) (core_31_label) (r_12_28) (s_28_24) (s_28_31) (s_28_30) (s_28_29) (r_28_31) (r_28_30) (r_28_29) (numa_axis_28.west) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (r_12_28) (s_28_24) (s_28_31) (s_28_30) (s_28_29) (r_28_31) (r_28_30) (r_28_29) (numa_axis_28.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,80mm) -- (\x2,80mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,85mm) -- (\x2,85mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,90mm) -- (\x2,90mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,95mm) -- (\x2,95mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,100mm) -- (\x2,100mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,105mm) -- (\x2,105mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,110mm) -- (\x2,110mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,115mm) -- (\x2,115mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,120mm) -- (\x2,120mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,125mm) -- (\x2,125mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,130mm) -- (\x2,130mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,135mm) -- (\x2,135mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,140mm) -- (\x2,140mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,145mm) -- (\x2,145mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,150mm) -- (\x2,150mm);
+\draw[color=black!30] let \p1 = (core_31_label.east), \p2 = (allobjects.east) in (\x1,155mm) -- (\x2,155mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: gruyere, topology: ring};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_gruyere_sequential.tex
New visualization applied to all combinations of machines and topologies except for rings

--- 2013-06-04 graphs/visu_gruyere_mst.tex
@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=red!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=red!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=red!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=red!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=green!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=green!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=green!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=green!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\draw[fill,color=blue!10] (-3cm,367.500000mm) rectangle (30cm,352.500000mm);
-\node at (0mm,360mm) {core 24};
-\draw[color=black!30] (20mm,360mm) -- (30cm,360mm);
-\draw[fill,color=blue!10] (-3cm,382.500000mm) rectangle (30cm,367.500000mm);
-\node at (0mm,375mm) {core 25};
-\draw[color=black!30] (20mm,375mm) -- (30cm,375mm);
-\draw[fill,color=blue!10] (-3cm,397.500000mm) rectangle (30cm,382.500000mm);
-\node at (0mm,390mm) {core 26};
-\draw[color=black!30] (20mm,390mm) -- (30cm,390mm);
-\draw[fill,color=blue!10] (-3cm,412.500000mm) rectangle (30cm,397.500000mm);
-\node at (0mm,405mm) {core 27};
-\draw[color=black!30] (20mm,405mm) -- (30cm,405mm);
-\draw[fill,color=orange!10] (-3cm,427.500000mm) rectangle (30cm,412.500000mm);
-\node at (0mm,420mm) {core 28};
-\draw[color=black!30] (20mm,420mm) -- (30cm,420mm);
-\draw[fill,color=orange!10] (-3cm,442.500000mm) rectangle (30cm,427.500000mm);
-\node at (0mm,435mm) {core 29};
-\draw[color=black!30] (20mm,435mm) -- (30cm,435mm);
-\draw[fill,color=orange!10] (-3cm,457.500000mm) rectangle (30cm,442.500000mm);
-\node at (0mm,450mm) {core 30};
-\draw[color=black!30] (20mm,450mm) -- (30cm,450mm);
-\draw[fill,color=orange!10] (-3cm,472.500000mm) rectangle (30cm,457.500000mm);
-\node at (0mm,465mm) {core 31};
-\draw[color=black!30] (20mm,465mm) -- (30cm,465mm);
-\node at (0mm,480mm) {Machine: gruyere, topology: mst};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};
-\draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_20) at (90mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (100mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (110mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (120mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
-\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_19) at (90mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_18) at (100mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_17) at (110mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
-\draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
-\draw[->,very thick,color=red] (s_4_8.center) -- (r_4_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_28) at (110mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_24) at (120mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (130mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (140mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (150mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (160mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_19) at (101mm,285mm) {};
-\draw[->] (s_16_19.center) -- (r_16_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_20) at (110mm,300mm) {};
-\draw[->,very thick,color=red] (s_4_20.center) -- (r_4_20.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_20_23) at (120mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_22) at (130mm,300mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_20_21) at (140mm,300mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (111mm,105mm) {};
-\draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_18) at (111mm,270mm) {};
-\draw[->] (s_16_18.center) -- (r_16_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_17) at (121mm,255mm) {};
-\draw[->] (s_16_17.center) -- (r_16_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (121mm,90mm) {};
-\draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_28) at (130mm,420mm) {};
-\draw[->,very thick,color=red] (s_8_28.center) -- (r_8_28.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_28_31) at (140mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_30) at (150mm,420mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_28_29) at (160mm,420mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_23) at (131mm,345mm) {};
-\draw[->] (s_20_23.center) -- (r_20_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (131mm,75mm) {};
-\draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_24) at (140mm,360mm) {};
-\draw[->,very thick,color=red] (s_8_24.center) -- (r_8_24.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_24_27) at (150mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_26) at (160mm,360mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_24_25) at (170mm,360mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_22) at (141mm,330mm) {};
-\draw[->] (s_20_22.center) -- (r_20_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (150mm,180mm) {};
-\draw[->,very thick,color=red] (s_8_12.center) -- (r_8_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (160mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (170mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (180mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (151mm,165mm) {};
-\draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_31) at (151mm,465mm) {};
-\draw[->] (s_28_31.center) -- (r_28_31.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_20_21) at (151mm,315mm) {};
-\draw[->] (s_20_21.center) -- (r_20_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_30) at (161mm,450mm) {};
-\draw[->] (s_28_30.center) -- (r_28_30.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_27) at (161mm,405mm) {};
-\draw[->] (s_24_27.center) -- (r_24_27.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (161mm,150mm) {};
-\draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (171mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_26) at (171mm,390mm) {};
-\draw[->] (s_24_26.center) -- (r_24_26.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_28_29) at (171mm,435mm) {};
-\draw[->] (s_28_29.center) -- (r_28_29.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (171mm,135mm) {};
-\draw[->] (s_8_9.center) -- (r_8_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (181mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_24_25) at (181mm,375mm) {};
-\draw[->] (s_24_25.center) -- (r_24_25.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (191mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node (core_16_label) at (0mm,80mm) {core 16};
+\node (core_17_label) at (0mm,85mm) {core 17};
+\node (core_18_label) at (0mm,90mm) {core 18};
+\node (core_19_label) at (0mm,95mm) {core 19};
+\node (core_20_label) at (0mm,100mm) {core 20};
+\node (core_21_label) at (0mm,105mm) {core 21};
+\node (core_22_label) at (0mm,110mm) {core 22};
+\node (core_23_label) at (0mm,115mm) {core 23};
+\node (core_24_label) at (0mm,120mm) {core 24};
+\node (core_25_label) at (0mm,125mm) {core 25};
+\node (core_26_label) at (0mm,130mm) {core 26};
+\node (core_27_label) at (0mm,135mm) {core 27};
+\node (core_28_label) at (0mm,140mm) {core 28};
+\node (core_29_label) at (0mm,145mm) {core 29};
+\node (core_30_label) at (0mm,150mm) {core 30};
+\node (core_31_label) at (0mm,155mm) {core 31};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_31) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_30) at (24mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_29) at (28mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_28) at (32mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_27) at (36mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_26) at (40mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_25) at (44mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_24) at (48mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_15) at (52mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_14) at (56mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_13) at (60mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_12) at (64mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_23) at (68mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_22) at (72mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_21) at (76mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_20) at (80mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_11) at (84mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_10) at (88mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_9) at (92mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_8) at (96mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_19) at (100mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_18) at (104mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_17) at (108mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_16) at (112mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_7) at (116mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_6) at (120mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_5) at (124mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_4) at (128mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_3) at (132mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (136mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (140mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_31) at (36mm,155mm) {};
+\draw[->,semithick,color=red] ($(s_0_31.east)-(1mm,0mm)$) -- ($(r_0_31.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_30) at (40mm,150mm) {};
+\draw[->,semithick,color=red] ($(s_0_30.east)-(1mm,0mm)$) -- ($(r_0_30.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_29) at (44mm,145mm) {};
+\draw[->,semithick,color=red] ($(s_0_29.east)-(1mm,0mm)$) -- ($(r_0_29.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_28) at (48mm,140mm) {};
+\draw[->,semithick,color=red] ($(s_0_28.east)-(1mm,0mm)$) -- ($(r_0_28.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_27) at (52mm,135mm) {};
+\draw[->,semithick,color=red] ($(s_0_27.east)-(1mm,0mm)$) -- ($(r_0_27.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_26) at (56mm,130mm) {};
+\draw[->,semithick,color=red] ($(s_0_26.east)-(1mm,0mm)$) -- ($(r_0_26.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_25) at (60mm,125mm) {};
+\draw[->,semithick,color=red] ($(s_0_25.east)-(1mm,0mm)$) -- ($(r_0_25.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_24) at (64mm,120mm) {};
+\draw[->,semithick,color=red] ($(s_0_24.east)-(1mm,0mm)$) -- ($(r_0_24.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_15) at (68mm,75mm) {};
+\draw[->,semithick,color=red] ($(s_0_15.east)-(1mm,0mm)$) -- ($(r_0_15.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_14) at (72mm,70mm) {};
+\draw[->,semithick,color=red] ($(s_0_14.east)-(1mm,0mm)$) -- ($(r_0_14.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_13) at (76mm,65mm) {};
+\draw[->,semithick,color=red] ($(s_0_13.east)-(1mm,0mm)$) -- ($(r_0_13.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_23) at (80mm,115mm) {};
+\draw[->,semithick,color=red] ($(s_0_23.east)-(1mm,0mm)$) -- ($(r_0_23.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_12) at (80mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_0_12.east)-(1mm,0mm)$) -- ($(r_0_12.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_22) at (84mm,110mm) {};
+\draw[->,semithick,color=red] ($(s_0_22.east)-(1mm,0mm)$) -- ($(r_0_22.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_21) at (88mm,105mm) {};
+\draw[->,semithick,color=red] ($(s_0_21.east)-(1mm,0mm)$) -- ($(r_0_21.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_20) at (92mm,100mm) {};
+\draw[->,semithick,color=red] ($(s_0_20.east)-(1mm,0mm)$) -- ($(r_0_20.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_11) at (96mm,55mm) {};
+\draw[->,semithick,color=red] ($(s_0_11.east)-(1mm,0mm)$) -- ($(r_0_11.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_10) at (100mm,50mm) {};
+\draw[->,semithick,color=red] ($(s_0_10.east)-(1mm,0mm)$) -- ($(r_0_10.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_9) at (104mm,45mm) {};
+\draw[->,semithick,color=red] ($(s_0_9.east)-(1mm,0mm)$) -- ($(r_0_9.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_19) at (108mm,95mm) {};
+\draw[->,semithick,color=red] ($(s_0_19.east)-(1mm,0mm)$) -- ($(r_0_19.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_8) at (108mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_0_8.east)-(1mm,0mm)$) -- ($(r_0_8.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_18) at (112mm,90mm) {};
+\draw[->,semithick,color=red] ($(s_0_18.east)-(1mm,0mm)$) -- ($(r_0_18.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_17) at (116mm,85mm) {};
+\draw[->,semithick,color=red] ($(s_0_17.east)-(1mm,0mm)$) -- ($(r_0_17.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_16) at (120mm,80mm) {};
+\draw[->,semithick,color=red] ($(s_0_16.east)-(1mm,0mm)$) -- ($(r_0_16.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_7) at (124mm,35mm) {};
+\draw[->,semithick,color=red] ($(s_0_7.east)-(1mm,0mm)$) -- ($(r_0_7.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_6) at (128mm,30mm) {};
+\draw[->,semithick,color=red] ($(s_0_6.east)-(1mm,0mm)$) -- ($(r_0_6.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_5) at (132mm,25mm) {};
+\draw[->,semithick,color=red] ($(s_0_5.east)-(1mm,0mm)$) -- ($(r_0_5.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_4) at (136mm,20mm) {};
+\draw[->,semithick,color=red] ($(s_0_4.east)-(1mm,0mm)$) -- ($(r_0_4.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_3) at (136mm,15mm) {};
+\draw[->] ($(s_0_3.east)-(1mm,0mm)$) -- ($(r_0_3.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (140mm,10mm) {};
+\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (144mm,5mm) {};
+\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_31) (s_0_30) (s_0_29) (s_0_28) (s_0_27) (s_0_26) (s_0_25) (s_0_24) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_23) (s_0_22) (s_0_21) (s_0_20) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_19) (s_0_18) (s_0_17) (s_0_16) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_31) (r_0_30) (r_0_29) (r_0_28) (r_0_27) (r_0_26) (r_0_25) (r_0_24) (r_0_15) (r_0_14) (r_0_13) (r_0_12) (r_0_23) (r_0_22) (r_0_21) (r_0_20) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (r_0_19) (r_0_18) (r_0_17) (r_0_16) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_31) (s_0_30) (s_0_29) (s_0_28) (s_0_27) (s_0_26) (s_0_25) (s_0_24) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_23) (s_0_22) (s_0_21) (s_0_20) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_19) (s_0_18) (s_0_17) (s_0_16) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_31) (r_0_30) (r_0_29) (r_0_28) (r_0_27) (r_0_26) (r_0_25) (r_0_24) (r_0_15) (r_0_14) (r_0_13) (r_0_23) (r_0_12) (r_0_22) (r_0_21) (r_0_20) (r_0_11) (r_0_10) (r_0_9) (r_0_19) (r_0_8) (r_0_18) (r_0_17) (r_0_16) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_31) (s_0_30) (s_0_29) (s_0_28) (s_0_27) (s_0_26) (s_0_25) (s_0_24) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_23) (s_0_22) (s_0_21) (s_0_20) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_19) (s_0_18) (s_0_17) (s_0_16) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_31) (r_0_30) (r_0_29) (r_0_28) (r_0_27) (r_0_26) (r_0_25) (r_0_24) (r_0_15) (r_0_14) (r_0_13) (r_0_12) (r_0_23) (r_0_22) (r_0_21) (r_0_20) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (r_0_19) (r_0_18) (r_0_17) (r_0_16) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (s_0_31) (s_0_30) (s_0_29) (s_0_28) (s_0_27) (s_0_26) (s_0_25) (s_0_24) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_23) (s_0_22) (s_0_21) (s_0_20) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_19) (s_0_18) (s_0_17) (s_0_16) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_31) (r_0_30) (r_0_29) (r_0_28) (r_0_27) (r_0_26) (r_0_25) (r_0_24) (r_0_15) (r_0_14) (r_0_13) (r_0_23) (r_0_12) (r_0_22) (r_0_21) (r_0_20) (r_0_11) (r_0_10) (r_0_9) (r_0_19) (r_0_8) (r_0_18) (r_0_17) (r_0_16) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_16) at (\x1,80mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_17) at (\x1,85mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_18) at (\x1,90mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_19) at (\x1,95mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_20) at (\x1,100mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_21) at (\x1,105mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_22) at (\x1,110mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_23) at (\x1,115mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_24) at (\x1,120mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_25) at (\x1,125mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_26) at (\x1,130mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_27) at (\x1,135mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_28) at (\x1,140mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_29) at (\x1,145mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_30) at (\x1,150mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_31) at (\x1,155mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_31) (s_0_30) (s_0_29) (s_0_28) (s_0_27) (s_0_26) (s_0_25) (s_0_24) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_23) (s_0_22) (s_0_21) (s_0_20) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_19) (s_0_18) (s_0_17) (s_0_16) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_31) (s_0_30) (s_0_29) (s_0_28) (s_0_27) (s_0_26) (s_0_25) (s_0_24) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_23) (s_0_22) (s_0_21) (s_0_20) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_19) (s_0_18) (s_0_17) (s_0_16) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (numa_axis_4.west) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (numa_axis_4.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (numa_axis_8.west) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (numa_axis_8.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_0_15) (r_0_14) (r_0_13) (r_0_12) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_0_15) (r_0_14) (r_0_13) (r_0_12) (numa_axis_12.west),rounded corners] {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_16_label) (core_17_label) (core_18_label) (core_19_label) (r_0_19) (r_0_18) (r_0_17) (r_0_16) (numa_axis_16.west) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (r_0_19) (r_0_18) (r_0_17) (r_0_16) (numa_axis_16.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_0_23) (r_0_22) (r_0_21) (r_0_20) (numa_axis_20.west) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_0_23) (r_0_22) (r_0_21) (r_0_20) (numa_axis_20.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_24_label) (core_25_label) (core_26_label) (core_27_label) (r_0_27) (r_0_26) (r_0_25) (r_0_24) (numa_axis_24.west) (core_24_label) (core_25_label) (core_26_label) (core_27_label) (r_0_27) (r_0_26) (r_0_25) (r_0_24) (numa_axis_24.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_28_label) (core_29_label) (core_30_label) (core_31_label) (r_0_31) (r_0_30) (r_0_29) (r_0_28) (numa_axis_28.west) (core_28_label) (core_29_label) (core_30_label) (core_31_label) (r_0_31) (r_0_30) (r_0_29) (r_0_28) (numa_axis_28.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,80mm) -- (\x2,80mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,85mm) -- (\x2,85mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,90mm) -- (\x2,90mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,95mm) -- (\x2,95mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,100mm) -- (\x2,100mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,105mm) -- (\x2,105mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,110mm) -- (\x2,110mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,115mm) -- (\x2,115mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,120mm) -- (\x2,120mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,125mm) -- (\x2,125mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,130mm) -- (\x2,130mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,135mm) -- (\x2,135mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,140mm) -- (\x2,140mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,145mm) -- (\x2,145mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,150mm) -- (\x2,150mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,155mm) -- (\x2,155mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: gruyere, topology: sequential};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_sbrinz_badtree.tex
New visualization applied to all combinations of machines and topologies except for rings

@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\node at (0mm,240mm) {Machine: sbrinz, topology: badtree};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_9) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_10) at (60mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_9) at (80mm,135mm) {};
-\draw[->,very thick,color=red] (s_0_9.center) -- (r_0_9.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_9_6) at (90mm,135mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_9_2) at (100mm,135mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_10) at (90mm,150mm) {};
-\draw[->,very thick,color=red] (s_0_10.center) -- (r_0_10.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_10_3) at (100mm,150mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_10_1) at (110mm,150mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_6) at (110mm,90mm) {};
-\draw[->,very thick,color=red] (s_9_6.center) -- (r_9_6.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_6_12) at (120mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (130mm,90mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_3) at (130mm,45mm) {};
-\draw[->,very thick,color=red] (s_10_3.center) -- (r_10_3.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_3_11) at (140mm,45mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (150mm,45mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_2) at (130mm,30mm) {};
-\draw[->,very thick,color=red] (s_9_2.center) -- (r_9_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_1) at (140mm,15mm) {};
-\draw[->,very thick,color=red] (s_10_1.center) -- (r_10_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_12) at (150mm,180mm) {};
-\draw[->,very thick,color=red] (s_6_12.center) -- (r_6_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_7) at (160mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_4) at (170mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (160mm,195mm) {};
-\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_13_5) at (170mm,195mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_11) at (170mm,165mm) {};
-\draw[->,very thick,color=red] (s_3_11.center) -- (r_3_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (180mm,120mm) {};
-\draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_7) at (190mm,105mm) {};
-\draw[->,very thick,color=red] (s_12_7.center) -- (r_12_7.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (200mm,105mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_7_14) at (210mm,105mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_5) at (200mm,75mm) {};
-\draw[->,very thick,color=red] (s_13_5.center) -- (r_13_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_4) at (200mm,60mm) {};
-\draw[->,very thick,color=red] (s_12_4.center) -- (r_12_4.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (230mm,225mm) {};
-\draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_14) at (240mm,210mm) {};
-\draw[->,very thick,color=red] (s_7_14.center) -- (r_7_14.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_9) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_10) at (24mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_9) at (32mm,45mm) {};
+\draw[->,semithick,color=red] ($(s_0_9.east)-(1mm,0mm)$) -- ($(r_0_9.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_9_6) at (36mm,45mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_9_2) at (40mm,45mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_10) at (36mm,50mm) {};
+\draw[->,semithick,color=red] ($(s_0_10.east)-(1mm,0mm)$) -- ($(r_0_10.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_10_3) at (40mm,50mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_10_1) at (44mm,50mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_9_6) at (44mm,30mm) {};
+\draw[->,semithick,color=red] ($(s_9_6.east)-(1mm,0mm)$) -- ($(r_9_6.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_12) at (48mm,30mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_13) at (52mm,30mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_9_2) at (52mm,10mm) {};
+\draw[->,semithick,color=red] ($(s_9_2.east)-(1mm,0mm)$) -- ($(r_9_2.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_10_3) at (52mm,15mm) {};
+\draw[->,semithick,color=red] ($(s_10_3.east)-(1mm,0mm)$) -- ($(r_10_3.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_11) at (56mm,15mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_8) at (60mm,15mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_10_1) at (56mm,5mm) {};
+\draw[->,semithick,color=red] ($(s_10_1.east)-(1mm,0mm)$) -- ($(r_10_1.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_12) at (60mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_6_12.east)-(1mm,0mm)$) -- ($(r_6_12.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_7) at (64mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_4) at (68mm,60mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_13) at (64mm,65mm) {};
+\draw[->,semithick,color=red] ($(s_6_13.east)-(1mm,0mm)$) -- ($(r_6_13.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_13_5) at (68mm,65mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_11) at (68mm,55mm) {};
+\draw[->,semithick,color=red] ($(s_3_11.east)-(1mm,0mm)$) -- ($(r_3_11.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_8) at (72mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_3_8.east)-(1mm,0mm)$) -- ($(r_3_8.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_7) at (76mm,35mm) {};
+\draw[->,semithick,color=red] ($(s_12_7.east)-(1mm,0mm)$) -- ($(r_12_7.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_7_15) at (80mm,35mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_7_14) at (84mm,35mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_4) at (80mm,20mm) {};
+\draw[->,semithick,color=red] ($(s_12_4.east)-(1mm,0mm)$) -- ($(r_12_4.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_13_5) at (80mm,25mm) {};
+\draw[->,semithick,color=red] ($(s_13_5.east)-(1mm,0mm)$) -- ($(r_13_5.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_7_15) at (92mm,75mm) {};
+\draw[->,semithick,color=red] ($(s_7_15.east)-(1mm,0mm)$) -- ($(r_7_15.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_7_14) at (96mm,70mm) {};
+\draw[->,semithick,color=red] ($(s_7_14.east)-(1mm,0mm)$) -- ($(r_7_14.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_9) (s_0_10) (r_0_9) (s_9_6) (s_9_2) (r_0_10) (s_10_3) (s_10_1) (r_9_6) (s_6_12) (s_6_13) (r_9_2) (r_10_3) (s_3_11) (s_3_8) (r_10_1) (r_6_12) (s_12_7) (s_12_4) (r_6_13) (s_13_5) (r_3_11) (r_3_8) (r_12_7) (s_7_15) (s_7_14) (r_13_5) (r_12_4) (r_7_15) (r_7_14) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_9) (s_0_10) (r_0_9) (s_9_6) (s_9_2) (r_0_10) (s_10_3) (s_10_1) (r_9_6) (s_6_12) (s_6_13) (r_9_2) (r_10_3) (s_3_11) (s_3_8) (r_10_1) (r_6_12) (s_12_7) (s_12_4) (r_6_13) (s_13_5) (r_3_11) (r_3_8) (r_12_7) (s_7_15) (s_7_14) (r_12_4) (r_13_5) (r_7_15) (r_7_14)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_9) (s_0_10) (r_0_9) (s_9_6) (s_9_2) (r_0_10) (s_10_3) (s_10_1) (r_9_6) (s_6_12) (s_6_13) (r_9_2) (r_10_3) (s_3_11) (s_3_8) (r_10_1) (r_6_12) (s_12_7) (s_12_4) (r_6_13) (s_13_5) (r_3_11) (r_3_8) (r_12_7) (s_7_15) (s_7_14) (r_13_5) (r_12_4) (r_7_15) (r_7_14) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_9) (s_0_10) (r_0_9) (s_9_6) (s_9_2) (r_0_10) (s_10_3) (s_10_1) (r_9_6) (s_6_12) (s_6_13) (r_9_2) (r_10_3) (s_3_11) (s_3_8) (r_10_1) (r_6_12) (s_12_7) (s_12_4) (r_6_13) (s_13_5) (r_3_11) (r_3_8) (r_12_7) (s_7_15) (s_7_14) (r_12_4) (r_13_5) (r_7_15) (r_7_14),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_9) (s_0_10) (r_9_2) (r_10_3) (s_3_11) (s_3_8) (r_10_1) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_9) (s_0_10) (r_9_2) (r_10_3) (s_3_11) (s_3_8) (r_10_1) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_9_6) (s_6_12) (s_6_13) (r_12_7) (s_7_15) (s_7_14) (r_13_5) (r_12_4) (numa_axis_4.west) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_9_6) (s_6_12) (s_6_13) (r_12_7) (s_7_15) (s_7_14) (r_12_4) (r_13_5) (numa_axis_4.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_9) (s_9_6) (s_9_2) (r_0_10) (s_10_3) (s_10_1) (r_3_11) (r_3_8) (numa_axis_8.west) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_9) (s_9_6) (s_9_2) (r_0_10) (s_10_3) (s_10_1) (r_3_11) (r_3_8) (numa_axis_8.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_6_12) (s_12_7) (s_12_4) (r_6_13) (s_13_5) (r_7_15) (r_7_14) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_6_12) (s_12_7) (s_12_4) (r_6_13) (s_13_5) (r_7_15) (r_7_14) (numa_axis_12.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: sbrinz, topology: badtree};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_sbrinz_binarytree.tex
New visualization applied to all combinations of machines and topologies except for rings

@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\node at (0mm,240mm) {Machine: sbrinz, topology: binarytree};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (60mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (61mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (71mm,15mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_1_4) at (81mm,15mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (71mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (91mm,30mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (82mm,45mm) {};
-\draw[->] (s_1_3.center) -- (r_1_3.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (92mm,45mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (102mm,45mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
-\draw[->,very thick,color=red] (s_2_6.center) -- (r_2_6.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_6_14) at (111mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (101mm,60mm) {};
-\draw[->,very thick,color=red] (s_1_4.center) -- (r_1_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (111mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (121mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (111mm,75mm) {};
-\draw[->,very thick,color=red] (s_2_5.center) -- (r_2_5.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (121mm,75mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (131mm,75mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (112mm,105mm) {};
-\draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (122mm,105mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (131mm,150mm) {};
-\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (132mm,120mm) {};
-\draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (141mm,135mm) {};
-\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (141mm,210mm) {};
-\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (151mm,165mm) {};
-\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (151mm,180mm) {};
-\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (151mm,195mm) {};
-\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (152mm,225mm) {};
-\draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (24mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (24mm,5mm) {};
+\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_1_3) at (28mm,5mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_1_4) at (32mm,5mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (28mm,10mm) {};
+\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_2_6) at (32mm,10mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_2_5) at (36mm,10mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_1_3) at (32mm,15mm) {};
+\draw[->] ($(s_1_3.east)-(1mm,0mm)$) -- ($(r_1_3.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_7) at (36mm,15mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_8) at (40mm,15mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_2_6) at (40mm,30mm) {};
+\draw[->,semithick,color=red] ($(s_2_6.east)-(1mm,0mm)$) -- ($(r_2_6.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_14) at (44mm,30mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_13) at (48mm,30mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_1_4) at (40mm,20mm) {};
+\draw[->,semithick,color=red] ($(s_1_4.east)-(1mm,0mm)$) -- ($(r_1_4.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_10) at (44mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_9) at (48mm,20mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_2_5) at (44mm,25mm) {};
+\draw[->,semithick,color=red] ($(s_2_5.east)-(1mm,0mm)$) -- ($(r_2_5.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_5_12) at (48mm,25mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_5_11) at (52mm,25mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_7) at (44mm,35mm) {};
+\draw[->,semithick,color=red] ($(s_3_7.east)-(1mm,0mm)$) -- ($(r_3_7.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_7_15) at (48mm,35mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_10) at (52mm,50mm) {};
+\draw[->,semithick,color=red] ($(s_4_10.east)-(1mm,0mm)$) -- ($(r_4_10.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_8) at (52mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_3_8.east)-(1mm,0mm)$) -- ($(r_3_8.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_14) at (56mm,70mm) {};
+\draw[->,semithick,color=red] ($(s_6_14.east)-(1mm,0mm)$) -- ($(r_6_14.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_9) at (56mm,45mm) {};
+\draw[->,semithick,color=red] ($(s_4_9.east)-(1mm,0mm)$) -- ($(r_4_9.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_5_12) at (60mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_5_12.east)-(1mm,0mm)$) -- ($(r_5_12.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_13) at (60mm,65mm) {};
+\draw[->,semithick,color=red] ($(s_6_13.east)-(1mm,0mm)$) -- ($(r_6_13.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_5_11) at (60mm,55mm) {};
+\draw[->,semithick,color=red] ($(s_5_11.east)-(1mm,0mm)$) -- ($(r_5_11.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_7_15) at (60mm,75mm) {};
+\draw[->,semithick,color=red] ($(s_7_15.east)-(1mm,0mm)$) -- ($(r_7_15.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_7) (s_3_8) (r_1_4) (s_4_10) (s_4_9) (r_2_6) (s_6_14) (s_6_13) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (r_4_10) (r_3_8) (r_4_9) (r_6_14) (r_6_13) (r_5_11) (r_5_12) (r_7_15) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_7) (s_3_8) (r_2_6) (s_6_14) (s_6_13) (r_1_4) (s_4_10) (s_4_9) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (r_4_10) (r_3_8) (r_6_14) (r_4_9) (r_5_12) (r_6_13) (r_5_11) (r_7_15)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_7) (s_3_8) (r_1_4) (s_4_10) (s_4_9) (r_2_6) (s_6_14) (s_6_13) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (r_4_10) (r_3_8) (r_4_9) (r_6_14) (r_6_13) (r_5_11) (r_5_12) (r_7_15) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_7) (s_3_8) (r_2_6) (s_6_14) (s_6_13) (r_1_4) (s_4_10) (s_4_9) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (r_4_10) (r_3_8) (r_6_14) (r_4_9) (r_5_12) (r_6_13) (r_5_11) (r_7_15),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_7) (s_3_8) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_1) (s_0_2) (r_0_1) (s_1_3) (s_1_4) (r_0_2) (s_2_6) (s_2_5) (r_1_3) (s_3_7) (s_3_8) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_1_4) (s_4_10) (s_4_9) (r_2_6) (s_6_14) (s_6_13) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (numa_axis_4.west) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_2_6) (s_6_14) (s_6_13) (r_1_4) (s_4_10) (s_4_9) (r_2_5) (s_5_12) (s_5_11) (r_3_7) (s_7_15) (numa_axis_4.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_4_10) (r_3_8) (r_4_9) (r_5_11) (numa_axis_8.west) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_4_10) (r_3_8) (r_4_9) (r_5_11) (numa_axis_8.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_6_14) (r_6_13) (r_5_12) (r_7_15) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_6_14) (r_5_12) (r_6_13) (r_7_15) (numa_axis_12.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: sbrinz, topology: binarytree};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_sbrinz_cluster.tex
New visualization applied to all combinations of machines and topologies except for rings

@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\node at (0mm,240mm) {Machine: sbrinz, topology: cluster};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (80mm,120mm) {};
-\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_12) at (90mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (100mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (110mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (120mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (80mm,60mm) {};
-\draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (90mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (100mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (110mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
-\draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (101mm,105mm) {};
-\draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_12) at (110mm,180mm) {};
-\draw[->,very thick,color=red] (s_8_12.center) -- (r_8_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (120mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (130mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (111mm,90mm) {};
-\draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (111mm,165mm) {};
-\draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (121mm,75mm) {};
-\draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (121mm,150mm) {};
-\draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (131mm,135mm) {};
-\draw[->] (s_8_9.center) -- (r_8_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (131mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (141mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_8) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_4) at (24mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_3) at (28mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (32mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (36mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_8) at (32mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_0_8.east)-(1mm,0mm)$) -- ($(r_0_8.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_12) at (36mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_11) at (40mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_10) at (44mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_9) at (48mm,40mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_4) at (32mm,20mm) {};
+\draw[->,semithick,color=red] ($(s_0_4.east)-(1mm,0mm)$) -- ($(r_0_4.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_7) at (36mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_6) at (40mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_5) at (44mm,20mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_3) at (32mm,15mm) {};
+\draw[->] ($(s_0_3.east)-(1mm,0mm)$) -- ($(r_0_3.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (36mm,10mm) {};
+\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_7) at (40mm,35mm) {};
+\draw[->] ($(s_4_7.east)-(1mm,0mm)$) -- ($(r_4_7.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (40mm,5mm) {};
+\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_12) at (44mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_8_12.east)-(1mm,0mm)$) -- ($(r_8_12.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_15) at (48mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_14) at (52mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_13) at (56mm,60mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_11) at (44mm,55mm) {};
+\draw[->] ($(s_8_11.east)-(1mm,0mm)$) -- ($(r_8_11.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_6) at (44mm,30mm) {};
+\draw[->] ($(s_4_6.east)-(1mm,0mm)$) -- ($(r_4_6.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_10) at (48mm,50mm) {};
+\draw[->] ($(s_8_10.east)-(1mm,0mm)$) -- ($(r_8_10.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_5) at (48mm,25mm) {};
+\draw[->] ($(s_4_5.east)-(1mm,0mm)$) -- ($(r_4_5.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_15) at (52mm,75mm) {};
+\draw[->] ($(s_12_15.east)-(1mm,0mm)$) -- ($(r_12_15.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_9) at (52mm,45mm) {};
+\draw[->] ($(s_8_9.east)-(1mm,0mm)$) -- ($(r_8_9.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_14) at (56mm,70mm) {};
+\draw[->] ($(s_12_14.east)-(1mm,0mm)$) -- ($(r_12_14.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_13) at (60mm,65mm) {};
+\draw[->] ($(s_12_13.east)-(1mm,0mm)$) -- ($(r_12_13.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_8) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_8) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_0_4) (s_4_7) (s_4_6) (s_4_5) (r_0_3) (r_0_2) (r_4_7) (r_0_1) (r_8_12) (s_12_15) (s_12_14) (s_12_13) (r_4_6) (r_8_11) (r_8_10) (r_4_5) (r_12_15) (r_8_9) (r_12_14) (r_12_13) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_8) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_8) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_0_4) (s_4_7) (s_4_6) (s_4_5) (r_0_3) (r_0_2) (r_4_7) (r_0_1) (r_8_12) (s_12_15) (s_12_14) (s_12_13) (r_8_11) (r_4_6) (r_8_10) (r_4_5) (r_12_15) (r_8_9) (r_12_14) (r_12_13)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_8) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_8) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_0_4) (s_4_7) (s_4_6) (s_4_5) (r_0_3) (r_0_2) (r_4_7) (r_0_1) (r_8_12) (s_12_15) (s_12_14) (s_12_13) (r_4_6) (r_8_11) (r_8_10) (r_4_5) (r_12_15) (r_8_9) (r_12_14) (r_12_13) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_8) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_8) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_0_4) (s_4_7) (s_4_6) (s_4_5) (r_0_3) (r_0_2) (r_4_7) (r_0_1) (r_8_12) (s_12_15) (s_12_14) (s_12_13) (r_8_11) (r_4_6) (r_8_10) (r_4_5) (r_12_15) (r_8_9) (r_12_14) (r_12_13),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_8) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_8) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_4) (s_4_7) (s_4_6) (s_4_5) (r_4_7) (r_4_6) (r_4_5) (numa_axis_4.west) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_4) (s_4_7) (s_4_6) (s_4_5) (r_4_7) (r_4_6) (r_4_5) (numa_axis_4.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_8) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_8_11) (r_8_10) (r_8_9) (numa_axis_8.west) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_8) (s_8_12) (s_8_11) (s_8_10) (s_8_9) (r_8_11) (r_8_10) (r_8_9) (numa_axis_8.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_8_12) (s_12_15) (s_12_14) (s_12_13) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_8_12) (s_12_15) (s_12_14) (s_12_13) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: sbrinz, topology: cluster};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_sbrinz_mst.tex
New visualization applied to all combinations of machines and topologies except for rings

@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\node at (0mm,240mm) {Machine: sbrinz, topology: mst};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (90mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (70mm,60mm) {};
-\draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_8) at (80mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_7) at (90mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_6) at (100mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_5) at (110mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (80mm,180mm) {};
-\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (90mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (100mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (110mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (81mm,45mm) {};
-\draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (91mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_8) at (100mm,120mm) {};
-\draw[->,very thick,color=red] (s_4_8.center) -- (r_4_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_11) at (110mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_10) at (120mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_9) at (130mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (101mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (101mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_7) at (101mm,105mm) {};
-\draw[->] (s_4_7.center) -- (r_4_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_6) at (111mm,90mm) {};
-\draw[->] (s_4_6.center) -- (r_4_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (111mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (121mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_5) at (121mm,75mm) {};
-\draw[->] (s_4_5.center) -- (r_4_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_11) at (121mm,165mm) {};
-\draw[->] (s_8_11.center) -- (r_8_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_10) at (131mm,150mm) {};
-\draw[->] (s_8_10.center) -- (r_8_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_9) at (141mm,135mm) {};
-\draw[->] (s_8_9.center) -- (r_8_9.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_4) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_12) at (24mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_3) at (28mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (32mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (36mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_4) at (28mm,20mm) {};
+\draw[->,semithick,color=red] ($(s_0_4.east)-(1mm,0mm)$) -- ($(r_0_4.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_8) at (32mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_7) at (36mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_6) at (40mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_5) at (44mm,20mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_12) at (32mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_0_12.east)-(1mm,0mm)$) -- ($(r_0_12.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_15) at (36mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_14) at (40mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_13) at (44mm,60mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_3) at (32mm,15mm) {};
+\draw[->] ($(s_0_3.east)-(1mm,0mm)$) -- ($(r_0_3.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (36mm,10mm) {};
+\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_8) at (40mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_4_8.east)-(1mm,0mm)$) -- ($(r_4_8.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_11) at (44mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_10) at (48mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_9) at (52mm,40mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_15) at (40mm,75mm) {};
+\draw[->] ($(s_12_15.east)-(1mm,0mm)$) -- ($(r_12_15.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (40mm,5mm) {};
+\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_7) at (40mm,35mm) {};
+\draw[->] ($(s_4_7.east)-(1mm,0mm)$) -- ($(r_4_7.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_6) at (44mm,30mm) {};
+\draw[->] ($(s_4_6.east)-(1mm,0mm)$) -- ($(r_4_6.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_14) at (44mm,70mm) {};
+\draw[->] ($(s_12_14.east)-(1mm,0mm)$) -- ($(r_12_14.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_13) at (48mm,65mm) {};
+\draw[->] ($(s_12_13.east)-(1mm,0mm)$) -- ($(r_12_13.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_5) at (48mm,25mm) {};
+\draw[->] ($(s_4_5.east)-(1mm,0mm)$) -- ($(r_4_5.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_11) at (48mm,55mm) {};
+\draw[->] ($(s_8_11.east)-(1mm,0mm)$) -- ($(r_8_11.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_10) at (52mm,50mm) {};
+\draw[->] ($(s_8_10.east)-(1mm,0mm)$) -- ($(r_8_10.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_9) at (56mm,45mm) {};
+\draw[->] ($(s_8_9.east)-(1mm,0mm)$) -- ($(r_8_9.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_4) (s_0_12) (s_0_3) (s_0_2) (s_0_1) (r_0_4) (s_4_8) (s_4_7) (s_4_6) (s_4_5) (r_0_12) (s_12_15) (s_12_14) (s_12_13) (r_0_3) (r_0_2) (r_4_8) (s_8_11) (s_8_10) (s_8_9) (r_12_15) (r_4_7) (r_0_1) (r_4_6) (r_12_14) (r_8_11) (r_4_5) (r_12_13) (r_8_10) (r_8_9) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_4) (s_0_12) (s_0_3) (s_0_2) (s_0_1) (r_0_4) (s_4_8) (s_4_7) (s_4_6) (s_4_5) (r_0_12) (s_12_15) (s_12_14) (s_12_13) (r_0_3) (r_0_2) (r_4_8) (s_8_11) (s_8_10) (s_8_9) (r_12_15) (r_0_1) (r_4_7) (r_4_6) (r_12_14) (r_12_13) (r_4_5) (r_8_11) (r_8_10) (r_8_9)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_4) (s_0_12) (s_0_3) (s_0_2) (s_0_1) (r_0_4) (s_4_8) (s_4_7) (s_4_6) (s_4_5) (r_0_12) (s_12_15) (s_12_14) (s_12_13) (r_0_3) (r_0_2) (r_4_8) (s_8_11) (s_8_10) (s_8_9) (r_12_15) (r_4_7) (r_0_1) (r_4_6) (r_12_14) (r_8_11) (r_4_5) (r_12_13) (r_8_10) (r_8_9) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_4) (s_0_12) (s_0_3) (s_0_2) (s_0_1) (r_0_4) (s_4_8) (s_4_7) (s_4_6) (s_4_5) (r_0_12) (s_12_15) (s_12_14) (s_12_13) (r_0_3) (r_0_2) (r_4_8) (s_8_11) (s_8_10) (s_8_9) (r_12_15) (r_0_1) (r_4_7) (r_4_6) (r_12_14) (r_12_13) (r_4_5) (r_8_11) (r_8_10) (r_8_9),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_4) (s_0_12) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_4) (s_0_12) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_4) (s_4_8) (s_4_7) (s_4_6) (s_4_5) (r_4_7) (r_4_6) (r_4_5) (numa_axis_4.west) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_4) (s_4_8) (s_4_7) (s_4_6) (s_4_5) (r_4_7) (r_4_6) (r_4_5) (numa_axis_4.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_4_8) (s_8_11) (s_8_10) (s_8_9) (r_8_11) (r_8_10) (r_8_9) (numa_axis_8.west) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_4_8) (s_8_11) (s_8_10) (s_8_9) (r_8_11) (r_8_10) (r_8_9) (numa_axis_8.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_0_12) (s_12_15) (s_12_14) (s_12_13) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_0_12) (s_12_15) (s_12_14) (s_12_13) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: sbrinz, topology: mst};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_sbrinz_sequential.tex
New visualization applied to all combinations of machines and topologies except for rings

@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=green!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=green!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=blue!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=blue!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=blue!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=blue!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=orange!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=orange!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=orange!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=orange!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\node at (0mm,240mm) {Machine: sbrinz, topology: sequential};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_11) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_10) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_9) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_8) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_15) at (90mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_14) at (100mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_13) at (110mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (120mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_7) at (130mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_6) at (140mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (150mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (160mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (170mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (180mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (190mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_11) at (80mm,165mm) {};
-\draw[->,very thick,color=red] (s_0_11.center) -- (r_0_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_10) at (90mm,150mm) {};
-\draw[->,very thick,color=red] (s_0_10.center) -- (r_0_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_9) at (100mm,135mm) {};
-\draw[->,very thick,color=red] (s_0_9.center) -- (r_0_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_8) at (110mm,120mm) {};
-\draw[->,very thick,color=red] (s_0_8.center) -- (r_0_8.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_15) at (110mm,225mm) {};
-\draw[->,very thick,color=red] (s_0_15.center) -- (r_0_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_14) at (120mm,210mm) {};
-\draw[->,very thick,color=red] (s_0_14.center) -- (r_0_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_13) at (130mm,195mm) {};
-\draw[->,very thick,color=red] (s_0_13.center) -- (r_0_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (140mm,180mm) {};
-\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_7) at (150mm,105mm) {};
-\draw[->,very thick,color=red] (s_0_7.center) -- (r_0_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_6) at (160mm,90mm) {};
-\draw[->,very thick,color=red] (s_0_6.center) -- (r_0_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (170mm,75mm) {};
-\draw[->,very thick,color=red] (s_0_5.center) -- (r_0_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (180mm,60mm) {};
-\draw[->,very thick,color=red] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (181mm,45mm) {};
-\draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (191mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (201mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_11) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_10) at (24mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_9) at (28mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_8) at (32mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_15) at (36mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_14) at (40mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_13) at (44mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_12) at (48mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_7) at (52mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_6) at (56mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_5) at (60mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_4) at (64mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_3) at (68mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (72mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (76mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_11) at (32mm,55mm) {};
+\draw[->,semithick,color=red] ($(s_0_11.east)-(1mm,0mm)$) -- ($(r_0_11.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_10) at (36mm,50mm) {};
+\draw[->,semithick,color=red] ($(s_0_10.east)-(1mm,0mm)$) -- ($(r_0_10.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_9) at (40mm,45mm) {};
+\draw[->,semithick,color=red] ($(s_0_9.east)-(1mm,0mm)$) -- ($(r_0_9.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_15) at (44mm,75mm) {};
+\draw[->,semithick,color=red] ($(s_0_15.east)-(1mm,0mm)$) -- ($(r_0_15.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_8) at (44mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_0_8.east)-(1mm,0mm)$) -- ($(r_0_8.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_14) at (48mm,70mm) {};
+\draw[->,semithick,color=red] ($(s_0_14.east)-(1mm,0mm)$) -- ($(r_0_14.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_13) at (52mm,65mm) {};
+\draw[->,semithick,color=red] ($(s_0_13.east)-(1mm,0mm)$) -- ($(r_0_13.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_12) at (56mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_0_12.east)-(1mm,0mm)$) -- ($(r_0_12.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_7) at (60mm,35mm) {};
+\draw[->,semithick,color=red] ($(s_0_7.east)-(1mm,0mm)$) -- ($(r_0_7.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_6) at (64mm,30mm) {};
+\draw[->,semithick,color=red] ($(s_0_6.east)-(1mm,0mm)$) -- ($(r_0_6.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_5) at (68mm,25mm) {};
+\draw[->,semithick,color=red] ($(s_0_5.east)-(1mm,0mm)$) -- ($(r_0_5.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_4) at (72mm,20mm) {};
+\draw[->,semithick,color=red] ($(s_0_4.east)-(1mm,0mm)$) -- ($(r_0_4.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_3) at (72mm,15mm) {};
+\draw[->] ($(s_0_3.east)-(1mm,0mm)$) -- ($(r_0_3.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (76mm,10mm) {};
+\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (80mm,5mm) {};
+\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_11) (r_0_10) (r_0_9) (r_0_15) (r_0_8) (r_0_14) (r_0_13) (r_0_12) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_11) (r_0_10) (r_0_9) (r_0_15) (r_0_8) (r_0_14) (r_0_13) (r_0_12) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_11) (r_0_10) (r_0_9) (r_0_15) (r_0_8) (r_0_14) (r_0_13) (r_0_12) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_11) (r_0_10) (r_0_9) (r_0_15) (r_0_8) (r_0_14) (r_0_13) (r_0_12) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (numa_axis_4.west) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (numa_axis_4.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (numa_axis_8.west) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (numa_axis_8.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_0_15) (r_0_14) (r_0_13) (r_0_12) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (r_0_15) (r_0_14) (r_0_13) (r_0_12) (numa_axis_12.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: sbrinz, topology: sequential};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_ziger_badtree.tex
New visualization applied to all combinations of machines and topologies except for rings

@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=red!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=red!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=green!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=green!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=green!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=green!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=blue!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=blue!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=blue!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=blue!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=blue!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=blue!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=orange!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=orange!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=orange!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=orange!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=orange!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=orange!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\node at (0mm,360mm) {Machine: ziger, topology: badtree};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_17) at (60mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
-\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_16_2) at (90mm,240mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_16_1) at (100mm,240mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_17) at (90mm,255mm) {};
-\draw[->,very thick,color=red] (s_0_17.center) -- (r_0_17.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_17_3) at (100mm,255mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_17_4) at (110mm,255mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_2) at (120mm,30mm) {};
-\draw[->,very thick,color=red] (s_16_2.center) -- (r_16_2.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_2_18) at (130mm,30mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_17_3) at (130mm,45mm) {};
-\draw[->,very thick,color=red] (s_17_3.center) -- (r_17_3.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_3_13) at (140mm,45mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_3_15) at (150mm,45mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_16_1) at (130mm,15mm) {};
-\draw[->,very thick,color=red] (s_16_1.center) -- (r_16_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_17_4) at (140mm,60mm) {};
-\draw[->,very thick,color=red] (s_17_4.center) -- (r_17_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_14) at (150mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (160mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_18) at (150mm,270mm) {};
-\draw[->,very thick,color=red] (s_2_18.center) -- (r_2_18.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_18_10) at (160mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_8) at (170mm,270mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_13) at (170mm,195mm) {};
-\draw[->,very thick,color=red] (s_3_13.center) -- (r_3_13.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_13_5) at (180mm,195mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_14) at (180mm,210mm) {};
-\draw[->,very thick,color=red] (s_4_14.center) -- (r_4_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_15) at (180mm,225mm) {};
-\draw[->,very thick,color=red] (s_3_15.center) -- (r_3_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (190mm,180mm) {};
-\draw[->,very thick,color=red] (s_4_12.center) -- (r_4_12.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_10) at (190mm,150mm) {};
-\draw[->,very thick,color=red] (s_18_10.center) -- (r_18_10.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_10_19) at (200mm,150mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (210mm,150mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_8) at (200mm,120mm) {};
-\draw[->,very thick,color=red] (s_18_8.center) -- (r_18_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_21) at (210mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (220mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_13_5) at (210mm,75mm) {};
-\draw[->,very thick,color=red] (s_13_5.center) -- (r_13_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_19) at (230mm,285mm) {};
-\draw[->,very thick,color=red] (s_10_19.center) -- (r_10_19.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_19_9) at (240mm,285mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_19_11) at (250mm,285mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_21) at (240mm,315mm) {};
-\draw[->,very thick,color=red] (s_8_21.center) -- (r_8_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (240mm,330mm) {};
-\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_22_7) at (250mm,330mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_22_6) at (260mm,330mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (250mm,300mm) {};
-\draw[->,very thick,color=red] (s_8_20.center) -- (r_8_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_19_9) at (270mm,135mm) {};
-\draw[->,very thick,color=red] (s_19_9.center) -- (r_19_9.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_9_23) at (280mm,135mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_22_7) at (280mm,105mm) {};
-\draw[->,very thick,color=red] (s_22_7.center) -- (r_22_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_19_11) at (280mm,165mm) {};
-\draw[->,very thick,color=red] (s_19_11.center) -- (r_19_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_22_6) at (290mm,90mm) {};
-\draw[->,very thick,color=red] (s_22_6.center) -- (r_22_6.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_23) at (310mm,345mm) {};
-\draw[->,very thick,color=red] (s_9_23.center) -- (r_9_23.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node (core_16_label) at (0mm,80mm) {core 16};
+\node (core_17_label) at (0mm,85mm) {core 17};
+\node (core_18_label) at (0mm,90mm) {core 18};
+\node (core_19_label) at (0mm,95mm) {core 19};
+\node (core_20_label) at (0mm,100mm) {core 20};
+\node (core_21_label) at (0mm,105mm) {core 21};
+\node (core_22_label) at (0mm,110mm) {core 22};
+\node (core_23_label) at (0mm,115mm) {core 23};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_16) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_17) at (24mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_16) at (32mm,80mm) {};
+\draw[->,semithick,color=red] ($(s_0_16.east)-(1mm,0mm)$) -- ($(r_0_16.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_16_2) at (36mm,80mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_16_1) at (40mm,80mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_17) at (36mm,85mm) {};
+\draw[->,semithick,color=red] ($(s_0_17.east)-(1mm,0mm)$) -- ($(r_0_17.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_17_3) at (40mm,85mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_17_4) at (44mm,85mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_16_2) at (48mm,10mm) {};
+\draw[->,semithick,color=red] ($(s_16_2.east)-(1mm,0mm)$) -- ($(r_16_2.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_2_18) at (52mm,10mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_17_3) at (52mm,15mm) {};
+\draw[->,semithick,color=red] ($(s_17_3.east)-(1mm,0mm)$) -- ($(r_17_3.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_13) at (56mm,15mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_15) at (60mm,15mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_16_1) at (52mm,5mm) {};
+\draw[->,semithick,color=red] ($(s_16_1.east)-(1mm,0mm)$) -- ($(r_16_1.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_17_4) at (56mm,20mm) {};
+\draw[->,semithick,color=red] ($(s_17_4.east)-(1mm,0mm)$) -- ($(r_17_4.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_14) at (60mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_12) at (64mm,20mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_2_18) at (60mm,90mm) {};
+\draw[->,semithick,color=red] ($(s_2_18.east)-(1mm,0mm)$) -- ($(r_2_18.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_10) at (64mm,90mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_8) at (68mm,90mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_13) at (68mm,65mm) {};
+\draw[->,semithick,color=red] ($(s_3_13.east)-(1mm,0mm)$) -- ($(r_3_13.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_13_5) at (72mm,65mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_14) at (72mm,70mm) {};
+\draw[->,semithick,color=red] ($(s_4_14.east)-(1mm,0mm)$) -- ($(r_4_14.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_15) at (72mm,75mm) {};
+\draw[->,semithick,color=red] ($(s_3_15.east)-(1mm,0mm)$) -- ($(r_3_15.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_12) at (76mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_4_12.east)-(1mm,0mm)$) -- ($(r_4_12.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_10) at (76mm,50mm) {};
+\draw[->,semithick,color=red] ($(s_18_10.east)-(1mm,0mm)$) -- ($(r_18_10.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_10_19) at (80mm,50mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_10_22) at (84mm,50mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_8) at (80mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_18_8.east)-(1mm,0mm)$) -- ($(r_18_8.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_21) at (84mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_20) at (88mm,40mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_13_5) at (84mm,25mm) {};
+\draw[->,semithick,color=red] ($(s_13_5.east)-(1mm,0mm)$) -- ($(r_13_5.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_10_19) at (92mm,95mm) {};
+\draw[->,semithick,color=red] ($(s_10_19.east)-(1mm,0mm)$) -- ($(r_10_19.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_19_9) at (96mm,95mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_19_11) at (100mm,95mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_21) at (96mm,105mm) {};
+\draw[->,semithick,color=red] ($(s_8_21.east)-(1mm,0mm)$) -- ($(r_8_21.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_10_22) at (96mm,110mm) {};
+\draw[->,semithick,color=red] ($(s_10_22.east)-(1mm,0mm)$) -- ($(r_10_22.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_22_7) at (100mm,110mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_22_6) at (104mm,110mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_20) at (100mm,100mm) {};
+\draw[->,semithick,color=red] ($(s_8_20.east)-(1mm,0mm)$) -- ($(r_8_20.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_19_9) at (108mm,45mm) {};
+\draw[->,semithick,color=red] ($(s_19_9.east)-(1mm,0mm)$) -- ($(r_19_9.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_9_23) at (112mm,45mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_19_11) at (112mm,55mm) {};
+\draw[->,semithick,color=red] ($(s_19_11.east)-(1mm,0mm)$) -- ($(r_19_11.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_22_7) at (112mm,35mm) {};
+\draw[->,semithick,color=red] ($(s_22_7.east)-(1mm,0mm)$) -- ($(r_22_7.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_22_6) at (116mm,30mm) {};
+\draw[->,semithick,color=red] ($(s_22_6.east)-(1mm,0mm)$) -- ($(r_22_6.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_9_23) at (124mm,115mm) {};
+\draw[->,semithick,color=red] ($(s_9_23.east)-(1mm,0mm)$) -- ($(r_9_23.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_16) (s_0_17) (r_0_16) (s_16_2) (s_16_1) (r_0_17) (s_17_3) (s_17_4) (r_16_2) (s_2_18) (r_16_1) (r_17_3) (s_3_13) (s_3_15) (r_17_4) (s_4_14) (s_4_12) (r_2_18) (s_18_10) (s_18_8) (r_3_13) (s_13_5) (r_4_14) (r_3_15) (r_18_10) (s_10_19) (s_10_22) (r_4_12) (r_18_8) (s_8_21) (s_8_20) (r_13_5) (r_10_19) (s_19_9) (s_19_11) (r_8_21) (r_10_22) (s_22_7) (s_22_6) (r_8_20) (r_19_9) (s_9_23) (r_22_7) (r_19_11) (r_22_6) (r_9_23) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_16) (s_0_17) (r_0_16) (s_16_2) (s_16_1) (r_0_17) (s_17_3) (s_17_4) (r_16_2) (s_2_18) (r_17_3) (s_3_13) (s_3_15) (r_16_1) (r_17_4) (s_4_14) (s_4_12) (r_2_18) (s_18_10) (s_18_8) (r_3_13) (s_13_5) (r_4_14) (r_3_15) (r_4_12) (r_18_10) (s_10_19) (s_10_22) (r_18_8) (s_8_21) (s_8_20) (r_13_5) (r_10_19) (s_19_9) (s_19_11) (r_8_21) (r_10_22) (s_22_7) (s_22_6) (r_8_20) (r_19_9) (s_9_23) (r_19_11) (r_22_7) (r_22_6) (r_9_23)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_16) (s_0_17) (r_0_16) (s_16_2) (s_16_1) (r_0_17) (s_17_3) (s_17_4) (r_16_2) (s_2_18) (r_16_1) (r_17_3) (s_3_13) (s_3_15) (r_17_4) (s_4_14) (s_4_12) (r_2_18) (s_18_10) (s_18_8) (r_3_13) (s_13_5) (r_4_14) (r_3_15) (r_18_10) (s_10_19) (s_10_22) (r_4_12) (r_18_8) (s_8_21) (s_8_20) (r_13_5) (r_10_19) (s_19_9) (s_19_11) (r_8_21) (r_10_22) (s_22_7) (s_22_6) (r_8_20) (r_19_9) (s_9_23) (r_22_7) (r_19_11) (r_22_6) (r_9_23) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_16) (s_0_17) (r_0_16) (s_16_2) (s_16_1) (r_0_17) (s_17_3) (s_17_4) (r_16_2) (s_2_18) (r_17_3) (s_3_13) (s_3_15) (r_16_1) (r_17_4) (s_4_14) (s_4_12) (r_2_18) (s_18_10) (s_18_8) (r_3_13) (s_13_5) (r_4_14) (r_3_15) (r_4_12) (r_18_10) (s_10_19) (s_10_22) (r_18_8) (s_8_21) (s_8_20) (r_13_5) (r_10_19) (s_19_9) (s_19_11) (r_8_21) (r_10_22) (s_22_7) (s_22_6) (r_8_20) (r_19_9) (s_9_23) (r_19_11) (r_22_7) (r_22_6) (r_9_23),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_16) at (\x1,80mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_17) at (\x1,85mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_18) at (\x1,90mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_19) at (\x1,95mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_20) at (\x1,100mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_21) at (\x1,105mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_22) at (\x1,110mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_23) at (\x1,115mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (s_0_16) (s_0_17) (r_16_2) (s_2_18) (r_16_1) (r_17_3) (s_3_13) (s_3_15) (r_17_4) (s_4_14) (s_4_12) (r_13_5) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (s_0_16) (s_0_17) (r_16_2) (s_2_18) (r_17_3) (s_3_13) (s_3_15) (r_16_1) (r_17_4) (s_4_14) (s_4_12) (r_13_5) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_18_10) (s_10_19) (s_10_22) (r_18_8) (s_8_21) (s_8_20) (r_19_9) (s_9_23) (r_22_7) (r_19_11) (r_22_6) (numa_axis_6.west) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_18_10) (s_10_19) (s_10_22) (r_18_8) (s_8_21) (s_8_20) (r_19_9) (s_9_23) (r_19_11) (r_22_7) (r_22_6) (numa_axis_6.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (r_0_16) (s_16_2) (s_16_1) (r_0_17) (s_17_3) (s_17_4) (r_3_13) (s_13_5) (r_4_14) (r_3_15) (r_4_12) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (r_0_16) (s_16_2) (s_16_1) (r_0_17) (s_17_3) (s_17_4) (r_3_13) (s_13_5) (r_4_14) (r_3_15) (r_4_12) (numa_axis_12.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_2_18) (s_18_10) (s_18_8) (r_10_19) (s_19_9) (s_19_11) (r_8_21) (r_10_22) (s_22_7) (s_22_6) (r_8_20) (r_9_23) (numa_axis_18.west) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_2_18) (s_18_10) (s_18_8) (r_10_19) (s_19_9) (s_19_11) (r_8_21) (r_10_22) (s_22_7) (s_22_6) (r_8_20) (r_9_23) (numa_axis_18.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,80mm) -- (\x2,80mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,85mm) -- (\x2,85mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,90mm) -- (\x2,90mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,95mm) -- (\x2,95mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,100mm) -- (\x2,100mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,105mm) -- (\x2,105mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,110mm) -- (\x2,110mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,115mm) -- (\x2,115mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: ziger, topology: badtree};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_ziger_binarytree.tex
New visualization applied to all combinations of machines and topologies except for rings

@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=red!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=red!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=green!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=green!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=green!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=green!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=blue!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=blue!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=blue!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=blue!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=blue!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=blue!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=orange!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=orange!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=orange!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=orange!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=orange!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=orange!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\node at (0mm,360mm) {Machine: ziger, topology: binarytree};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (60mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (61mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_2_5) at (71mm,30mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_2_6) at (81mm,30mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (71mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_1_4) at (81mm,15mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_1_3) at (91mm,15mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_5) at (82mm,75mm) {};
-\draw[->] (s_2_5.center) -- (r_2_5.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_5_11) at (92mm,75mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_5_12) at (102mm,75mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_4) at (92mm,60mm) {};
-\draw[->] (s_1_4.center) -- (r_1_4.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_4_10) at (102mm,60mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_4_9) at (112mm,60mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_2_6) at (101mm,90mm) {};
-\draw[->,very thick,color=red] (s_2_6.center) -- (r_2_6.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_6_14) at (111mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_13) at (121mm,90mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_1_3) at (102mm,45mm) {};
-\draw[->] (s_1_3.center) -- (r_1_3.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_3_8) at (112mm,45mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_3_7) at (122mm,45mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_11) at (112mm,165mm) {};
-\draw[->,very thick,color=red] (s_5_11.center) -- (r_5_11.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_11_23) at (122mm,165mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_10) at (122mm,150mm) {};
-\draw[->,very thick,color=red] (s_4_10.center) -- (r_4_10.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (132mm,150mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_10_21) at (142mm,150mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_14) at (131mm,210mm) {};
-\draw[->,very thick,color=red] (s_6_14.center) -- (r_6_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_4_9) at (132mm,135mm) {};
-\draw[->,very thick,color=red] (s_4_9.center) -- (r_4_9.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_9_20) at (142mm,135mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_9_19) at (152mm,135mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_5_12) at (132mm,180mm) {};
-\draw[->,very thick,color=red] (s_5_12.center) -- (r_5_12.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_8) at (132mm,120mm) {};
-\draw[->,very thick,color=red] (s_3_8.center) -- (r_3_8.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_8_18) at (142mm,120mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_8_17) at (152mm,120mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_13) at (141mm,195mm) {};
-\draw[->,very thick,color=red] (s_6_13.center) -- (r_6_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_3_7) at (142mm,105mm) {};
-\draw[->,very thick,color=red] (s_3_7.center) -- (r_3_7.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_7_16) at (152mm,105mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_7_15) at (162mm,105mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_11_23) at (152mm,345mm) {};
-\draw[->,very thick,color=red] (s_11_23.center) -- (r_11_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (162mm,330mm) {};
-\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_16) at (172mm,240mm) {};
-\draw[->,very thick,color=red] (s_7_16.center) -- (r_7_16.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_18) at (172mm,270mm) {};
-\draw[->,very thick,color=red] (s_8_18.center) -- (r_8_18.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_20) at (172mm,300mm) {};
-\draw[->,very thick,color=red] (s_9_20.center) -- (r_9_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_8_17) at (172mm,255mm) {};
-\draw[->,very thick,color=red] (s_8_17.center) -- (r_8_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_10_21) at (172mm,315mm) {};
-\draw[->,very thick,color=red] (s_10_21.center) -- (r_10_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_7_15) at (182mm,225mm) {};
-\draw[->,very thick,color=red] (s_7_15.center) -- (r_7_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_9_19) at (182mm,285mm) {};
-\draw[->,very thick,color=red] (s_9_19.center) -- (r_9_19.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node (core_16_label) at (0mm,80mm) {core 16};
+\node (core_17_label) at (0mm,85mm) {core 17};
+\node (core_18_label) at (0mm,90mm) {core 18};
+\node (core_19_label) at (0mm,95mm) {core 19};
+\node (core_20_label) at (0mm,100mm) {core 20};
+\node (core_21_label) at (0mm,105mm) {core 21};
+\node (core_22_label) at (0mm,110mm) {core 22};
+\node (core_23_label) at (0mm,115mm) {core 23};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (24mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (24mm,10mm) {};
+\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_2_5) at (28mm,10mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_2_6) at (32mm,10mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (28mm,5mm) {};
+\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_1_4) at (32mm,5mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_1_3) at (36mm,5mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_2_5) at (32mm,25mm) {};
+\draw[->] ($(s_2_5.east)-(1mm,0mm)$) -- ($(r_2_5.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_5_11) at (36mm,25mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_5_12) at (40mm,25mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_1_4) at (36mm,20mm) {};
+\draw[->] ($(s_1_4.east)-(1mm,0mm)$) -- ($(r_1_4.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_10) at (40mm,20mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_9) at (44mm,20mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_2_6) at (40mm,30mm) {};
+\draw[->,semithick,color=red] ($(s_2_6.east)-(1mm,0mm)$) -- ($(r_2_6.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_14) at (44mm,30mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_13) at (48mm,30mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_1_3) at (40mm,15mm) {};
+\draw[->] ($(s_1_3.east)-(1mm,0mm)$) -- ($(r_1_3.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_8) at (44mm,15mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_7) at (48mm,15mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_5_11) at (44mm,55mm) {};
+\draw[->,semithick,color=red] ($(s_5_11.east)-(1mm,0mm)$) -- ($(r_5_11.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_11_23) at (48mm,55mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_10) at (48mm,50mm) {};
+\draw[->,semithick,color=red] ($(s_4_10.east)-(1mm,0mm)$) -- ($(r_4_10.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_10_22) at (52mm,50mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_10_21) at (56mm,50mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_14) at (52mm,70mm) {};
+\draw[->,semithick,color=red] ($(s_6_14.east)-(1mm,0mm)$) -- ($(r_6_14.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_9) at (52mm,45mm) {};
+\draw[->,semithick,color=red] ($(s_4_9.east)-(1mm,0mm)$) -- ($(r_4_9.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_9_20) at (56mm,45mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_9_19) at (60mm,45mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_5_12) at (52mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_5_12.east)-(1mm,0mm)$) -- ($(r_5_12.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_8) at (52mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_3_8.east)-(1mm,0mm)$) -- ($(r_3_8.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_18) at (56mm,40mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_17) at (60mm,40mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_13) at (56mm,65mm) {};
+\draw[->,semithick,color=red] ($(s_6_13.east)-(1mm,0mm)$) -- ($(r_6_13.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_7) at (56mm,35mm) {};
+\draw[->,semithick,color=red] ($(s_3_7.east)-(1mm,0mm)$) -- ($(r_3_7.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_7_16) at (60mm,35mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_7_15) at (64mm,35mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_11_23) at (60mm,115mm) {};
+\draw[->,semithick,color=red] ($(s_11_23.east)-(1mm,0mm)$) -- ($(r_11_23.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_10_22) at (64mm,110mm) {};
+\draw[->,semithick,color=red] ($(s_10_22.east)-(1mm,0mm)$) -- ($(r_10_22.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_7_16) at (68mm,80mm) {};
+\draw[->,semithick,color=red] ($(s_7_16.east)-(1mm,0mm)$) -- ($(r_7_16.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_18) at (68mm,90mm) {};
+\draw[->,semithick,color=red] ($(s_8_18.east)-(1mm,0mm)$) -- ($(r_8_18.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_10_21) at (68mm,105mm) {};
+\draw[->,semithick,color=red] ($(s_10_21.east)-(1mm,0mm)$) -- ($(r_10_21.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_17) at (68mm,85mm) {};
+\draw[->,semithick,color=red] ($(s_8_17.east)-(1mm,0mm)$) -- ($(r_8_17.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_9_20) at (68mm,100mm) {};
+\draw[->,semithick,color=red] ($(s_9_20.east)-(1mm,0mm)$) -- ($(r_9_20.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_7_15) at (72mm,75mm) {};
+\draw[->,semithick,color=red] ($(s_7_15.east)-(1mm,0mm)$) -- ($(r_7_15.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_9_19) at (72mm,95mm) {};
+\draw[->,semithick,color=red] ($(s_9_19.east)-(1mm,0mm)$) -- ($(r_9_19.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_2) (s_0_1) (r_0_2) (s_2_5) (s_2_6) (r_0_1) (s_1_4) (s_1_3) (r_2_5) (s_5_11) (s_5_12) (r_1_4) (s_4_10) (s_4_9) (r_2_6) (s_6_14) (s_6_13) (r_1_3) (s_3_8) (s_3_7) (r_5_11) (s_11_23) (r_4_10) (s_10_22) (s_10_21) (r_6_14) (r_5_12) (r_4_9) (s_9_20) (s_9_19) (r_3_8) (s_8_18) (s_8_17) (r_6_13) (r_3_7) (s_7_16) (s_7_15) (r_11_23) (r_10_22) (r_8_17) (r_9_20) (r_8_18) (r_7_16) (r_10_21) (r_9_19) (r_7_15) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_2) (s_0_1) (r_0_2) (s_2_5) (s_2_6) (r_0_1) (s_1_4) (s_1_3) (r_2_5) (s_5_11) (s_5_12) (r_1_4) (s_4_10) (s_4_9) (r_2_6) (s_6_14) (s_6_13) (r_1_3) (s_3_8) (s_3_7) (r_5_11) (s_11_23) (r_4_10) (s_10_22) (s_10_21) (r_6_14) (r_4_9) (s_9_20) (s_9_19) (r_5_12) (r_3_8) (s_8_18) (s_8_17) (r_6_13) (r_3_7) (s_7_16) (s_7_15) (r_11_23) (r_10_22) (r_7_16) (r_8_18) (r_10_21) (r_8_17) (r_9_20) (r_7_15) (r_9_19)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_2) (s_0_1) (r_0_2) (s_2_5) (s_2_6) (r_0_1) (s_1_4) (s_1_3) (r_2_5) (s_5_11) (s_5_12) (r_1_4) (s_4_10) (s_4_9) (r_2_6) (s_6_14) (s_6_13) (r_1_3) (s_3_8) (s_3_7) (r_5_11) (s_11_23) (r_4_10) (s_10_22) (s_10_21) (r_6_14) (r_5_12) (r_4_9) (s_9_20) (s_9_19) (r_3_8) (s_8_18) (s_8_17) (r_6_13) (r_3_7) (s_7_16) (s_7_15) (r_11_23) (r_10_22) (r_8_17) (r_9_20) (r_8_18) (r_7_16) (r_10_21) (r_9_19) (r_7_15) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_2) (s_0_1) (r_0_2) (s_2_5) (s_2_6) (r_0_1) (s_1_4) (s_1_3) (r_2_5) (s_5_11) (s_5_12) (r_1_4) (s_4_10) (s_4_9) (r_2_6) (s_6_14) (s_6_13) (r_1_3) (s_3_8) (s_3_7) (r_5_11) (s_11_23) (r_4_10) (s_10_22) (s_10_21) (r_6_14) (r_4_9) (s_9_20) (s_9_19) (r_5_12) (r_3_8) (s_8_18) (s_8_17) (r_6_13) (r_3_7) (s_7_16) (s_7_15) (r_11_23) (r_10_22) (r_7_16) (r_8_18) (r_10_21) (r_8_17) (r_9_20) (r_7_15) (r_9_19),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_16) at (\x1,80mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_17) at (\x1,85mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_18) at (\x1,90mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_19) at (\x1,95mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_20) at (\x1,100mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_21) at (\x1,105mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_22) at (\x1,110mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_23) at (\x1,115mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (s_0_2) (s_0_1) (r_0_2) (s_2_5) (s_2_6) (r_0_1) (s_1_4) (s_1_3) (r_2_5) (s_5_11) (s_5_12) (r_1_4) (s_4_10) (s_4_9) (r_1_3) (s_3_8) (s_3_7) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (s_0_2) (s_0_1) (r_0_2) (s_2_5) (s_2_6) (r_0_1) (s_1_4) (s_1_3) (r_2_5) (s_5_11) (s_5_12) (r_1_4) (s_4_10) (s_4_9) (r_1_3) (s_3_8) (s_3_7) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_2_6) (s_6_14) (s_6_13) (r_5_11) (s_11_23) (r_4_10) (s_10_22) (s_10_21) (r_4_9) (s_9_20) (s_9_19) (r_3_8) (s_8_18) (s_8_17) (r_3_7) (s_7_16) (s_7_15) (numa_axis_6.west) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_2_6) (s_6_14) (s_6_13) (r_5_11) (s_11_23) (r_4_10) (s_10_22) (s_10_21) (r_4_9) (s_9_20) (s_9_19) (r_3_8) (s_8_18) (s_8_17) (r_3_7) (s_7_16) (s_7_15) (numa_axis_6.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (r_6_14) (r_5_12) (r_6_13) (r_8_17) (r_7_16) (r_7_15) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (r_6_14) (r_5_12) (r_6_13) (r_7_16) (r_8_17) (r_7_15) (numa_axis_12.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_11_23) (r_10_22) (r_9_20) (r_8_18) (r_10_21) (r_9_19) (numa_axis_18.west) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_11_23) (r_10_22) (r_8_18) (r_10_21) (r_9_20) (r_9_19) (numa_axis_18.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,80mm) -- (\x2,80mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,85mm) -- (\x2,85mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,90mm) -- (\x2,90mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,95mm) -- (\x2,95mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,100mm) -- (\x2,100mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,105mm) -- (\x2,105mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,110mm) -- (\x2,110mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,115mm) -- (\x2,115mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: ziger, topology: binarytree};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_ziger_cluster.tex
New visualization applied to all combinations of machines and topologies except for rings

@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=red!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=red!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=green!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=green!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=green!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=green!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=blue!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=blue!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=blue!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=blue!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=blue!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=blue!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=orange!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=orange!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=orange!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=orange!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=orange!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=orange!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\node at (0mm,360mm) {Machine: ziger, topology: cluster};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (90mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (100mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (110mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (70mm,270mm) {};
-\draw[->,very thick,color=red] (s_0_18.center) -- (r_0_18.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_18_6) at (80mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_23) at (90mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_22) at (100mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_21) at (110mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_20) at (120mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_19) at (130mm,270mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (81mm,75mm) {};
-\draw[->] (s_0_5.center) -- (r_0_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (90mm,180mm) {};
-\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_17) at (100mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_16) at (110mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (120mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (130mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (91mm,60mm) {};
-\draw[->] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (101mm,45mm) {};
-\draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_23) at (101mm,345mm) {};
-\draw[->] (s_18_23.center) -- (r_18_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_6) at (110mm,90mm) {};
-\draw[->,very thick,color=red] (s_18_6.center) -- (r_18_6.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_6_11) at (120mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_10) at (130mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_9) at (140mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_8) at (150mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_7) at (160mm,90mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_17) at (111mm,255mm) {};
-\draw[->] (s_12_17.center) -- (r_12_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (111mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_22) at (111mm,330mm) {};
-\draw[->] (s_18_22.center) -- (r_18_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_16) at (121mm,240mm) {};
-\draw[->] (s_12_16.center) -- (r_12_16.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (121mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_21) at (121mm,315mm) {};
-\draw[->] (s_18_21.center) -- (r_18_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_11) at (131mm,165mm) {};
-\draw[->] (s_6_11.center) -- (r_6_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_20) at (131mm,300mm) {};
-\draw[->] (s_18_20.center) -- (r_18_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (131mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_19) at (141mm,285mm) {};
-\draw[->] (s_18_19.center) -- (r_18_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (141mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_10) at (141mm,150mm) {};
-\draw[->] (s_6_10.center) -- (r_6_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_9) at (151mm,135mm) {};
-\draw[->] (s_6_9.center) -- (r_6_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_8) at (161mm,120mm) {};
-\draw[->] (s_6_8.center) -- (r_6_8.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_7) at (171mm,105mm) {};
-\draw[->] (s_6_7.center) -- (r_6_7.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node (core_16_label) at (0mm,80mm) {core 16};
+\node (core_17_label) at (0mm,85mm) {core 17};
+\node (core_18_label) at (0mm,90mm) {core 18};
+\node (core_19_label) at (0mm,95mm) {core 19};
+\node (core_20_label) at (0mm,100mm) {core 20};
+\node (core_21_label) at (0mm,105mm) {core 21};
+\node (core_22_label) at (0mm,110mm) {core 22};
+\node (core_23_label) at (0mm,115mm) {core 23};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_18) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_12) at (24mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_5) at (28mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_4) at (32mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_3) at (36mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (40mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (44mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_18) at (28mm,90mm) {};
+\draw[->,semithick,color=red] ($(s_0_18.east)-(1mm,0mm)$) -- ($(r_0_18.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_6) at (32mm,90mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_23) at (36mm,90mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_22) at (40mm,90mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_21) at (44mm,90mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_20) at (48mm,90mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_19) at (52mm,90mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_5) at (32mm,25mm) {};
+\draw[->] ($(s_0_5.east)-(1mm,0mm)$) -- ($(r_0_5.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_12) at (36mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_0_12.east)-(1mm,0mm)$) -- ($(r_0_12.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_17) at (40mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_16) at (44mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_15) at (48mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_14) at (52mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_13) at (56mm,60mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_4) at (36mm,20mm) {};
+\draw[->] ($(s_0_4.east)-(1mm,0mm)$) -- ($(r_0_4.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_23) at (40mm,115mm) {};
+\draw[->] ($(s_18_23.east)-(1mm,0mm)$) -- ($(r_18_23.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_3) at (40mm,15mm) {};
+\draw[->] ($(s_0_3.east)-(1mm,0mm)$) -- ($(r_0_3.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_6) at (44mm,30mm) {};
+\draw[->,semithick,color=red] ($(s_18_6.east)-(1mm,0mm)$) -- ($(r_18_6.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_11) at (48mm,30mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_10) at (52mm,30mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_9) at (56mm,30mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_8) at (60mm,30mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_7) at (64mm,30mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_22) at (44mm,110mm) {};
+\draw[->] ($(s_18_22.east)-(1mm,0mm)$) -- ($(r_18_22.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_17) at (44mm,85mm) {};
+\draw[->] ($(s_12_17.east)-(1mm,0mm)$) -- ($(r_12_17.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (44mm,10mm) {};
+\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (48mm,5mm) {};
+\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_16) at (48mm,80mm) {};
+\draw[->] ($(s_12_16.east)-(1mm,0mm)$) -- ($(r_12_16.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_21) at (48mm,105mm) {};
+\draw[->] ($(s_18_21.east)-(1mm,0mm)$) -- ($(r_18_21.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_15) at (52mm,75mm) {};
+\draw[->] ($(s_12_15.east)-(1mm,0mm)$) -- ($(r_12_15.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_11) at (52mm,55mm) {};
+\draw[->] ($(s_6_11.east)-(1mm,0mm)$) -- ($(r_6_11.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_20) at (52mm,100mm) {};
+\draw[->] ($(s_18_20.east)-(1mm,0mm)$) -- ($(r_18_20.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_10) at (56mm,50mm) {};
+\draw[->] ($(s_6_10.east)-(1mm,0mm)$) -- ($(r_6_10.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_14) at (56mm,70mm) {};
+\draw[->] ($(s_12_14.east)-(1mm,0mm)$) -- ($(r_12_14.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_19) at (56mm,95mm) {};
+\draw[->] ($(s_18_19.east)-(1mm,0mm)$) -- ($(r_18_19.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_9) at (60mm,45mm) {};
+\draw[->] ($(s_6_9.east)-(1mm,0mm)$) -- ($(r_6_9.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_13) at (60mm,65mm) {};
+\draw[->] ($(s_12_13.east)-(1mm,0mm)$) -- ($(r_12_13.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_8) at (64mm,40mm) {};
+\draw[->] ($(s_6_8.east)-(1mm,0mm)$) -- ($(r_6_8.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_7) at (68mm,35mm) {};
+\draw[->] ($(s_6_7.east)-(1mm,0mm)$) -- ($(r_6_7.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_18) (s_0_12) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_18) (s_18_6) (s_18_23) (s_18_22) (s_18_21) (s_18_20) (s_18_19) (r_0_5) (r_0_12) (s_12_17) (s_12_16) (s_12_15) (s_12_14) (s_12_13) (r_0_4) (r_0_3) (r_18_23) (r_18_6) (s_6_11) (s_6_10) (s_6_9) (s_6_8) (s_6_7) (r_0_2) (r_18_22) (r_12_17) (r_0_1) (r_18_21) (r_12_16) (r_6_11) (r_18_20) (r_12_15) (r_6_10) (r_18_19) (r_12_14) (r_6_9) (r_12_13) (r_6_8) (r_6_7) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_18) (s_0_12) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_18) (s_18_6) (s_18_23) (s_18_22) (s_18_21) (s_18_20) (s_18_19) (r_0_5) (r_0_12) (s_12_17) (s_12_16) (s_12_15) (s_12_14) (s_12_13) (r_0_4) (r_18_23) (r_0_3) (r_18_6) (s_6_11) (s_6_10) (s_6_9) (s_6_8) (s_6_7) (r_18_22) (r_12_17) (r_0_2) (r_0_1) (r_12_16) (r_18_21) (r_12_15) (r_6_11) (r_18_20) (r_6_10) (r_12_14) (r_18_19) (r_6_9) (r_12_13) (r_6_8) (r_6_7)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_18) (s_0_12) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_18) (s_18_6) (s_18_23) (s_18_22) (s_18_21) (s_18_20) (s_18_19) (r_0_5) (r_0_12) (s_12_17) (s_12_16) (s_12_15) (s_12_14) (s_12_13) (r_0_4) (r_0_3) (r_18_23) (r_18_6) (s_6_11) (s_6_10) (s_6_9) (s_6_8) (s_6_7) (r_0_2) (r_18_22) (r_12_17) (r_0_1) (r_18_21) (r_12_16) (r_6_11) (r_18_20) (r_12_15) (r_6_10) (r_18_19) (r_12_14) (r_6_9) (r_12_13) (r_6_8) (r_6_7) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_18) (s_0_12) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_18) (s_18_6) (s_18_23) (s_18_22) (s_18_21) (s_18_20) (s_18_19) (r_0_5) (r_0_12) (s_12_17) (s_12_16) (s_12_15) (s_12_14) (s_12_13) (r_0_4) (r_18_23) (r_0_3) (r_18_6) (s_6_11) (s_6_10) (s_6_9) (s_6_8) (s_6_7) (r_18_22) (r_12_17) (r_0_2) (r_0_1) (r_12_16) (r_18_21) (r_12_15) (r_6_11) (r_18_20) (r_6_10) (r_12_14) (r_18_19) (r_6_9) (r_12_13) (r_6_8) (r_6_7),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_16) at (\x1,80mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_17) at (\x1,85mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_18) at (\x1,90mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_19) at (\x1,95mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_20) at (\x1,100mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_21) at (\x1,105mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_22) at (\x1,110mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_23) at (\x1,115mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (s_0_18) (s_0_12) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (s_0_18) (s_0_12) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_18_6) (s_6_11) (s_6_10) (s_6_9) (s_6_8) (s_6_7) (r_6_11) (r_6_10) (r_6_9) (r_6_8) (r_6_7) (numa_axis_6.west) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_18_6) (s_6_11) (s_6_10) (s_6_9) (s_6_8) (s_6_7) (r_6_11) (r_6_10) (r_6_9) (r_6_8) (r_6_7) (numa_axis_6.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (r_0_12) (s_12_17) (s_12_16) (s_12_15) (s_12_14) (s_12_13) (r_12_17) (r_12_16) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (r_0_12) (s_12_17) (s_12_16) (s_12_15) (s_12_14) (s_12_13) (r_12_17) (r_12_16) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_0_18) (s_18_6) (s_18_23) (s_18_22) (s_18_21) (s_18_20) (s_18_19) (r_18_23) (r_18_22) (r_18_21) (r_18_20) (r_18_19) (numa_axis_18.west) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_0_18) (s_18_6) (s_18_23) (s_18_22) (s_18_21) (s_18_20) (s_18_19) (r_18_23) (r_18_22) (r_18_21) (r_18_20) (r_18_19) (numa_axis_18.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,80mm) -- (\x2,80mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,85mm) -- (\x2,85mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,90mm) -- (\x2,90mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,95mm) -- (\x2,95mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,100mm) -- (\x2,100mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,105mm) -- (\x2,105mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,110mm) -- (\x2,110mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,115mm) -- (\x2,115mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: ziger, topology: cluster};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_ziger_mst.tex
New visualization applied to all combinations of machines and topologies except for rings

@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=red!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=red!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=green!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=green!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=green!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=green!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=blue!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=blue!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=blue!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=blue!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=blue!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=blue!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=orange!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=orange!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=orange!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=orange!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=orange!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=orange!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\node at (0mm,360mm) {Machine: ziger, topology: mst};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_6) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (90mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (100mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (110mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_6) at (70mm,90mm) {};
-\draw[->,very thick,color=red] (s_0_6.center) -- (r_0_6.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_6_12) at (80mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_11) at (90mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_10) at (100mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_9) at (110mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_8) at (120mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_7) at (130mm,90mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (80mm,270mm) {};
-\draw[->,very thick,color=red] (s_0_18.center) -- (r_0_18.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_18_23) at (90mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_22) at (100mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_21) at (110mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_20) at (120mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_19) at (130mm,270mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (81mm,75mm) {};
-\draw[->] (s_0_5.center) -- (r_0_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (91mm,60mm) {};
-\draw[->] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_12) at (100mm,180mm) {};
-\draw[->,very thick,color=red] (s_6_12.center) -- (r_6_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_17) at (110mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_16) at (120mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (130mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (140mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (150mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_11) at (101mm,165mm) {};
-\draw[->] (s_6_11.center) -- (r_6_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (101mm,45mm) {};
-\draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_23) at (101mm,345mm) {};
-\draw[->] (s_18_23.center) -- (r_18_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (111mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_22) at (111mm,330mm) {};
-\draw[->] (s_18_22.center) -- (r_18_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_10) at (111mm,150mm) {};
-\draw[->] (s_6_10.center) -- (r_6_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_9) at (121mm,135mm) {};
-\draw[->] (s_6_9.center) -- (r_6_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (121mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_17) at (121mm,255mm) {};
-\draw[->] (s_12_17.center) -- (r_12_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_21) at (121mm,315mm) {};
-\draw[->] (s_18_21.center) -- (r_18_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_8) at (131mm,120mm) {};
-\draw[->] (s_6_8.center) -- (r_6_8.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_16) at (131mm,240mm) {};
-\draw[->] (s_12_16.center) -- (r_12_16.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_20) at (131mm,300mm) {};
-\draw[->] (s_18_20.center) -- (r_18_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_7) at (141mm,105mm) {};
-\draw[->] (s_6_7.center) -- (r_6_7.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_19) at (141mm,285mm) {};
-\draw[->] (s_18_19.center) -- (r_18_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (141mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (151mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (161mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node (core_16_label) at (0mm,80mm) {core 16};
+\node (core_17_label) at (0mm,85mm) {core 17};
+\node (core_18_label) at (0mm,90mm) {core 18};
+\node (core_19_label) at (0mm,95mm) {core 19};
+\node (core_20_label) at (0mm,100mm) {core 20};
+\node (core_21_label) at (0mm,105mm) {core 21};
+\node (core_22_label) at (0mm,110mm) {core 22};
+\node (core_23_label) at (0mm,115mm) {core 23};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_6) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_18) at (24mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_5) at (28mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_4) at (32mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_3) at (36mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (40mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (44mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_6) at (28mm,30mm) {};
+\draw[->,semithick,color=red] ($(s_0_6.east)-(1mm,0mm)$) -- ($(r_0_6.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_12) at (32mm,30mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_11) at (36mm,30mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_10) at (40mm,30mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_9) at (44mm,30mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_8) at (48mm,30mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_6_7) at (52mm,30mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_18) at (32mm,90mm) {};
+\draw[->,semithick,color=red] ($(s_0_18.east)-(1mm,0mm)$) -- ($(r_0_18.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_23) at (36mm,90mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_22) at (40mm,90mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_21) at (44mm,90mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_20) at (48mm,90mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_19) at (52mm,90mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_5) at (32mm,25mm) {};
+\draw[->] ($(s_0_5.east)-(1mm,0mm)$) -- ($(r_0_5.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_4) at (36mm,20mm) {};
+\draw[->] ($(s_0_4.east)-(1mm,0mm)$) -- ($(r_0_4.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_12) at (40mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_6_12.east)-(1mm,0mm)$) -- ($(r_6_12.west)+(1mm,0mm)$); 
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_17) at (44mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_16) at (48mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_15) at (52mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_14) at (56mm,60mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_12_13) at (60mm,60mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_11) at (40mm,55mm) {};
+\draw[->] ($(s_6_11.east)-(1mm,0mm)$) -- ($(r_6_11.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_3) at (40mm,15mm) {};
+\draw[->] ($(s_0_3.east)-(1mm,0mm)$) -- ($(r_0_3.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_23) at (40mm,115mm) {};
+\draw[->] ($(s_18_23.east)-(1mm,0mm)$) -- ($(r_18_23.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (44mm,10mm) {};
+\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_22) at (44mm,110mm) {};
+\draw[->] ($(s_18_22.east)-(1mm,0mm)$) -- ($(r_18_22.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_10) at (44mm,50mm) {};
+\draw[->] ($(s_6_10.east)-(1mm,0mm)$) -- ($(r_6_10.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_9) at (48mm,45mm) {};
+\draw[->] ($(s_6_9.east)-(1mm,0mm)$) -- ($(r_6_9.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (48mm,5mm) {};
+\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_17) at (48mm,85mm) {};
+\draw[->] ($(s_12_17.east)-(1mm,0mm)$) -- ($(r_12_17.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_21) at (48mm,105mm) {};
+\draw[->] ($(s_18_21.east)-(1mm,0mm)$) -- ($(r_18_21.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_8) at (52mm,40mm) {};
+\draw[->] ($(s_6_8.east)-(1mm,0mm)$) -- ($(r_6_8.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_20) at (52mm,100mm) {};
+\draw[->] ($(s_18_20.east)-(1mm,0mm)$) -- ($(r_18_20.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_16) at (52mm,80mm) {};
+\draw[->] ($(s_12_16.east)-(1mm,0mm)$) -- ($(r_12_16.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_6_7) at (56mm,35mm) {};
+\draw[->] ($(s_6_7.east)-(1mm,0mm)$) -- ($(r_6_7.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_15) at (56mm,75mm) {};
+\draw[->] ($(s_12_15.east)-(1mm,0mm)$) -- ($(r_12_15.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_19) at (56mm,95mm) {};
+\draw[->] ($(s_18_19.east)-(1mm,0mm)$) -- ($(r_18_19.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_14) at (60mm,70mm) {};
+\draw[->] ($(s_12_14.east)-(1mm,0mm)$) -- ($(r_12_14.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_12_13) at (64mm,65mm) {};
+\draw[->] ($(s_12_13.east)-(1mm,0mm)$) -- ($(r_12_13.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_6) (s_0_18) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_6) (s_6_12) (s_6_11) (s_6_10) (s_6_9) (s_6_8) (s_6_7) (r_0_18) (s_18_23) (s_18_22) (s_18_21) (s_18_20) (s_18_19) (r_0_5) (r_0_4) (r_6_12) (s_12_17) (s_12_16) (s_12_15) (s_12_14) (s_12_13) (r_6_11) (r_0_3) (r_18_23) (r_0_2) (r_6_10) (r_18_22) (r_0_1) (r_12_17) (r_6_9) (r_18_21) (r_6_8) (r_18_20) (r_12_16) (r_6_7) (r_18_19) (r_12_15) (r_12_14) (r_12_13) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_6) (s_0_18) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_6) (s_6_12) (s_6_11) (s_6_10) (s_6_9) (s_6_8) (s_6_7) (r_0_18) (s_18_23) (s_18_22) (s_18_21) (s_18_20) (s_18_19) (r_0_5) (r_0_4) (r_6_12) (s_12_17) (s_12_16) (s_12_15) (s_12_14) (s_12_13) (r_6_11) (r_0_3) (r_18_23) (r_0_2) (r_18_22) (r_6_10) (r_6_9) (r_0_1) (r_12_17) (r_18_21) (r_6_8) (r_18_20) (r_12_16) (r_6_7) (r_12_15) (r_18_19) (r_12_14) (r_12_13)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_6) (s_0_18) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_6) (s_6_12) (s_6_11) (s_6_10) (s_6_9) (s_6_8) (s_6_7) (r_0_18) (s_18_23) (s_18_22) (s_18_21) (s_18_20) (s_18_19) (r_0_5) (r_0_4) (r_6_12) (s_12_17) (s_12_16) (s_12_15) (s_12_14) (s_12_13) (r_6_11) (r_0_3) (r_18_23) (r_0_2) (r_6_10) (r_18_22) (r_0_1) (r_12_17) (r_6_9) (r_18_21) (r_6_8) (r_18_20) (r_12_16) (r_6_7) (r_18_19) (r_12_15) (r_12_14) (r_12_13) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_6) (s_0_18) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_6) (s_6_12) (s_6_11) (s_6_10) (s_6_9) (s_6_8) (s_6_7) (r_0_18) (s_18_23) (s_18_22) (s_18_21) (s_18_20) (s_18_19) (r_0_5) (r_0_4) (r_6_12) (s_12_17) (s_12_16) (s_12_15) (s_12_14) (s_12_13) (r_6_11) (r_0_3) (r_18_23) (r_0_2) (r_18_22) (r_6_10) (r_6_9) (r_0_1) (r_12_17) (r_18_21) (r_6_8) (r_18_20) (r_12_16) (r_6_7) (r_12_15) (r_18_19) (r_12_14) (r_12_13),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_16) at (\x1,80mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_17) at (\x1,85mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_18) at (\x1,90mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_19) at (\x1,95mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_20) at (\x1,100mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_21) at (\x1,105mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_22) at (\x1,110mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_23) at (\x1,115mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (s_0_6) (s_0_18) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (s_0_6) (s_0_18) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_6) (s_6_12) (s_6_11) (s_6_10) (s_6_9) (s_6_8) (s_6_7) (r_6_11) (r_6_10) (r_6_9) (r_6_8) (r_6_7) (numa_axis_6.west) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_6) (s_6_12) (s_6_11) (s_6_10) (s_6_9) (s_6_8) (s_6_7) (r_6_11) (r_6_10) (r_6_9) (r_6_8) (r_6_7) (numa_axis_6.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (r_6_12) (s_12_17) (s_12_16) (s_12_15) (s_12_14) (s_12_13) (r_12_17) (r_12_16) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (r_6_12) (s_12_17) (s_12_16) (s_12_15) (s_12_14) (s_12_13) (r_12_17) (r_12_16) (r_12_15) (r_12_14) (r_12_13) (numa_axis_12.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_0_18) (s_18_23) (s_18_22) (s_18_21) (s_18_20) (s_18_19) (r_18_23) (r_18_22) (r_18_21) (r_18_20) (r_18_19) (numa_axis_18.west) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_0_18) (s_18_23) (s_18_22) (s_18_21) (s_18_20) (s_18_19) (r_18_23) (r_18_22) (r_18_21) (r_18_20) (r_18_19) (numa_axis_18.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,80mm) -- (\x2,80mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,85mm) -- (\x2,85mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,90mm) -- (\x2,90mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,95mm) -- (\x2,95mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,100mm) -- (\x2,100mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,105mm) -- (\x2,105mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,110mm) -- (\x2,110mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,115mm) -- (\x2,115mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: ziger, topology: mst};
+\end{pgfonlayer}

### 2013-06-07 graphs/visu_ziger_sequential.tex
New visualization applied to all combinations of machines and topologies except for rings

--- 2013-06-04 graphs/visu_ziger_cluster.tex
@@
-\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
-\node at (0mm,0mm) {core 00};
-\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
-\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
-\node at (0mm,15mm) {core 01};
-\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
-\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
-\node at (0mm,30mm) {core 02};
-\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
-\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
-\node at (0mm,45mm) {core 03};
-\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
-\draw[fill,color=red!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
-\node at (0mm,60mm) {core 04};
-\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
-\draw[fill,color=red!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
-\node at (0mm,75mm) {core 05};
-\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
-\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
-\node at (0mm,90mm) {core 06};
-\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
-\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
-\node at (0mm,105mm) {core 07};
-\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
-\draw[fill,color=green!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
-\node at (0mm,120mm) {core 08};
-\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
-\draw[fill,color=green!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
-\node at (0mm,135mm) {core 09};
-\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
-\draw[fill,color=green!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
-\node at (0mm,150mm) {core 10};
-\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
-\draw[fill,color=green!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
-\node at (0mm,165mm) {core 11};
-\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
-\draw[fill,color=blue!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
-\node at (0mm,180mm) {core 12};
-\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
-\draw[fill,color=blue!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
-\node at (0mm,195mm) {core 13};
-\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
-\draw[fill,color=blue!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
-\node at (0mm,210mm) {core 14};
-\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
-\draw[fill,color=blue!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
-\node at (0mm,225mm) {core 15};
-\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
-\draw[fill,color=blue!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
-\node at (0mm,240mm) {core 16};
-\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
-\draw[fill,color=blue!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
-\node at (0mm,255mm) {core 17};
-\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
-\draw[fill,color=orange!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
-\node at (0mm,270mm) {core 18};
-\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
-\draw[fill,color=orange!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
-\node at (0mm,285mm) {core 19};
-\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
-\draw[fill,color=orange!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
-\node at (0mm,300mm) {core 20};
-\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
-\draw[fill,color=orange!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
-\node at (0mm,315mm) {core 21};
-\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
-\draw[fill,color=orange!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
-\node at (0mm,330mm) {core 22};
-\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
-\draw[fill,color=orange!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
-\node at (0mm,345mm) {core 23};
-\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
-\node at (0mm,360mm) {Machine: ziger, topology: cluster};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_18) at (50mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_12) at (60mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_5) at (70mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_4) at (80mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_3) at (90mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_2) at (100mm,0mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_0_1) at (110mm,0mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_18) at (70mm,270mm) {};
-\draw[->,very thick,color=red] (s_0_18.center) -- (r_0_18.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_18_6) at (80mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_23) at (90mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_22) at (100mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_21) at (110mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_20) at (120mm,270mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_18_19) at (130mm,270mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_5) at (81mm,75mm) {};
-\draw[->] (s_0_5.center) -- (r_0_5.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_12) at (90mm,180mm) {};
-\draw[->,very thick,color=red] (s_0_12.center) -- (r_0_12.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_12_17) at (100mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_16) at (110mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_15) at (120mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_14) at (130mm,180mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_12_13) at (140mm,180mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_4) at (91mm,60mm) {};
-\draw[->] (s_0_4.center) -- (r_0_4.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_3) at (101mm,45mm) {};
-\draw[->] (s_0_3.center) -- (r_0_3.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_23) at (101mm,345mm) {};
-\draw[->] (s_18_23.center) -- (r_18_23.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_6) at (110mm,90mm) {};
-\draw[->,very thick,color=red] (s_18_6.center) -- (r_18_6.center); 
-\node[draw,fill=red!20,minimum size=10mm] (s_6_11) at (120mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_10) at (130mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_9) at (140mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_8) at (150mm,90mm) {};
-\node[draw,fill=red!20,minimum size=10mm] (s_6_7) at (160mm,90mm) {};
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_17) at (111mm,255mm) {};
-\draw[->] (s_12_17.center) -- (r_12_17.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_2) at (111mm,30mm) {};
-\draw[->] (s_0_2.center) -- (r_0_2.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_22) at (111mm,330mm) {};
-\draw[->] (s_18_22.center) -- (r_18_22.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_16) at (121mm,240mm) {};
-\draw[->] (s_12_16.center) -- (r_12_16.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_0_1) at (121mm,15mm) {};
-\draw[->] (s_0_1.center) -- (r_0_1.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_21) at (121mm,315mm) {};
-\draw[->] (s_18_21.center) -- (r_18_21.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_11) at (131mm,165mm) {};
-\draw[->] (s_6_11.center) -- (r_6_11.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_20) at (131mm,300mm) {};
-\draw[->] (s_18_20.center) -- (r_18_20.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_15) at (131mm,225mm) {};
-\draw[->] (s_12_15.center) -- (r_12_15.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_18_19) at (141mm,285mm) {};
-\draw[->] (s_18_19.center) -- (r_18_19.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_14) at (141mm,210mm) {};
-\draw[->] (s_12_14.center) -- (r_12_14.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_10) at (141mm,150mm) {};
-\draw[->] (s_6_10.center) -- (r_6_10.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_9) at (151mm,135mm) {};
-\draw[->] (s_6_9.center) -- (r_6_9.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_12_13) at (151mm,195mm) {};
-\draw[->] (s_12_13.center) -- (r_12_13.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_8) at (161mm,120mm) {};
-\draw[->] (s_6_8.center) -- (r_6_8.center); 
-\node[draw,fill=blue!20,minimum size=10mm] (r_6_7) at (171mm,105mm) {};
-\draw[->] (s_6_7.center) -- (r_6_7.center);
+\node (core_0_label) at (0mm,0mm) {core 00};
+\node (core_1_label) at (0mm,5mm) {core 01};
+\node (core_2_label) at (0mm,10mm) {core 02};
+\node (core_3_label) at (0mm,15mm) {core 03};
+\node (core_4_label) at (0mm,20mm) {core 04};
+\node (core_5_label) at (0mm,25mm) {core 05};
+\node (core_6_label) at (0mm,30mm) {core 06};
+\node (core_7_label) at (0mm,35mm) {core 07};
+\node (core_8_label) at (0mm,40mm) {core 08};
+\node (core_9_label) at (0mm,45mm) {core 09};
+\node (core_10_label) at (0mm,50mm) {core 10};
+\node (core_11_label) at (0mm,55mm) {core 11};
+\node (core_12_label) at (0mm,60mm) {core 12};
+\node (core_13_label) at (0mm,65mm) {core 13};
+\node (core_14_label) at (0mm,70mm) {core 14};
+\node (core_15_label) at (0mm,75mm) {core 15};
+\node (core_16_label) at (0mm,80mm) {core 16};
+\node (core_17_label) at (0mm,85mm) {core 17};
+\node (core_18_label) at (0mm,90mm) {core 18};
+\node (core_19_label) at (0mm,95mm) {core 19};
+\node (core_20_label) at (0mm,100mm) {core 20};
+\node (core_21_label) at (0mm,105mm) {core 21};
+\node (core_22_label) at (0mm,110mm) {core 22};
+\node (core_23_label) at (0mm,115mm) {core 23};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_17) at (20mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_16) at (24mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_15) at (28mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_14) at (32mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_13) at (36mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_12) at (40mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_23) at (44mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_22) at (48mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_21) at (52mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_20) at (56mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_19) at (60mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_18) at (64mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_11) at (68mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_10) at (72mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_9) at (76mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_8) at (80mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_7) at (84mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_6) at (88mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_5) at (92mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_4) at (96mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_3) at (100mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_2) at (104mm,0mm) {};
+\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_1) at (108mm,0mm) {};
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_17) at (32mm,85mm) {};
+\draw[->,semithick,color=red] ($(s_0_17.east)-(1mm,0mm)$) -- ($(r_0_17.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_16) at (36mm,80mm) {};
+\draw[->,semithick,color=red] ($(s_0_16.east)-(1mm,0mm)$) -- ($(r_0_16.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_15) at (40mm,75mm) {};
+\draw[->,semithick,color=red] ($(s_0_15.east)-(1mm,0mm)$) -- ($(r_0_15.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_14) at (44mm,70mm) {};
+\draw[->,semithick,color=red] ($(s_0_14.east)-(1mm,0mm)$) -- ($(r_0_14.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_13) at (48mm,65mm) {};
+\draw[->,semithick,color=red] ($(s_0_13.east)-(1mm,0mm)$) -- ($(r_0_13.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_23) at (52mm,115mm) {};
+\draw[->,semithick,color=red] ($(s_0_23.east)-(1mm,0mm)$) -- ($(r_0_23.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_12) at (52mm,60mm) {};
+\draw[->,semithick,color=red] ($(s_0_12.east)-(1mm,0mm)$) -- ($(r_0_12.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_22) at (56mm,110mm) {};
+\draw[->,semithick,color=red] ($(s_0_22.east)-(1mm,0mm)$) -- ($(r_0_22.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_21) at (60mm,105mm) {};
+\draw[->,semithick,color=red] ($(s_0_21.east)-(1mm,0mm)$) -- ($(r_0_21.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_20) at (64mm,100mm) {};
+\draw[->,semithick,color=red] ($(s_0_20.east)-(1mm,0mm)$) -- ($(r_0_20.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_19) at (68mm,95mm) {};
+\draw[->,semithick,color=red] ($(s_0_19.east)-(1mm,0mm)$) -- ($(r_0_19.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_18) at (72mm,90mm) {};
+\draw[->,semithick,color=red] ($(s_0_18.east)-(1mm,0mm)$) -- ($(r_0_18.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_11) at (76mm,55mm) {};
+\draw[->,semithick,color=red] ($(s_0_11.east)-(1mm,0mm)$) -- ($(r_0_11.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_10) at (80mm,50mm) {};
+\draw[->,semithick,color=red] ($(s_0_10.east)-(1mm,0mm)$) -- ($(r_0_10.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_9) at (84mm,45mm) {};
+\draw[->,semithick,color=red] ($(s_0_9.east)-(1mm,0mm)$) -- ($(r_0_9.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_8) at (88mm,40mm) {};
+\draw[->,semithick,color=red] ($(s_0_8.east)-(1mm,0mm)$) -- ($(r_0_8.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_7) at (92mm,35mm) {};
+\draw[->,semithick,color=red] ($(s_0_7.east)-(1mm,0mm)$) -- ($(r_0_7.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_6) at (96mm,30mm) {};
+\draw[->,semithick,color=red] ($(s_0_6.east)-(1mm,0mm)$) -- ($(r_0_6.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_5) at (96mm,25mm) {};
+\draw[->] ($(s_0_5.east)-(1mm,0mm)$) -- ($(r_0_5.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_4) at (100mm,20mm) {};
+\draw[->] ($(s_0_4.east)-(1mm,0mm)$) -- ($(r_0_4.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_3) at (104mm,15mm) {};
+\draw[->] ($(s_0_3.east)-(1mm,0mm)$) -- ($(r_0_3.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_2) at (108mm,10mm) {};
+\draw[->] ($(s_0_2.east)-(1mm,0mm)$) -- ($(r_0_2.west)+(1mm,0mm)$); 
+\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_1) at (112mm,5mm) {};
+\draw[->] ($(s_0_1.east)-(1mm,0mm)$) -- ($(r_0_1.west)+(1mm,0mm)$); 
+\begin{pgfonlayer}{background}
+\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_17) (s_0_16) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_23) (s_0_22) (s_0_21) (s_0_20) (s_0_19) (s_0_18) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_17) (r_0_16) (r_0_15) (r_0_14) (r_0_13) (r_0_23) (r_0_12) (r_0_22) (r_0_21) (r_0_20) (r_0_19) (r_0_18) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_17) (s_0_16) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_23) (s_0_22) (s_0_21) (s_0_20) (s_0_19) (s_0_18) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_17) (r_0_16) (r_0_15) (r_0_14) (r_0_13) (r_0_23) (r_0_12) (r_0_22) (r_0_21) (r_0_20) (r_0_19) (r_0_18) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1)] (allobjects) {};
+\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_17) (s_0_16) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_23) (s_0_22) (s_0_21) (s_0_20) (s_0_19) (s_0_18) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_17) (r_0_16) (r_0_15) (r_0_14) (r_0_13) (r_0_23) (r_0_12) (r_0_22) (r_0_21) (r_0_20) (r_0_19) (r_0_18) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_17) (s_0_16) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_23) (s_0_22) (s_0_21) (s_0_20) (s_0_19) (s_0_18) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_17) (r_0_16) (r_0_15) (r_0_14) (r_0_13) (r_0_23) (r_0_12) (r_0_22) (r_0_21) (r_0_20) (r_0_19) (r_0_18) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (r_0_7) (r_0_6) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1),scale=1.1] (bg) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_16) at (\x1,80mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_17) at (\x1,85mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_18) at (\x1,90mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_19) at (\x1,95mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_20) at (\x1,100mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_21) at (\x1,105mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_22) at (\x1,110mm) {};
+\draw let \p1 = (allobjects.east) in node[] (numa_axis_23) at (\x1,115mm) {};
+\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (s_0_17) (s_0_16) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_23) (s_0_22) (s_0_21) (s_0_20) (s_0_19) (s_0_18) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (s_0_17) (s_0_16) (s_0_15) (s_0_14) (s_0_13) (s_0_12) (s_0_23) (s_0_22) (s_0_21) (s_0_20) (s_0_19) (s_0_18) (s_0_11) (s_0_10) (s_0_9) (s_0_8) (s_0_7) (s_0_6) (s_0_5) (s_0_4) (s_0_3) (s_0_2) (s_0_1) (r_0_5) (r_0_4) (r_0_3) (r_0_2) (r_0_1) (numa_axis_0.west),rounded corners] {};
+\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (r_0_7) (r_0_6) (numa_axis_6.west) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_0_11) (r_0_10) (r_0_9) (r_0_8) (r_0_7) (r_0_6) (numa_axis_6.west),rounded corners] {};
+\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (r_0_17) (r_0_16) (r_0_15) (r_0_14) (r_0_13) (r_0_12) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (r_0_17) (r_0_16) (r_0_15) (r_0_14) (r_0_13) (r_0_12) (numa_axis_12.west),rounded corners] {};
+\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_0_23) (r_0_22) (r_0_21) (r_0_20) (r_0_19) (r_0_18) (numa_axis_18.west) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_0_23) (r_0_22) (r_0_21) (r_0_20) (r_0_19) (r_0_18) (numa_axis_18.west),rounded corners] {};
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,80mm) -- (\x2,80mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,85mm) -- (\x2,85mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,90mm) -- (\x2,90mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,95mm) -- (\x2,95mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,100mm) -- (\x2,100mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,105mm) -- (\x2,105mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,110mm) -- (\x2,110mm);
+\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,115mm) -- (\x2,115mm);
+\node[draw=black,anchor=north,fill=black!20] at (bg.north) {Machine: ziger, topology: sequential};
+\end{pgfonlayer}

### 2013-06-07 graphs/model.py

@@ -31,7 +31,11 @@ class Model(object):
         return None
 
     def get_cores_per_node(self):
-        return self.get_num_cores() / self.get_num_numa_nodes()
+        assert self.get_num_numa_nodes() is not None # Should be overriden in childs
+        if self.get_num_numa_nodes()>0:
+            return self.get_num_cores() / self.get_num_numa_nodes()
+        else:
+            return self.get_num_cores()
 
     def get_cost_within_numa(self):
         return 1

### 2013-06-07 graphs/run_simulation.py

@@ -4,6 +4,7 @@ import simulator
 import random
 import string
 import os
+import subprocess
 
 f = open('visall.tex', 'w+')
 
@@ -31,26 +32,38 @@ def figure(content, caption='',
     if not ref.startswith('fig:'):
         ref = 'fig:%s' % ref
     return (
-        '\\begin{figure}[h!]\n'
+        '\\begin{figure}[ht!]\n'
         '%s\n'
         '\\caption{%s}\n'
         '\\label{%s}\n'
         '\\end{figure}\n'
         ) % (content, caption, ref)
 
+def append_to_report():
+    for m in simulator.machines:
+        m = ''.join([i for i in m if not i.isdigit()])
+        w(command('newpage'))
+        w(command('clearpage'))
+        w(section(m))
+        for t in simulator.topologies:
+            tex = 'visu_%s_%s' % (m, t)
+            if os.path.exists(tex + '.tex'):
+                w(section(t, 2))
+                opt = [ 'transform shape' ]
+                w(figure(tikz('\\input{graphs/%s}' % tex, opt), 
+                         'Atomic broadcast on %s using %s topology' % (m, t),
+                         'ab_%s_%s' % (m, t)))
+                w(command('clearpage'))
+
+def run_all_simulations():
+    for m in simulator.machines:
+        for t in simulator.topologies:
+            if t != 'ring' and m != 'appenzeller':
+                res = subprocess.call(['./simulator.py', m, t])
+                assert res == 0
+
 # --------------------------------------------------
 
-for m in simulator.machines:
-    m = ''.join([i for i in m if not i.isdigit()])
-    w(command('newpage'))
-    w(command('clearpage'))
-    w(section(m))
-    for t in simulator.topologies:
-        tex = 'visu_%s_%s' % (m, t)
-        if os.path.exists(tex + '.tex'):
-            w(section(t, 2))
-            opt = [ 'transform shape', 'scale=.25' ]
-            w(figure(tikz('\\input{graphs/%s}' % tex, opt), 
-                     'Atomic broadcast on %s using %s topology' % (m, t),
-                     'ab_%s_%s' % (m, t)))
-            w(command('clearpage'))
+run_all_simulations()
+append_to_report()
+

### 2013-06-07 graphs/simulator.py

@@ -79,6 +79,7 @@ def build_and_simulate():
     """
     Build a tree model and simulate sending a message along it
     """
+    # XXX The arguments are totally broken. Fix them!
     parser = argparse.ArgumentParser(
         description='Simulator for multicore machines')
     parser.add_argument('--evaluate-model', dest="action", action="store_const",
@@ -95,6 +96,8 @@ def build_and_simulate():
     parser.add_argument('overlay', choices=topologies,
                         help="Overlay to use for atomic broadcast")
     args = parser.parse_args()
+
+    print "machine: %s, topology: %s" % (args.machine, args.overlay)
 
     m = arg_machine(args.machine)
     assert m != None

### 2013-06-09 paper.tex
New visualization applied to all combinations of machines and topologies except for rings
Migration to event based send events (rather than sending them sequentially). This is a first step towards building the topology iteratively and adaptively during evaluation. Visualization seems to be broken now, though

@@
 % configuration
-\usetikzlibrary{shapes,positioning,calc,snakes,arrows,shapes}
+\usetikzlibrary{shapes,positioning,calc,snakes,arrows,shapes,fit,backgrounds}
 \pgfplotsset{width=.9\linewidth}
@@
 
-Next, we evaluate ring topologies. Rings have the advantage that the
-implicitly acknowledge messages once they arrive back to the
-sender. This is beneficial for some algorithms such as quorums, where
-nodes report back to the sender. This, however, only works if forwarding
-along the ring is only done after all local nodes acknowledge a
-message.
+Next, we evaluate ring topologies. Rings experience a certain level of
+redundancy. The sending node receives the node back on the ring. This
+is unnecessary for applications with uni-directional traffic executed
+on reliable communication channels
+
+For applications that require some form of feedback (as well as
+unreliable channels, which we do not consider at this point), rings
+have the advantage that they can piggy-back some information that will
+eventually arrive back on the sender. This is beneficial for some
+algorithms such as quorums, where nodes report the result of the
+quorum back to the sender.
 
@@
 To add more parallelism, we add a second ring, which we send the
-message on in parallel. The overlay ring network is visualized in
-Figure~\ref{fig:gruyere_ring}. Node that the link from node 20 to 8 is
-a two hop link and, thus, has a cost of 20 instead of the usual 10.
+message on in parallel. Acknowledgments, however, only work if
+forwarding along the ring is only done after all local nodes (as in
+nodes from the outer rings) acknowledge a message. In
+Figure~\ref{fig:gruyere_ring}, we visualize an example of two
+intertwined ring topologies. Node that the link from node 20 to 8 is a
+two hop link and, thus, has a cost of 20 instead of the usual 10.
 

### 2013-06-09 graphs/evaluate.py

@@ -4,7 +4,9 @@ import draw
 import config
 import pdb
 
-# Evaluation is round-based
+# Evaluation is event based. We realize this using a priority heap
+# with the time at which the event is happening as priority and pop
+# the top of this queue in every step.
 
 # Assumptions:
 # 1) nodes never have to process different events at the same time
@@ -14,9 +16,18 @@ import pdb
 round = 0
 event_queue = []
 model = {}
+# Some topologies require state (e.g. rings). We store this state
+# in a list of node states (sequence number for rings)
 node_state = []
 last_node = -1
+# Keep track of which nodes are active
+# * lists of nodes that: 
+#  -> received the message already (nodes_active)
+#  -> did _not_ yet receive the message (nodes_inactive)
+nodes_active = []
+nodes_inactive = []
 
+# ==================================================
 class NodeState(object):
     """
     Store node state for evaluation
@@ -24,6 +35,7 @@ class NodeState(object):
     def __init__(self):
         self.seq_no = 0
 
+# ==================================================
 class Result():
     """
     Store result of evaluation
@@ -32,7 +44,7 @@ class Result():
         self.time = time
         self.last_node = last_node
 
-
+# ==================================================
 def evalute(topo, root, m, sched):
     """
     Evaluate the latency of sending an individual message along the tree
@@ -56,10 +68,12 @@ def evalute(topo, root, m, sched):
 
     # Construct visualization instance
     global visu
-    visu = draw.Output(("visu_%s_%s.tex" % (m.get_name(), topo.get_name())), 
+    visu = draw.Output(("visu_%s_%s_send_events.tex" % \
+                        (m.get_name(), topo.get_name())), 
                        m, topo)
-    
-    send(root, round, [])
+
+    nodes_active.append(root)
+    heapq.heappush(event_queue, (round, events.Send(root, None)))
 
     while not terminate():
         consume_event()
@@ -90,6 +104,10 @@ def consume_event():
     if isinstance(e, events.Receive):
         receive(e.src, e.dest)
 
+    if isinstance(e, events.Send):
+        assert e.dest is None
+        send(e.src)
+
 def propagate(src, dest):
     """
     Process propagation event.
@@ -100,20 +118,32 @@ def propagate(src, dest):
 
 def receive(src, dest):
     """
-    Receive a message on dest
-    Send will be called to trigger sending of messages to children
+    Receive a message on dest XXX This is a bit of a misnomer. _dest_
[…]

### 2013-06-09 graphs/events.py

@@ -5,10 +5,21 @@ class Event():
         self.dest = dest
 
 class Send(Event):
-    "Represents a send operation"
+    """
+    Represents a send operation. When dequeued, a node is ready to
+    send a message (i.e. the node is active and idle)
+    """
 
 class Receive(Event):
-    "Represents a receive operation"
+    """
+    Represents a receive operation. When dequeued, a message is
+    received from the wire and the receiving node can start receiving
+    the message.
+    """
 
 class Propagate(Event):
-    "Represent propagation of event"
+    """
+    Represent propagation of event. This is enqueued from send(). When
+    dequeued, it means that the message has been sent from the sender
+    and started to propagate.
+    """

### 2013-06-10 graphs/ziger_ump_breakdown.tex
Added the UMP breakdown of ziger1 to the paper

Figure~\ref{pgfplot:201306061829} shows the breakdown of the cost for sending UMP messages depending on which cores communicate. The measurement has been executed on ziger1. Propagation time is calculated from the round-trip time minus send and receive time on sender minus processing time on server
\pgfplotsset{width=\linewidth}
\begin{figure}
  \caption{UMP breakdown}
  \label{pgfplot:201306061829}
  \begin{tikzpicture}
    \begin{axis}[
        ybar stacked,ymin=0,legend style={ at={(0.5,-0.20)}, anchor=north, legend columns=-1},
        xlabel={target core},
        ylabel={cycles}
        ]
    \addplot coordinates {
      (1,300.000000)
      (2,300.000000)
      (3,300.000000)
      (4,300.000000)
      (5,300.000000)
      (6,300.000000)
      (7,300.000000)
      (8,300.000000)
      (9,300.000000)
      (10,300.000000)
      (11,300.000000)
      (12,300.000000)
      (13,300.000000)
      (14,300.000000)
      (15,300.000000)
      (16,300.000000)
      (17,300.000000)
      (18,300.000000)
      (19,300.000000)
      (20,300.000000)
      (21,300.000000)
      (22,300.000000)
      (23,300.000000)
    };
    \addplot coordinates {
      (1,244.197531)
      (2,246.407407)
      (3,245.567901)
      (4,244.543210)
      (5,243.530864)
      (6,245.061728)
      (7,245.901235)
      (8,247.481481)
      (9,245.901235)
      (10,243.197531)
      (11,246.530864)
      (12,243.913580)
      (13,246.259259)
      (14,243.469136)
      (15,242.283951)
      (16,244.851852)
      (17,242.209877)
      (18,258.012346)
      (19,256.765432)
      (20,256.592593)
      (21,255.382716)
      (22,258.666667)
      (23,255.567901)
    };
    \addplot coordinates {
      (1,98.388889)
      (2,102.181481)
      (3,101.376543)
      (4,99.783951)
      (5,93.748148)
      (6,187.491358)
      (7,176.212346)
      (8,173.327160)
      (9,178.597531)
      (10,173.375309)
      (11,167.481481)
      (12,175.728395)
      (13,179.177778)
      (14,180.565432)
      (15,183.571605)
      (16,181.665432)
      (17,189.946914)
      (18,331.055556)
      (19,333.632099)
      (20,315.514815)
      (21,313.348148)
      (22,314.414815)
      (23,337.682716)
    };
    \addplot coordinates {
      (1,262.716049)
      (2,250.864198)
      (3,253.271605)
      (4,264.481481)
      (5,262.876543)
      (6,406.592593)
      (7,417.086420)
      (8,414.913580)
      (9,417.024691)
      (10,416.345679)
      (11,417.320988)
      (12,432.172840)
      (13,427.814815)
      (14,429.234568)
      (15,424.814815)
      (16,426.283951)
      (17,425.444444)
      (18,506.333333)
      (19,503.679012)
      (20,518.222222)
      (21,522.506173)
      (22,517.111111)
      (23,504.703704)
    };
     \legend{server cost, send, propagation, receive}
    \end{axis}
  \end{tikzpicture}
\end{figure}

### 2013-06-10 paper.tex
Added the UMP breakdown of ziger1 to the paper

--- 2013-06-04 paper.tex
@@
 
-\paragraph{Atomic broadcast} \stefan{Explain the guarantees provided
-  by atomic broadcasts}. Atomic broadcasts are frequently used to
+\paragraph{Atomic broadcast} An Atomic broadcasts is a broadcast
+messaging protocol that is reliable in the sense that if a message is
+received by one of the participating nodes, it is also received by all
+other nodes. Furthermore, the order of messages as seen by all
+participants is the same. Atomic broadcasts are frequently used to
 implement higher-level distributed algorithms on top of it: examples
@@
 nodes. Broadcasts are one of the most important communication
-operations for parallel applications~\cite{Bruck1992} \stefan{Database
+operations for parallel applications~\cite{Bruck1992}. \stefan{Database
   joins}.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{appendices}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{UMP performance}
+
+\input{graphs/ziger_ump_breakdown}
+
 \newpage

### 2013-06-10 graphs/helpers.py

@@ -190,7 +190,7 @@ def statistics(l):
 
 def _pgf_plot_header(f, plotname, caption, xlabel, ylabel, attr=[], desc='...'):
     label = "pgfplot:%s" % plotname
-    s = (("Plot~\\ref{%s} shows %s\n"
+    s = (("Figure~\\ref{%s} shows %s\n"
           "\\pgfplotsset{width=\linewidth}\n"
           "\\begin{figure}\n"
           "  \\caption{%s}\n"

### 2013-06-11 graphs/ziger_ump_breakdown.tex
Some outstanding things

@@
-Figure~\ref{pgfplot:201306061829} shows the breakdown of the cost for sending UMP messages depending on which cores communicate.
-The measurement has been executed on ziger1.
-Propagation time is calculated from the round-trip time minus send and receive time on sender minus processing time on server
+Figure~\ref{pgfplot:201306061829} shows the breakdown of the cost for
+sending UMP messages on ziger1 for communication between core 0 and
+all other cores.
+
+Latency is calculated from the round-trip time minus send and receive
+time on sender minus processing time on server. However, send time on
+one end of a channel seems to overlap with received time on the other
+end of the channel, which makes it hard to calculate actual
+latency. Thus, we assume the server processing time to be 300 cycles.
+
+\stefan{We can measure latency on a machine with synchronized clocks
+  when adding timestamps as payload to the ump messages.}
+
+Send time is independent of which core the message is send
+to. Internally, the send operation is a write operation to the local
+cache. The cache coherency protocol will then invalidate all other
+copies of this line in the system.
+
+Receive time on the other hand does depend on which cores
+communicate. When polling the cache-line, which is invalid at this
+time, the cache coherency protocol will transfer this cache-line from
+the sending to the receiving core.
+
 \pgfplotsset{width=\linewidth}

### 2013-06-17 graphs/helpers.py
Generating _two_ header files now, one with the actual C variable representing the model, the other with some meta data. Stupid me! Should have done this from the start. j;agkwl go;iqw

@@ -52,9 +52,16 @@ def output_quorum_configuration(model, graph, root, sched, topo):
 
     # Generate c code
     stream = open("model.h", "w")
-    __c_header(stream, model.evaluation.last_node, type(model), type(topo))
+    defstream = open("model_defs.h", "w")
+    __c_header_model_defs(defstream, 
+                          model.evaluation.last_node, 
+                          type(model), 
+                          type(topo),
+                          len(mat))
+    __c_header_model(stream)
     __matrix_to_c(stream, mat)
     __c_footer(stream)
+    __c_footer(defstream)
 
 
 def walk_graph(g, root, func, mat, sched):
@@ -109,8 +116,9 @@ def __matrix_to_c(stream, mat):
 
     """
     dim = len(mat)
-    stream.write(("#define MODEL_NUM_CORES %d\n\n" % dim))
-    stream.write(("int model[%d][%d] = {\n" % (dim, dim)))
+    stream.write("int model[MODEL_NUM_CORES][MODEL_NUM_CORES] = {\n")
+    # x-axis labens
+    stream.write(("//   %s\n" % ' '.join([ "%2d" % x for x in range(dim) ])))
     for x in range(dim):
         stream.write("    {")
         for y in range(dim):
@@ -118,19 +126,26 @@ def __matrix_to_c(stream, mat):
             if y+1 != dim:
                 stream.write(",")
         stream.write("}")
-        if x+1 != dim:
-            stream.write(",")
+        stream.write(',' if x+1 != dim else ' ')
+        stream.write((" // %2d" % x))
         stream.write("\n")
     stream.write("};\n\n")
 
 
-def __c_header(stream, last_node, machine, topology):
-    stream.write('#ifndef MULTICORE_MODEL\n')
-    stream.write('#define MULTICORE_MODEL 1\n\n')
+def __c_header(stream, name):
+    stream.write('#ifndef %s\n' % name)
+    stream.write('#define %s 1\n\n' % name)
+
+def __c_header_model_defs(stream, last_node, machine, topology, dim):
+    __c_header(stream, 'MULTICORE_MODEL_DEFS')                               
     stream.write('#define MACHINE "%s"\n' % machine)
     stream.write('#define TOPOLOGY "%s"\n' % topology)
-    stream.write('#define LAST_NODE %d\n\n' % last_node)
+    stream.write('#define LAST_NODE %d\n' % last_node)
[…]

### 2013-06-17 graphs/run_experiments.sh

@@ -3,7 +3,7 @@
 MODEL=model.h
 QDIR=$HOME/bf/quorum/usr/quorum/
 TMP=`mktemp`
-RESULTDIR=~/measurements/atomic_broadcast/
+RESULTDIR=~/measurements/atomic_broadcast_new_model/
 PATTERN="Quorum.*everything done.*exiting"
 
 # check the output
@@ -20,7 +20,7 @@ function wait_result() {
 		sleep 2
 		i=$(($i+1))
 
-		if [[ i -ge 150 ]]
+		if [[ i -ge 300 ]]
 		then
 			echo "Timeout, restarting machine"
 			rackpower -r $m
@@ -32,18 +32,18 @@ function wait_result() {
 # main
 # --------------------------------------------------
 # gruyere sbrinz1
-for m in ziger1 gruyere sbrinz1 
+for m in appenzeller # sbrinz1 #gruyere sbrinz1 # ziger1 
 do
 	# ring,cluster,mst,bintree,sequential,badtree
 	# cluster mst bintree sequential 
-    for t in badtree cluster mst bintree sequential 
+    for t in badtree cluster mst bintree sequential adaptivetree
     do
 	# Cleanup 
 	rm -f $MODEL
 	echo "" >$TMP
 	
 	# Run the simulator
-	./simulator.py $m $t
+	./simulator.py $m $t || exit 1
 
 	# Quit if generating the model failed
 	if [[ ! -e $MODEL ]]

### 2013-06-19 paper.tex
UMP breakdown is a section
Generating _two_ header files now, one with the actual C variable representing the model, the other with some meta data. Stupid me! Should have done this from the start. j;agkwl go;iqw
New reference. Separate pdf for visualizations.

@@
 characteristics, interconnect topologies, propagation time on
-interconnect and use of shared caches. These characteristics are hard
+interconnect and use of shared caches. These characteristics are hard~\cite{Cavage2013}
 to understand, but important to consider for application performance.
@@
 \end{inparaenum}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=\linewidth]{Overview_Model_Evaluation_Parser}
+  \caption{Overview of configuration of atomic broadcast using a Model 
+    \stefan{Draw figure properly}}
+  \label{fig:overview}
+\end{figure}
 
@@
 \section{Implementation}
+\label{sec:implementation}
 
@@
 \subsubsection{Real hardware}
+
+\stefan{Describe benchmark application} 
+\begin{itemize}
+\item One process on every core
+\item Management process on core 2 (i.e.\ not core 0)
+\item Uses atomic broadcast as described in Section~\ref{sec:implementation}
+\end{itemize}
 
@@
 \begin{itemize}
+\item Keywords: decomposition~\cite{Cavage2013}
 \item Other topologies (mainly based on~\cite{Bruck1992}):
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{UMP performance}
+\section{UMP performance}
 
@@
 \input{measurements/sbrinz1_topologies}
-
-\input{graphs/visall}
+\input{measurements/appenzeller_topologies}
+
+%\input{graphs/visall}
 

### 2013-06-25 paper.tex
More measurements

@@
 \usepackage[toc,page]{appendix}
+\usepackage{fancyhdr}
 % ==================================================
@@
 \usepackage{pgfplots}
+
 % configuration
@@
 \pgfplotsset{width=.9\linewidth}
+\usepgfplotslibrary{external}
+%\tikzexternalize
 
@@
 \newcommand{\textc}[1]{{\color{gray} {\footnotesize #1}}}
+
+\fancyhf{}
+\fancyfoot[L]{\today}
+\pagestyle{fancy}
+
+% machines
+\newcommand{\ziger}{Ziger (AMD Istanbul 4x6x1)}
 
@@
   rather than the latency expressed in a concrete time.
+  \begin{description}
+  \item[send time] We assume this independent of which node we
+    communicate with (which is true for most of our machines when
+    using sender-side buffering)
+  \item[receive] On shared memory machines, receiving messages is
+    realized by reading a memory location. When the sender writes the
+    message, the receiver's copy of the cache-line is invalid. The
+    next read on it causes a transfer of the cache line from the
+    sender's to the receiver's cache, which seems to have a cost that
+    is growing with the number of hops on the interconnect for our
+    machines (although, on some machines, this is only roughly true:
+    communication with different NUMA nodes at the same interconnect
+    hop distance varies a bit. We ignore this fact for now.)
+  \end{description}
 \item[bounded delivery]
@@
 We now make up a machine model for evaluation. This model is based on
-a 8x4x1 AMD Shanghai machine. The topology of such a machine is shown
+a 8x4x1 AMD Barcelona machine. The topology of such a machine is shown
 in Figure~\ref{fig:gruyere}.
@@
   \end{tikzpicture}
-  \caption{Interconnect topology of 8x4x1 AMD Shanghai machine}
+  \caption{Interconnect topology of 8x4x1 AMD Barcelona machine}
   \label{fig:gruyere}
@@
 NUMA domain corresponds to one cluster.
+
+%--------------------------------------------------
+\subsubsection{Adaptive Tree}
+
+\stefan{Describe how this works and how we pick links}
 
@@
 interconnect driver. It provides reliable channels with in-order
-delivery. Flow control is build in for reliability. Communication
-starts at the root node, which acts as a
-sequentializer. See~\ref{algo:ab} for details.
+delivery and sender-side buffering \stefan{Verify this}. Flow control
+is build in for reliability. Communication starts at the root node,
+which acts as a sequentializer. See~\ref{algo:ab} for details.
 
@@
 
+\section{Shared memory performance}
+
+Plot~\ref{pgfplot:201306191213} shows some measurements for using a
+shared memory FIFO queue for communication. Core 0 sends message by
+enqueuing them to the FIFO, while all other cores poll on the queue
+for new messages.
+
+The measurement assumes the tsc clocks to be synchronized. The queues
+are also infinite. Messages are never garbage-collected.
+
+\begin{figure}
+  \caption{Shared memory FIFO performance on brie}
+  \label{pgfplot:201306191213}
+  \begin{tikzpicture}
+    \begin{axis}[
+      ybar,
+      error bars/y dir=both,%
+      error bars/y explicit,%
+      xlabel=core,
+      xtick={1,2,3},
+      ylabel={cost [cycles]}]
+
+    \addplot coordinates {
+      (1,488.6) +- (32.1,32.1)
+      (2,761.7) +- (124.1,124.1)
+      (3,862.5) +- (118.3,118.3)
+    };
+    \end{axis}
+  \end{tikzpicture}
+\end{figure}
+
+Plot~\ref{pgfplot:201306191238} shows the same experiment for tomme.
+
+\begin{figure}
+  \caption{Shared memory FIFO performance on tomme}
+  \label{pgfplot:201306191238}
+  \begin{tikzpicture}
+    \begin{axis}[
+      ybar,
+      error bars/y dir=both,
+      error bars/y explicit,
+      xlabel=core,
+      ylabel={Cost [cycles]}]
+    \addplot coordinates {
+      (1,417.6) +- (71.0,71.0)
+      (2,776.2) +- (110.4,110.4)
+      (3,774.6) +- (111.9,111.9)
+      (4,648.0) +- (175.9,175.9)
+      (5,551.2) +- (257.5,257.5)
+      (6,652.6) +- (179.2,179.2)
+      (7,688.6) +- (116.3,116.3)
+      (8,691.2) +- (133.0,133.0)
+      (9,721.6) +- (55.8,55.8)
+      (10,633.8) +- (135.0,135.0)
+      (11,673.8) +- (86.4,86.4)
+      (12,705.0) +- (81.8,81.8)
+      (13,612.6) +- (199.1,199.1)
+      (14,699.2) +- (90.3,90.3)
+      (15,691.6) +- (93.0,93.0)
+    };
+    \end{axis}
+  \end{tikzpicture}
+\end{figure}
+
+Plot~\ref{pgfplot:201306191603} shows it for gruyere. These do not
+make sense. The numbers are far too high, especially since gruyere is
+supposed to be synchronized.
+
+This suggest that my implementation is broken ..
+
+\begin{figure}
+  \caption{Plot}
+  \label{pgfplot:201306191603}
+  \begin{tikzpicture}
+    \begin{axis}[
+      ybar,
+      error bars/y dir=both,
+      error bars/y explicit,
+      xlabel=FIXME,
+      ylabel={Cost [cycles]}]
+    \addplot coordinates {
+      (1,2399.4) +- (3585.1,3585.1)
+      (2,8924.9) +- (11981.8,11981.8)
+      (3,4922.3) +- (4685.1,4685.1)
+      (4,6638.2) +- (3521.0,3521.0)
+      (5,5608.7) +- (4185.6,4185.6)
+      (6,5337.5) +- (3846.6,3846.6)
+      (7,5844.6) +- (2836.9,2836.9)
+      (8,5089.0) +- (3135.3,3135.3)
+      (9,5264.0) +- (3919.9,3919.9)
+      (10,5711.7) +- (3793.0,3793.0)
+      (11,5266.9) +- (3712.1,3712.1)
+      (12,8197.6) +- (3819.3,3819.3)
+      (13,8668.6) +- (3645.8,3645.8)
+      (14,8923.8) +- (2964.8,2964.8)
+      (15,7195.3) +- (2407.2,2407.2)
+      (16,8176.2) +- (3185.2,3185.2)
+      (17,8770.7) +- (3001.8,3001.8)
+      (18,4171.5) +- (2011.4,2011.4)
+      (19,8453.5) +- (3280.2,3280.2)
+      (20,13695.1) +- (3137.6,3137.6)
+      (21,13806.8) +- (2914.0,2914.0)
+      (22,13692.4) +- (2730.3,2730.3)
+      (23,14435.9) +- (2983.7,2983.7)
+      (24,9797.6) +- (3821.4,3821.4)
+      (25,8955.7) +- (4364.6,4364.6)
+      (26,7929.3) +- (3493.3,3493.3)
+      (27,11541.9) +- (3076.2,3076.2)
+      (28,10851.3) +- (4241.4,4241.4)
+      (29,8736.3) +- (3280.4,3280.4)
+      (30,11648.2) +- (2969.7,2969.7)
+      (31,7821.5) +- (2477.0,2477.0)
+    };
+    \end{axis}
+  \end{tikzpicture}
+\end{figure}
+
+Plot~\ref{pgfplot:201306191624} shows the same with more
+iterations. The result is not more stable than the one before,
+though.
+
+\begin{figure}
+  \caption{Plot}
+  \label{pgfplot:201306191624}
+  \begin{tikzpicture}
+    \begin{axis}[
+      ybar,
+      error bars/y dir=both,
+      error bars/y explicit,
+      xlabel=FIXME,
+      ylabel={Cost [cycles]}]
+    \addplot coordinates {
+      (1,11197.7) +- (8150.8,8150.8)
+      (2,10971.4) +- (6418.6,6418.6)
+      (3,10364.3) +- (7409.8,7409.8)
+      (4,9460.5) +- (6846.3,6846.3)
+      (5,11629.7) +- (7938.9,7938.9)
+      (6,12266.8) +- (8895.5,8895.5)
+      (7,12313.0) +- (8030.9,8030.9)
+      (8,13079.3) +- (7031.2,7031.2)
+      (9,10919.1) +- (6272.3,6272.3)
+      (10,4758.1) +- (3364.5,3364.5)
+      (11,4093.8) +- (2121.7,2121.7)
+      (12,10077.3) +- (1152.3,1152.3)
+      (13,8632.7) +- (1601.4,1601.4)
+      (14,6381.6) +- (1607.5,1607.5)
+      (15,8215.2) +- (1799.2,1799.2)
+      (16,6973.4) +- (1713.0,1713.0)
+      (17,8631.0) +- (1750.3,1750.3)
+      (18,13615.4) +- (2873.1,2873.1)
+      (19,11311.9) +- (1996.6,1996.6)
+      (20,17855.8) +- (2420.9,2420.9)
+      (21,15193.0) +- (1923.7,1923.7)
+      (22,18920.0) +- (2393.1,2393.1)
+      (23,19870.6) +- (2618.8,2618.8)
+      (24,17947.8) +- (4379.8,4379.8)
+      (25,21783.5) +- (4202.5,4202.5)
+      (26,24329.6) +- (3695.0,3695.0)
+      (27,22965.0) +- (3667.8,3667.8)
+      (28,20440.8) +- (4380.6,4380.6)
+      (29,17405.7) +- (4385.3,4385.3)
+      (30,19202.7) +- (4509.1,4509.1)
+      (31,21855.2) +- (3850.9,3850.9)
+    };
+    \end{axis}
+  \end{tikzpicture}
+\end{figure}
+
 \newpage
 \input{measurements/gruyere_topologies}
+
+Table~\ref{tab:ziger1} shows an overview of topologies for atomic
+broadcast on \ziger. We compare these numbers to cost-estimations from
+our simulator that incorporates detailed UMP breakdown measurements
+done on the same machine. Our estimations are close to what we observe
+when running on real hardware. In particular, the order of efficiency
+of the topologies matches reality.
+
+The only exception is sequential execution. Our simulator predicts
+much worse performance than actually given by hardware. We believe the
+cause for this could be hardware extensions (e.g.\ hardware broadcast
+units or snooping).
+
+What is particularly interesting is that a badly chosen tree with lots
+of communication across NUMA nodes is actually worse than sequentially
+sending messages.
+
 \input{measurements/ziger1_topologies}
-\input{measurements/sbrinz1_topologies}
+\input{measurements/sbrinz_topologies}
 \input{measurements/appenzeller_topologies}

### 2013-06-28 paper.tex
Moving to Laptop

@@
 \usepgfplotslibrary{external}
-%\tikzexternalize
+\tikzexternalize
 
@@
 \fancyfoot[L]{\today}
+\fancyfoot[R]{\thepage}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrulewidth}{0pt}
 \pagestyle{fancy}
@@
 
+\subsection{Pairwise performance}
+
+Figure~\ref{pgfplot:20130627} shows the UMP RTT time for each pair of
+cores. The benchmark seems to be broken, since sending messages to
+core 40 and higher is really expensive. On the other hand. Sending
+messages from these cores back to cores with low IDs (which are on the
+other end of the machine) seems unreasonably cheap.
+
+What we would expect is a symmetric plot. Sending a message from core
+$n$ to $m$ should be about equally expensive than sending a message
+from $m$ to $n$.
+
+\pgfplotsset{width=\linewidth}
+\begin{figure}
+  \caption{pair-wise latency for appenzeller}
+  \label{pgfplot:20130627}
+  \begin{tikzpicture}
+    \begin{axis}[
+      zlabel={cost [cycles]},
+      xlabel={sending core},
+      ylabel={receiving core},
+      scaled z ticks = false,
+      z tick label style={/pgf/number format/fixed}
+      ]
+    \addplot3[surf] file {measurements/appenzeller_pairwise_ump.dat};
+    \end{axis}
+  \end{tikzpicture}
+\end{figure}
+
+\pgfplotsset{width=\linewidth}
+\begin{figure}
+  \caption{pair-wise latency for gottardo}
+  \label{pgfplot:20130627}
+  \begin{tikzpicture}[scale=.75]
+    \begin{axis}[scaled z ticks=false,z tick label style={/pgf/number format/fixed},zlabel={cost [cycles]},xlabel={sending core},ylabel={receiving core}]
+    \addplot3[surf] file {measurements/gottardo_pairwise_ump.dat};
+    \end{axis}
+  \end{tikzpicture}
+\end{figure}
+
 \section{Shared memory performance}

### 2013-06-28 graphs/evaluate_pariwise-latency.py

@@ -1,0 +1,58 @@
+#!/usr/bin/env python
+
+import sys
+import fileinput
+import re
+
+sys.path.append('/home/skaestle/bf/quorum/tools/harness')
+sys.path.append('/home/skaestle/bf/quorum/tools/harness/tests')
+sys.path.append('/home/skaestle/bf/quorum/tools/harness/machines')
+
+sys.path.append('/home/skaestle/bin/')
+
+import helpers
+import argparse
+
+parser = argparse.ArgumentParser(
+    description='Evaluation of UMP')
+parser.add_argument('machine')
+args = parser.parse_args()
+
+r = []
+
+for line in sys.stdin.readlines():
+    line = line.rstrip()
+    if not re.match('^[0-9]', line):
+        continue
+    ls = line.split()
+    if not len(ls)>3:
+        continue
+    (x, y, z) = map(float, (ls[0], ls[1], ls[2]))
+    r.append((x,y,z))
+
+r = sorted(r, key = lambda x : (x[1], x[0]))
+last = -1
+
+fname_res = '/tmp/res.dat'
+f_res = open(fname_res, 'w+')
+
+for (x,y,z) in r:
+    if y != last:
+        f_res.write('\n')
+        last = y
+    f_res.write('%d %d %f\n' % (x,y,z))
+
+f_res.close()
+
+fname = '/tmp/plot3.tex'
+f = open(fname, 'w+')
+
+helpers._latex_header(f)
+helpers.do_pgf_3d_plot(f, fname_res, 
+                       'pair-wise latency for %s' % args.machine, 
+                       'sending core', 'receiving core', 'cost [cycles]')
+helpers._latex_footer(f)
+
+f.close()
+
+helpers.run_pdflatex(fname)

### 2013-06-28 graphs/helpers.py

@@ -233,11 +233,11 @@ def _pgf_plot_header(f, plotname, caption, xlabel, ylabel, attr=[], desc='...'):
     label = "pgfplot:%s" % plotname
     s = (("Figure~\\ref{%s} shows %s\n"
           "\\pgfplotsset{width=\linewidth}\n") % (label, desc))
-    t = (("    \\begin{axis}[\n"
-          "        %s,\n" 
-          "        xlabel={%s},\n"
-          "        ylabel={%s}\n"
-          "        ]\n") % (','.join(attr), xlabel, ylabel))
+    if xlabel:
+        attr.append('xlabel={%s}' % xlabel)
+    if ylabel:
+        attr.append('ylabel={%s}' % ylabel)
+    t = ("    \\begin{axis}[%s]\n") % (','.join(attr))
     f.write(s)
     _pgf_header(f, caption, label)
     f.write(t)
@@ -277,6 +277,22 @@ def do_pgf_plot(f, data, caption='', xlabel='', ylabel=''):
     f.write("    };\n");
     _pgf_plot_footer(f)
 
+def do_pgf_3d_plot(f, datafile, caption='', xlabel=None, ylabel=None, zlabel=None):
+    """
+    Generate PGF plot code for the given data
+    @param f File to write the code to
+    @param data Data points to print as list of tuples (x, y, err)
+    """
+    attr = ['scaled z ticks=false',
+            'z tick label style={/pgf/number format/fixed}']
+    if zlabel:
+        attr.append('zlabel={%s}' % zlabel)
+    now = datetime.today()
+    plotname = "%02d%02d%02d" % (now.year, now.month, now.day)
+    _pgf_plot_header(f, plotname, caption, xlabel, ylabel, attr)
+    f.write(("    \\addplot3[surf] file {%s};\n") % datafile)
+    _pgf_plot_footer(f)
+
 def do_pgf_multi_plot(f, multidata, caption='FIXME', xlabel='FIXME', ylabel='FIXME'):
     """
     Same as do_pgf_multi_plot
@@ -304,13 +320,12 @@ def do_pgf_multi_plot(f, multidata, caption='FIXME', xlabel='FIXME', ylabel='FIX
 
         machines.append(legentry)
 
-#   "Invert" two dimensional list
+    # "Invert" two dimensional list
     data_new = [[0 for i in range(len(data))] for j in range(len(data[0]))]
     for y in range(len(data[0])):
         for x in range(len(data)):
[…]

### 2013-07-01 paper.tex
Improved Introduction

@@
 Distributed algorithms are increasingly used to overcome scalability
-challenges on multicore machines. Examples are
+challenges of multicore machines. Examples are
 databases~\cite{Salomie2011, Wiesmann2000} and operating
@@
 % What do you want to enable?
-We want to investigate how to achieve better performance of atomic
-broadcast across a wide range of multicore machines without manually
-tuning the implementation to concrete machines.
+We want to investigate how to achieve better performance of these distributed
+algorithms across a wide range of multicore machines without manually
+tuning the implementation to characteristics of individual machines.
 
 % What problem are you solving, and why is it hard?
-The problem is complexity and diversity of modern multicore
-machines. Multicores come in many flavors depending on vendor and
-generation of the machine. All of these machines have fundamentally
-different characteristics such as number of nodes, NUMA
-characteristics, interconnect topologies, propagation time on
-interconnect and use of shared caches. These characteristics are hard~\cite{Cavage2013}
-to understand, but important to consider for application performance.
+The problem we are tackling is an increase in complexity and diversity
+of modern multicore machines. Multicores come in many flavors
+depending on vendor and product line of the machine. They also change
+heavily over time. Consequently, characteristics of such machines are
+fundamentally different. Examples are the number of cores, NUMA
+configurations, interconnect topologies, propagation time on the
+interconnect and availability of shared resources such as
+caches. These characteristics are hard~\cite{Cavage2013} to
+understand, but important to consider for application performance.
 
@@
 Instead of manually tuning algorithms to characteristics of individual
-machines, we automatically configure distributed algorithm
-implementations based on a machine model. We represent this model as an
-annotated graph. One question we are looking at is which information
-should actually be part of this machine model.
+machines, we automatically configure distributed algorithm based on a
+machine model. This is populate with online measurements to express
+detailed information about machine characteristics. We then use
+this model to predict algorithm performance for the specific machine
+and select a good implementation automatically and dynamically at
+run-time.
 
 % How will you go about it?
-We base the configuration of algorithms on \emph{overlay networks}, which we
-automatically configure. We execute our configuration stage on a model
-representing the concrete machine the algorithm is intended to run
-on. %
-Our idea is to then explore different approaches for finding overlay
-networks based on the network model graph. Approaches we are currently
-investigating are: minimum spanning tree algorithms, binary trees,
-clustering techniques as well as treating the problem
-hierarchically. Assuming the overlay network, we then need to decide
-on every node which message to send first. This is a \emph{scheduling}
-problem.
+As an example, we investigate atomic broadcasts for multicore
+machines. The space of possible implementations is large reaching from
+shared memory implementations to message based topologies for
+different topologies of overlay networks. Such topologies are: minimum
+spanning trees, binary trees, rings as well as clustering-based
+approaches. Assuming the overlay network, we then need to decide for
+every node the order in which to send messages. This is a
+\emph{scheduling} problem.
 

### 2013-07-01 figs/Overview_Model_Evaluation_Parser.tex
Started to TeX the architecture figure

--- 2013-06-25 paper.tex
@@
-\documentclass{article}
+%\documentclass[portrait]{a0poster}
+\documentclass[a4wide]{article}
 \usepackage{url,color,xspace,verbatim,subfig,ctable,multirow,listings}
@@
 \usepackage[ruled,vlined]{algorithm2e}
-\usepackage[toc,page]{appendix}
-\usepackage{fancyhdr}
+
 % ==================================================
@@
 \usepackage{pgfplots}
-
 % configuration
 \usetikzlibrary{shapes,positioning,calc,snakes,arrows,shapes,fit,backgrounds}
-\pgfplotsset{width=.9\linewidth}
-\usepgfplotslibrary{external}
-%\tikzexternalize
 
-\lstset{
-  language=C,
-  basicstyle=\ttfamily \small,
-  flexiblecolumns=false,
-  basewidth={0.5em,0.45em},
-  boxpos=t,
-}
-
-\newcommand{\etal}{{\it et al.}\xspace}
-\newcommand{\naive}{na\"{\i}ve\xspace}
-\newcommand{\Naive}{Na\"{\i}ve\xspace}
-\newcommand{\textc}[1]{{\color{gray} {\footnotesize #1}}}
-
-\fancyhf{}
-\fancyfoot[L]{\today}
-\pagestyle{fancy}
-
-% machines
-\newcommand{\ziger}{Ziger (AMD Istanbul 4x6x1)}
-
-\definecolor{skRed}{RGB}{155,25,25}
-\newcommand{\stefan}[1]{
-  {\color{skRed}[{\color{red}{SK}} #1]}}
-
-\setcounter{section}{0} % Start sections with 1, not 0
 \begin{document}
-
-\title{Adaptive broadcast tree for multicores}
-
-% email address
-\newcommand{\eaddr}{stefan.kaestle@inf.ethz.ch}
-\newcommand{\email}{\href{mailto:\eaddr}{\eaddr}}
-
-\author{Stefan Kaestle\\
-  \email \\
-  Systems Group, ETH Zurich}
-
-\maketitle
-
-% keywords: modeling, simulation, overlay networks, scheduling
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-
-Distributed algorithms are increasingly used to overcome scalability
-challenges on multicore machines. Examples are
-databases~\cite{Salomie2011, Wiesmann2000} and operating
-systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}.
-
-% What do you want to enable?
-We want to investigate how to achieve better performance of atomic
-broadcast across a wide range of multicore machines without manually
-tuning the implementation to concrete machines.
-
-% What problem are you solving, and why is it hard?
-The problem is complexity and diversity of modern multicore
-machines. Multicores come in many flavors depending on vendor and
-generation of the machine. All of these machines have fundamentally
-different characteristics such as number of nodes, NUMA
-characteristics, interconnect topologies, propagation time on
-interconnect and use of shared caches. These characteristics are hard~\cite{Cavage2013}
-to understand, but important to consider for application performance.
-
-% New ideas
-Instead of manually tuning algorithms to characteristics of individual
-machines, we automatically configure distributed algorithm
-implementations based on a machine model. We represent this model as an
-annotated graph. One question we are looking at is which information
-should actually be part of this machine model.
-
-% How will you go about it?
-We base the configuration of algorithms on \emph{overlay networks}, which we
-automatically configure. We execute our configuration stage on a model
-representing the concrete machine the algorithm is intended to run
-on. %
-Our idea is to then explore different approaches for finding overlay
-networks based on the network model graph. Approaches we are currently
-investigating are: minimum spanning tree algorithms, binary trees,
-clustering techniques as well as treating the problem
-hierarchically. Assuming the overlay network, we then need to decide
-on every node which message to send first. This is a \emph{scheduling}
-problem.
-
-% How do we show it works
-We auto-configure a wide range of different multicore machines and
-compare the performance of our implementation with hand-tuned
-implementations on all of these machines.
-% Hypothesis
-Our hypothesis is that automatic tuning of distributed algorithms 
-to machine characteristics is worth
-doing. Obviously, we cannot achieve performance of hand-tuned
-implementations, but we hope to get close enough to argue that loosing
-a bit of performance to avoid tedious manual reconfiguration is worth
-if for many applications (while others, where performance
-\emph{really} matters, might still want to manually configure their
-stuff).
-
-% three-step approach
-We break the problem down into three steps:
-\begin{inparaenum}[\itshape 1\upshape)]
-\item We first represent multicore machines by a model. We describe
-  this model in Section~\ref{sec:model},
-\item We then find an overlay for a concrete network model. This
-  overlay network describes a topology (such as a tree or a ring) for
-  communication within the machine. Algorithms to select overlay
-  networks are described in Section~\ref{sec:overlay}, and
-\item Given the overlay, we need to decide for every node in which
-  order to send messages. We investigate this scheduling problem in
-  Section~\ref{sec:scheduling}.
-\end{inparaenum}
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=\linewidth]{Overview_Model_Evaluation_Parser}
-  \caption{Overview of configuration of atomic broadcast using a Model 
-    \stefan{Draw figure properly}}
-  \label{fig:overview}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Distributed algorithms}
-\label{sec:distalgo}
-
-In order to evaluate our ideas, we pick two concrete distributed
-algorithms and implement them for a multicore machine:
-
-\paragraph{Atomic broadcast} An Atomic broadcasts is a broadcast
-messaging protocol that is reliable in the sense that if a message is
-received by one of the participating nodes, it is also received by all
-other nodes. Furthermore, the order of messages as seen by all
-participants is the same. Atomic broadcasts are frequently used to
-implement higher-level distributed algorithms on top of it: examples
-are replication such as state machine replication. As a first step, we
-evaluate the performance of sending one message as a broadcast to all
-nodes. Broadcasts are one of the most important communication
-operations for parallel applications~\cite{Bruck1992}. \stefan{Database
-  joins}.
-
-\paragraph{Barriers} \stefan{Explain}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The multicore network model}
-\label{sec:model}
-
-% selecting hard
-Characteristics of the network influence the performance of
-distributed algorithms. 
-% model
-We express these network characteristics in a multicore network
-model. This model at this stage is by no means complete. We are going to
-extend it over time to address more complexities of current and future
-multicores.
-% static
-Our network model is \emph{static}, which in particular implies that
-we do not consider run-time effect such as congestion for the moment.
-
-% graph
-We represent the multicore network as a \emph{directed graph}. The nodes in
-this graph correspond to cores, and edges to communication channels
-between nodes. The machines we consider for now only have
-bi-directional communication links. Other machines (like the SCC) have
-uni-directional links, which is why we model the graph as directed
-graph.
-% shared memory -> fully meshed
-This graph is \emph{fully meshed} for shared memory machines. Every core can
-communicate with every other node via the cache coherence protocol.
-
-% machines hierarchical
-Multicore machines are hierarchical. Processor cores are grouped in
-NUMA nodes with shared caches. These NUMA nodes are then connected to
-each other by increasingly complex interconnect networks. 
-% NUMA affinity -> model
-We encode NUMA node affinity in our model. This allows to break down
-programming of a multicore machine into two distinct instances. We
-solve one instance of the problem between NUMA nodes, and then, in a
-second step, within each NUMA node. These two steps can be executed
-independently and different algorithms can be used in both case.
-
-% why it makes sense?
-If cores on the same NUMA node share a cache, it makes sense to
-leverage this hardware feature to implement shared-memory algorithms
-on top of it. %
-Communication across NUMA nodes is realized sending messages across
-the packet-based interconnect network. Using message-passing based
-implementations is the natural choice. %
-Shared memory algorithms and message-passing based algorithms can be
-composed together to program hierarchical machines similarly to what
-was previously shown for composing of shared-memory
-algorithms~\cite{Alistarh2012}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Node characteristics} 
-\label{sec:model_nodes}
-
-\stefan{Not sure yet if we really need this, but it should be helpful
-  for treating the machine hierarchically}
-
-Every node (i.e.\ core) in the system has characteristics associated
-with it.
-
-\begin{description}
-\item[NUMA affinity] A list of cores on the same NUMA node.
-\item[Synchrony] Synchronous systems are characterized by two
-  attributes: First, cores execute their programs in lock-steps and
-  second that message delivery time is bound.
-  % 
-  The existence of lock-steps implies the existence of a global time.
-  This is often true on multicore machines since cores are driven by
-  the same quartz or, if not, they are synchronized such that the
-  jitter is less than a cycle, which leads to cores seeing the same
-  time. %
-  Bounded delivery time is harder to reason about. CPUs on multicores
-  are typically time-multiplexed. On such systems, several programs
-  execute on the same processing unit one at a time. A scheduler
-  decides the order in which to run these applications. In very
-  contented systems, timely receipt of messages cannot be guaranteed
-  globally for all applications since many of them compete for a CPU
-  core. Even if we could guarantee timely delivery of messages by use
-  of a deterministic scheduler, worst-case propagation times would
-  still be orders of magnitude higher than best-case propagation
-  (which is essentially zero). \stefan{gang-scheduling?}
-\item[Failure] Can nodes fail? If so, how? (Byzantine, crash). We do
-  not consider failures at the moment, but believe that we will
-  inevitably have to do so for future multicores, where it is unlikely
-  that hardware can hide failures from software.
-\end{description}
-
-%-------------------------------------------------
-\subsection{NUMA characteristics}
-\label{sec:model_numa_nodes}
-
-\stefan{Maybe characteristics of NUMA nodes do not have to be encoded
-  separately, but as part of the node characteristics?}
-
-Some characteristics of multicore communication stem from the NUMA
-hierarchy. Thus, such characteristics can be encoded separately in the
-model.
-
-\begin{description}
-\item[hop count] Number of hops to every other NUMA node. The cost of
-  sending a message in a multicore machines does not so much depend on
-  the distance on the interconnect networks as on the number of hops
-  on such a path. Propagation on the wire is essentially for free due
-  to short distances between cores. %
-  On a multi-hop path, however, packages traversing the interconnect
-  need to be buffered. This is expensive. Depending on the machine,
-  some routing is executed on every intermediate route, which
-  increases the latency further.
-\item[hop count histogram] For every NUMA node, we want to know how
-  many other NUMA nodes can be reached with $n$ hops. This tells us
-  something about how well such nodes are connected to other NUMA
-  nodes. The intuition is that it makes sense to send a message to a
-  well connected NUMA node early in time, to ``spread'' out a message
-  as quickly as possible.
-\end{description}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Link characteristics} 
-\label{sec:model_links}
-
-The network model is defined by communication channels, which in turn
-are defined by a set of attributes (here sorted by priority):
-
-\begin{description}
-\item[cost breakdown] (quantitative) of message send cost:
-  dominating propagation time vs.\ dominating send and receive time on
-  multicores (per-node). Our model is currently limited to only the
-  breakdown of the cost for sending messages. Maybe we do not strictly
-  need to know about propagation time, as it is negligible independent
-  of were messages are sent. Relevant seems to be the number of hops
-  rather than the latency expressed in a concrete time.
-  \begin{description}
-  \item[send time] We assume this independent of which node we
-    communicate with (which is true for most of our machines when
-    using sender-side buffering)
-  \item[receive] On shared memory machines, receiving messages is
-    realized by reading a memory location. When the sender writes the
-    message, the receiver's copy of the cache-line is invalid. The
-    next read on it causes a transfer of the cache line from the
-    sender's to the receiver's cache, which seems to have a cost that
-    is growing with the number of hops on the interconnect for our
-    machines (although, on some machines, this is only roughly true:
-    communication with different NUMA nodes at the same interconnect
-    hop distance varies a bit. We ignore this fact for now.)
-  \end{description}
-\item[bounded delivery]
-\item[reliability] (loss, link failure, in-order delivery, phantoms,
-  corruption, duplicated messages): 
-  multicore interconnect networks often are
-\end{description}
-
-% Assumptions
-We assume that the cost of sending a message to the same node is 0,
-which is not true, since even using a highly optimized implementation
-for local communication (like LMP) has a non-negligible cost.
-
-% Limitations
-What we do not consider yet is link congestion.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Acquiring the model}
-
-% Model given
-We assume that the model is given. We just define one ourselves for
-now or build one manually for a particular machine. In a real-world
-scenario, this does not work. The model needs to be created
-automatically for a particular machine (due to the diversity of
-machines, and also the pace at which hardware changes)
-
-We now make up a machine model for evaluation. This model is based on
-a 8x4x1 AMD Barcelona machine. The topology of such a machine is shown
-in Figure~\ref{fig:gruyere}.
-
-Each of the eight NUMA nodes consists of four cores. We approximate the
-cost of sending messages within nodes as $1$ and across nodes as
-$10*num(hops)$.
-
-Send and receive time are $10$ each, i.e.\ in the order of propagation
-over a cross-NUMA link.
 
@@
   \begin{tikzpicture}[
-    xscale=.7,
-    yscale=.5,
-    every node/.style={draw,fill=red!10,minimum width=2cm,minimum height=1cm}
+    topo/.style={
+      draw,
+      minimum height=1cm,
+      minimum width=3cm,
+      rotate=90,
+    }
     ]
-    \node (c1) at ( 0, 4) {node 0};
-    \node (c2) at ( 4, 4) {node 1};
-    \node (c3) at ( 8, 4) {node 2};
-    \node (c4) at (12, 4) {node 3};
+    \node[draw] (model) {Model};
+    \node[draw] (sim) [left=of model] {Simulator};
 
-    \node (c5) at ( 0, 0) {node 4};
-    \node (c6) at ( 4, 0) {node 5};
-    \node (c7) at ( 8, 0) {node 6};
-    \node (c8) at (12, 0) {node 7};
+    \draw[fill=red!10]
+        ($(sim.north)+(0,1)+0*(.5,.2)$) rectangle +(1,3)
+            node[midway,rotate=90,anchor=south] {min spanning tree};
+    \draw[fill=red!10]
+        ($(sim.north)+(0,1)+1*(.5,.2)$) rectangle +(1,3) 
+            node[midway,rotate=90,anchor=south] {binary tree};
+    \draw[fill=red!10]
+        ($(sim.north)+(0,1)+2*(.5,.2)$) rectangle +(1,3) 
+            node[midway,rotate=90,anchor=south] {adaptive tree};
+    \draw[fill=red!10]
+        ($(sim.north)+(0,1)+3*(.5,.2)$) rectangle +(1,3)
+            node[midway,rotate=90,anchor=south] {sequential};
 
-    % top horizontal
-    \draw[thick] (c1) -- (c2);
-    \draw[thick] (c2) -- (c3);
-    \draw[thick] (c3) -- (c4);
-    % bottom horizontal
-    \draw[thick] (c5) -- (c6);
-    \draw[thick] (c6) -- (c7);
-    \draw[thick] (c7) -- (c8);
-    % vertical
-    \draw[thick] (c1) -- (c5);
-    \draw[thick] (c2) -- (c6);
-    \draw[thick] (c3) -- (c7);
-    \draw[thick] (c4) -- (c8);
-    % cross
-    \draw[thick] (c3) -- (c8);
-    \draw[thick] (c4) -- (c7);
-  \end{tikzpicture}
-  \caption{Interconnect topology of 8x4x1 AMD Barcelona machine}
-  \label{fig:gruyere}
-\end{figure}
+    \draw[->] (model.west) -- (sim.east) node[midway,above] {input};
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overlay selection}
-\label{sec:overlay}
-
-For a specific model, we now need to find ``the right'' implementation
-of algorithms to program it. We build our atomic broadcast based on a
-subset of links offered by the model such that all nodes of a given
-multicore machine can be reached. Atomic broadcast guarantees that 1)
-if one node receives a message, all other nodes receive it as well,
-and 2) that all nodes see the message in the same order.
-
-First, we discuss what kind of topologies we use to communicate
-between nodes. We evaluate tree based implementations: binary trees,
-minimum spanning trees, hierarchical tress and clustering
-techniques. Other potentially interesting topologies are rings.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Tree Topology}
-
-We now look at tree-based atomic broadcast implementations. The first
-challenge is to find efficient spanning trees for arbitrary
-machines. We now discuss different strategies to select trees based on
-the model representing the machine.
-
-Several optimizations are possible. First, nodes further up the tree
-should have a higher degree i.e.\ send more messages so that they do
-not idle~\cite{Bar-Noy1994}. An example of such a tree is a Fibonacci
-tree, which is known to be optimal for the case that send and receive
-time are equal~\cite{Bar-Noy1994}.
-
-In contrast, we assume that the model is given, which allows us to
-simulate sending messages along the broadcast tree. Whenever a node is
-idle in the model, it will send a message to one of the cores, that
-did not receive any messages yet. For the special case that send
-equals receive time, this should also yield a Fibonacci tree.
-
-%-------------------------------------------------
-\subsubsection{Binary Tree}
-
-A very \naive strategy to build a tree from machine models is the use
-of a binary tree with root in core 0. Every node $n$ has two children
-$2(n+1)-1$ and $2(n+1)$.
-
-The benefit of such a tree is that the time complexity is guaranteed
-to be $O(\log{n})$. The downside is that it is not considering the
-machine topology. Unnecessary communication across NUMA nodes might be
-introduced.
-
-We show an example for such a tree for a 8x4x1 AMD Barcelona machine
-(gruyere) in Figure~\ref{fig:qrm_tree_gruyere}.
-
-\begin{figure}
-  \input{qrm_tree_gruyere}
-  \caption{\Naive binary tree of cores for broadcast on gruyere}
-  \label{fig:qrm_tree_gruyere}
-\end{figure}
-
-%-------------------------------------------------
-\subsubsection{Minimum-Spanning Tree}
-\label{sec:mst_tree}
-
-We can apply a minimum spanning tree algorithm to the machine model
-graph to find a number of links such that these links connect all
-nodes at a minimum cost.
-
-We have implemented such an algorithm and found out, that it is not a
-good solution in the general case, since it does not consider
-parallelism. Naturally, we would like to parallelize send operations
-to different nodes, which allows them to send messages in parallel.
-
-An example is obvious in Figure~\ref{fig:mst_gruyere_operations}. The
-level of parallelism is only two. Cores 00 to 15 are dealt with in
-parallel to cores 16 to 31. Other than that, there is no further
-parallelism although it is possible to ``split up'' communication with
-every new ``round'' (i.e.\ send operations of nodes).
-
-An important variable in constructing such a tree is the degree of
-nodes. If the send cost $t_s$ is smaller than the propagation time
-$t_p$, $d = \lfloor \frac{t_p}{t_s} \rfloor$ messages can be send to
-hide propagation of messages. Hence, a tree with degree $d$ should be
-ideal to minimize latency. For multicore interconnect networks,
-however, we expect $d<1$. Thus, we do not look into this in detail
-right now.
-
-Reducing the degree of nodes also helps for the select operation. It
-reduces the number of memory locations to poll, and therefore the
-latency of detecting messages.
-
-We show the multicast tree automatically generated from a fully meshed
-machine model by applying a minimum spanning tree algorithm in
-Figure~\ref{fig:mst_gruyere}.
-
-\begin{figure}
-\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
-  \pgfsetlinewidth{1bp}
-\input{graphs/mst_gruyere}
-\end{tikzpicture}
-\caption{Multicast tree automatically found for a 8x4x1 multicore}
-\label{fig:mst_gruyere}
-\end{figure}
-
-%-------------------------------------------------
-\subsubsection{Hierarchical}
-
-We now consider NUMA node for coming up with a broadcast tree. We
-select one coordinator node in every node and build a binary tree
-for the coordinators. We call this topology connecting nodes across
-NUMA domains the \emph{outer} network.
-
-Each coordinator is also responsible for sending a message to all
-other cores of the node. We currently do this sequentially, since the
-number of cores in a node is typically very small. Alternatively, a
-binary tree could be used as well. We call overlay networks within
-NUMA nodes \emph{inner} networks.
-
-We show an example hierarchical tree in
-Figure~\ref{fig:gruyere_hierarchy}.
-
-\begin{figure}
-\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
-  \pgfsetlinewidth{.5bp}
-\input{graphs/final_gruyere_hierarchical}
-\end{tikzpicture}
-\caption{Hierarchical tree for a 8x4x1 multicore. Nodes 0, 4, 8, 12,
-  16, 20, 24 and 28 are coordinators. They are arranged in a binary
-  tree starting at node 0. Communication within NUMA nodes is
-  sequential (as an example: coordinator node 24 sends a message to
-  all cores on the same NUMA node, namely 25, 26 and 27)}
-\label{fig:gruyere_hierarchy}
-\end{figure}
-
-%-------------------------------------------------
-\subsubsection{Clustering}
-
-\stefan{Have not implemented this, but it might be interesting to try
-  out later}
-
-We discussed earlier in Section~\ref{sec:model} that
-multicore machines are hierarchical.%
-
-We divide the space into clusters. In every round, we further split up
-all cluster into smaller clusters and connect them with the minimal
-link.
-
-We find this link by searching for links that have start and
-end node in different regions of the most recent split. Out of these
-links, we pick the cheapest ones. We ignore links whose start or end
-node have a too high degree in the spanning tree already.
-
-Assuming that the choice of node IDs represents the topology to some
-extend, splitting them up into distinct clusters avoids contention, as
-two separate sub-trees are processed in different areas of the
-interconnect network.
-
-Another idea is to employ clustering on NUMA domains such that every
-NUMA domain corresponds to one cluster.
-
-%--------------------------------------------------
-\subsubsection{Adaptive Tree}
-
-\stefan{Describe how this works and how we pick links}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Ring topology}
-
-Next, we evaluate ring topologies. Rings experience a certain level of
-redundancy. The sending node receives the node back on the ring. This
-is unnecessary for applications with uni-directional traffic executed
-on reliable communication channels
-
-For applications that require some form of feedback (as well as
-unreliable channels, which we do not consider at this point), rings
-have the advantage that they can piggy-back some information that will
-eventually arrive back on the sender. This is beneficial for some
-algorithms such as quorums, where nodes report the result of the
-quorum back to the sender.
-
-The downside is that some state is required on every node to remember
-whether or not a message was received before. If messages are just
-forwarded as they arrive, message transport does never terminate.
-
-To add more parallelism, we add a second ring, which we send the
-message on in parallel. Acknowledgments, however, only work if
-forwarding along the ring is only done after all local nodes (as in
-nodes from the outer rings) acknowledge a message. In
-Figure~\ref{fig:gruyere_ring}, we visualize an example of two
-intertwined ring topologies. Node that the link from node 20 to 8 is a
-two hop link and, thus, has a cost of 20 instead of the usual 10.
-
-\begin{figure}
-\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
-  \pgfsetlinewidth{.5bp}
-\input{graphs/final_ring}
-\end{tikzpicture}
-\caption{Outer overlay as ring with sequential inner overlay for a
-  8x4x1 multicore}
-\label{fig:gruyere_ring}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Scheduling}
-\label{sec:scheduling}
-
-% Tree -> scheduling
-Assuming the tree (or some other kind of overlay network), there is a
-\emph{scheduling problems} for the order in which to send messages to
-children. The intuition is to send on long-delay links first to hide
-the more expensive latencies, as this link is dominating total send
-cost.
-
-In Figure~\ref{fig:mst_gruyere_operations}, we visualize sending of a
-broadcast message in \naive order. We use the MST given in
-Figure~\ref{fig:mst_gruyere}.  When core 08 sends its six messages, it
-does so in random order (here: in increasing node ID order). This is
-inefficient, as the latency of the broadcast is dominated by cores 12,
-24 and 28 rather than cores 9, 10 and 11.
-
-\begin{figure}[htb]
-  \centering
-  \begin{tikzpicture}[scale=.35,transform shape]
-    % Insert visualization
-    \input{visu_only_mst}
-  \end{tikzpicture}
-  \caption{Visualization of operations for sending a message along the
-    tree. Red boxes represent send operations, blue boxes represent
-    receive operations and arrows messages sent between cores. The
-    tree has been acquired using an MST algorithm.}
-  \label{fig:mst_gruyere_operations}
-\end{figure}
-
-In Figure~\ref{fig:mst_gruyere_operations_sorted} we schedule sending
-of messages based on link cost. We sort the outgoing edges by their
-weights and send on the most expensive links first. See
-Algorithm~\ref{algo:scheduling_link_weight}
-
-\begin{algorithm}[htb]
-\SetCommentSty{textc}
-\SetKwFunction{weight}{edge\_weight}%
-\SetKwFunction{sort}{sort\_by\_edge\_weight}%
-\SetKwFunction{icsend}{send}%
-  %
-  \KwData{Node $n$ sending messages, \\ %
-    broadcast tree as graph $(V, E)$, \\ %
-    weight function \weight{$E$}
-    %
-  }
-  % 
-  \BlankLine
-  $nb \leftarrow \{ c: \exists (self, c) \in E \}$\tcp*{Get children}
-  $nb \leftarrow $ \sort{$nb$, \weight{}}\tcp*{Sort by edge weight}
-  \For(\tcp*{For all children}){$c \leftarrow nb$}{
-    \icsend{$c$}
-  }
-  % 
-  \caption{Scheduling in order of outgoing link weight}
-  \label{algo:scheduling_link_weight}
-\end{algorithm}
-
-\begin{figure}[htb]
-  \centering
-  \begin{tikzpicture}[scale=.35,transform shape]
-    % Insert visualization
-    \input{visu_mst_sort}
-  \end{tikzpicture}
-  \caption{Visualization of operations for sending a message along the
-    tree. Red boxes represent send operations, blue boxes represent
-    receive operations and arrows messages sent between cores. After
-    running the MST algorithm, we optimize scheduling in every node to
-    send messages in decreasing order of their latency.}
-  \label{fig:mst_gruyere_operations_sorted}
-\end{figure}
-
-A better schedule for sending messages to the children of core 8 would
-be to start with the child from which the longest path emerges.
-
-\stefan{TODO: write down algorithm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Implementation}
-\label{sec:implementation}
-
-% Our implementation
-Assuming the tree, we now implement an atomic broadcast for multicore
-machines. Our implementation is based on the Barrelfish UMP
-interconnect driver. It provides reliable channels with in-order
-delivery and sender-side buffering \stefan{Verify this}. Flow control
-is build in for reliability. Communication starts at the root node,
-which acts as a sequentializer. See~\ref{algo:ab} for details.
-
-\begin{algorithm}[htb]
-\SetCommentSty{textc}
-\SetKwInOut{Assumptions}{assumptions}
-\Assumptions{Underlying communication channel is reliable and in-order}
-\SetKwProg{Fn}{Function}{}{end}%
-\SetKwFunction{receive}{on\_receive}%
-\SetKwFunction{waitchild}{wait\_for\_children}%
-\SetKwFunction{send}{send}%
-\SetKwFunction{icsend}{send\_bc\_request}%
-\SetKwFunction{icsendack}{send\_bc\_ack}%
-\SetKwFunction{handlemessages}{handle\_other\_messages}%
-  %
-  \KwData{List of processes $p$, broadcast tree as graph $(V, E)$}
-  \KwResult{Tree based atomic broadcast using a sequentializer}
-  % 
-  \BlankLine
-  \Fn(\tcp*{Receive a message}){\receive{$client$, $m$}}{
-    \For(\tcp*{For all children}){$c \leftarrow \{ c: \exists (self, c) \in E \} $}{
-      \icsend{c}
-    }
-    \waitchild{}\;
-    \icsendack{$client$}\;
-  }
-  % 
-  \BlankLine
-  \Fn(\tcp*{Send a message}){\send{void}}{
-    \tcc{Need to wait for acknowledgment before returning to
-      caller. Otherwise, sender might see his own request before some
-      other request, that the sequentializer decided to handle first}
-    \icsend{$V_{root}$}\tcp*{Relay msg (sequentializer)}
-    \While{no answer received}{
-      \handlemessages{}\tcp*{Otherwise, deadlocks}
-    }
-  }
-  \caption{Atomic broadcast on reliable communication channels}
-  \label{algo:ab}
-
-\end{algorithm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Issues with the Barrelfish implementation}
-
-When implementing the protocol in Barrelfish, we found several
-practical problems, which we will discuss briefly in this section.
-We kick-start our protocol connecting every process with all other
-processes to get a fully-meshed network of channels.
-We use a round-based algorithm to open channels. Then, every node
-knows exactly the source of an incoming connection. We formalize this
-algorithm in Algorithm~\ref{algo:ab_bind}.
-This is required for Barrelfish UMP communication channels since on
-bind, no source identifier is send along\footnote{Check if this is
-  actually true, and even if it is true, if is a Barrelfish problem,
-  and not a general one}.
-
-\begin{algorithm}[htb]
-  %
-  \SetKwInOut{Assumptions}{assumptions}
-  \Assumptions{Processes have unique contiguous
-    identifiers starting at 0}
-  \BlankLine
-  %
-  \SetKwArray{c}{channels}
-  \SetKwFunction{connectNode}{connectNode}
-  \SetKwFunction{listen}{listen}
-  \SetKwFunction{barrier}{barrier}
-  % 
-  \KwData{process id $p$, round $r$, %
-    each process an array of channels \c}
-  \KwResult{Fully-meshed network of processes}
-  % 
-  \BlankLine
-  %
-  $r \leftarrow 0$\;
-  \For{$i \leftarrow 0$ \KwTo $num(p)$}{
-    \eIf{$p=i$}{
-      \For{$o \leftarrow i+1$ \KwTo $num(p)$}{
-        \c{$o$} $\leftarrow$ \connectNode{$o$}\;
-      }
-    }{
-        \c{$i$} $\leftarrow$ \listen{}\;
-    }
-    \barrier{} \tcp*{Otherwise, reordering possible}
-  }
-  \caption{Establish fully-meshed network of channels}
-  \label{algo:ab_bind}
-\end{algorithm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Evaluation}
-
-\stefan{Compare to pure shared-memory implementations, otherwise
-  reviewers might argue that there is no need for distributed
-  algorithms.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Atomic broadcast}
-
-%--------------------------------------------------
-\subsubsection{Comparison to shared-memory implementations}
-
-A shared memory equivalent implementation for atomic broadcasts could
-be:
-\begin{itemize}
-\item Messages should (but don't have to be) cache-line size. This
-  prevents false-sharing. Larger messages can be fragmented. 
-\item A FIFO queue that guarantees the order of messages (and therefore
-  a lock)
-\item A counter that is incremented whenever a process reads the
-  message from the FIFO queue. To guarantee atomic broadcast
-  attributes, elements from the queue must not be removed before all
-  processes have read it.
-\end{itemize}
-
-This sounds pretty expensive. Need to evaluate this. The question is
-whether any sane person would use such a queue for high level
-applications. If so, which ones?
-
-There are some libraries providing synchronization primitives such as
-barriers, critical sections, atomic updates and locks.
-
-\begin{itemize}
-\item Is there an OpenMP equivalent? \emph{OpenMP} has a shared-memory
-  based programming model that is targeted to the HPC
-  world. \stefan{So what exactly is the relationship between OpenMP
-    and MPI? MPI seems to be more low-level. Does OpenMP implement
-    MPI?}
-\item \emph{Pthreads} also has a shared-memory model for low-end
-  systems~\cite{OpenMP_paper}
-\end{itemize}
-
-%-------------------------------------------------
-\subsubsection{Simulation}
-
-This section shows results for a simulation based on the model
-introduced in Section~\ref{sec:mst_tree}. The time given is a
-fictional time unit at this point.
-
-\begin{table}[htb]
-  \centering
-  \begin{tabular}{lllll}
-    \toprule
-    topology & scheduling & time & factor & figure \\
-    \midrule
-    MST & naive                     & 241 & 1.00 & 
-        \ref{fig:mst_gruyere_operations} \\
-    MST & highest link weight first & 151 & 0.63 & 
-        \ref{fig:mst_gruyere_operations_sorted} \\
-    MST & longest path first        & 151 & 0.63 & 
-        \stefan{? AFAIK, same as
-        \ref{fig:mst_gruyere_operations_sorted} } \\
-    hierarchical & highest link weight first & 151 & 0.63 &
-        \ref{fig:visu_hierarchy} \\
-    ring & highest link weight first & 181 & 0.75 &
-        \ref{fig:visu_ring} \\
-    \bottomrule
-  \end{tabular}
-  \caption{Simulation results for simplified machine model}
-  \label{tab:sim_results}
-\end{table}
-
-Scheduling based on the longest path does not make a difference for
-the current MST, but will be better in many cases. \stefan{We need to
-  find a model where this is actually true. But we also need to
-  evaluate if the increase in complexity is worth it}
-
-\begin{figure}[htb]
-  \centering
-  \begin{tikzpicture}[scale=.35,transform shape]
-    % Insert visualization
-    \input{visu_hierarchy}
-  \end{tikzpicture}
-  \caption{Visualization of hierarchical tree broadcast. A binary tree
-    spans across NUMA nodes followed by sequential send operations
-    within the NUMA node. %
-    Red boxes represent send operations, blue boxes represent receive
-    operations and arrows messages sent between cores.  }
-  \label{fig:visu_hierarchy}
-\end{figure}
-
-\begin{figure}[htb]
-  \centering
-  \begin{tikzpicture}[scale=.35,transform shape]
-    % Insert visualization
-    \input{visu_ring}
-  \end{tikzpicture}
-  \caption{Visualization of ring based broadcast. Two rings
-    spans across NUMA nodes followed by sequential send operations
-    within the NUMA node. %
-    Red boxes represent send operations, blue boxes represent receive
-    operations and arrows messages sent between
-    cores. \stefan{Scheduling is broken. If we want acks, we can only
-      forward a message along the ring when all the local nodes
-      acknowledge a message}}
-  \label{fig:visu_ring}
-\end{figure}
-
-%-------------------------------------------------
-\subsubsection{Real hardware}
-
-\stefan{Describe benchmark application} 
-\begin{itemize}
-\item One process on every core
-\item Management process on core 2 (i.e.\ not core 0)
-\item Uses atomic broadcast as described in Section~\ref{sec:implementation}
-\end{itemize}
-
-\paragraph{Binary tree on sbrinz2}
-
-Plot~\ref{pgfplot:201305101058} shows the time in cycles until a
-message send from core $n$ is received back via the broadcast tree
-show in Figure~\ref{fig:binary_tree_sbrinz2}. We were expecting
-increasing cost with the depth of the tree. If a message is sent from
-one of the leave nodes, it takes longer to receive this message back
-on the tree.
-
-The result is quite unexpected. We would expect nodes far down in the
-tree to experience a longer waiting time for receiving own messages
-back on the tree (due to more hops). This observation does not seem to
-be true.
-
-Lukas Humbel, who was also working on sbrinz1 was observing that the
-Barrelfish core IDs might not properly correspond to physical core
-IDs. This could explain the numbers we observe in our measurement.
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=\linewidth]{binary_tree_sbrinz2}
-  \caption{Binary tree for sbrinz2}
-  \label{fig:binary_tree_sbrinz2}
-\end{figure}
-
-\begin{figure}
-  \caption{Cost for receiving a message back on the tree. This is the
-    time for which the send call needs to be blocked to retain atomic
-    broadcast properties.}
-  \label{pgfplot:201305101058}
-  \begin{tikzpicture}
-    \begin{axis}[%
-        xlabel=sender core ID,%
-        ylabel={Cost [cycles]}%
-        ]
-    \addplot[%
-        color=red,%
-        mark=x,%  
-        error bars/y dir=both,%
-        error bars/y explicit%
-        ] coordinates {
-      (1,276.1) +- (291.3,291.3)
-      (2,876.1) +- (56.6,56.6)
-      (3,863.0) +- (108.3,108.3)
-      (4,899.7) +- (102.3,102.3)
-      (5,893.5) +- (44.5,44.5)
-      (6,880.5) +- (39.4,39.4)
-      (7,520.9) +- (41.7,41.7)
-      (8,171.9) +- (91.5,91.5)
-      (9,155.7) +- (51.4,51.4)
-      (10,174.6) +- (99.9,99.9)
-      (11,175.1) +- (99.3,99.3)
-      (12,154.5) +- (50.5,50.5)
-      (13,176.8) +- (109.7,109.7)
-      (14,173.1) +- (99.4,99.4)
-      (15,150.4) +- (43.3,43.3)
-    };
-    \end{axis}
+    \draw[->] (sim.north) -- +(0,5)
   \end{tikzpicture}
@@
 
-\paragraph{Older numbers}
-
-Plot~\ref{pgfplot:201303141819} shows the cost of flooding a sub-tree
-(with the 50\% worst measurements dropped). The group communication is
-based on a binary tree. Core 0 is the root, cores 1 and 2 are its
-children etc.
-
-The average cost is really high (probably a scheduling issue). But the
-minimal numbers show what is possible. The numbers achieved are easily
-explainable. The cost is increasing logarithmic with the number of
-nodes reached by the broadcast (as expected). Every level in the tree
-adds an additional 2500 to 3000 cycles to the tree. Node 0 takes
-significantly longer. I don't know yet why that is.
-
-\begin{figure}
-  \caption{Execution time for a broadcast with ACK on gruyere. The
-    cost is for execution for the sub-graph starting at the given
-    node. Refer to Figure~\ref{fig:qrm_tree_gruyere} for a
-    visualization of the broadcast tree used. }
-  \label{pgfplot:201303141819}
-  \begin{tikzpicture}
-    \begin{axis}[
-      xlabel=core id,
-      scaled y ticks = false, % prevent 10^x stuff
-      y tick label style={/pgf/number format/fixed},
-      ylabel={cost for subtree [cycles]}]
-    \addplot[
-      color=red,
-      very thin,
-      mark=*,
-      mark options={%
-        scale=.4
-      },
-      error bars/y dir=both,
-      error bars/y explicit] coordinates {
-      (0,9932.3) +- (564.4,564.4)
-      (1,8240.1) +- (298.5,298.5)
-      (2,8259.6) +- (549.4,549.4)
-      (3,6206.3) +- (225.1,225.1)
-      (4,5914.9) +- (399.2,399.2)
-      (5,6033.5) +- (462.2,462.2)
-      (6,6070.4) +- (434.3,434.3)
-      (7,4530.4) +- (188.6,188.6)
-      (8,3163.4) +- (246.1,246.1)
-      (9,3403.0) +- (285.3,285.3)
-      (10,3650.7) +- (336.5,336.5)
-      (11,3559.0) +- (318.8,318.8)
-      (12,3558.1) +- (284.8,284.8)
-      (13,3567.5) +- (304.5,304.5)
-      (14,3476.3) +- (290.2,290.2)
-      (15,2711.7) +- (151.9,151.9)
-      (16,614.0) +- (17.5,17.5)
-      (17,606.2) +- (17.3,17.3)
-      (18,636.2) +- (72.5,72.5)
-      (19,641.3) +- (46.3,46.3)
-      (20,583.8) +- (46.7,46.7)
-      (21,577.8) +- (38.3,38.3)
-      (22,561.8) +- (18.1,18.1)
-      (23,603.5) +- (56.6,56.6)
-      (24,589.0) +- (33.4,33.4)
-      (25,582.9) +- (33.2,33.2)
-      (26,571.7) +- (16.3,16.3)
-      (27,581.6) +- (36.6,36.6)
-      (28,564.0) +- (16.4,16.4)
-      (29,564.0) +- (20.8,20.8)
-      (30,551.6) +- (13.0,13.0)
-      (31,596.2) +- (51.4,51.4)
-    };
-    \end{axis}
-  \end{tikzpicture}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Related work}
-
-A multicore aware broadcast has been implemented in~\cite{Tu2008}. It
-takes the cache architecture of the machine (and only one particular?)
-into consideration for building the broadcast. It is however for
-larger messages (starting at 4K) and it does not seem to be performing
-very well (numbers are given in microseconds -6). 4K messages are 52
-microseconds, which is 150000 cycles. For synchronization primitives,
-a cache line is sufficient.
-
-Another tree implementation with MPI in mind was done
-in~\cite{Graham2008}. They have comparable numbers to what we found,
-but they cannot automatically tune to different machine
-characteristics. Our hypothesis is that we can do achieve higher
-average performance across a wide range of different multicore
-machines without manually adapting the implementation.
-
-Alistarh\etal~\cite{Alistarh2012} show composition of shared-memory
-algorithms that perform efficiently under different conditions at
-negligible overhead. A similar approach can potentially be applied to
-deal with diversity of multicore machines. However, we would have
-to extend it to support both shared-memory and message-passing
-implementations.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Future work}
-
-\newcommand{\nary}{$n$-ary\xspace}
-
-\begin{itemize}
-\item Keywords: decomposition~\cite{Cavage2013}
-\item Other topologies (mainly based on~\cite{Bruck1992}):
-  \begin{itemize}
-  \item Fibonacci trees: more efficient since nodes further up the
-    tree send more messages, but not considering the hierarchy of the
-    machine 
-  \item \nary trees: play with the out-degree of nodes. The ideal
-    value for the out-degree depends on the machine. For
-    $t_{propagation} << max(t_{send}, t_{receive})$, $n = 2$ should be
-    optimal, since it still increases parallelism, but the latency
-    induced by the $n$ send operation is not too high.
-  \end{itemize}
-\item Think about synchronous implementations and see if they are
-  applicable for some of our machines.
-\item Arguing that group communication/atomic broadcast is important
-  and showing that we can do it well might be enough (appeal to atomic
-  broadcasts as the foundation for other distributed algorithms, and
-  the MPI primitives, that can/need to be mapped to
-  group-communication (have a list of them)
-  \begin{itemize}
-  \item MPI\_Bcast: send a broadcast message to every node (including
-    the sending one)
-  \item MPI\_Scatter
-  \item MPI\_Gather
-  \item MPI\_Reduce
-  \end{itemize}
-  These primitives are synchronous. They return only once every other
-  node received the message. 
-\item Need higher-level applications, such as:
-  \begin{itemize}
-  \item capability system? \stefan{Ask Simon how expensive revocation
-      currently is}
-  \item a database with replication and consistency maintenance
-    \begin{itemize}
-    \item SharedDB? (buffers between operators, but no synchronization
-      except for access to buffers, which are multiple writers, one
-      reader)
-    \item Crescando (some kind of state machine replication)
-    \end{itemize}
-  \end{itemize}
-\item MPI collectives (as in~\cite{Tu2008})
-\item \emph{Load balancing in a tree} We could build several rings,
-  that do not always include all coordinators and work with read- and
-  write-sets. We can select these rings such that they nicely
-  integrate with the physical topology. They can also have different
-  sizes (e.g.\ a smaller one for read operations and larger ones for
-  writes).
-\item \emph{Aggregation for convergecast} %
-  Convergecast is a way of collecting information from nodes (i.e.\ it
-  is kind of the reverse of a broadcast). On the return path,
-  information can be aggregated. One example is batching, where several
-  pieces of information are grouped in the same message to reduce packet
-  processing overhead. Another example is aggregation, i.e.\
-  pre-processing of data. One example is pre-calculating the average
-  value of child messages if the sink node is not interested in
-  individual values. %
-  Similarly to what has been done in wireless sensor networks (where it
-  also matters to reduce the number of messages, but for other reasons:
-  power consumption), we can do aggregation in nodes. In difference to
-  traditional distributed systems, this works, because it is easy to
-  deploy custom software on every node in the network. Classical
-  distributed systems do not typically allow this. Furthermore, reducing
-  the number of messages at the price of higher complexity does not make
-  sense in classical systems. %
-  Examples for aggregation: number of nodes agreeing to something, find
-  capabilities (concatenate core ids). 
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Octopus}
-
-Octopus is a coordination service implementation for the Barrelfish
-Multikernel operating system based on a key-value store
-data-backend. It is, however, centralized. The idea is to make Octopus
-a decentralized application.
-
-For that, we extend Octopus such that it can be replicated within a
-multicore machine. This will retain scalability for future manycore
-machines and potentially outperform a centralized version of Octopus
-especially in contented systems.
-
-%--------------------------------------------------
-\subsubsection{Key-value store}
-
-One foundation block of Octopus is a key-value store. Since there is
-only one copy, the data in there is always consistent. If replicated,
-some sort of consistency guarantee would have to be implemented. One
-example is \emph{linearizability}, i.e.\ ``accesses occur one at a time
-in, some sequential order that is consistent with the order of
-invocations and responses''~\cite{lynch}.
-
-One concrete idea is to have one copy of the Octopus data-store
-replicated on every NUMA node. One core on every node acts as
-\emph{coordinator}, we call the other nodes \emph{slaves}.
-Coordinators communicate on a ring. Communication on a local NUMA node
-can be realized using read-only shared memory for read access. Write
-access needs to be globally ordered and hence communication with other
-replicas is required.
-
-Slaves direct their updates to the local coordinator. Coordinators
-send the update request $r$ along the ring and wait for them to be
-send back. While passing on requests, coordinators can set a flag to
-indicate conflicts. A conflict is another colliding request $r_o$ that
-is already in flight. I think we will have to send activity vectors
-along with this information! Otherwise, the coordinators requesting
-$r$ and $r_o$ will both prevent the other thing from happening and
-none of them will be applied! Maybe we need a two-phase commit.
-
-The idea of having a ring is somewhat related to SharedDB. It
-optimizes for throughput, not latency!
-
-%-------------------------------------------------
-\subsubsection{Synchronization}
-
-It is doubtful that a key-value store as a backend for synchronization
-primitives as we want to show efficiency rather than ease of use and
-flexibility. We probably rather want to implement new synchronization
-algorithms from scratch. See Section~\ref{barriers} for ideas.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Barriers}
-\label{barriers}
-
-The idea is to explore barrier implementations. The idea is to
-leverage information about the NUMA topology for better performance of
-barrier intensive workloads. Every NUMA node has a coordinator node,
-that knows how many threads on that node want to enter the
-barrier. There is only local communication (possibly using a
-share-memory implementation to exploit the shared cache) until the
-point where all NUMA local threads did enter the barrier.  Then there
-is ``global'' communication with other coordinators on other nodes
-using a message-passing based algorithm. We believe that this scales
-better than pure shared-memory implementations due to less
-interconnect contention.
-
-We will have to compare the performance of such an implementation with
-a purely shared-memory based implementation like pthreads and
-something entirely message-passing based like MPI versions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\bibliographystyle{plain}
-\bibliography{defs,db,mendeley}
-
-\label{LastPage}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{appendices}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{UMP performance}
-
-\input{graphs/ziger_ump_breakdown}
-
-\section{Shared memory performance}
-
-Plot~\ref{pgfplot:201306191213} shows some measurements for using a
-shared memory FIFO queue for communication. Core 0 sends message by
-enqueuing them to the FIFO, while all other cores poll on the queue
-for new messages.
-
-The measurement assumes the tsc clocks to be synchronized. The queues
-are also infinite. Messages are never garbage-collected.
-
-\begin{figure}
-  \caption{Shared memory FIFO performance on brie}
-  \label{pgfplot:201306191213}
-  \begin{tikzpicture}
-    \begin{axis}[
-      ybar,
-      error bars/y dir=both,%
-      error bars/y explicit,%
-      xlabel=core,
-      xtick={1,2,3},
-      ylabel={cost [cycles]}]
-
-    \addplot coordinates {
-      (1,488.6) +- (32.1,32.1)
-      (2,761.7) +- (124.1,124.1)
-      (3,862.5) +- (118.3,118.3)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-Plot~\ref{pgfplot:201306191238} shows the same experiment for tomme.
-
-\begin{figure}
-  \caption{Shared memory FIFO performance on tomme}
-  \label{pgfplot:201306191238}
-  \begin{tikzpicture}
-    \begin{axis}[
-      ybar,
-      error bars/y dir=both,
-      error bars/y explicit,
-      xlabel=core,
-      ylabel={Cost [cycles]}]
-    \addplot coordinates {
-      (1,417.6) +- (71.0,71.0)
-      (2,776.2) +- (110.4,110.4)
-      (3,774.6) +- (111.9,111.9)
-      (4,648.0) +- (175.9,175.9)
-      (5,551.2) +- (257.5,257.5)
-      (6,652.6) +- (179.2,179.2)
-      (7,688.6) +- (116.3,116.3)
-      (8,691.2) +- (133.0,133.0)
-      (9,721.6) +- (55.8,55.8)
-      (10,633.8) +- (135.0,135.0)
-      (11,673.8) +- (86.4,86.4)
-      (12,705.0) +- (81.8,81.8)
-      (13,612.6) +- (199.1,199.1)
-      (14,699.2) +- (90.3,90.3)
-      (15,691.6) +- (93.0,93.0)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-Plot~\ref{pgfplot:201306191603} shows it for gruyere. These do not
-make sense. The numbers are far too high, especially since gruyere is
-supposed to be synchronized.
-
-This suggest that my implementation is broken ..
-
-\begin{figure}
-  \caption{Plot}
-  \label{pgfplot:201306191603}
-  \begin{tikzpicture}
-    \begin{axis}[
-      ybar,
-      error bars/y dir=both,
-      error bars/y explicit,
-      xlabel=FIXME,
-      ylabel={Cost [cycles]}]
-    \addplot coordinates {
-      (1,2399.4) +- (3585.1,3585.1)
-      (2,8924.9) +- (11981.8,11981.8)
-      (3,4922.3) +- (4685.1,4685.1)
-      (4,6638.2) +- (3521.0,3521.0)
-      (5,5608.7) +- (4185.6,4185.6)
-      (6,5337.5) +- (3846.6,3846.6)
-      (7,5844.6) +- (2836.9,2836.9)
-      (8,5089.0) +- (3135.3,3135.3)
-      (9,5264.0) +- (3919.9,3919.9)
-      (10,5711.7) +- (3793.0,3793.0)
-      (11,5266.9) +- (3712.1,3712.1)
-      (12,8197.6) +- (3819.3,3819.3)
-      (13,8668.6) +- (3645.8,3645.8)
-      (14,8923.8) +- (2964.8,2964.8)
-      (15,7195.3) +- (2407.2,2407.2)
-      (16,8176.2) +- (3185.2,3185.2)
-      (17,8770.7) +- (3001.8,3001.8)
-      (18,4171.5) +- (2011.4,2011.4)
-      (19,8453.5) +- (3280.2,3280.2)
-      (20,13695.1) +- (3137.6,3137.6)
-      (21,13806.8) +- (2914.0,2914.0)
-      (22,13692.4) +- (2730.3,2730.3)
-      (23,14435.9) +- (2983.7,2983.7)
-      (24,9797.6) +- (3821.4,3821.4)
-      (25,8955.7) +- (4364.6,4364.6)
-      (26,7929.3) +- (3493.3,3493.3)
-      (27,11541.9) +- (3076.2,3076.2)
-      (28,10851.3) +- (4241.4,4241.4)
-      (29,8736.3) +- (3280.4,3280.4)
-      (30,11648.2) +- (2969.7,2969.7)
-      (31,7821.5) +- (2477.0,2477.0)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-Plot~\ref{pgfplot:201306191624} shows the same with more
-iterations. The result is not more stable than the one before,
-though.
-
-\begin{figure}
-  \caption{Plot}
-  \label{pgfplot:201306191624}
-  \begin{tikzpicture}
-    \begin{axis}[
-      ybar,
-      error bars/y dir=both,
-      error bars/y explicit,
-      xlabel=FIXME,
-      ylabel={Cost [cycles]}]
-    \addplot coordinates {
-      (1,11197.7) +- (8150.8,8150.8)
-      (2,10971.4) +- (6418.6,6418.6)
-      (3,10364.3) +- (7409.8,7409.8)
-      (4,9460.5) +- (6846.3,6846.3)
-      (5,11629.7) +- (7938.9,7938.9)
-      (6,12266.8) +- (8895.5,8895.5)
-      (7,12313.0) +- (8030.9,8030.9)
-      (8,13079.3) +- (7031.2,7031.2)
-      (9,10919.1) +- (6272.3,6272.3)
-      (10,4758.1) +- (3364.5,3364.5)
-      (11,4093.8) +- (2121.7,2121.7)
-      (12,10077.3) +- (1152.3,1152.3)
-      (13,8632.7) +- (1601.4,1601.4)
-      (14,6381.6) +- (1607.5,1607.5)
-      (15,8215.2) +- (1799.2,1799.2)
-      (16,6973.4) +- (1713.0,1713.0)
-      (17,8631.0) +- (1750.3,1750.3)
-      (18,13615.4) +- (2873.1,2873.1)
-      (19,11311.9) +- (1996.6,1996.6)
-      (20,17855.8) +- (2420.9,2420.9)
-      (21,15193.0) +- (1923.7,1923.7)
-      (22,18920.0) +- (2393.1,2393.1)
-      (23,19870.6) +- (2618.8,2618.8)
-      (24,17947.8) +- (4379.8,4379.8)
-      (25,21783.5) +- (4202.5,4202.5)
-      (26,24329.6) +- (3695.0,3695.0)
-      (27,22965.0) +- (3667.8,3667.8)
-      (28,20440.8) +- (4380.6,4380.6)
-      (29,17405.7) +- (4385.3,4385.3)
-      (30,19202.7) +- (4509.1,4509.1)
-      (31,21855.2) +- (3850.9,3850.9)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-\newpage
-\input{measurements/gruyere_topologies}
-
-Table~\ref{tab:ziger1} shows an overview of topologies for atomic
-broadcast on \ziger. We compare these numbers to cost-estimations from
-our simulator that incorporates detailed UMP breakdown measurements
-done on the same machine. Our estimations are close to what we observe
-when running on real hardware. In particular, the order of efficiency
-of the topologies matches reality.
-
-The only exception is sequential execution. Our simulator predicts
-much worse performance than actually given by hardware. We believe the
-cause for this could be hardware extensions (e.g.\ hardware broadcast
-units or snooping).
-
-What is particularly interesting is that a badly chosen tree with lots
-of communication across NUMA nodes is actually worse than sequentially
-sending messages.
-
-\input{measurements/ziger1_topologies}
-\input{measurements/sbrinz_topologies}
-\input{measurements/appenzeller_topologies}
-
-%\input{graphs/visall}
-
-\end{appendices}
-
 \end{document}

### 2013-07-02 graphs/numa_model.py
Moving to Laptop

@@ -2,6 +2,7 @@
 
 import model
 import helpers
+import re
 
 from pygraph.classes.graph import graph
 from pygraph.algorithms.minmax import shortest_path
@@ -89,6 +90,19 @@ class NUMAModel(model.Model):
 
         return g_numa
 
+    def _parse_receive_result_file(self, f):
+        """
+        Parse pairwise receive cost results measure with the UMP receive
+        benchmark in the Barrelfish tree.
 
+        We then use these measurements for the receive cost in the simulator
+        @param f: Handle to results.dat file of UMP latency benchmark
+        """
+        for l in f.readlines():
+            l = l.rstrip()
+            m = re.match('\d+\s+\d+\s+[0-9.]+\s+[0-9.]+', l)
+            if m:
+                print l
+        
         
 

### 2013-07-02 graphs/sbrinz.py

@@ -12,7 +12,11 @@ class Sbrinz(numa_model.NUMAModel):
 
     # From: ../results/ds_ump_receive-existing-sbrinz2-20130621-135817/results.dat
     # Note: the cost for accessing a one-hop node not uniform (but we keep it simple)
-    recv_cost = { 0: 10, 1: 30, 2: 47 }
+    # Keeping this for backward reference for now
+    # recv_cost = { 0: 10, 1: 30, 2: 47 }
+
+    # We now get the receive cost from a benchmark (usr/bench/ump/receive.c)
+    # recv_cost is stored in numa_model now
 
     def __init__(self):
         """
@@ -20,6 +24,8 @@ class Sbrinz(numa_model.NUMAModel):
         """
         g = super(Sbrinz, self)._build_graph()
         super(Sbrinz, self).__init__(g)
+        super(Sbrinz, self)._parse_receive_result_file(
+            open('measurements/receive_sbrinz'))
 
     # --------------------------------------------------
     # Characteritics of model

### 2013-07-02 graphs/simulator.py

@@ -83,13 +83,14 @@ def build_and_simulate():
     """
     # XXX The arguments are totally broken. Fix them!
     parser = argparse.ArgumentParser(
-        description='Simulator for multicore machines')
+        description=('Simulator for multicore machines. The default action is '
+        'to simulate the given combination of topology and machine'))
     parser.add_argument('--evaluate-model', dest="action", action="store_const",
                         const="evaluate", default="simulate", 
                         help="Dump machine model instead of simulating")
     parser.add_argument('--evaluate-machine', dest="action", action="store_const",
                         const="evaluate-machine", default="simulate", 
-                        help="Dump machine model instead of simulating")
+                        help="?")
     parser.add_argument('--evaluate-all-machines', dest="action", 
                         action="store_const",
                         const="evaluate-all-machines", default="simulate", 

### 2013-07-12 pitch.tex
AB pitch: Version sent to Kornilios

--- 2013-06-25 paper.tex
@@
 \usepackage[colorlinks=true]{hyperref}
-\usepackage[ruled,vlined]{algorithm2e}
+\usepackage[ruled]{algorithm2e}
 \usepackage[toc,page]{appendix}
@@
 % keywords: modeling, simulation, overlay networks, scheduling
+\newcommand{\ska}{$\rightarrow$\xspace}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\paragraph{What do you want to enable?} 
+Atomic broadcast for multicores. \stefan{Maybe even more high-level:
+  Performance of distributed algorithms like replication that are
+  built on top of AB}
 
-Distributed algorithms are increasingly used to overcome scalability
-challenges on multicore machines. Examples are
-databases~\cite{Salomie2011, Wiesmann2000} and operating
-systems~\cite{fos:osr09, tornado:osdi99, barrelfish:sosp09}.
+\paragraph{What problem are you solving, and why is it hard?} 
+Tuning of AB to machine characteristics. This is hard because
+multicores are complex hierarchical system. Furthermore, there is a
+huge variety of such machines with different characteristics
+influencing performance.
 
-% What do you want to enable?
-We want to investigate how to achieve better performance of atomic
-broadcast across a wide range of multicore machines without manually
-tuning the implementation to concrete machines.
+\paragraph{What new idea(s) will solve the problems?}
+Machine model for automatic tuning as well as use of hybrid
+implementations and composition to deal with hierarchies.
 
-% What problem are you solving, and why is it hard?
-The problem is complexity and diversity of modern multicore
-machines. Multicores come in many flavors depending on vendor and
-generation of the machine. All of these machines have fundamentally
-different characteristics such as number of nodes, NUMA
-characteristics, interconnect topologies, propagation time on
-interconnect and use of shared caches. These characteristics are hard~\cite{Cavage2013}
-to understand, but important to consider for application performance.
+\paragraph{How will you go about it?}
+Online measurements to augment Model \ska evaluation of different
+implementations for machine (also combination of message-passing and
+shared-memory) \ska pick best fit \ska auto-tune implementation
 
-% New ideas
-Instead of manually tuning algorithms to characteristics of individual
-machines, we automatically configure distributed algorithm
-implementations based on a machine model. We represent this model as an
-annotated graph. One question we are looking at is which information
-should actually be part of this machine model.
+\paragraph{How will you know and show it works?}
+Compare different AB implementations. Show that performance depends on
+machine. Show that our evaluation picks the best one. Verify
+performance benefit for high-level application.
 
-% How will you go about it?
-We base the configuration of algorithms on \emph{overlay networks}, which we
-automatically configure. We execute our configuration stage on a model
-representing the concrete machine the algorithm is intended to run
-on. %
-Our idea is to then explore different approaches for finding overlay
-networks based on the network model graph. Approaches we are currently
-investigating are: minimum spanning tree algorithms, binary trees,
-clustering techniques as well as treating the problem
-hierarchically. Assuming the overlay network, we then need to decide
-on every node which message to send first. This is a \emph{scheduling}
-problem.
+\paragraph{What's the related work?}
+People do shared-memory, as well as message passing based
+implementations. But not both simultaneously!? They also do automatic
+tuning of algorithms (e.g.\ load-balancing,
+parallel programs, databases according to workload, network stacks)
+but not for distributed algorithms on multicores?! \stefan{Guerraoui}
 
-% How do we show it works
-We auto-configure a wide range of different multicore machines and
-compare the performance of our implementation with hand-tuned
-implementations on all of these machines.
-% Hypothesis
-Our hypothesis is that automatic tuning of distributed algorithms 
-to machine characteristics is worth
-doing. Obviously, we cannot achieve performance of hand-tuned
-implementations, but we hope to get close enough to argue that loosing
-a bit of performance to avoid tedious manual reconfiguration is worth
-if for many applications (while others, where performance
-\emph{really} matters, might still want to manually configure their
-stuff).
-
-% three-step approach
-We break the problem down into three steps:
-\begin{inparaenum}[\itshape 1\upshape)]
-\item We first represent multicore machines by a model. We describe
-  this model in Section~\ref{sec:model},
-\item We then find an overlay for a concrete network model. This
-  overlay network describes a topology (such as a tree or a ring) for
-  communication within the machine. Algorithms to select overlay
-  networks are described in Section~\ref{sec:overlay}, and
-\item Given the overlay, we need to decide for every node in which
-  order to send messages. We investigate this scheduling problem in
-  Section~\ref{sec:scheduling}.
-\end{inparaenum}
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=\linewidth]{Overview_Model_Evaluation_Parser}
-  \caption{Overview of configuration of atomic broadcast using a Model 
-    \stefan{Draw figure properly}}
-  \label{fig:overview}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Distributed algorithms}
-\label{sec:distalgo}
-
-In order to evaluate our ideas, we pick two concrete distributed
-algorithms and implement them for a multicore machine:
-
-\paragraph{Atomic broadcast} An Atomic broadcasts is a broadcast
-messaging protocol that is reliable in the sense that if a message is
-received by one of the participating nodes, it is also received by all
-other nodes. Furthermore, the order of messages as seen by all
-participants is the same. Atomic broadcasts are frequently used to
-implement higher-level distributed algorithms on top of it: examples
-are replication such as state machine replication. As a first step, we
-evaluate the performance of sending one message as a broadcast to all
-nodes. Broadcasts are one of the most important communication
-operations for parallel applications~\cite{Bruck1992}. \stefan{Database
-  joins}.
-
-\paragraph{Barriers} \stefan{Explain}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The multicore network model}
-\label{sec:model}
-
-% selecting hard
-Characteristics of the network influence the performance of
-distributed algorithms. 
-% model
-We express these network characteristics in a multicore network
-model. This model at this stage is by no means complete. We are going to
-extend it over time to address more complexities of current and future
-multicores.
-% static
-Our network model is \emph{static}, which in particular implies that
-we do not consider run-time effect such as congestion for the moment.
-
-% graph
-We represent the multicore network as a \emph{directed graph}. The nodes in
-this graph correspond to cores, and edges to communication channels
-between nodes. The machines we consider for now only have
-bi-directional communication links. Other machines (like the SCC) have
-uni-directional links, which is why we model the graph as directed
-graph.
-% shared memory -> fully meshed
-This graph is \emph{fully meshed} for shared memory machines. Every core can
-communicate with every other node via the cache coherence protocol.
-
-% machines hierarchical
-Multicore machines are hierarchical. Processor cores are grouped in
-NUMA nodes with shared caches. These NUMA nodes are then connected to
-each other by increasingly complex interconnect networks. 
-% NUMA affinity -> model
-We encode NUMA node affinity in our model. This allows to break down
-programming of a multicore machine into two distinct instances. We
-solve one instance of the problem between NUMA nodes, and then, in a
-second step, within each NUMA node. These two steps can be executed
-independently and different algorithms can be used in both case.
-
-% why it makes sense?
-If cores on the same NUMA node share a cache, it makes sense to
-leverage this hardware feature to implement shared-memory algorithms
-on top of it. %
-Communication across NUMA nodes is realized sending messages across
-the packet-based interconnect network. Using message-passing based
-implementations is the natural choice. %
-Shared memory algorithms and message-passing based algorithms can be
-composed together to program hierarchical machines similarly to what
-was previously shown for composing of shared-memory
-algorithms~\cite{Alistarh2012}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Node characteristics} 
-\label{sec:model_nodes}
-
-\stefan{Not sure yet if we really need this, but it should be helpful
-  for treating the machine hierarchically}
-
-Every node (i.e.\ core) in the system has characteristics associated
-with it.
-
-\begin{description}
-\item[NUMA affinity] A list of cores on the same NUMA node.
-\item[Synchrony] Synchronous systems are characterized by two
-  attributes: First, cores execute their programs in lock-steps and
-  second that message delivery time is bound.
-  % 
-  The existence of lock-steps implies the existence of a global time.
-  This is often true on multicore machines since cores are driven by
-  the same quartz or, if not, they are synchronized such that the
-  jitter is less than a cycle, which leads to cores seeing the same
-  time. %
-  Bounded delivery time is harder to reason about. CPUs on multicores
-  are typically time-multiplexed. On such systems, several programs
-  execute on the same processing unit one at a time. A scheduler
-  decides the order in which to run these applications. In very
-  contented systems, timely receipt of messages cannot be guaranteed
-  globally for all applications since many of them compete for a CPU
-  core. Even if we could guarantee timely delivery of messages by use
-  of a deterministic scheduler, worst-case propagation times would
-  still be orders of magnitude higher than best-case propagation
-  (which is essentially zero). \stefan{gang-scheduling?}
-\item[Failure] Can nodes fail? If so, how? (Byzantine, crash). We do
-  not consider failures at the moment, but believe that we will
-  inevitably have to do so for future multicores, where it is unlikely
-  that hardware can hide failures from software.
-\end{description}
-
-%-------------------------------------------------
-\subsection{NUMA characteristics}
-\label{sec:model_numa_nodes}
-
-\stefan{Maybe characteristics of NUMA nodes do not have to be encoded
-  separately, but as part of the node characteristics?}
-
-Some characteristics of multicore communication stem from the NUMA
-hierarchy. Thus, such characteristics can be encoded separately in the
-model.
-
-\begin{description}
-\item[hop count] Number of hops to every other NUMA node. The cost of
-  sending a message in a multicore machines does not so much depend on
-  the distance on the interconnect networks as on the number of hops
-  on such a path. Propagation on the wire is essentially for free due
-  to short distances between cores. %
-  On a multi-hop path, however, packages traversing the interconnect
-  need to be buffered. This is expensive. Depending on the machine,
-  some routing is executed on every intermediate route, which
-  increases the latency further.
-\item[hop count histogram] For every NUMA node, we want to know how
-  many other NUMA nodes can be reached with $n$ hops. This tells us
-  something about how well such nodes are connected to other NUMA
-  nodes. The intuition is that it makes sense to send a message to a
-  well connected NUMA node early in time, to ``spread'' out a message
-  as quickly as possible.
-\end{description}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Link characteristics} 
-\label{sec:model_links}
-
-The network model is defined by communication channels, which in turn
-are defined by a set of attributes (here sorted by priority):
-
-\begin{description}
-\item[cost breakdown] (quantitative) of message send cost:
-  dominating propagation time vs.\ dominating send and receive time on
-  multicores (per-node). Our model is currently limited to only the
-  breakdown of the cost for sending messages. Maybe we do not strictly
-  need to know about propagation time, as it is negligible independent
-  of were messages are sent. Relevant seems to be the number of hops
-  rather than the latency expressed in a concrete time.
-  \begin{description}
-  \item[send time] We assume this independent of which node we
-    communicate with (which is true for most of our machines when
-    using sender-side buffering)
-  \item[receive] On shared memory machines, receiving messages is
-    realized by reading a memory location. When the sender writes the
-    message, the receiver's copy of the cache-line is invalid. The
-    next read on it causes a transfer of the cache line from the
-    sender's to the receiver's cache, which seems to have a cost that
-    is growing with the number of hops on the interconnect for our
-    machines (although, on some machines, this is only roughly true:
-    communication with different NUMA nodes at the same interconnect
-    hop distance varies a bit. We ignore this fact for now.)
-  \end{description}
-\item[bounded delivery]
-\item[reliability] (loss, link failure, in-order delivery, phantoms,
-  corruption, duplicated messages): 
-  multicore interconnect networks often are
-\end{description}
-
-% Assumptions
-We assume that the cost of sending a message to the same node is 0,
-which is not true, since even using a highly optimized implementation
-for local communication (like LMP) has a non-negligible cost.
-
-% Limitations
-What we do not consider yet is link congestion.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Acquiring the model}
-
-% Model given
-We assume that the model is given. We just define one ourselves for
-now or build one manually for a particular machine. In a real-world
-scenario, this does not work. The model needs to be created
-automatically for a particular machine (due to the diversity of
-machines, and also the pace at which hardware changes)
-
-We now make up a machine model for evaluation. This model is based on
-a 8x4x1 AMD Barcelona machine. The topology of such a machine is shown
-in Figure~\ref{fig:gruyere}.
-
-Each of the eight NUMA nodes consists of four cores. We approximate the
-cost of sending messages within nodes as $1$ and across nodes as
-$10*num(hops)$.
-
-Send and receive time are $10$ each, i.e.\ in the order of propagation
-over a cross-NUMA link.
-
-\begin{figure}[htb]
-  \centering
-  \begin{tikzpicture}[
-    xscale=.7,
-    yscale=.5,
-    every node/.style={draw,fill=red!10,minimum width=2cm,minimum height=1cm}
-    ]
-    \node (c1) at ( 0, 4) {node 0};
-    \node (c2) at ( 4, 4) {node 1};
-    \node (c3) at ( 8, 4) {node 2};
-    \node (c4) at (12, 4) {node 3};
-
-    \node (c5) at ( 0, 0) {node 4};
-    \node (c6) at ( 4, 0) {node 5};
-    \node (c7) at ( 8, 0) {node 6};
-    \node (c8) at (12, 0) {node 7};
-
-    % top horizontal
-    \draw[thick] (c1) -- (c2);
-    \draw[thick] (c2) -- (c3);
-    \draw[thick] (c3) -- (c4);
-    % bottom horizontal
-    \draw[thick] (c5) -- (c6);
-    \draw[thick] (c6) -- (c7);
-    \draw[thick] (c7) -- (c8);
-    % vertical
-    \draw[thick] (c1) -- (c5);
-    \draw[thick] (c2) -- (c6);
-    \draw[thick] (c3) -- (c7);
-    \draw[thick] (c4) -- (c8);
-    % cross
-    \draw[thick] (c3) -- (c8);
-    \draw[thick] (c4) -- (c7);
-  \end{tikzpicture}
-  \caption{Interconnect topology of 8x4x1 AMD Barcelona machine}
-  \label{fig:gruyere}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Overlay selection}
-\label{sec:overlay}
-
-For a specific model, we now need to find ``the right'' implementation
-of algorithms to program it. We build our atomic broadcast based on a
-subset of links offered by the model such that all nodes of a given
-multicore machine can be reached. Atomic broadcast guarantees that 1)
-if one node receives a message, all other nodes receive it as well,
-and 2) that all nodes see the message in the same order.
-
-First, we discuss what kind of topologies we use to communicate
-between nodes. We evaluate tree based implementations: binary trees,
-minimum spanning trees, hierarchical tress and clustering
-techniques. Other potentially interesting topologies are rings.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Tree Topology}
-
-We now look at tree-based atomic broadcast implementations. The first
-challenge is to find efficient spanning trees for arbitrary
-machines. We now discuss different strategies to select trees based on
-the model representing the machine.
-
-Several optimizations are possible. First, nodes further up the tree
-should have a higher degree i.e.\ send more messages so that they do
-not idle~\cite{Bar-Noy1994}. An example of such a tree is a Fibonacci
-tree, which is known to be optimal for the case that send and receive
-time are equal~\cite{Bar-Noy1994}.
-
-In contrast, we assume that the model is given, which allows us to
-simulate sending messages along the broadcast tree. Whenever a node is
-idle in the model, it will send a message to one of the cores, that
-did not receive any messages yet. For the special case that send
-equals receive time, this should also yield a Fibonacci tree.
-
-%-------------------------------------------------
-\subsubsection{Binary Tree}
-
-A very \naive strategy to build a tree from machine models is the use
-of a binary tree with root in core 0. Every node $n$ has two children
-$2(n+1)-1$ and $2(n+1)$.
-
-The benefit of such a tree is that the time complexity is guaranteed
-to be $O(\log{n})$. The downside is that it is not considering the
-machine topology. Unnecessary communication across NUMA nodes might be
-introduced.
-
-We show an example for such a tree for a 8x4x1 AMD Barcelona machine
-(gruyere) in Figure~\ref{fig:qrm_tree_gruyere}.
-
-\begin{figure}
-  \input{qrm_tree_gruyere}
-  \caption{\Naive binary tree of cores for broadcast on gruyere}
-  \label{fig:qrm_tree_gruyere}
-\end{figure}
-
-%-------------------------------------------------
-\subsubsection{Minimum-Spanning Tree}
-\label{sec:mst_tree}
-
-We can apply a minimum spanning tree algorithm to the machine model
-graph to find a number of links such that these links connect all
-nodes at a minimum cost.
-
-We have implemented such an algorithm and found out, that it is not a
-good solution in the general case, since it does not consider
-parallelism. Naturally, we would like to parallelize send operations
-to different nodes, which allows them to send messages in parallel.
-
-An example is obvious in Figure~\ref{fig:mst_gruyere_operations}. The
-level of parallelism is only two. Cores 00 to 15 are dealt with in
-parallel to cores 16 to 31. Other than that, there is no further
-parallelism although it is possible to ``split up'' communication with
-every new ``round'' (i.e.\ send operations of nodes).
-
-An important variable in constructing such a tree is the degree of
-nodes. If the send cost $t_s$ is smaller than the propagation time
-$t_p$, $d = \lfloor \frac{t_p}{t_s} \rfloor$ messages can be send to
-hide propagation of messages. Hence, a tree with degree $d$ should be
-ideal to minimize latency. For multicore interconnect networks,
-however, we expect $d<1$. Thus, we do not look into this in detail
-right now.
-
-Reducing the degree of nodes also helps for the select operation. It
-reduces the number of memory locations to poll, and therefore the
-latency of detecting messages.
-
-We show the multicast tree automatically generated from a fully meshed
-machine model by applying a minimum spanning tree algorithm in
-Figure~\ref{fig:mst_gruyere}.
-
-\begin{figure}
-\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
-  \pgfsetlinewidth{1bp}
-\input{graphs/mst_gruyere}
-\end{tikzpicture}
-\caption{Multicast tree automatically found for a 8x4x1 multicore}
-\label{fig:mst_gruyere}
-\end{figure}
-
-%-------------------------------------------------
-\subsubsection{Hierarchical}
-
-We now consider NUMA node for coming up with a broadcast tree. We
-select one coordinator node in every node and build a binary tree
-for the coordinators. We call this topology connecting nodes across
-NUMA domains the \emph{outer} network.
-
-Each coordinator is also responsible for sending a message to all
-other cores of the node. We currently do this sequentially, since the
-number of cores in a node is typically very small. Alternatively, a
-binary tree could be used as well. We call overlay networks within
-NUMA nodes \emph{inner} networks.
-
-We show an example hierarchical tree in
-Figure~\ref{fig:gruyere_hierarchy}.
-
-\begin{figure}
-\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
-  \pgfsetlinewidth{.5bp}
-\input{graphs/final_gruyere_hierarchical}
-\end{tikzpicture}
-\caption{Hierarchical tree for a 8x4x1 multicore. Nodes 0, 4, 8, 12,
-  16, 20, 24 and 28 are coordinators. They are arranged in a binary
-  tree starting at node 0. Communication within NUMA nodes is
-  sequential (as an example: coordinator node 24 sends a message to
-  all cores on the same NUMA node, namely 25, 26 and 27)}
-\label{fig:gruyere_hierarchy}
-\end{figure}
-
-%-------------------------------------------------
-\subsubsection{Clustering}
-
-\stefan{Have not implemented this, but it might be interesting to try
-  out later}
-
-We discussed earlier in Section~\ref{sec:model} that
-multicore machines are hierarchical.%
-
-We divide the space into clusters. In every round, we further split up
-all cluster into smaller clusters and connect them with the minimal
-link.
-
-We find this link by searching for links that have start and
-end node in different regions of the most recent split. Out of these
-links, we pick the cheapest ones. We ignore links whose start or end
-node have a too high degree in the spanning tree already.
-
-Assuming that the choice of node IDs represents the topology to some
-extend, splitting them up into distinct clusters avoids contention, as
-two separate sub-trees are processed in different areas of the
-interconnect network.
-
-Another idea is to employ clustering on NUMA domains such that every
-NUMA domain corresponds to one cluster.
-
-%--------------------------------------------------
-\subsubsection{Adaptive Tree}
-
-\stefan{Describe how this works and how we pick links}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Ring topology}
-
-Next, we evaluate ring topologies. Rings experience a certain level of
-redundancy. The sending node receives the node back on the ring. This
-is unnecessary for applications with uni-directional traffic executed
-on reliable communication channels
-
-For applications that require some form of feedback (as well as
-unreliable channels, which we do not consider at this point), rings
-have the advantage that they can piggy-back some information that will
-eventually arrive back on the sender. This is beneficial for some
-algorithms such as quorums, where nodes report the result of the
-quorum back to the sender.
-
-The downside is that some state is required on every node to remember
-whether or not a message was received before. If messages are just
-forwarded as they arrive, message transport does never terminate.
-
-To add more parallelism, we add a second ring, which we send the
-message on in parallel. Acknowledgments, however, only work if
-forwarding along the ring is only done after all local nodes (as in
-nodes from the outer rings) acknowledge a message. In
-Figure~\ref{fig:gruyere_ring}, we visualize an example of two
-intertwined ring topologies. Node that the link from node 20 to 8 is a
-two hop link and, thus, has a cost of 20 instead of the usual 10.
-
-\begin{figure}
-\begin{tikzpicture}[>=latex,line join=bevel,scale=.5]
-  \pgfsetlinewidth{.5bp}
-\input{graphs/final_ring}
-\end{tikzpicture}
-\caption{Outer overlay as ring with sequential inner overlay for a
-  8x4x1 multicore}
-\label{fig:gruyere_ring}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Scheduling}
-\label{sec:scheduling}
-
-% Tree -> scheduling
-Assuming the tree (or some other kind of overlay network), there is a
-\emph{scheduling problems} for the order in which to send messages to
-children. The intuition is to send on long-delay links first to hide
-the more expensive latencies, as this link is dominating total send
-cost.
-
-In Figure~\ref{fig:mst_gruyere_operations}, we visualize sending of a
-broadcast message in \naive order. We use the MST given in
-Figure~\ref{fig:mst_gruyere}.  When core 08 sends its six messages, it
-does so in random order (here: in increasing node ID order). This is
-inefficient, as the latency of the broadcast is dominated by cores 12,
-24 and 28 rather than cores 9, 10 and 11.
-
-\begin{figure}[htb]
-  \centering
-  \begin{tikzpicture}[scale=.35,transform shape]
-    % Insert visualization
-    \input{visu_only_mst}
-  \end{tikzpicture}
-  \caption{Visualization of operations for sending a message along the
-    tree. Red boxes represent send operations, blue boxes represent
-    receive operations and arrows messages sent between cores. The
-    tree has been acquired using an MST algorithm.}
-  \label{fig:mst_gruyere_operations}
-\end{figure}
-
-In Figure~\ref{fig:mst_gruyere_operations_sorted} we schedule sending
-of messages based on link cost. We sort the outgoing edges by their
-weights and send on the most expensive links first. See
-Algorithm~\ref{algo:scheduling_link_weight}
-
-\begin{algorithm}[htb]
-\SetCommentSty{textc}
-\SetKwFunction{weight}{edge\_weight}%
-\SetKwFunction{sort}{sort\_by\_edge\_weight}%
-\SetKwFunction{icsend}{send}%
-  %
-  \KwData{Node $n$ sending messages, \\ %
-    broadcast tree as graph $(V, E)$, \\ %
-    weight function \weight{$E$}
-    %
-  }
-  % 
-  \BlankLine
-  $nb \leftarrow \{ c: \exists (self, c) \in E \}$\tcp*{Get children}
-  $nb \leftarrow $ \sort{$nb$, \weight{}}\tcp*{Sort by edge weight}
-  \For(\tcp*{For all children}){$c \leftarrow nb$}{
-    \icsend{$c$}
-  }
-  % 
-  \caption{Scheduling in order of outgoing link weight}
-  \label{algo:scheduling_link_weight}
-\end{algorithm}
-
-\begin{figure}[htb]
-  \centering
-  \begin{tikzpicture}[scale=.35,transform shape]
-    % Insert visualization
-    \input{visu_mst_sort}
-  \end{tikzpicture}
-  \caption{Visualization of operations for sending a message along the
-    tree. Red boxes represent send operations, blue boxes represent
-    receive operations and arrows messages sent between cores. After
-    running the MST algorithm, we optimize scheduling in every node to
-    send messages in decreasing order of their latency.}
-  \label{fig:mst_gruyere_operations_sorted}
-\end{figure}
-
-A better schedule for sending messages to the children of core 8 would
-be to start with the child from which the longest path emerges.
-
-\stefan{TODO: write down algorithm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Implementation}
-\label{sec:implementation}
-
-% Our implementation
-Assuming the tree, we now implement an atomic broadcast for multicore
-machines. Our implementation is based on the Barrelfish UMP
-interconnect driver. It provides reliable channels with in-order
-delivery and sender-side buffering \stefan{Verify this}. Flow control
-is build in for reliability. Communication starts at the root node,
-which acts as a sequentializer. See~\ref{algo:ab} for details.
-
-\begin{algorithm}[htb]
-\SetCommentSty{textc}
-\SetKwInOut{Assumptions}{assumptions}
-\Assumptions{Underlying communication channel is reliable and in-order}
-\SetKwProg{Fn}{Function}{}{end}%
-\SetKwFunction{receive}{on\_receive}%
-\SetKwFunction{waitchild}{wait\_for\_children}%
-\SetKwFunction{send}{send}%
-\SetKwFunction{icsend}{send\_bc\_request}%
-\SetKwFunction{icsendack}{send\_bc\_ack}%
-\SetKwFunction{handlemessages}{handle\_other\_messages}%
-  %
-  \KwData{List of processes $p$, broadcast tree as graph $(V, E)$}
-  \KwResult{Tree based atomic broadcast using a sequentializer}
-  % 
-  \BlankLine
-  \Fn(\tcp*{Receive a message}){\receive{$client$, $m$}}{
-    \For(\tcp*{For all children}){$c \leftarrow \{ c: \exists (self, c) \in E \} $}{
-      \icsend{c}
-    }
-    \waitchild{}\;
-    \icsendack{$client$}\;
-  }
-  % 
-  \BlankLine
-  \Fn(\tcp*{Send a message}){\send{void}}{
-    \tcc{Need to wait for acknowledgment before returning to
-      caller. Otherwise, sender might see his own request before some
-      other request, that the sequentializer decided to handle first}
-    \icsend{$V_{root}$}\tcp*{Relay msg (sequentializer)}
-    \While{no answer received}{
-      \handlemessages{}\tcp*{Otherwise, deadlocks}
-    }
-  }
-  \caption{Atomic broadcast on reliable communication channels}
-  \label{algo:ab}
-
-\end{algorithm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Issues with the Barrelfish implementation}
-
-When implementing the protocol in Barrelfish, we found several
-practical problems, which we will discuss briefly in this section.
-We kick-start our protocol connecting every process with all other
-processes to get a fully-meshed network of channels.
-We use a round-based algorithm to open channels. Then, every node
-knows exactly the source of an incoming connection. We formalize this
-algorithm in Algorithm~\ref{algo:ab_bind}.
-This is required for Barrelfish UMP communication channels since on
-bind, no source identifier is send along\footnote{Check if this is
-  actually true, and even if it is true, if is a Barrelfish problem,
-  and not a general one}.
-
-\begin{algorithm}[htb]
-  %
-  \SetKwInOut{Assumptions}{assumptions}
-  \Assumptions{Processes have unique contiguous
-    identifiers starting at 0}
-  \BlankLine
-  %
-  \SetKwArray{c}{channels}
-  \SetKwFunction{connectNode}{connectNode}
-  \SetKwFunction{listen}{listen}
-  \SetKwFunction{barrier}{barrier}
-  % 
-  \KwData{process id $p$, round $r$, %
-    each process an array of channels \c}
-  \KwResult{Fully-meshed network of processes}
-  % 
-  \BlankLine
-  %
-  $r \leftarrow 0$\;
-  \For{$i \leftarrow 0$ \KwTo $num(p)$}{
-    \eIf{$p=i$}{
-      \For{$o \leftarrow i+1$ \KwTo $num(p)$}{
-        \c{$o$} $\leftarrow$ \connectNode{$o$}\;
-      }
-    }{
-        \c{$i$} $\leftarrow$ \listen{}\;
-    }
-    \barrier{} \tcp*{Otherwise, reordering possible}
-  }
-  \caption{Establish fully-meshed network of channels}
-  \label{algo:ab_bind}
-\end{algorithm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Evaluation}
-
-\stefan{Compare to pure shared-memory implementations, otherwise
-  reviewers might argue that there is no need for distributed
-  algorithms.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Atomic broadcast}
-
-%--------------------------------------------------
-\subsubsection{Comparison to shared-memory implementations}
-
-A shared memory equivalent implementation for atomic broadcasts could
-be:
-\begin{itemize}
-\item Messages should (but don't have to be) cache-line size. This
-  prevents false-sharing. Larger messages can be fragmented. 
-\item A FIFO queue that guarantees the order of messages (and therefore
-  a lock)
-\item A counter that is incremented whenever a process reads the
-  message from the FIFO queue. To guarantee atomic broadcast
-  attributes, elements from the queue must not be removed before all
-  processes have read it.
-\end{itemize}
-
-This sounds pretty expensive. Need to evaluate this. The question is
-whether any sane person would use such a queue for high level
-applications. If so, which ones?
-
-There are some libraries providing synchronization primitives such as
-barriers, critical sections, atomic updates and locks.
-
-\begin{itemize}
-\item Is there an OpenMP equivalent? \emph{OpenMP} has a shared-memory
-  based programming model that is targeted to the HPC
-  world. \stefan{So what exactly is the relationship between OpenMP
-    and MPI? MPI seems to be more low-level. Does OpenMP implement
-    MPI?}
-\item \emph{Pthreads} also has a shared-memory model for low-end
-  systems~\cite{OpenMP_paper}
-\end{itemize}
-
-%-------------------------------------------------
-\subsubsection{Simulation}
-
-This section shows results for a simulation based on the model
-introduced in Section~\ref{sec:mst_tree}. The time given is a
-fictional time unit at this point.
-
-\begin{table}[htb]
-  \centering
-  \begin{tabular}{lllll}
-    \toprule
-    topology & scheduling & time & factor & figure \\
-    \midrule
-    MST & naive                     & 241 & 1.00 & 
-        \ref{fig:mst_gruyere_operations} \\
-    MST & highest link weight first & 151 & 0.63 & 
-        \ref{fig:mst_gruyere_operations_sorted} \\
-    MST & longest path first        & 151 & 0.63 & 
-        \stefan{? AFAIK, same as
-        \ref{fig:mst_gruyere_operations_sorted} } \\
-    hierarchical & highest link weight first & 151 & 0.63 &
-        \ref{fig:visu_hierarchy} \\
-    ring & highest link weight first & 181 & 0.75 &
-        \ref{fig:visu_ring} \\
-    \bottomrule
-  \end{tabular}
-  \caption{Simulation results for simplified machine model}
-  \label{tab:sim_results}
-\end{table}
-
-Scheduling based on the longest path does not make a difference for
-the current MST, but will be better in many cases. \stefan{We need to
-  find a model where this is actually true. But we also need to
-  evaluate if the increase in complexity is worth it}
-
-\begin{figure}[htb]
-  \centering
-  \begin{tikzpicture}[scale=.35,transform shape]
-    % Insert visualization
-    \input{visu_hierarchy}
-  \end{tikzpicture}
-  \caption{Visualization of hierarchical tree broadcast. A binary tree
-    spans across NUMA nodes followed by sequential send operations
-    within the NUMA node. %
-    Red boxes represent send operations, blue boxes represent receive
-    operations and arrows messages sent between cores.  }
-  \label{fig:visu_hierarchy}
-\end{figure}
-
-\begin{figure}[htb]
-  \centering
-  \begin{tikzpicture}[scale=.35,transform shape]
-    % Insert visualization
-    \input{visu_ring}
-  \end{tikzpicture}
-  \caption{Visualization of ring based broadcast. Two rings
-    spans across NUMA nodes followed by sequential send operations
-    within the NUMA node. %
-    Red boxes represent send operations, blue boxes represent receive
-    operations and arrows messages sent between
-    cores. \stefan{Scheduling is broken. If we want acks, we can only
-      forward a message along the ring when all the local nodes
-      acknowledge a message}}
-  \label{fig:visu_ring}
-\end{figure}
-
-%-------------------------------------------------
-\subsubsection{Real hardware}
-
-\stefan{Describe benchmark application} 
-\begin{itemize}
-\item One process on every core
-\item Management process on core 2 (i.e.\ not core 0)
-\item Uses atomic broadcast as described in Section~\ref{sec:implementation}
-\end{itemize}
-
-\paragraph{Binary tree on sbrinz2}
-
-Plot~\ref{pgfplot:201305101058} shows the time in cycles until a
-message send from core $n$ is received back via the broadcast tree
-show in Figure~\ref{fig:binary_tree_sbrinz2}. We were expecting
-increasing cost with the depth of the tree. If a message is sent from
-one of the leave nodes, it takes longer to receive this message back
-on the tree.
-
-The result is quite unexpected. We would expect nodes far down in the
-tree to experience a longer waiting time for receiving own messages
-back on the tree (due to more hops). This observation does not seem to
-be true.
-
-Lukas Humbel, who was also working on sbrinz1 was observing that the
-Barrelfish core IDs might not properly correspond to physical core
-IDs. This could explain the numbers we observe in our measurement.
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=\linewidth]{binary_tree_sbrinz2}
-  \caption{Binary tree for sbrinz2}
-  \label{fig:binary_tree_sbrinz2}
-\end{figure}
-
-\begin{figure}
-  \caption{Cost for receiving a message back on the tree. This is the
-    time for which the send call needs to be blocked to retain atomic
-    broadcast properties.}
-  \label{pgfplot:201305101058}
-  \begin{tikzpicture}
-    \begin{axis}[%
-        xlabel=sender core ID,%
-        ylabel={Cost [cycles]}%
-        ]
-    \addplot[%
-        color=red,%
-        mark=x,%  
-        error bars/y dir=both,%
-        error bars/y explicit%
-        ] coordinates {
-      (1,276.1) +- (291.3,291.3)
-      (2,876.1) +- (56.6,56.6)
-      (3,863.0) +- (108.3,108.3)
-      (4,899.7) +- (102.3,102.3)
-      (5,893.5) +- (44.5,44.5)
-      (6,880.5) +- (39.4,39.4)
-      (7,520.9) +- (41.7,41.7)
-      (8,171.9) +- (91.5,91.5)
-      (9,155.7) +- (51.4,51.4)
-      (10,174.6) +- (99.9,99.9)
-      (11,175.1) +- (99.3,99.3)
-      (12,154.5) +- (50.5,50.5)
-      (13,176.8) +- (109.7,109.7)
-      (14,173.1) +- (99.4,99.4)
-      (15,150.4) +- (43.3,43.3)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-\paragraph{Older numbers}
-
-Plot~\ref{pgfplot:201303141819} shows the cost of flooding a sub-tree
-(with the 50\% worst measurements dropped). The group communication is
-based on a binary tree. Core 0 is the root, cores 1 and 2 are its
-children etc.
-
-The average cost is really high (probably a scheduling issue). But the
-minimal numbers show what is possible. The numbers achieved are easily
-explainable. The cost is increasing logarithmic with the number of
-nodes reached by the broadcast (as expected). Every level in the tree
-adds an additional 2500 to 3000 cycles to the tree. Node 0 takes
-significantly longer. I don't know yet why that is.
-
-\begin{figure}
-  \caption{Execution time for a broadcast with ACK on gruyere. The
-    cost is for execution for the sub-graph starting at the given
-    node. Refer to Figure~\ref{fig:qrm_tree_gruyere} for a
-    visualization of the broadcast tree used. }
-  \label{pgfplot:201303141819}
-  \begin{tikzpicture}
-    \begin{axis}[
-      xlabel=core id,
-      scaled y ticks = false, % prevent 10^x stuff
-      y tick label style={/pgf/number format/fixed},
-      ylabel={cost for subtree [cycles]}]
-    \addplot[
-      color=red,
-      very thin,
-      mark=*,
-      mark options={%
-        scale=.4
-      },
-      error bars/y dir=both,
-      error bars/y explicit] coordinates {
-      (0,9932.3) +- (564.4,564.4)
-      (1,8240.1) +- (298.5,298.5)
-      (2,8259.6) +- (549.4,549.4)
-      (3,6206.3) +- (225.1,225.1)
-      (4,5914.9) +- (399.2,399.2)
-      (5,6033.5) +- (462.2,462.2)
-      (6,6070.4) +- (434.3,434.3)
-      (7,4530.4) +- (188.6,188.6)
-      (8,3163.4) +- (246.1,246.1)
-      (9,3403.0) +- (285.3,285.3)
-      (10,3650.7) +- (336.5,336.5)
-      (11,3559.0) +- (318.8,318.8)
-      (12,3558.1) +- (284.8,284.8)
-      (13,3567.5) +- (304.5,304.5)
-      (14,3476.3) +- (290.2,290.2)
-      (15,2711.7) +- (151.9,151.9)
-      (16,614.0) +- (17.5,17.5)
-      (17,606.2) +- (17.3,17.3)
-      (18,636.2) +- (72.5,72.5)
-      (19,641.3) +- (46.3,46.3)
-      (20,583.8) +- (46.7,46.7)
-      (21,577.8) +- (38.3,38.3)
-      (22,561.8) +- (18.1,18.1)
-      (23,603.5) +- (56.6,56.6)
-      (24,589.0) +- (33.4,33.4)
-      (25,582.9) +- (33.2,33.2)
-      (26,571.7) +- (16.3,16.3)
-      (27,581.6) +- (36.6,36.6)
-      (28,564.0) +- (16.4,16.4)
-      (29,564.0) +- (20.8,20.8)
-      (30,551.6) +- (13.0,13.0)
-      (31,596.2) +- (51.4,51.4)
-    };
-    \end{axis}
-  \end{tikzpicture}
-
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Related work}
-
-A multicore aware broadcast has been implemented in~\cite{Tu2008}. It
-takes the cache architecture of the machine (and only one particular?)
-into consideration for building the broadcast. It is however for
-larger messages (starting at 4K) and it does not seem to be performing
-very well (numbers are given in microseconds -6). 4K messages are 52
-microseconds, which is 150000 cycles. For synchronization primitives,
-a cache line is sufficient.
-
-Another tree implementation with MPI in mind was done
-in~\cite{Graham2008}. They have comparable numbers to what we found,
-but they cannot automatically tune to different machine
-characteristics. Our hypothesis is that we can do achieve higher
-average performance across a wide range of different multicore
-machines without manually adapting the implementation.
-
-Alistarh\etal~\cite{Alistarh2012} show composition of shared-memory
-algorithms that perform efficiently under different conditions at
-negligible overhead. A similar approach can potentially be applied to
-deal with diversity of multicore machines. However, we would have
-to extend it to support both shared-memory and message-passing
-implementations.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Future work}
-
-\newcommand{\nary}{$n$-ary\xspace}
-
-\begin{itemize}
-\item Keywords: decomposition~\cite{Cavage2013}
-\item Other topologies (mainly based on~\cite{Bruck1992}):
-  \begin{itemize}
-  \item Fibonacci trees: more efficient since nodes further up the
-    tree send more messages, but not considering the hierarchy of the
-    machine 
-  \item \nary trees: play with the out-degree of nodes. The ideal
-    value for the out-degree depends on the machine. For
-    $t_{propagation} << max(t_{send}, t_{receive})$, $n = 2$ should be
-    optimal, since it still increases parallelism, but the latency
-    induced by the $n$ send operation is not too high.
-  \end{itemize}
-\item Think about synchronous implementations and see if they are
-  applicable for some of our machines.
-\item Arguing that group communication/atomic broadcast is important
-  and showing that we can do it well might be enough (appeal to atomic
-  broadcasts as the foundation for other distributed algorithms, and
-  the MPI primitives, that can/need to be mapped to
-  group-communication (have a list of them)
-  \begin{itemize}
-  \item MPI\_Bcast: send a broadcast message to every node (including
-    the sending one)
-  \item MPI\_Scatter
-  \item MPI\_Gather
-  \item MPI\_Reduce
-  \end{itemize}
-  These primitives are synchronous. They return only once every other
-  node received the message. 
-\item Need higher-level applications, such as:
-  \begin{itemize}
-  \item capability system? \stefan{Ask Simon how expensive revocation
-      currently is}
-  \item a database with replication and consistency maintenance
-    \begin{itemize}
-    \item SharedDB? (buffers between operators, but no synchronization
-      except for access to buffers, which are multiple writers, one
-      reader)
-    \item Crescando (some kind of state machine replication)
-    \end{itemize}
-  \end{itemize}
-\item MPI collectives (as in~\cite{Tu2008})
-\item \emph{Load balancing in a tree} We could build several rings,
-  that do not always include all coordinators and work with read- and
-  write-sets. We can select these rings such that they nicely
-  integrate with the physical topology. They can also have different
-  sizes (e.g.\ a smaller one for read operations and larger ones for
-  writes).
-\item \emph{Aggregation for convergecast} %
-  Convergecast is a way of collecting information from nodes (i.e.\ it
-  is kind of the reverse of a broadcast). On the return path,
-  information can be aggregated. One example is batching, where several
-  pieces of information are grouped in the same message to reduce packet
-  processing overhead. Another example is aggregation, i.e.\
-  pre-processing of data. One example is pre-calculating the average
-  value of child messages if the sink node is not interested in
-  individual values. %
-  Similarly to what has been done in wireless sensor networks (where it
-  also matters to reduce the number of messages, but for other reasons:
-  power consumption), we can do aggregation in nodes. In difference to
-  traditional distributed systems, this works, because it is easy to
-  deploy custom software on every node in the network. Classical
-  distributed systems do not typically allow this. Furthermore, reducing
-  the number of messages at the price of higher complexity does not make
-  sense in classical systems. %
-  Examples for aggregation: number of nodes agreeing to something, find
-  capabilities (concatenate core ids). 
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Octopus}
-
-Octopus is a coordination service implementation for the Barrelfish
-Multikernel operating system based on a key-value store
-data-backend. It is, however, centralized. The idea is to make Octopus
-a decentralized application.
-
-For that, we extend Octopus such that it can be replicated within a
-multicore machine. This will retain scalability for future manycore
-machines and potentially outperform a centralized version of Octopus
-especially in contented systems.
-
-%--------------------------------------------------
-\subsubsection{Key-value store}
-
-One foundation block of Octopus is a key-value store. Since there is
-only one copy, the data in there is always consistent. If replicated,
-some sort of consistency guarantee would have to be implemented. One
-example is \emph{linearizability}, i.e.\ ``accesses occur one at a time
-in, some sequential order that is consistent with the order of
-invocations and responses''~\cite{lynch}.
-
-One concrete idea is to have one copy of the Octopus data-store
-replicated on every NUMA node. One core on every node acts as
-\emph{coordinator}, we call the other nodes \emph{slaves}.
-Coordinators communicate on a ring. Communication on a local NUMA node
-can be realized using read-only shared memory for read access. Write
-access needs to be globally ordered and hence communication with other
-replicas is required.
-
-Slaves direct their updates to the local coordinator. Coordinators
-send the update request $r$ along the ring and wait for them to be
-send back. While passing on requests, coordinators can set a flag to
-indicate conflicts. A conflict is another colliding request $r_o$ that
-is already in flight. I think we will have to send activity vectors
-along with this information! Otherwise, the coordinators requesting
-$r$ and $r_o$ will both prevent the other thing from happening and
-none of them will be applied! Maybe we need a two-phase commit.
-
-The idea of having a ring is somewhat related to SharedDB. It
-optimizes for throughput, not latency!
-
-%-------------------------------------------------
-\subsubsection{Synchronization}
-
-It is doubtful that a key-value store as a backend for synchronization
-primitives as we want to show efficiency rather than ease of use and
-flexibility. We probably rather want to implement new synchronization
-algorithms from scratch. See Section~\ref{barriers} for ideas.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Barriers}
-\label{barriers}
-
-The idea is to explore barrier implementations. The idea is to
-leverage information about the NUMA topology for better performance of
-barrier intensive workloads. Every NUMA node has a coordinator node,
-that knows how many threads on that node want to enter the
-barrier. There is only local communication (possibly using a
-share-memory implementation to exploit the shared cache) until the
-point where all NUMA local threads did enter the barrier.  Then there
-is ``global'' communication with other coordinators on other nodes
-using a message-passing based algorithm. We believe that this scales
-better than pure shared-memory implementations due to less
-interconnect contention.
-
-We will have to compare the performance of such an implementation with
-a purely shared-memory based implementation like pthreads and
-something entirely message-passing based like MPI versions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\bibliographystyle{plain}
-\bibliography{defs,db,mendeley}
-
-\label{LastPage}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{appendices}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{UMP performance}
-
-\input{graphs/ziger_ump_breakdown}
-
-\section{Shared memory performance}
-
-Plot~\ref{pgfplot:201306191213} shows some measurements for using a
-shared memory FIFO queue for communication. Core 0 sends message by
-enqueuing them to the FIFO, while all other cores poll on the queue
-for new messages.
-
-The measurement assumes the tsc clocks to be synchronized. The queues
-are also infinite. Messages are never garbage-collected.
-
-\begin{figure}
-  \caption{Shared memory FIFO performance on brie}
-  \label{pgfplot:201306191213}
-  \begin{tikzpicture}
-    \begin{axis}[
-      ybar,
-      error bars/y dir=both,%
-      error bars/y explicit,%
-      xlabel=core,
-      xtick={1,2,3},
-      ylabel={cost [cycles]}]
-
-    \addplot coordinates {
-      (1,488.6) +- (32.1,32.1)
-      (2,761.7) +- (124.1,124.1)
-      (3,862.5) +- (118.3,118.3)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-Plot~\ref{pgfplot:201306191238} shows the same experiment for tomme.
-
-\begin{figure}
-  \caption{Shared memory FIFO performance on tomme}
-  \label{pgfplot:201306191238}
-  \begin{tikzpicture}
-    \begin{axis}[
-      ybar,
-      error bars/y dir=both,
-      error bars/y explicit,
-      xlabel=core,
-      ylabel={Cost [cycles]}]
-    \addplot coordinates {
-      (1,417.6) +- (71.0,71.0)
-      (2,776.2) +- (110.4,110.4)
-      (3,774.6) +- (111.9,111.9)
-      (4,648.0) +- (175.9,175.9)
-      (5,551.2) +- (257.5,257.5)
-      (6,652.6) +- (179.2,179.2)
-      (7,688.6) +- (116.3,116.3)
-      (8,691.2) +- (133.0,133.0)
-      (9,721.6) +- (55.8,55.8)
-      (10,633.8) +- (135.0,135.0)
-      (11,673.8) +- (86.4,86.4)
-      (12,705.0) +- (81.8,81.8)
-      (13,612.6) +- (199.1,199.1)
-      (14,699.2) +- (90.3,90.3)
-      (15,691.6) +- (93.0,93.0)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-Plot~\ref{pgfplot:201306191603} shows it for gruyere. These do not
-make sense. The numbers are far too high, especially since gruyere is
-supposed to be synchronized.
-
-This suggest that my implementation is broken ..
-
-\begin{figure}
-  \caption{Plot}
-  \label{pgfplot:201306191603}
-  \begin{tikzpicture}
-    \begin{axis}[
-      ybar,
-      error bars/y dir=both,
-      error bars/y explicit,
-      xlabel=FIXME,
-      ylabel={Cost [cycles]}]
-    \addplot coordinates {
-      (1,2399.4) +- (3585.1,3585.1)
-      (2,8924.9) +- (11981.8,11981.8)
-      (3,4922.3) +- (4685.1,4685.1)
-      (4,6638.2) +- (3521.0,3521.0)
-      (5,5608.7) +- (4185.6,4185.6)
-      (6,5337.5) +- (3846.6,3846.6)
-      (7,5844.6) +- (2836.9,2836.9)
-      (8,5089.0) +- (3135.3,3135.3)
-      (9,5264.0) +- (3919.9,3919.9)
-      (10,5711.7) +- (3793.0,3793.0)
-      (11,5266.9) +- (3712.1,3712.1)
-      (12,8197.6) +- (3819.3,3819.3)
-      (13,8668.6) +- (3645.8,3645.8)
-      (14,8923.8) +- (2964.8,2964.8)
-      (15,7195.3) +- (2407.2,2407.2)
-      (16,8176.2) +- (3185.2,3185.2)
-      (17,8770.7) +- (3001.8,3001.8)
-      (18,4171.5) +- (2011.4,2011.4)
-      (19,8453.5) +- (3280.2,3280.2)
-      (20,13695.1) +- (3137.6,3137.6)
-      (21,13806.8) +- (2914.0,2914.0)
-      (22,13692.4) +- (2730.3,2730.3)
-      (23,14435.9) +- (2983.7,2983.7)
-      (24,9797.6) +- (3821.4,3821.4)
-      (25,8955.7) +- (4364.6,4364.6)
-      (26,7929.3) +- (3493.3,3493.3)
-      (27,11541.9) +- (3076.2,3076.2)
-      (28,10851.3) +- (4241.4,4241.4)
-      (29,8736.3) +- (3280.4,3280.4)
-      (30,11648.2) +- (2969.7,2969.7)
-      (31,7821.5) +- (2477.0,2477.0)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-Plot~\ref{pgfplot:201306191624} shows the same with more
-iterations. The result is not more stable than the one before,
-though.
-
-\begin{figure}
-  \caption{Plot}
-  \label{pgfplot:201306191624}
-  \begin{tikzpicture}
-    \begin{axis}[
-      ybar,
-      error bars/y dir=both,
-      error bars/y explicit,
-      xlabel=FIXME,
-      ylabel={Cost [cycles]}]
-    \addplot coordinates {
-      (1,11197.7) +- (8150.8,8150.8)
-      (2,10971.4) +- (6418.6,6418.6)
-      (3,10364.3) +- (7409.8,7409.8)
-      (4,9460.5) +- (6846.3,6846.3)
-      (5,11629.7) +- (7938.9,7938.9)
-      (6,12266.8) +- (8895.5,8895.5)
-      (7,12313.0) +- (8030.9,8030.9)
-      (8,13079.3) +- (7031.2,7031.2)
-      (9,10919.1) +- (6272.3,6272.3)
-      (10,4758.1) +- (3364.5,3364.5)
-      (11,4093.8) +- (2121.7,2121.7)
-      (12,10077.3) +- (1152.3,1152.3)
-      (13,8632.7) +- (1601.4,1601.4)
-      (14,6381.6) +- (1607.5,1607.5)
-      (15,8215.2) +- (1799.2,1799.2)
-      (16,6973.4) +- (1713.0,1713.0)
-      (17,8631.0) +- (1750.3,1750.3)
-      (18,13615.4) +- (2873.1,2873.1)
-      (19,11311.9) +- (1996.6,1996.6)
-      (20,17855.8) +- (2420.9,2420.9)
-      (21,15193.0) +- (1923.7,1923.7)
-      (22,18920.0) +- (2393.1,2393.1)
-      (23,19870.6) +- (2618.8,2618.8)
-      (24,17947.8) +- (4379.8,4379.8)
-      (25,21783.5) +- (4202.5,4202.5)
-      (26,24329.6) +- (3695.0,3695.0)
-      (27,22965.0) +- (3667.8,3667.8)
-      (28,20440.8) +- (4380.6,4380.6)
-      (29,17405.7) +- (4385.3,4385.3)
-      (30,19202.7) +- (4509.1,4509.1)
-      (31,21855.2) +- (3850.9,3850.9)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-\newpage
-\input{measurements/gruyere_topologies}
-
-Table~\ref{tab:ziger1} shows an overview of topologies for atomic
-broadcast on \ziger. We compare these numbers to cost-estimations from
-our simulator that incorporates detailed UMP breakdown measurements
-done on the same machine. Our estimations are close to what we observe
-when running on real hardware. In particular, the order of efficiency
-of the topologies matches reality.
-
-The only exception is sequential execution. Our simulator predicts
-much worse performance than actually given by hardware. We believe the
-cause for this could be hardware extensions (e.g.\ hardware broadcast
-units or snooping).
-
-What is particularly interesting is that a badly chosen tree with lots
-of communication across NUMA nodes is actually worse than sequentially
-sending messages.
-
-\input{measurements/ziger1_topologies}
-\input{measurements/sbrinz_topologies}
-\input{measurements/appenzeller_topologies}
-
-%\input{graphs/visall}
-
-\end{appendices}
+\paragraph{What is your hypothesis?}
+We can do better with hybrid models. Automatic tuning achieves good
+performance, without programmers having to deal with complex hardware details.
 

### 2013-07-24 paper.tex
Rerun of all (gruyere, gottardo, sbrinz, tomme, ziger) UMP breakdowns to refine models and all topologies with the new models

@@
 other nodes. Furthermore, the order of messages as seen by all
-participants is the same. Atomic broadcasts are frequently used to
-implement higher-level distributed algorithms on top of it: examples
-are replication such as state machine replication. As a first step, we
-evaluate the performance of sending one message as a broadcast to all
+participants is the same. Messages are immutable, i.e.\ all receivers
+read exactly the same message.
+
+Atomic broadcasts are frequently used to implement higher-level
+distributed algorithms on top of it: examples are replication such as
+state machine replication. As a first step, we evaluate the
+performance of sending one message as a broadcast to all
 nodes. Broadcasts are one of the most important communication
-operations for parallel applications~\cite{Bruck1992}. \stefan{Database
-  joins}.
+operations for parallel applications~\cite{Bruck1992}.%
+\stefan{Also: Database joins}.
 
@@
 
-\stefan{Have not implemented this, but it might be interesting to try
-  out later}
-
 We discussed earlier in Section~\ref{sec:model} that
-multicore machines are hierarchical.%
-
-We divide the space into clusters. In every round, we further split up
-all cluster into smaller clusters and connect them with the minimal
-link.
-
-We find this link by searching for links that have start and
-end node in different regions of the most recent split. Out of these
-links, we pick the cheapest ones. We ignore links whose start or end
-node have a too high degree in the spanning tree already.
-
-Assuming that the choice of node IDs represents the topology to some
-extend, splitting them up into distinct clusters avoids contention, as
-two separate sub-trees are processed in different areas of the
-interconnect network.
-
-Another idea is to employ clustering on NUMA domains such that every
-NUMA domain corresponds to one cluster.
+multicore machines are hierarchical. We discuss here a more
+methodical approach for communication withing hybrid networks.
+
+The idea is to find clusters of cores for whom shared memory
+algorithms are more efficient then their message passing-based
+counter-parts.
+
+In a shared memory implementation, the cost of enqueueing a message to
+a shared memory queue is $t_{write}$. The reads ideally (i.e.\ not
+considering contention) happen in parallel, which means $t_{read}$
+independent of how many clients read the data, but cause $n$-fault
+traffic on the interconnect.
+
+We now assume that the receiving cores shared a cache. Each message is
+then available locally for further read operations by other cores
+after the first core was issuing a read. This first read forces the
+cache-coherency protocol to update (or pull) the message that was
+invalidated by the sender write operation.
+
+A shared memory implementation is more efficient for a group of cores
+$c_1 \ldots c_n \in C$ if $t_{write} + t_{rem-read} +
+(n-1)*t_{local-read}$ is smaller then the cost of sending a message
+along the most efficient message-passing topology for this set of
+cores.
+
+\begin{algorithm}[htb]
+  %%%%% 
+  \SetCommentSty{textc}
+  \SetKwFunction{sort}{sort} %
+  \SetKwFunction{cost}{cost} %
+  \SetKwFunction{pop}{pop} %
+  \SetKwFunction{shortestmp}{shortest\_mp} %
+  \SetKwFunction{costshm}{cost\_shm} %
+  \SetKwFunction{cluster}{get\_cluster} %
+  \SetKwFunction{icsend}{send} %
+  %%%%
+  \KwData{Edges E from model}
+  %%%%%
+
+  \While{True}{
+    links $\leftarrow$ \sort{E}\;
+    \Repeat{stderr small enough}{
+      (start, end) = \pop{links}\;
+      clusters += start, end\;
+    }
+    clusters $\leftarrow $ \cluster{}\;
+    \eIf{\cost{\shortestmp{cores}} $<$ \costshm{cores}}{
+      cores $\leftarrow$ cluster\;
+    }{
+      break \;
+    }
+  }
+  \If{cores}{
+    Compose algorithm
+  }
+  %%%%%
+  \caption{Algorithm to find shared memory clusters}
+  \label{algo:clustering}
+\end{algorithm}
 
@@
 
-\begin{figure}[htb]
-  \centering
-  \begin{tikzpicture}[scale=.35,transform shape]
-    % Insert visualization
-    \input{visu_only_mst}
-  \end{tikzpicture}
-  \caption{Visualization of operations for sending a message along the
-    tree. Red boxes represent send operations, blue boxes represent
-    receive operations and arrows messages sent between cores. The
-    tree has been acquired using an MST algorithm.}
-  \label{fig:mst_gruyere_operations}
-\end{figure}
-
 In Figure~\ref{fig:mst_gruyere_operations_sorted} we schedule sending
@@
 \end{algorithm}
-
-\begin{figure}[htb]
-  \centering
-  \begin{tikzpicture}[scale=.35,transform shape]
-    % Insert visualization
-    \input{visu_mst_sort}
-  \end{tikzpicture}
-  \caption{Visualization of operations for sending a message along the
-    tree. Red boxes represent send operations, blue boxes represent
-    receive operations and arrows messages sent between cores. After
-    running the MST algorithm, we optimize scheduling in every node to
-    send messages in decreasing order of their latency.}
-  \label{fig:mst_gruyere_operations_sorted}
-\end{figure}
 
@@
         \ref{fig:mst_gruyere_operations_sorted} } \\
-    hierarchical & highest link weight first & 151 & 0.63 &
-        \ref{fig:visu_hierarchy} \\
-    ring & highest link weight first & 181 & 0.75 &
-        \ref{fig:visu_ring} \\
+    hierarchical & highest link weight first & 151 & 0.63 & \\
+    ring & highest link weight first & 181 & 0.75 & \\
     \bottomrule
@@
   evaluate if the increase in complexity is worth it}
-
-\begin{figure}[htb]
-  \centering
-  \begin{tikzpicture}[scale=.35,transform shape]
-    % Insert visualization
-    \input{visu_hierarchy}
-  \end{tikzpicture}
-  \caption{Visualization of hierarchical tree broadcast. A binary tree
-    spans across NUMA nodes followed by sequential send operations
-    within the NUMA node. %
-    Red boxes represent send operations, blue boxes represent receive
-    operations and arrows messages sent between cores.  }
-  \label{fig:visu_hierarchy}
-\end{figure}
-
-\begin{figure}[htb]
-  \centering
-  \begin{tikzpicture}[scale=.35,transform shape]
-    % Insert visualization
-    \input{visu_ring}
-  \end{tikzpicture}
-  \caption{Visualization of ring based broadcast. Two rings
-    spans across NUMA nodes followed by sequential send operations
-    within the NUMA node. %
-    Red boxes represent send operations, blue boxes represent receive
-    operations and arrows messages sent between
-    cores. \stefan{Scheduling is broken. If we want acks, we can only
-      forward a message along the ring when all the local nodes
-      acknowledge a message}}
-  \label{fig:visu_ring}
-\end{figure}
 
@@
 \end{itemize}
-
-\paragraph{Binary tree on sbrinz2}
-
-Plot~\ref{pgfplot:201305101058} shows the time in cycles until a
-message send from core $n$ is received back via the broadcast tree
-show in Figure~\ref{fig:binary_tree_sbrinz2}. We were expecting
-increasing cost with the depth of the tree. If a message is sent from
-one of the leave nodes, it takes longer to receive this message back
-on the tree.
-
-The result is quite unexpected. We would expect nodes far down in the
-tree to experience a longer waiting time for receiving own messages
-back on the tree (due to more hops). This observation does not seem to
-be true.
-
-Lukas Humbel, who was also working on sbrinz1 was observing that the
-Barrelfish core IDs might not properly correspond to physical core
-IDs. This could explain the numbers we observe in our measurement.
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=\linewidth]{binary_tree_sbrinz2}
-  \caption{Binary tree for sbrinz2}
-  \label{fig:binary_tree_sbrinz2}
-\end{figure}
-
-\begin{figure}
-  \caption{Cost for receiving a message back on the tree. This is the
-    time for which the send call needs to be blocked to retain atomic
-    broadcast properties.}
-  \label{pgfplot:201305101058}
-  \begin{tikzpicture}
-    \begin{axis}[%
-        xlabel=sender core ID,%
-        ylabel={Cost [cycles]}%
-        ]
-    \addplot[%
-        color=red,%
-        mark=x,%  
-        error bars/y dir=both,%
-        error bars/y explicit%
-        ] coordinates {
-      (1,276.1) +- (291.3,291.3)
-      (2,876.1) +- (56.6,56.6)
-      (3,863.0) +- (108.3,108.3)
-      (4,899.7) +- (102.3,102.3)
-      (5,893.5) +- (44.5,44.5)
-      (6,880.5) +- (39.4,39.4)
-      (7,520.9) +- (41.7,41.7)
-      (8,171.9) +- (91.5,91.5)
-      (9,155.7) +- (51.4,51.4)
-      (10,174.6) +- (99.9,99.9)
-      (11,175.1) +- (99.3,99.3)
-      (12,154.5) +- (50.5,50.5)
-      (13,176.8) +- (109.7,109.7)
-      (14,173.1) +- (99.4,99.4)
-      (15,150.4) +- (43.3,43.3)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-\paragraph{Older numbers}
-
-Plot~\ref{pgfplot:201303141819} shows the cost of flooding a sub-tree
-(with the 50\% worst measurements dropped). The group communication is
-based on a binary tree. Core 0 is the root, cores 1 and 2 are its
-children etc.
-
-The average cost is really high (probably a scheduling issue). But the
-minimal numbers show what is possible. The numbers achieved are easily
-explainable. The cost is increasing logarithmic with the number of
-nodes reached by the broadcast (as expected). Every level in the tree
-adds an additional 2500 to 3000 cycles to the tree. Node 0 takes
-significantly longer. I don't know yet why that is.
-
-\begin{figure}
-  \caption{Execution time for a broadcast with ACK on gruyere. The
-    cost is for execution for the sub-graph starting at the given
-    node. Refer to Figure~\ref{fig:qrm_tree_gruyere} for a
-    visualization of the broadcast tree used. }
-  \label{pgfplot:201303141819}
-  \begin{tikzpicture}
-    \begin{axis}[
-      xlabel=core id,
-      scaled y ticks = false, % prevent 10^x stuff
-      y tick label style={/pgf/number format/fixed},
-      ylabel={cost for subtree [cycles]}]
-    \addplot[
-      color=red,
-      very thin,
-      mark=*,
-      mark options={%
-        scale=.4
-      },
-      error bars/y dir=both,
-      error bars/y explicit] coordinates {
-      (0,9932.3) +- (564.4,564.4)
-      (1,8240.1) +- (298.5,298.5)
-      (2,8259.6) +- (549.4,549.4)
-      (3,6206.3) +- (225.1,225.1)
-      (4,5914.9) +- (399.2,399.2)
-      (5,6033.5) +- (462.2,462.2)
-      (6,6070.4) +- (434.3,434.3)
-      (7,4530.4) +- (188.6,188.6)
-      (8,3163.4) +- (246.1,246.1)
-      (9,3403.0) +- (285.3,285.3)
-      (10,3650.7) +- (336.5,336.5)
-      (11,3559.0) +- (318.8,318.8)
-      (12,3558.1) +- (284.8,284.8)
-      (13,3567.5) +- (304.5,304.5)
-      (14,3476.3) +- (290.2,290.2)
-      (15,2711.7) +- (151.9,151.9)
-      (16,614.0) +- (17.5,17.5)
-      (17,606.2) +- (17.3,17.3)
-      (18,636.2) +- (72.5,72.5)
-      (19,641.3) +- (46.3,46.3)
-      (20,583.8) +- (46.7,46.7)
-      (21,577.8) +- (38.3,38.3)
-      (22,561.8) +- (18.1,18.1)
-      (23,603.5) +- (56.6,56.6)
-      (24,589.0) +- (33.4,33.4)
-      (25,582.9) +- (33.2,33.2)
-      (26,571.7) +- (16.3,16.3)
-      (27,581.6) +- (36.6,36.6)
-      (28,564.0) +- (16.4,16.4)
-      (29,564.0) +- (20.8,20.8)
-      (30,551.6) +- (13.0,13.0)
-      (31,596.2) +- (51.4,51.4)
-    };
-    \end{axis}
-  \end{tikzpicture}
-
-\end{figure}
 
@@
 
-\begin{appendices}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{UMP performance}
-
-\input{graphs/ziger_ump_breakdown}
-
-\subsection{Pairwise performance}
-
-Figure~\ref{pgfplot:20130627} shows the UMP RTT time for each pair of
-cores. The benchmark seems to be broken, since sending messages to
-core 40 and higher is really expensive. On the other hand. Sending
-messages from these cores back to cores with low IDs (which are on the
-other end of the machine) seems unreasonably cheap.
-
-What we would expect is a symmetric plot. Sending a message from core
-$n$ to $m$ should be about equally expensive than sending a message
-from $m$ to $n$.
-
-\pgfplotsset{width=\linewidth}
-\begin{figure}
-  \caption{pair-wise latency for appenzeller}
-  \label{pgfplot:20130627}
-  \begin{tikzpicture}
-    \begin{axis}[
-      zlabel={cost [cycles]},
-      xlabel={sending core},
-      ylabel={receiving core},
-      scaled z ticks = false,
-      z tick label style={/pgf/number format/fixed}
-      ]
-    \addplot3[surf] file {measurements/appenzeller_pairwise_ump.dat};
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-\pgfplotsset{width=\linewidth}
-\begin{figure}
-  \caption{pair-wise latency for gottardo}
-  \label{pgfplot:20130627}
-  \begin{tikzpicture}[scale=.75]
-    \begin{axis}[scaled z ticks=false,z tick label style={/pgf/number format/fixed},zlabel={cost [cycles]},xlabel={sending core},ylabel={receiving core}]
-    \addplot3[surf] file {measurements/gottardo_pairwise_ump.dat};
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-\section{Shared memory performance}
-
-Plot~\ref{pgfplot:201306191213} shows some measurements for using a
-shared memory FIFO queue for communication. Core 0 sends message by
-enqueuing them to the FIFO, while all other cores poll on the queue
-for new messages.
-
-The measurement assumes the tsc clocks to be synchronized. The queues
-are also infinite. Messages are never garbage-collected.
-
-\begin{figure}
-  \caption{Shared memory FIFO performance on brie}
-  \label{pgfplot:201306191213}
-  \begin{tikzpicture}
-    \begin{axis}[
-      ybar,
-      error bars/y dir=both,%
-      error bars/y explicit,%
-      xlabel=core,
-      xtick={1,2,3},
-      ylabel={cost [cycles]}]
-
-    \addplot coordinates {
-      (1,488.6) +- (32.1,32.1)
-      (2,761.7) +- (124.1,124.1)
-      (3,862.5) +- (118.3,118.3)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-Plot~\ref{pgfplot:201306191238} shows the same experiment for tomme.
-
-\begin{figure}
-  \caption{Shared memory FIFO performance on tomme}
-  \label{pgfplot:201306191238}
-  \begin{tikzpicture}
-    \begin{axis}[
-      ybar,
-      error bars/y dir=both,
-      error bars/y explicit,
-      xlabel=core,
-      ylabel={Cost [cycles]}]
-    \addplot coordinates {
-      (1,417.6) +- (71.0,71.0)
-      (2,776.2) +- (110.4,110.4)
-      (3,774.6) +- (111.9,111.9)
-      (4,648.0) +- (175.9,175.9)
-      (5,551.2) +- (257.5,257.5)
-      (6,652.6) +- (179.2,179.2)
-      (7,688.6) +- (116.3,116.3)
-      (8,691.2) +- (133.0,133.0)
-      (9,721.6) +- (55.8,55.8)
-      (10,633.8) +- (135.0,135.0)
-      (11,673.8) +- (86.4,86.4)
-      (12,705.0) +- (81.8,81.8)
-      (13,612.6) +- (199.1,199.1)
-      (14,699.2) +- (90.3,90.3)
-      (15,691.6) +- (93.0,93.0)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-Plot~\ref{pgfplot:201306191603} shows it for gruyere. These do not
-make sense. The numbers are far too high, especially since gruyere is
-supposed to be synchronized.
-
-This suggest that my implementation is broken ..
-
-\begin{figure}
-  \caption{Plot}
-  \label{pgfplot:201306191603}
-  \begin{tikzpicture}
-    \begin{axis}[
-      ybar,
-      error bars/y dir=both,
-      error bars/y explicit,
-      xlabel=FIXME,
-      ylabel={Cost [cycles]}]
-    \addplot coordinates {
-      (1,2399.4) +- (3585.1,3585.1)
-      (2,8924.9) +- (11981.8,11981.8)
-      (3,4922.3) +- (4685.1,4685.1)
-      (4,6638.2) +- (3521.0,3521.0)
-      (5,5608.7) +- (4185.6,4185.6)
-      (6,5337.5) +- (3846.6,3846.6)
-      (7,5844.6) +- (2836.9,2836.9)
-      (8,5089.0) +- (3135.3,3135.3)
-      (9,5264.0) +- (3919.9,3919.9)
-      (10,5711.7) +- (3793.0,3793.0)
-      (11,5266.9) +- (3712.1,3712.1)
-      (12,8197.6) +- (3819.3,3819.3)
-      (13,8668.6) +- (3645.8,3645.8)
-      (14,8923.8) +- (2964.8,2964.8)
-      (15,7195.3) +- (2407.2,2407.2)
-      (16,8176.2) +- (3185.2,3185.2)
-      (17,8770.7) +- (3001.8,3001.8)
-      (18,4171.5) +- (2011.4,2011.4)
-      (19,8453.5) +- (3280.2,3280.2)
-      (20,13695.1) +- (3137.6,3137.6)
-      (21,13806.8) +- (2914.0,2914.0)
-      (22,13692.4) +- (2730.3,2730.3)
-      (23,14435.9) +- (2983.7,2983.7)
-      (24,9797.6) +- (3821.4,3821.4)
-      (25,8955.7) +- (4364.6,4364.6)
-      (26,7929.3) +- (3493.3,3493.3)
-      (27,11541.9) +- (3076.2,3076.2)
-      (28,10851.3) +- (4241.4,4241.4)
-      (29,8736.3) +- (3280.4,3280.4)
-      (30,11648.2) +- (2969.7,2969.7)
-      (31,7821.5) +- (2477.0,2477.0)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-Plot~\ref{pgfplot:201306191624} shows the same with more
-iterations. The result is not more stable than the one before,
-though.
-
-\begin{figure}
-  \caption{Plot}
-  \label{pgfplot:201306191624}
-  \begin{tikzpicture}
-    \begin{axis}[
-      ybar,
-      error bars/y dir=both,
-      error bars/y explicit,
-      xlabel=FIXME,
-      ylabel={Cost [cycles]}]
-    \addplot coordinates {
-      (1,11197.7) +- (8150.8,8150.8)
-      (2,10971.4) +- (6418.6,6418.6)
-      (3,10364.3) +- (7409.8,7409.8)
-      (4,9460.5) +- (6846.3,6846.3)
-      (5,11629.7) +- (7938.9,7938.9)
-      (6,12266.8) +- (8895.5,8895.5)
-      (7,12313.0) +- (8030.9,8030.9)
-      (8,13079.3) +- (7031.2,7031.2)
-      (9,10919.1) +- (6272.3,6272.3)
-      (10,4758.1) +- (3364.5,3364.5)
-      (11,4093.8) +- (2121.7,2121.7)
-      (12,10077.3) +- (1152.3,1152.3)
-      (13,8632.7) +- (1601.4,1601.4)
-      (14,6381.6) +- (1607.5,1607.5)
-      (15,8215.2) +- (1799.2,1799.2)
-      (16,6973.4) +- (1713.0,1713.0)
-      (17,8631.0) +- (1750.3,1750.3)
-      (18,13615.4) +- (2873.1,2873.1)
-      (19,11311.9) +- (1996.6,1996.6)
-      (20,17855.8) +- (2420.9,2420.9)
-      (21,15193.0) +- (1923.7,1923.7)
-      (22,18920.0) +- (2393.1,2393.1)
-      (23,19870.6) +- (2618.8,2618.8)
-      (24,17947.8) +- (4379.8,4379.8)
-      (25,21783.5) +- (4202.5,4202.5)
-      (26,24329.6) +- (3695.0,3695.0)
-      (27,22965.0) +- (3667.8,3667.8)
-      (28,20440.8) +- (4380.6,4380.6)
-      (29,17405.7) +- (4385.3,4385.3)
-      (30,19202.7) +- (4509.1,4509.1)
-      (31,21855.2) +- (3850.9,3850.9)
-    };
-    \end{axis}
-  \end{tikzpicture}
-\end{figure}
-
-\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+
 \input{measurements/gruyere_topologies}
 
-Table~\ref{tab:ziger1} shows an overview of topologies for atomic
-broadcast on \ziger. We compare these numbers to cost-estimations from
-our simulator that incorporates detailed UMP breakdown measurements
-done on the same machine. Our estimations are close to what we observe
-when running on real hardware. In particular, the order of efficiency
-of the topologies matches reality.
-
-The only exception is sequential execution. Our simulator predicts
-much worse performance than actually given by hardware. We believe the
-cause for this could be hardware extensions (e.g.\ hardware broadcast
-units or snooping).
-
-What is particularly interesting is that a badly chosen tree with lots
-of communication across NUMA nodes is actually worse than sequentially
-sending messages.
-
-\input{measurements/ziger1_topologies}
+Table~\ref{tab:gottardo} shows results for various atomic broadcasts
+trees on real hardware as well as our simulator.
+
+The simulator is not very accurate in this case due to the send time
+measured being essentially zero on Intel machines. This measurement
+does not consider the constant overhead in software for sending a
+message that was not part of the original send benchmark.
+
+We either need to send and receive benchmarks with the exact same
+framework or measure the constant overhead and add it to the send
+cost.
+
+Sequentially sending messages is still expensive even though the send
+itself is cheap on Intel machines. This is somewhat unexpected, as the
+sender has very low overhead in sending all messages
+itself. Sequentially sending all messages however induces several
+expensive message transfers across NUMA nodes.
+
+\input{measurements/gottardo_topologies}
+
 \input{measurements/sbrinz_topologies}
-\input{measurements/appenzeller_topologies}
-
-%\input{graphs/visall}
-
-\end{appendices}
+\input{measurements/tomme_topologies}
+\input{measurements/ziger_topologies}
 

### 2013-07-24 pitch.tex
Rerun of all (gruyere, gottardo, sbrinz, tomme, ziger) UMP breakdowns to refine models and all topologies with the new models

@@
 \paragraph{What do you want to enable?} 
-Atomic broadcast for multicores. \stefan{Maybe even more high-level:
+Efficient atomic broadcast for multicores. \stefan{Maybe even more high-level:
   Performance of distributed algorithms like replication that are
@@
 Tuning of AB to machine characteristics. This is hard because
-multicores are complex hierarchical system. Furthermore, there is a
+multicores are complex hierarchical systems. Furthermore, there is a
 huge variety of such machines with different characteristics
@@
 \paragraph{How will you go about it?}
-Online measurements to augment Model \ska evaluation of different
+Online measurements to parametrize Model \ska evaluation of different
 implementations for machine (also combination of message-passing and
@@
 Compare different AB implementations. Show that performance depends on
-machine. Show that our evaluation picks the best one. Verify
+machine. Show that our evaluation picks the best one (significantly
+better than base-line, which is naive or simple tree). Verify
 performance benefit for high-level application.
@@
 \paragraph{What is your hypothesis?}
-We can do better with hybrid models. Automatic tuning achieves good
+Topology matters. We can do better with hybrid models. Automatic tuning achieves good
 performance, without programmers having to deal with complex hardware details.

### 2013-07-24 graphs/config.py

@@ -4,6 +4,7 @@
 SCHEDULING_SORT=True
 SCHEDULING_SORT_ID=False
 SCHEDULING_SORT_LONGEST_PATH=False
+USE_UMP_NUMA=True
 
 topologies = [
 #    "ring", 
@@ -27,5 +28,6 @@ machines = [
 import os
 
 def get_ab_machine_results(machine, overlay):
+    machine = ''.join([i for i in machine if not i.isdigit()])
     return ('%s/measurements/atomic_broadcast_new_model/%s_%s' %
             (os.getenv('HOME'), machine, overlay))

### 2013-07-24 graphs/evaluate.py

@@ -5,6 +5,7 @@ import config
 import pdb
 import logging
 import sched_adaptive
+import hybrid_model
 
 # Evaluation is event based. We realize this using a priority heap
 # with the time at which the event is happening as priority and pop
@@ -66,7 +67,11 @@ class Evaluate():
         @param sched: Scheduler for sending messages
 
         """
-        self.topology = topo.get_broadcast_tree()
+
+        for l in topo.get_broadcast_tree():
+            if isinstance(l, hybrid_model.MPTree):
+                self.topology = l.graph
+
         self.schedule = sched
         self.model = m
         self.sim_round = 0

### 2013-07-24 graphs/evaluate_pariwise-latency.py

@@ -15,7 +15,10 @@ import argparse
 
 parser = argparse.ArgumentParser(
     description='Evaluation of UMP')
-parser.add_argument('--machine', default='unknown')
+parser.add_argument('--machine', default='unknown machine')
+parser.add_argument('--test', default='unknown test')
+parser.add_argument('--notView', dest='view', action='store_const', const=False, default=True)
+parser.add_argument('--output', default='/tmp/plot3')
 args = parser.parse_args()
 
 r = []
@@ -33,7 +36,7 @@ for line in sys.stdin.readlines():
 r = sorted(r, key = lambda x : (x[1], x[0]))
 last = -1
 
-fname_res = '/tmp/res.dat'
+fname_res = args.output + '.dat'
 f_res = open(fname_res, 'w+')
 
 for (x,y,z) in r:
@@ -44,15 +47,18 @@ for (x,y,z) in r:
 
 f_res.close()
 
-fname = '/tmp/plot3.tex'
+fname = args.output + '.tex'
 f = open(fname, 'w+')
 
-helpers._latex_header(f)
+helpers._latex_header(f, ['\\pgfplotsset{width=.9\linewidth}',
+                          '\\usepgfplotslibrary{external}',
+                          '\\tikzexternalize'])
 helpers.do_pgf_3d_plot(f, fname_res, 
-                       'pair-wise latency for %s' % args.machine, 
+                       '%s for %s' % (args.test, args.machine),
                        'sending core', 'receiving core', 'cost [cycles]')
+
 helpers._latex_footer(f)
 
 f.close()
 
-helpers.run_pdflatex(fname)
+helpers.run_pdflatex(fname, args.view)

### 2013-07-24 graphs/general.py

@@ -1,0 +1,1 @@
+/home/skaestle/bin/general.py

### 2013-07-24 graphs/gottardo.py

@@ -17,9 +17,9 @@ class Gottardo(numa_model.NUMAModel):
         g = super(Gottardo, self)._build_graph()
         super(Gottardo, self).__init__(g)
         super(Gottardo, self)._parse_receive_result_file(
-            open('measurements/receive_%s' % self.get_name()))
+            'measurements/receive_%s' % self.get_name())
         super(Gottardo, self)._parse_send_result_file(
-            open('measurements/send_%s' % self.get_name()))
+            'measurements/send_%s' % self.get_name())
 
     # --------------------------------------------------
     # Characteritics of model

### 2013-07-24 graphs/gruyere.py

@@ -17,6 +17,16 @@ class Gruyere(numa_model.NUMAModel):
         """
         g = super(Gruyere, self)._build_graph()
         super(Gruyere, self).__init__(g)
+        super(Gruyere, self)._parse_receive_result_file(
+            'measurements/receive_%s' % self.get_name())
+        super(Gruyere, self)._parse_send_result_file(
+            'measurements/send_%s' % self.get_name())
+
+    def get_send_cost(self, src, dest):
+        return super(Gruyere, self)._get_send_cost(src, dest)
+
+    def get_receive_cost(self, src, dest):
+        return super(Gruyere, self)._get_receive_cost(src, dest)
 
     # --------------------------------------------------
     # Characteritics of model

### 2013-07-24 graphs/hybrid_model.py

@@ -21,3 +21,4 @@ class MPTree(HybridModule):
     
     def __init__(self, graph):
         self.graph = graph
+

### 2013-07-24 graphs/numa_model.py

@@ -3,6 +3,7 @@
 import model
 import helpers
 import re
+import config
 
 from pygraph.classes.graph import graph
 from pygraph.algorithms.minmax import shortest_path
@@ -100,7 +101,7 @@ class NUMAModel(model.Model):
 
         return g_numa
 
-    def _parse_receive_result_file(self, f):
+    def _parse_receive_result_file(self, fname):
         """
         Parse pairwise receive cost results measure with the UMP receive
         benchmark in the Barrelfish tree.
@@ -109,7 +110,8 @@ class NUMAModel(model.Model):
         @param f: Handle to results.dat file of UMP receive benchmark
 
         """
-        print self.recv_cost
+        fname = fname + '_NUMA' if config.USE_UMP_NUMA else '_noNUMA'
+        f = open(fname)
         assert not self.recv_cost
         for l in f.readlines():
             l = l.rstrip()
@@ -122,7 +124,7 @@ class NUMAModel(model.Model):
                 assert (src, dest) not in self.recv_cost
                 self.recv_cost[(src, dest)] = cost/10
 
-    def _parse_send_result_file(self, f):
+    def _parse_send_result_file(self, fname):
         """
         Parse pairwise send cost results measure with the UMP send
         benchmark in the Barrelfish tree.
@@ -131,6 +133,8 @@ class NUMAModel(model.Model):
         @param f: Handle to results.dat file of UMP send benchmark
 
         """
+        fname = fname + '_NUMA' if config.USE_UMP_NUMA else '_noNUMA'
+        f = open(fname)
         assert not self.send_cost
         for l in f.readlines():
             l = l.rstrip()

### 2013-07-24 graphs/run_experiments.sh

@@ -3,8 +3,15 @@
 MODEL=model.h
 QDIR=$HOME/bf/quorum/usr/quorum/
 TMP=`mktemp`
-RESULTDIR=~/measurements/atomic_broadcast_new_model/
 PATTERN="Quorum.*everything done.*exiting"
+
+function get_result_file()
+{
+	python <<EOF
+import config
+print config.get_ab_machine_results('$1', '$2')
+EOF
+}
 
 # check the output
 # --------------------------------------------------
@@ -31,9 +38,9 @@ function wait_result() {
 
 # main
 # --------------------------------------------------
-for m in sbrinz2
+for m in gruyere ziger1
 do
-    for t in badtree cluster mst bintree sequential adaptivetree
+    for t in mst cluster adaptivetree bintree sequential badtree
     do
 	# Cleanup 
 	rm -f $MODEL
@@ -72,7 +79,9 @@ do
 	echo "Benchmark terminating"
 
 	# Copy result
-	cp -b $TMP $RESULTDIR/${m}_${t}
+	touch $TMP
+	RESULT=$(get_result_file $m $t)
+	cp -b $TMP $RESULT
 	rm $TMP
 	
 	./simulator.py --evaluate-model $m $t

### 2013-07-24 graphs/sbrinz.py

@@ -18,28 +18,25 @@ class Sbrinz(numa_model.NUMAModel):
         g = super(Sbrinz, self)._build_graph()
         super(Sbrinz, self).__init__(g)
 
-        r = open('measurements/receive_sbrinz')
-        s = open('measurements/send_sbrinz')
+        r = 'measurements/receive_sbrinz'
+        s = 'measurements/send_sbrinz'
 
         numa_model.NUMAModel._parse_receive_result_file(self, r)
         numa_model.NUMAModel._parse_send_result_file(self, s)
-
-        r.close()
-        s.close()
 
     # --------------------------------------------------
     # Characteritics of model
     def get_name(self):
         return "sbrinz"
 
-    def get_send_cost(self, src, dest):
-        return super(Sbrinz, self)._get_send_cost(src, dest)
-
     def get_num_numa_nodes(self):
         return 4
 
     def get_num_cores(self):
         return 16
+
+    def get_send_cost(self, src, dest):
+        return super(Sbrinz, self)._get_send_cost(src, dest)
 
     def get_receive_cost(self, src, dest):
         return super(Sbrinz, self)._get_receive_cost(src, dest)

### 2013-07-24 graphs/simulator.py

@@ -53,11 +53,11 @@ import ziger
 import sbrinz
 import gottardo
 import appenzeller
+import tomme
 import rack
 
 def arg_machine_class(string):
     """
-    Remove digits from machine name!
 
     """
     if string == "gruyere":
@@ -72,6 +72,8 @@ def arg_machine_class(string):
         return gottardo.Gottardo
     elif string == 'appenzeller':
         return appenzeller.Appenzeller
+    elif string == 'tomme':
+        return tomme.Tomme
     else:
         raise Exception('Unknown machine')
     
@@ -81,9 +83,9 @@ def arg_machine(machine_name):
     Return instance of the machine given as argument
 
     """
-    string = ''.join([i for i in machine_name if not i.isdigit()])
+    machine_name = ''.join([i for i in machine_name if not i.isdigit()])
 
-    if string == 'rack':
+    if machine_name == 'rack':
         return rack.Rack(sbrinz.Sbrinz)
 
     else:

### 2013-07-24 graphs/tomme.py

@@ -18,9 +18,9 @@ class Tomme(numa_model.NUMAModel):
         g = super(Tomme, self)._build_graph()
         super(Tomme, self).__init__(g)
         super(Tomme, self)._parse_receive_result_file(
-            open('measurements/receive_%s' % self.get_name()))
+            'measurements/receive_%s' % self.get_name())
         super(Tomme, self)._parse_send_result_file(
-            open('measurements/send_%s' % self.get_name()))
+            'measurements/send_%s' % self.get_name())
 
     # --------------------------------------------------
     # Characteritics of model

### 2013-07-24 measurements/ziger_topologies.tex
Adding topology results

\begin{table}[htb]
  \centering
  \begin{tabular}{lrrrrr}
  \toprule
  & \multicolumn{3}{c}{Real hardware} & \multicolumn{2}{c}{Simulation} \\
  topology & time [cycles] & factor & stderr & time [units] & factor \\
  \midrule
  cluster & 2634.91 & 1.017 & 48.11 & 334 & 1.100 \\
  mst & 3178.59 & 1.227 & 43.28 & 343 & 1.129 \\
  bintree & 3380.46 & 1.305 & 42.70 & 377 & 1.242 \\
  sequential & 3841.91 & 1.483 & 239.48 & 672 & 2.214 \\
  badtree & 5711.52 & 2.204 & 30.49 & 714 & 2.354 \\
  adaptivetree & 2591.14 & \colorbox{gray}{1.000} & 45.12 & 303 & \colorbox{gray}{1.000} \\
  \midrule
  \end{tabular}
  \caption{Evaluation of different topologies for ziger}
  \label{tab:ziger}
\end{table}

### 2013-08-06 measurements/ziger_topologies.tex
Adding missing experiments

@@
   \toprule
-  & \multicolumn{3}{c}{Real hardware} & \multicolumn{2}{c}{Simulation} \\
-  topology & time [cycles] & factor & stderr & time [units] & factor \\
+  & \multicolumn{3}{c}{Real hardware [cycles]} & \multicolumn{2}{c}{Simulation [units]} \\
+  topology & time & factor & stderr & time & factor \\
   \midrule
@@
   \end{tabular}
-  \caption{Evaluation of different topologies for ziger}
+  \caption{Topology evaluation for \ziger}
   \label{tab:ziger}

### 2013-08-06 graphs/appenzeller.py

@@ -17,6 +17,10 @@ class Appenzeller(numa_model.NUMAModel):
         """
         g = super(Appenzeller, self)._build_graph()
         super(Appenzeller, self).__init__(g)
+        super(Appenzeller, self)._parse_receive_result_file(
+            'measurements/receive_%s' % self.get_name())
+        super(Appenzeller, self)._parse_send_result_file(
+            'measurements/send_%s' % self.get_name())
 
     # --------------------------------------------------
     # Characteritics of model
@@ -56,3 +60,9 @@ class Appenzeller(numa_model.NUMAModel):
         helpers.output_graph(g_numa, 'appenzeller_numa');
 
         return g_numa
+
+    def get_send_cost(self, src, dest):
+        return super(Appenzeller, self)._get_send_cost(src, dest)
+
+    def get_receive_cost(self, src, dest):
+        return super(Appenzeller, self)._get_receive_cost(src, dest)

### 2013-08-06 graphs/run_experiments.sh

@@ -38,7 +38,7 @@ function wait_result() {
 
 # main
 # --------------------------------------------------
-for m in gruyere ziger1
+for m in appenzeller
 do
     for t in mst cluster adaptivetree bintree sequential badtree
     do

### 2013-09-16 measurements/ziger_topologies.tex
Lot's of other things (including new results)

@@
-\begin{table}[htb]
-  \centering
-  \begin{tabular}{lrrrrr}
-  \toprule
-  & \multicolumn{3}{c}{Real hardware [cycles]} & \multicolumn{2}{c}{Simulation [units]} \\
-  topology & time & factor & stderr & time & factor \\
-  \midrule
-  cluster & 2634.91 & 1.017 & 48.11 & 334 & 1.100 \\
-  mst & 3178.59 & 1.227 & 43.28 & 343 & 1.129 \\
-  bintree & 3380.46 & 1.305 & 42.70 & 377 & 1.242 \\
-  sequential & 3841.91 & 1.483 & 239.48 & 672 & 2.214 \\
-  badtree & 5711.52 & 2.204 & 30.49 & 714 & 2.354 \\
-  adaptivetree & 2591.14 & \colorbox{gray}{1.000} & 45.12 & 303 & \colorbox{gray}{1.000} \\
-  \midrule
-  \end{tabular}
-  \caption{Topology evaluation for \ziger}
-  \label{tab:ziger}
-\end{table}
+\begin{figure}
+  \caption{topology results for \ziger}
+  \label{pgfplot:20130905}
+  \begin{tikzpicture}[scale=1]
+    \begin{axis}[ybar,ymin=0,symbolic x coords={cluster,mst,bintree,badtree,adaptivetree},xtick=data,error bars/y dir=both,error bars/y explicit,legend style={ at={(0.5,1.03)}, anchor=south },legend columns=2,xlabel={topology},ylabel={cost [cycles]}]
+    \addplot coordinates {
+      (cluster,     3674.399889) +- (182.956438,182.956438)
+      (mst,         3752.560889) +- (242.747418,242.747418)
+      (bintree,     3776.717889) +- (277.739474,277.739474)
+      (badtree,     5311.408333) +- ( 72.719583, 72.719583)
+      (adaptivetree,3202.816778) +- (270.823914,270.823914)
+    };
+    \addplot coordinates {
+      (cluster,     3546.492553)
+      (mst,         3477.927649)
+      (bintree,     3849.849689)
+      (badtree,     6171.924742)
+      (adaptivetree,3202.816778)
+    };
+    \legend{real hardware, simulation};
+    \end{axis}
+  \end{tikzpicture}
+\end{figure}

### 2013-09-16 graphs/appenzeller.py

@@ -57,8 +57,6 @@ class Appenzeller(numa_model.NUMAModel):
                     
         assert errors == 16
 
-        helpers.output_graph(g_numa, 'appenzeller_numa');
-
         return g_numa
 
     def get_send_cost(self, src, dest):

### 2013-09-16 graphs/config.py

@@ -4,15 +4,17 @@
 SCHEDULING_SORT=True
 SCHEDULING_SORT_ID=False
 SCHEDULING_SORT_LONGEST_PATH=False
-USE_UMP_NUMA=True
+USE_UMP_NUMA=False
+USE_UMPQ=True
 
 topologies = [
 #    "ring", 
     "cluster", 
     "mst", 
     "bintree",
-    "sequential",
+#    "sequential", SK: Can't predict this very closely right now due to the write-buffer
     "badtree",
+    "fibonacci",
     "adaptivetree"
     ]
 machines = [
@@ -25,9 +27,45 @@ machines = [
     'appenzeller'
     ]
 
+def result_suffix():
+    return _result_suffix(USE_UMP_NUMA, USE_UMPQ)
+
+
+def _result_suffix(numa, umpq):
+    if umpq:
+        return '_UMPQ'
+    elif numa:
+        return '_NUMA'
+    else:
+        return '_noNUMA'
+
 import os
 
-def get_ab_machine_results(machine, overlay):
+# Set these manually
+# --------------------------------------------------
+MULTICAST_RATIO=.5 # Probability for each node to be used for the multicast.
+
+# WARNING!!! These will be changed at runtime
+# --------------------------------------------------
+DO_MULTICAST=False
+
+def get_ab_machine_results(machine, overlay, flounder=False, umpq=False):
     machine = ''.join([i for i in machine if not i.isdigit()])
-    return ('%s/measurements/atomic_broadcast_new_model/%s_%s' %
-            (os.getenv('HOME'), machine, overlay))
+
+    suffix = get_machine_result_suffix(flounder, umpq)
+
+    return ('%s/measurements/atomic_broadcast_new_model/%s_%s%s' %
+            (os.getenv('HOME'), machine, overlay, suffix))
+
+def get_machine_result_suffix(flounder, umpq):
+    assert not flounder or not umpq
+    suffix = ''
+    if flounder:
+        suffix = '_flounder'
+    elif umpq:
+        suffix = '_UMPQ'
+    return suffix
+
+
+def translate_machine_name(n):
+    return ''.join([i for i in n if not i.isdigit()])

### 2013-09-16 graphs/helpers.py

@@ -6,6 +6,7 @@ import os
 sys.path.append('..')
 sys.path.append('/usr/lib/graphviz/python/')
 sys.path.append('/usr/lib64/graphviz/python/')
+sys.path.append('/home/skaestle/bin/')
 import gv
 import Queue
 import numpy
@@ -14,13 +15,13 @@ import logging
 import pdb
 import traceback
 import re
-import simulation
-import shm
 import hybrid_model
 import general
-from config import topologies, machines, get_ab_machine_results
+
+from config import topologies, machines, get_ab_machine_results, get_machine_result_suffix
 
 from datetime import *
+from tools import statistics, statistics_cropped
 
 from pygraph.classes.graph import graph
 from pygraph.classes.digraph import digraph
@@ -55,6 +56,8 @@ def output_quorum_configuration(model, hierarchies, root, sched, topo):
           sending messages for a group/cluster of cores
 
     """
+    import shm
+
     d = core_index_dict(model.graph.nodes())
     print d
 
@@ -88,6 +91,8 @@ def output_quorum_configuration(model, hierarchies, root, sched, topo):
 
 SEND_SHM_IDX=SHM_SLAVE_START
 def send_shm(module, mat, core_dict):
+    import shm
+
     global SEND_SHM_IDX
     assert isinstance(module, shm.ShmSpmc)
     assert module.sender in module.receivers
@@ -242,44 +247,6 @@ def unpack_line(line):
     el = str.split(line)
     assert len(el) == 5
     return _unpack_line_header(el[0]) + (int(el[2]), int(el[4]))
-
-
-def statistics_cropped(l, r=.1):
-    """
-    Print statistics for the given list of integers
-    @param r Crop ratio. .1 corresponds to dropping the 10% highest values
-    @return A tuple (mean, stderr, min, max)
-    """
-    if not isinstance(l, list) or len(l)<1:
-        return None
-
-    crop = int(len(l)*r)
-    m = 0
-    for i in range(crop):
-        m = 0
-        for e in l:
-            m = max(m, e)
-        l.remove(m)
-
-    return statistics(l)
-
-
-def statistics(l):
-    """
-    Print statistics for the given list of integers
-    @return A tuple (mean, stderr, median, min, max)
-    """
-    if not isinstance(l, list) or len(l)<1:
-        return None
-
-    nums = numpy.array(l)
-
-    m = nums.mean(axis=0)
[…]

### 2013-09-16 graphs/hybrid_model.py

@@ -1,5 +1,4 @@
 import helpers
-import gottardo
 
 from pygraph.classes.digraph import digraph
 

### 2013-09-16 graphs/model.py

@@ -2,7 +2,6 @@
 
 import pdb
 import logging
-import evaluate
 import topology_parser
 
 from pygraph.algorithms.minmax import shortest_path

### 2013-09-16 graphs/numa_model.py

@@ -46,6 +46,7 @@ class NUMAModel(model.Model):
     def _build_numa_graph(self):
         return None
 
+
     def _build_graph(self):
         """
         Build a graph model for a NUMA machine
@@ -61,6 +62,7 @@ class NUMAModel(model.Model):
 
         return gr
 
+
     def _auto_generate_numa_information(self):
         res = []
         l = []
@@ -74,8 +76,10 @@ class NUMAModel(model.Model):
         res.append(l)
         return res
 
+
     def get_numa_information(self):
         return self._auto_generate_numa_information()
+
 
     def _build_numa_graph(self):
         """
@@ -101,6 +105,7 @@ class NUMAModel(model.Model):
 
         return g_numa
 
+
     def _parse_receive_result_file(self, fname):
         """
         Parse pairwise receive cost results measure with the UMP receive
@@ -110,7 +115,7 @@ class NUMAModel(model.Model):
         @param f: Handle to results.dat file of UMP receive benchmark
 
         """
-        fname = fname + '_NUMA' if config.USE_UMP_NUMA else '_noNUMA'
+        fname = fname + config.result_suffix()
         f = open(fname)
         assert not self.recv_cost
         for l in f.readlines():
@@ -122,7 +127,7 @@ class NUMAModel(model.Model):
                                              float(m.group(3)),
                                              float(m.group(4)))
                 assert (src, dest) not in self.recv_cost
-                self.recv_cost[(src, dest)] = cost/10
+                self.recv_cost[(src, dest)] = cost
 
     def _parse_send_result_file(self, fname):
         """
@@ -133,7 +138,7 @@ class NUMAModel(model.Model):
         @param f: Handle to results.dat file of UMP send benchmark
 
         """
-        fname = fname + '_NUMA' if config.USE_UMP_NUMA else '_noNUMA'
+        fname = fname + config.result_suffix()
         f = open(fname)
         assert not self.send_cost
         for l in f.readlines():
@@ -145,20 +150,26 @@ class NUMAModel(model.Model):
                                              float(m.group(3)),
                                              float(m.group(4)))
                 assert (src, dest) not in self.send_cost
-                self.send_cost[(src, dest)] = cost/10
+                self.send_cost[(src, dest)] = cost
+
 
     def _get_receive_cost(self, src, dest):
         """
         Return the receive cost for a pair (src, dest) of cores
         
         """
+        if (src==dest):
+            return 0
         assert (src, dest) in self.recv_cost
[…]

### 2013-09-16 graphs/overlay.py

@@ -1,17 +1,19 @@
 # Copyright (c) 2007, 2008, 2009, 2010, 2011, 2012, 2013 ETH Zurich.
 
-import model
 import scheduling
 import sort_longest
 import sched_adaptive
-import hybrid_model
+import config
+import helpers
+
+import random
 
 from pygraph.classes.graph import graph
 from pygraph.classes.digraph import digraph
 
 def get_overlay_class(overlay_name):
     """
-
+    Return subclass of overlay that matches the given name
 
     """
 
@@ -22,6 +24,7 @@ def get_overlay_class(overlay_name):
     import sequential
     import badtree
     import adaptive
+    import fibonacci
 
     if overlay_name == "mst":
         r = mst.Mst
@@ -44,6 +47,9 @@ def get_overlay_class(overlay_name):
 
     elif overlay_name == "adaptivetree":
         r = adaptive.AdapativeTree
+
+    elif overlay_name == "fibonacci":
+        r = fibonacci.Fibonacci
 
     else:
         raise Exception('Unknown topology')
@@ -70,9 +76,10 @@ class Overlay(object):
         """
         Initialize the clustering algorithm
         """
+        import model
         assert isinstance(mod, model.Model)
         self.mod = mod
-        self.broadcast_tree = None
+        self.tree = None
 
     def _get_broadcast_tree(self):
         return None
@@ -91,6 +98,18 @@ class Overlay(object):
     def get_name(self):
         return None
     
+    def get_tree(self):
+        """
+        Return previously generated tree. Functions generating a tree are:
+        :py:func:`get_broadcast_tree`, :py:func:`get_random_multicast_tree` 
+        or :py:func:`get_multicast_tree`.
+
+        :returns: Previously generated tree
+        :rtype: List of :py:class:`hybrid_model.HybridModule`
+
+        """
+        return self.tree
+
     def get_broadcast_tree(self):
         """
         Return broadcast tree
@@ -98,18 +117,66 @@ class Overlay(object):
         Will call _get_broadcast_tree on first execution and store
         tree in broadcast_tree
         """
-        if self.broadcast_tree is None:
+        assert not config.DO_MULTICAST
+
+        if self.tree is None:
             tmp = self._get_broadcast_tree()
+            helpers.output_graph(
+                tmp,
+                '%s_%s' % (self.mod.get_name(), self.get_name()),
+                'dot')
             if isinstance(tmp, graph) or isinstance(tmp, digraph):
[…]

### 2013-09-16 graphs/run_experiments.sh

@@ -19,6 +19,7 @@ function wait_result() {
 
 	m=$1
 	i=0
+	j=0
 
 	# one iteration = 2 seconds
 	# This should terminate after 5 minutes = 300 seconds = 150 iterations
@@ -27,18 +28,24 @@ function wait_result() {
 		sleep 2
 		i=$(($i+1))
 
-		if [[ i -ge 300 ]]
+		if [[ $i -ge 300 ]]
 		then
 			echo "Timeout, restarting machine"
 			rackpower -r $m
 			i=0
+			j=$(($j+1))
+			if [[ $j -ge 10 ]]
+			then
+				echo "Aborting machine restarts after 10 tries"
+				exit 1
+			fi
 		fi
     done
 }
 
 # main
 # --------------------------------------------------
-for m in appenzeller
+for m in $@
 do
     for t in mst cluster adaptivetree bintree sequential badtree
     do
@@ -81,10 +88,10 @@ do
 	# Copy result
 	touch $TMP
 	RESULT=$(get_result_file $m $t)
-	cp -b $TMP $RESULT
+	cp -b $TMP ${RESULT}_flounder
 	rm $TMP
 	
-	./simulator.py --evaluate-model $m $t
+#	./simulator.py --evaluate-model $m $t
     done
 done
 

### 2013-09-16 graphs/simulation.py

@@ -17,7 +17,7 @@ import overlay
 from pygraph.classes.graph import graph
 from pygraph.classes.digraph import digraph
 
-def _simulation_wrapper(ol, m, gr):
+def _simulation_wrapper(ol, m, gr, multicast=False):
     """
     Wrapper for simulationg machines
 
@@ -28,7 +28,15 @@ def _simulation_wrapper(ol, m, gr):
     r = overlay.get_overlay(ol, m)
 
     root = r.get_root_node()
-    hybmod_list = r.get_broadcast_tree()
+
+    if multicast:
+        # Build multicast tree for the first half 
+        n = r.mod.get_graph().nodes()
+        l = len(n)/2
+
+        hybmod_list = r.get_multicast_tree(n[:l])
+    else:
+        hybmod_list = r.get_broadcast_tree()
 
     # --------------------------------------------------
     # Output graphs

### 2013-09-16 graphs/simulator.py

@@ -83,7 +83,7 @@ def arg_machine(machine_name):
     Return instance of the machine given as argument
 
     """
-    machine_name = ''.join([i for i in machine_name if not i.isdigit()])
+    machine_name = config.translate_machine_name(machine_name)
 
     if machine_name == 'rack':
         return rack.Rack(sbrinz.Sbrinz)
@@ -105,8 +105,14 @@ def build_and_simulate():
     parser.add_argument('--evaluate-model', dest="action", action="store_const",
                         const="evaluate", default="simulate", 
                         help="Dump machine model instead of simulating")
-    parser.add_argument('--evaluate-machine', dest="action", action="store_const",
-                        const="evaluate-machine", default="simulate", 
+    parser.add_argument('--evaluate-flounder', dest="action", action="store_const",
+                        const="evaluate-flounder", default="simulate", 
+                        help="?")
+    parser.add_argument('--evaluate-ump', dest="action", action="store_const",
+                        const="evaluate-ump", default="simulate", 
+                        help="?")
+    parser.add_argument('--evaluate-umpq', dest="action", action="store_const",
+                        const="evaluate-umpq", default="simulate", 
                         help="?")
     parser.add_argument('--evaluate-all-machines', dest="action", 
                         action="store_const",
@@ -115,6 +121,8 @@ def build_and_simulate():
     parser.add_argument('--ump-breakdown', dest="action", action="store_const",
                         const="ump-breakdown", default="simulate", 
                         help="Dump machine model instead of simulating")
+    parser.add_argument('--multicast', action='store_const', default=False, 
+                        const=True, help='Perfom multicast rather than broadcast')
     parser.add_argument('machine',
                         help="Machine to simulate")
     parser.add_argument('overlay', 
@@ -129,13 +137,18 @@ def build_and_simulate():
     assert m != None
     gr = m.get_graph()
     
+
+    if args.multicast:
+        print "Building a multicast"
+        config.DO_MULTICAST=True
+
     # --------------------------------------------------
     # Switch main action
     # XXX Cleanup required
     if args.action == "simulate":
         (topo, ev, root, sched, topology) = \
-            simulation._simulation_wrapper(args.overlay, m, gr)
-        hierarchies = topo.get_broadcast_tree()
+            simulation._simulation_wrapper(args.overlay, m, gr, args.multicast)
[…]

### 2013-09-16 graphs/test.py

@@ -12,6 +12,7 @@ import evaluate
 import config
 import model
 import helpers
+import algorithms
 
 # Machines
 import gruyere
@@ -39,7 +40,43 @@ import ziger
 # print z.get_numa_information()
 
 
-helpers.output_machine_results("testmachine", 
-                               [(100, 5), (200, 10), (300, 15)], 
-                               [(10, 5.5), (20, 10.1), (30, 12.3)]
-                               )
+# helpers.output_machine_results("testmachine", 
+#                                [(100, 5), (200, 10), (300, 15)], 
+#                                [(10, 5.5), (20, 10.1), (30, 12.3)]
+#                                )
+
+#algorithms.clustering()
+
+# Number of nodes in Fibonacci tree:
+# http://xlinux.nist.gov/dads/HTML/fibonacciTree.html
+# F(i+2)-1 for Fibonacci tree of size i
+for i in range(11):
+    nodes = []
+    edges = []
+    fibno = algorithms.F(i+2) - 1
+    algorithms.fibonacci(i, nodes, edges)
+    print "%d %d %d" % (i, len(nodes), fibno)
+
+NUM_NODES = 32
+
+nodes = []
+edges = []
+algorithms.fibonacci(7, nodes, edges)
+
+f = open('/tmp/fibonacci.dot', 'w+')
+f.write('digraph {\n')
+
+nodes = sorted(nodes, cmp=lambda x, y: cmp(len(x),len(y)))
+
+for (idx, n) in enumerate(nodes):
+    if idx<NUM_NODES:
+        attr = ['fillcolor=palegreen','style=filled','label="core %d"' % idx]
+    else:
+        attr = ['label="unused %d"' % (idx-NUM_NODES)]
+    f.write('%s [%s];\n' % (n,','.join(attr)));
+
+for (s,e) in edges:
+    f.write('%s -> %s;\n' % (s,e))
+
+f.write('}\n')
+f.close

### 2013-09-28 full_nos.tex
Move everything one layer up

%%
\pgfsetcolor{black}
  % Edge: 2 -- 0
  \draw [] (68.686bp,77.481bp) .. controls (64.257bp,77.481bp) and (59.669bp,77.481bp)  .. (55.241bp,77.481bp);
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (61.963bp,67.481bp) node {$10$};
  % Edge: 3 -- 0
  \draw [] (79.131bp,33.832bp) .. controls (68.76bp,42.686bp) and (55.49bp,54.014bp)  .. (45.068bp,62.911bp);
  \draw (72.099bp,60.372bp) node {$10$};
  % Edge: 1 -- 3
  \draw [] (55.234bp,19.5bp) .. controls (59.663bp,19.5bp) and (64.251bp,19.5bp)  .. (68.68bp,19.5bp);
  \draw (61.957bp,9.5bp) node {$10$};
  % Edge: 3 -- 2
  \draw [] (95.92bp,37.528bp) .. controls (95.92bp,44.442bp) and (95.92bp,52.333bp)  .. (95.92bp,59.265bp);
  \draw (105.92bp,48.396bp) node {$1$};
  % Edge: 0 -- 1
  \draw [] (28bp,59.453bp) .. controls (28bp,52.539bp) and (28bp,44.648bp)  .. (28bp,37.716bp);
  \draw (38bp,48.585bp) node {$1$};
  % Edge: 1 -- 2
  \draw [] (44.789bp,33.832bp) .. controls (55.16bp,42.686bp) and (68.43bp,54.014bp)  .. (78.852bp,62.911bp);
  \draw (71.821bp,36.372bp) node {$10$};
  % Node: 1
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (28bp,19bp) ellipse (27bp and 18bp);
  \draw (28bp,19.5bp) node {$1$};
\end{scope}
  % Node: 0
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (28bp,77bp) ellipse (27bp and 18bp);
  \draw (28bp,77.481bp) node {$0$};
\end{scope}
  % Node: 3
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (96bp,20bp) ellipse (27bp and 18bp);
  \draw (95.92bp,19.5bp) node {$3$};
\end{scope}
  % Node: 2
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (96bp,77bp) ellipse (27bp and 18bp);
  \draw (95.92bp,77.481bp) node {$2$};
\end{scope}
%

### 2013-09-28 mst_gruyere.tex
Move everything one layer up

%%
\pgfsetcolor{black}
  % Edge: 0 -- 16
  \draw [] (166.21bp,141.75bp) .. controls (154.21bp,137.5bp) and (139.75bp,132.37bp)  .. (127.78bp,128.12bp);
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (142.99bp,147.94bp) node {$10$};
  % Edge: 24 -- 8
  \draw [] (397.66bp,275.03bp) .. controls (391.25bp,258.58bp) and (381.78bp,234.27bp)  .. (375.41bp,217.94bp);
  \draw (372.53bp,251.48bp) node {$10$};
  % Edge: 3 -- 0
  \draw [] (144.86bp,183.29bp) .. controls (153.27bp,177.19bp) and (163.2bp,169.98bp)  .. (171.63bp,163.85bp);
  \draw (150.24bp,162.57bp) node {$1$};
  % Edge: 13 -- 12
  \draw [] (425.39bp,40.785bp) .. controls (420.15bp,53.394bp) and (413.1bp,70.342bp)  .. (407.87bp,82.936bp);
  \draw (404.63bp,57.86bp) node {$1$};
  % Edge: 28 -- 30
  \draw [] (481.35bp,212.31bp) .. controls (490.97bp,220.54bp) and (503.03bp,230.85bp)  .. (512.69bp,239.11bp);
  \draw (488.02bp,236.71bp) node {$1$};
  % Edge: 20 -- 21
  \draw [] (201.17bp,312.44bp) .. controls (191.17bp,315.94bp) and (179.56bp,319.99bp)  .. (169.53bp,323.49bp);
  \draw (189.35bp,329.97bp) node {$1$};
  % Edge: 14 -- 12
  \draw [] (455.7bp,72.393bp) .. controls (445.22bp,77.713bp) and (432.7bp,84.068bp)  .. (422.25bp,89.375bp);
  \draw (444.97bp,92.884bp) node {$1$};
  % Edge: 24 -- 25
  \draw [] (427.6bp,302.81bp) .. controls (438.25bp,307.43bp) and (450.85bp,312.89bp)  .. (461.46bp,317.49bp);
  \draw (449.53bp,298.15bp) node {$1$};
  % Edge: 23 -- 20
  \draw [] (239.16bp,369.78bp) .. controls (236.13bp,355.61bp) and (231.94bp,336.05bp)  .. (228.93bp,321.97bp);
  \draw (245.04bp,343.88bp) node {$1$};
  % Edge: 10 -- 8
  \draw [] (392.35bp,177.85bp) .. controls (389.69bp,180.39bp) and (386.93bp,183.02bp)  .. (384.27bp,185.56bp);
  \draw (379.31bp,171.71bp) node {$1$};
  % Edge: 28 -- 29
  \draw [] (480.24bp,183.31bp) .. controls (489.9bp,174.24bp) and (502.25bp,162.63bp)  .. (511.95bp,153.51bp);
  \draw (487.09bp,158.41bp) node {$1$};
  % Edge: 9 -- 8
  \draw [] (385.56bp,225.98bp) .. controls (383.61bp,223.03bp) and (381.57bp,219.97bp)  .. (379.61bp,217.03bp);
  \draw (371.59bp,228.5bp) node {$1$};
  % Edge: 26 -- 24
  \draw [] (434.35bp,350.12bp) .. controls (428.09bp,338.07bp) and (419.78bp,322.07bp)  .. (413.53bp,310.04bp);
  \draw (435.94bp,324.08bp) node {$1$};
  % Edge: 8 -- 11
  \draw [] (363.03bp,182.61bp) .. controls (360.85bp,175.62bp) and (358.35bp,167.62bp)  .. (356.17bp,160.64bp);
  \draw (347.6bp,174.63bp) node {$1$};
  % Edge: 6 -- 4
  \draw [] (239.87bp,225.9bp) .. controls (242.6bp,224.69bp) and (245.39bp,223.47bp)  .. (248.12bp,222.27bp);
  \draw (247.99bp,236.08bp) node {$1$};
  % Edge: 15 -- 12
  \draw [] (380.96bp,36.652bp) .. controls (385.14bp,50.203bp) and (390.9bp,68.839bp)  .. (395.1bp,82.452bp);
  \draw (400.03bp,56.552bp) node {$1$};
  % Edge: 20 -- 4
  \draw [] (233.67bp,286.83bp) .. controls (241.82bp,270.43bp) and (254bp,245.9bp)  .. (262.13bp,229.53bp);
  \draw (261.9bp,264.18bp) node {$10$};
  % Edge: 18 -- 16
  \draw [] (85.864bp,50.894bp) .. controls (89.75bp,65.773bp) and (95.245bp,86.812bp)  .. (99.13bp,101.68bp);
  \draw (81.497bp,79.29bp) node {$1$};
  % Edge: 27 -- 24
  \draw [] (391.64bp,357.44bp) .. controls (394.41bp,343.6bp) and (398.24bp,324.53bp)  .. (401.01bp,310.7bp);
  \draw (385.32bp,332.07bp) node {$1$};
  % Edge: 2 -- 0
  \draw [] (174.87bp,98.4bp) .. controls (178bp,108.92bp) and (181.93bp,122.13bp)  .. (185.04bp,132.6bp);
  \draw (191.95bp,112.5bp) node {$1$};
  % Edge: 28 -- 8
  \draw [] (437.62bp,198.71bp) .. controls (424.53bp,199.05bp) and (408.85bp,199.46bp)  .. (395.75bp,199.8bp);
  \draw (416.68bp,189.25bp) node {$10$};
  % Edge: 19 -- 16
  \draw [] (55.352bp,98.839bp) .. controls (63.514bp,102.34bp) and (72.694bp,106.28bp)  .. (80.851bp,109.78bp);
  \draw (63.102bp,116.31bp) node {$1$};
  % Edge: 4 -- 0
  \draw [] (252.83bp,198.58bp) .. controls (239.51bp,188.29bp) and (221.39bp,174.3bp)  .. (208.08bp,164.03bp);
  \draw (221.46bp,193.3bp) node {$10$};
  % Edge: 8 -- 12
  \draw [] (374.34bp,182.6bp) .. controls (380.17bp,164.37bp) and (389.15bp,136.27bp)  .. (394.96bp,118.1bp);
  \draw (398.65bp,154.35bp) node {$10$};
  % Edge: 20 -- 22
  \draw [] (215.78bp,321.25bp) .. controls (209.51bp,332.8bp) and (201.28bp,347.96bp)  .. (195.03bp,359.48bp);
  \draw (193.4bp,334.37bp) node {$1$};
  % Edge: 1 -- 0
  \draw [] (205.21bp,80.92bp) .. controls (201.98bp,95.938bp) and (197.42bp,117.17bp)  .. (194.19bp,132.19bp);
  \draw (188.7bp,104.55bp) node {$1$};
  % Edge: 4 -- 8
  \draw [] (297.43bp,209.11bp) .. controls (311.25bp,207.44bp) and (328.07bp,205.41bp)  .. (341.89bp,203.74bp);
  \draw (318.66bp,195.43bp) node {$10$};
  % Edge: 17 -- 16
  \draw [] (48.717bp,151.05bp) .. controls (59.414bp,144.95bp) and (72.429bp,137.53bp)  .. (83.123bp,131.43bp);
  \draw (71.92bp,153.24bp) node {$1$};
  % Edge: 4 -- 7
  \draw [] (268.29bp,194.2bp) .. controls (267.36bp,187.11bp) and (266.29bp,178.99bp)  .. (265.36bp,171.91bp);
  \draw (256.82bp,183.06bp) node {$1$};
  % Edge: 5 -- 4
  \draw [] (275.2bp,254.93bp) .. controls (274.38bp,247.23bp) and (273.43bp,238.29bp)  .. (272.61bp,230.59bp);
  \draw (263.9bp,242.76bp) node {$1$};
  % Edge: 28 -- 31
  \draw [] (492bp,197.27bp) .. controls (500.87bp,197.04bp) and (510.71bp,196.77bp)  .. (519.58bp,196.54bp);
  \draw (505.79bp,206.91bp) node {$1$};
  % Node: 24
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (405bp,293bp) ellipse (27bp and 18bp);
  \draw (404.59bp,292.83bp) node {$24$};
\end{scope}
  % Node: 25
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (484bp,327bp) ellipse (27bp and 18bp);
  \draw (484.14bp,327.33bp) node {$25$};
\end{scope}
  % Node: 26
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (443bp,367bp) ellipse (27bp and 18bp);
  \draw (443.33bp,367.42bp) node {$26$};
\end{scope}
  % Node: 27
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (388bp,375bp) ellipse (27bp and 18bp);
  \draw (388.04bp,375.34bp) node {$27$};
\end{scope}
  % Node: 20
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (225bp,304bp) ellipse (27bp and 18bp);
  \draw (225.1bp,304.09bp) node {$20$};
\end{scope}
  % Node: 21
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (145bp,332bp) ellipse (27bp and 18bp);
  \draw (145.34bp,331.94bp) node {$21$};
\end{scope}
  % Node: 22
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (186bp,377bp) ellipse (27bp and 18bp);
  \draw (185.78bp,376.53bp) node {$22$};
\end{scope}
  % Node: 23
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (243bp,388bp) ellipse (27bp and 18bp);
  \draw (243.05bp,387.99bp) node {$23$};
\end{scope}
  % Node: 28
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (465bp,198bp) ellipse (27bp and 18bp);
  \draw (464.62bp,198bp) node {$28$};
\end{scope}
  % Node: 29
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (528bp,139bp) ellipse (27bp and 18bp);
  \draw (527.83bp,138.57bp) node {$29$};
\end{scope}
  % Node: 1
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (209bp,63bp) ellipse (27bp and 18bp);
  \draw (209.11bp,62.79bp) node {$1$};
\end{scope}
  % Node: 0
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (190bp,150bp) ellipse (27bp and 18bp);
  \draw (190.3bp,150.29bp) node {$0$};
\end{scope}
  % Node: 3
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (126bp,197bp) ellipse (27bp and 18bp);
  \draw (126.37bp,196.72bp) node {$3$};
\end{scope}
  % Node: 2
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (170bp,80bp) ellipse (27bp and 18bp);
  \draw (169.52bp,80.402bp) node {$2$};
\end{scope}
  % Node: 5
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (277bp,273bp) ellipse (27bp and 18bp);
  \draw (277.14bp,273.19bp) node {$5$};
\end{scope}
  % Node: 4
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (271bp,212bp) ellipse (27bp and 18bp);
  \draw (270.67bp,212.35bp) node {$4$};
\end{scope}
  % Node: 7
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (263bp,154bp) ellipse (27bp and 18bp);
  \draw (263.01bp,153.98bp) node {$7$};
\end{scope}
  % Node: 6
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (217bp,236bp) ellipse (27bp and 18bp);
  \draw (217.18bp,235.87bp) node {$6$};
\end{scope}
  % Node: 9
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (397bp,243bp) ellipse (27bp and 18bp);
  \draw (396.64bp,242.62bp) node {$9$};
\end{scope}
  % Node: 8
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (369bp,201bp) ellipse (27bp and 18bp);
  \draw (368.62bp,200.5bp) node {$8$};
\end{scope}
  % Node: 11
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (351bp,143bp) ellipse (27bp and 18bp);
  \draw (350.65bp,142.96bp) node {$11$};
\end{scope}
  % Node: 10
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (408bp,163bp) ellipse (27bp and 18bp);
  \draw (407.85bp,163.05bp) node {$10$};
\end{scope}
  % Node: 13
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (433bp,23bp) ellipse (27bp and 18bp);
  \draw (432.66bp,23.301bp) node {$13$};
\end{scope}
  % Node: 12
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (401bp,100bp) ellipse (27bp and 18bp);
  \draw (400.63bp,100.35bp) node {$12$};
\end{scope}
  % Node: 15
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (376bp,19bp) ellipse (27bp and 18bp);
  \draw (375.51bp,19bp) node {$15$};
\end{scope}
  % Node: 14
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (478bp,61bp) ellipse (27bp and 18bp);
  \draw (477.53bp,61.31bp) node {$14$};
\end{scope}
  % Node: 17
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (28bp,163bp) ellipse (27bp and 18bp);
  \draw (28bp,162.87bp) node {$17$};
\end{scope}
  % Node: 16
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (104bp,120bp) ellipse (27bp and 18bp);
  \draw (103.82bp,119.62bp) node {$16$};
\end{scope}
  % Node: 19
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (32bp,89bp) ellipse (27bp and 18bp);
  \draw (32.345bp,88.971bp) node {$19$};
\end{scope}
  % Node: 18
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (81bp,33bp) ellipse (27bp and 18bp);
  \draw (81.173bp,32.931bp) node {$18$};
\end{scope}
  % Node: 31
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (547bp,196bp) ellipse (27bp and 18bp);
  \draw (546.84bp,195.81bp) node {$31$};
\end{scope}
  % Node: 30
\begin{scope}
  \definecolor{strokecol}{rgb}{0.0,0.0,0.0};
  \pgfsetstrokecolor{strokecol}
  \draw (530bp,254bp) ellipse (27bp and 18bp);
  \draw (529.59bp,253.56bp) node {$30$};
\end{scope}
%

### 2016-03-14 draw.py
visu: revived visualization

@@ -9,7 +9,7 @@ class Output():
     height_per_core = 5
     obj_per_node = dict()
     obj = []
-    scale_x = .4
+    scale_x = .05
     last_node = None
 
     "Wrapper to enable visualization output to file"
@@ -25,7 +25,7 @@ class Output():
             # Label
             node_name = 'core_%s_label' % c
             self.__add_object(c, node_name)
-            self.f.write("\\node (%s) at (0mm,%dmm) {core %5s};\n" % \
+            self.f.write("\\node (%s) at (0mm,%dmm) {%5s};\n" % \
                              (node_name, self._y_coord_for_core(c), c))
 
     def __add_object(self, core, label):
@@ -57,7 +57,7 @@ class Output():
         return cost * self.scale_x
 
     def _scale_height(self, size):
-        return size*.3
+        return size*.4
 
     def send(self, core, to, time, cost):
         "Visualize send operation"
@@ -70,8 +70,13 @@ class Output():
                               self._y_coord_for_core(core)))
         self.__add_object(core, name)
 
+        
     def receive(self, core, sender, time, cost):
         "Visualize receive operation"
+
+        print "Adding receive events at %d -- %d <- %d, cost %d" % \
+            (time, core, sender, cost)
+        
         # Box indicating receive operation
         name = 'r_%s_%s' % (sender, core)
         self.f.write("\\node[draw,fill=blue!20,minimum width=%dmm, minimum height=%dmm,anchor=west] "\
@@ -93,7 +98,7 @@ class Output():
         self.f.write("\\draw[->%s] ($(s_%s_%s.east)-(1mm,0mm)$) -- ($(r_%s_%s.west)+(1mm,0mm)$); \n" % \
                          (','.join(settings), sender, core, sender, core))
 
-    def finalize(self):
+    def finalize(self, final_time):
         # header
         self.f.write("\\begin{pgfonlayer}{background}\n")
         # grey background box spanning all objects
@@ -113,7 +118,9 @@ class Output():
         for i in range(self.model.get_num_numa_nodes()):
             cidx = i % int(len(self.color_map))
             color = self.color_map[cidx]
-            self.obj_per_node[i].append('numa_axis_%d.west' % (i * self.model.get_cores_per_node()))
+            coreid = self.model.get_numa_node_by_id(i)[0]
+                
+            self.obj_per_node[i].append('numa_axis_%d.west' % (coreid))
[…]

### 2016-03-14 evaluate.py

@@ -7,6 +7,11 @@ import logging
 import sched_adaptive
 import copy # for heapq
 
+
+# We assume that the propagation time is zero. The cost for
+# transporting messages is captured in t_send and t_receive.
+T_PROPAGATE = 0
+
 class bcolors:
     HEADER = '\033[95m'
     OKBLUE = '\033[94m'
@@ -448,8 +453,9 @@ class Evaluate():
             self.node_state[core] = NodeState()
 
         # Construct visualization instance
-        visu_name = ("visu/visu_%s_%s_send_events.tex" % 
-                     (m.get_name(), topo.get_name()))
+        visu_name = ("visu/visu_%s_%s_%s.tex" % 
+                     (m.get_name(), topo.get_name(),
+                      self.protocol.get_name().replace(' ', '_')))
         self.visu = draw.Output(visu_name, m, topo)
 
         # Set initial state
@@ -462,6 +468,7 @@ class Evaluate():
         # evaluate the cost of the protocol in real hardware starting
         # at the last node
         # * Send cost
+        final_time = self.sim_round
         r = Result(self.sim_round, self.last_node, visu_name)
         print "Terminating(%d,%s,%s) - cost %d for last_node -> root" % \
             (self.sim_round, str(self.last_node), str(root), 
@@ -470,7 +477,7 @@ class Evaluate():
              self.model.get_receive_cost(self.last_node, root))
         self.sim_round += self.model.get_send_cost(self.last_node, root);
         # * Propagation
-        self.sim_round += self.topology.edge_weight((self.last_node, root))
+        self.sim_round += T_PROPAGATE
         # * Receive cost
         self.sim_round += self.model.get_receive_cost(self.last_node, root);
         r.time = self.sim_round
@@ -478,7 +485,7 @@ class Evaluate():
         # XXX Check if this includes the receive cost on the last node (it should)
         self.model.set_evaluation_result(r)
 
-        self.visu.finalize()
+        self.visu.finalize(int(final_time))
 
         return r
 
@@ -555,7 +562,7 @@ class Evaluate():
                     assert ts >= enqueue_at
                     enqueue_at = _new
         
-        w = self.topology.edge_weight((src, dest))
+        w = T_PROPAGATE
         heapq.heappush(self.event_queue, (enqueue_at + w, events.Receive(src, dest)))
 
         # Node (src) has just sent a message, increment send batch size

### 2016-03-14 model.py

@@ -153,8 +153,10 @@ class Model(object):
         return None
 
     def get_numa_node(self, core1):
-        """
-        Return all cores that are on the same NUMA node then the given core
+        """Return all cores that are on the same NUMA node then the given core.
+
+        This works as long as get_numa_information is implemented
+        correctly for a given machine.
         """
         numa_node = []
         for node in self.graph.nodes():

### 2016-03-14 netos_machine.py

@@ -71,6 +71,23 @@ class NetosMachine(model.Model):
     def get_numa_information(self):
         return self.machine_topology['NUMA'].get()
 
+
+    def get_numa_node_by_id(self, nidx):
+        """Get all cores on the given NUMA node
+        """
+        return self.machine_topology['NUMA'].get()[nidx]
+    
+    
+    def get_numa_id(self, c):
+        """ Return the ID of the NUMA node of core c
+        """
+
+        nidx = -1
+        for nodes in self.machine_topology['NUMA']:
+            nidx += 1
+            if c in nodes:
+               return nidx
+    
     
     def get_num_cores(self):
         return self.machine_topology['numcpus']

### 2016-03-14 topology_parser.py

@@ -114,7 +114,7 @@ def parse_machine_db(machine):
                     (s, e) = c.split('-')
                     _cluster += range(int(s), int(e)+1)
                 else:
-                    _cluster.append(c)
+                    _cluster.append(int(c))
 
             print _cluster
             res['NUMA'].add_cluster(_cluster)

### 2016-03-15 draw.py
visu: create timeline of atomic broadcast

@@ -1,6 +1,9 @@
 # Draw result of evaluation
 
 import helpers
+import config
+import subprocess
+import shlex
 
 class Output():
 
@@ -142,8 +145,36 @@ class Output():
         
         # footer
         self.f.write("\\end{pgfonlayer}\n")
+        self.f.close()
+
+
+        # Generate a PNG? Currently, this works only for atomic broadcasts
+        if config.args.visu and 'atomic_broadcast' in self.name:
+            self.__generate_image()
+        
         
     def __core_label_to_y_index(self):
         return helpers.core_index_dict(self.model.get_graph().nodes())
 
+
+
+    def __generate_image(self):
+
+        with open('test.tex', 'w') as f:
+
+            _out = self.name.replace('.tex', '.png')
+            print 'Generating visualization .. '
+
+            for line in open('template.tex', 'r'):
+                f.write(line.replace('{%file%}', self.name))
+                
+            f.close()
         
+            try:
+                print subprocess.check_output(shlex.split('rm -f test-figure0.pdf'))
+                print subprocess.check_output(shlex.split('pdflatex -shell-escape -interaction nonstopmode test'))
+                print subprocess.check_output(shlex.split('convert -verbose -density 300 test-figure0.pdf %s' % _out))
+
+            except Exception as e:
+                print 'Generating visualization failed, aborting'
+                raise e

### 2016-03-15 simulator.py

@@ -163,7 +163,10 @@ def build_and_simulate():
     parser.add_argument('--group', default=None,
                         help=("Coma separated list of node IDs that should be "
                               "part of the multicast group"))
-    parser.add_argument('--debug', action='store_const', default=False, const=True)
+    parser.add_argument('--visu', help='Visualize generated graph',
+                        action='store_const', default=False, const=True)
+    parser.add_argument('--debug',
+                        action='store_const', default=False, const=True)
     parser.add_argument('--server', action='store_const', default=False, const=True)
 
     try:

### 2016-05-18 general.py
fixing issue with tikz and ctable
Signed-off-by: Reto Achermann <reto.achermann@inf.ethz.ch>

@@ -192,7 +192,7 @@ def do_pgf_multi_plot(f, multidata, caption='FIXME', xlabel='FIXME', ylabel='FIX
 def _latex_header(f, args=[]):
     header = (
         "\\documentclass[a4wide]{article}\n"
-        "\\usepackage{url,color,xspace,verbatim,subfig,ctable,multirow,listings}\n"
+        "\\usepackage{url,color,xspace,verbatim,subfig,multirow,listings}\n"
         "\\usepackage[utf8]{inputenc}\n"
         "\\usepackage[T1]{fontenc}\n"
         "\\usepackage{txfonts}\n"
@@ -273,4 +273,3 @@ def run_pdflatex(fname, openFile=True):
                         fname], cwd=d) == 0:
         if openFile:
             subprocess.call(['okular', fname.replace('.tex', '.pdf')])
-
